### 2017-07-10 chap10_25mar08.tex
added current paper stuff

\documentclass {book}
\usepackage{amsmath, amssymb, fullpage, natbib}
\usepackage{array}

\begin{document}

\chapter{Assurance Testing}\label{ch10}
\chaptermark{Assurance Testing}

\begin{quote}
\textit{Planning for Bayesian assurance testing involves
determining a test plan that guarantees that a reliability-related
quantity of interest meets or exceeds a specified requirement at a
desired level of confidence. Within a Bayesian hierarchical
framework, this chapter determines test plans for binomial, Poisson, and
Weibull testing. Also, we develop Weibull assurance test plans
using available data from an associated accelerated life testing
program.}
\end{quote} \index[sub]{assurance testing}\index[sub]{test!assurance}

\section{Introduction}\label{ch10:sec1}
This chapter focuses on developing a test plan \index[sub]{test
plan} for assuring (or demonstrating) that, at a desired level of
confidence, a reliability-related quantity of interest meets or
exceeds a specified requirement. For binomial testing, we test $n$
devices either as a demand for successful operation or for a
specified length of time and observe the total number of devices
failing the test $x$. For example, a tester may try an emergency
diesel generator (EDG) to see if it will start on demand, or a
tester may place a sample of a particular nonwoven material under
stress for a given length of time to see if it survives the test.
The reliability-related quantity of interest for both examples is
the probability $\pi$ that an item survives the test, and the
required binomial test plan\index[sub]{binomial!test plan}
consists of the total number of devices tested $n$ as well as the
maximum allowed number of failures $c$.

Although practitioners often use ``assuring'' and
``demonstrating'' synonymously, \citet{ME04}  distinguishes
between reliability demonstration and reliability assurance
testing. A traditional \emph{reliability demonstration
test}\index[sub]{reliability!demonstration test} is essentially a
\emph{classical} (i.e., frequency based) hypothesis test, which
uses only the data from the test to assess whether the
reliability-related quantity of interest meets or exceeds the
requirement. Consider how many modern systems, such as
communication devices and transportation systems, are highly
reliable. For these systems, reliability demonstration tests often
require an impractical amount of testing. In response to this
dilemma, \citet{ME04} defines an alternative \emph{reliability
assurance test}\index[sub]{reliability!assurance test}
\index[sub]{reliability!testing} as one that uses additional
supplementary data and information to reduce the required amount
of testing. The additional data and information may include
appropriate reliability models, earlier test results on the same
or similar devices, expert judgment regarding performance,
knowledge of the environmental conditions under which the devices
are used, benchmark design information on similar devices, prior
knowledge of possible failure modes, etc. Because all of the
Bayesian test plans considered in this chapter use such
supplementary data and information, we refer to them as
reliability assurance tests.\index[aut]{Meeker,
W.}\index[aut]{Escobar, L.}\index[aut]{Meeker,
W.}\index[aut]{Escobar, L.}

Life testing \index[sub]{test!life} has many aspects in common
with assurance testing. However, the primary goal in designing a
life test tends to be quite different than assuring conformance to
a specified reliability requirement. In designing such life tests,
we often have as our primary goal improving the estimation
precision of certain reliability-related quantities of interest.
However, such differences notwithstanding, the basic ideas
underlying life and assurance testing are similar, namely, to
address such questions as ``How many devices do I need to test?'',
``How long do I need to test each device?'', or ``What is the
maximum number of failures permitted for a successful test?''

Because data from an assumed sampling distribution provide the
basis for deciding whether the population of products being tested
meets the specified requirement, there are two kinds of errors to
make. A population of unreliable products (one that does not meet
the requirement) may, in fact, pass the test, whereas a reliable
population may fail it. This important acknowledgment makes us
think about the (probabilistic) \emph{risks} that we incur in
conducting the test. The precise form of the risks is an important
consideration in classical assurance tests and is an important
consideration in developing Bayesian assurance tests as well. The
\emph{test criteria}\index[sub]{test criteria} are precise
probabilistic statements regarding the risks we are willing to
incur when developing a test plan. The following sections discuss
several of the more popular criteria.

To begin our discussion of test criteria, suppose that $\pi$
denotes some reliability-related quantity of interest such that
large values of $\pi$ are more desirable than small values. Note
that reliability is one such quantity, while the mean and
quantiles of a specified failure time distribution are others. It
is common to base both classical and Bayesian test plans on two
specified levels of $\pi$: $\pi_0$, an \emph{acceptable
reliability level}\index[sub]{acceptable reliability
level}\index[sub]{ARL} (ARL), and $\pi_1$, a \emph{rejectable
reliability level}\index[sub]{rejectable reliability
level}\index[sub]{RRL} (RRL), where $\pi_1 \leq  \pi_0$. The
literature sometimes refers to the region $\pi_1 \leq \pi \leq
\pi_0$ as the \emph{indifference region}\index[sub]{indifference
region}. Although the precise definition of ARL and RRL differ
between the classical and Bayesian test criteria, we use them in
an equivalent way.

\subsection{Classical Risk Criteria}\label{ch10:sec1:ss1}
It is quite common to use two criteria in determining classical
test plans. The \emph{producer's risk}
\index[sub]{risk!producer's} is the probability of failing the
test when $\pi = \pi_0$, whereas the \emph{consumer's risk}
\index[sub]{risk!consumer's} is the probability of passing the
test when $\pi = \pi_1$.
\index[sub]{risk!producer's}\index[sub]{risk!consumer's} Suppose
that we specify a maximum value, $\alpha$, of the producer's risk
and a maximum value, $\beta$, of the consumer's risk. For binomial
testing, these criteria become
\begin{eqnarray}\label{ch10:eqn1}
Producer's\mbox{ }Risk & = & \PP (Test\mbox{ }Is\mbox{ }Failed
\con \pi_{0})\\
& = & \PP (y>c \con\pi_0)\nonumber\\
& = &
\sum_{y=c+1}^{n}\left(_y^n\right)(1-\pi_{0})^{y}\pi_{0}^{n-y} \leq
\alpha \, , \nonumber
\end{eqnarray}
and
\begin{eqnarray}\label{ch10:eqn2}
Consumer's\mbox{ }Risk & = & \PP( Test\mbox{ }Is\mbox{
}Passed \con \pi_1)\\
& = & \PP(y \leq c \con\pi_1) \nonumber\\
& = & \sum_{y=0}^{c} \left(_y^n\right)(1-\pi_{1})^
{y}\pi_{1}^{n-y} \leq \beta \, , \nonumber
\end{eqnarray}
where $\pi_1 \leq \pi_0$, $n$ is the number of test units, and $c$
is the maximum number of failures allowed.

To choose a test plan for specified values of $(\alpha, \pi_0,
\beta, \pi_1)$, we find the required binomial test plan $(n,c)$ by
simultaneously solving Eqs.~\ref{ch10:eqn1} and \ref{ch10:eqn2}.
Numerous textbooks provide additional details of this purely
classical approach, for example, see \citet{TT95}.
\index[aut]{Tobias, P.}\index[aut]{Trindade, D.}

\subsection{Average Risk
Criteria}\label{ch10:sec1:ss2}\index[sub]{risk!average}
\citet{E70} first proposed using average operating characteristics
and corresponding risk criteria. These risk criteria are similar
to the classical criteria in Sect.~\ref{ch10:sec1:ss1}, except
that now we condition on the events $\pi\geq\pi_0$ and
$\pi\leq\pi_1$, respectively. To do this requires a suitable prior
distribution for $\pi$,  as specified by $p(\pi)$. The
\emph{average producer's risk}\index[sub]{risk!average producer's}
is the probability of failing the test when $\pi\geq\pi_0$.
Choosing a maximum allowable average producer's risk $\alpha$, the
binomial test plan $(n,c)$ is \index[aut]{Easterling, R.}
\begin{eqnarray}\label{ch10:eqn3}
Average\mbox{ }Producer's\mbox{ }Risk & = &
\PP(Test\mbox{ }Is\mbox{ }Failed \con\pi \geq \pi_0)\\
& = & \frac {\PP(y>c,\pi \geq \pi_{0})}{\PP(\pi \geq \pi_{0})}\nonumber\\
& = & \frac{\int^{1}_{\pi_{0}} \left[ \sum^{n}_{y=c+1}
 \left(_y^n\right)(1-\pi)^{y}\pi^{n-y}\right]
p(\pi) \D \pi}{\int^{1}_{\pi_{0}}p(\pi) \D \pi}\nonumber\\
& = & \frac{\int^{1}_{\pi_{0}} \left[1 -\sum^{c}_{y=0}
\left(_y^n\right)(1-\pi)^{y}\pi^{n-y}\right]p(\pi) \D \pi}{
\int^{1}_{\pi_{0}}p(\pi)\D \pi} \leq \alpha \, .\nonumber
\end{eqnarray}
Likewise, the corresponding \emph{average consumer's
risk}\index[sub]{risk!average consumer's} is the probability of
passing the test when $\pi\leq\pi_1$. Choosing a maximum allowable
average consumer's risk $\beta$, the binomial test plan $(n,c)$ is
\begin{eqnarray}\label{ch10:eqn4}
Average\mbox{ }Consumer's\mbox{ }Risk & = &
\PP(Test\mbox{ }Is\mbox{ }Passed \con \pi \leq \pi_{1})\\
& = & \frac{\PP(y \leq c,\pi \leq \pi_{1})}{\PP(\pi \leq
\pi_1)}\nonumber\\
& = & \frac{\int^{\pi_1}_{0} \left[\sum^{c}_{y=0}
\left(_y^n\right)(1-\pi)^{y}\pi^{n-y}\right] p(\pi) \D
\pi}{\int^{\pi_1}_{0}p(\pi) \D \pi} \leq \beta \, .\nonumber
\end{eqnarray}
\citet{MW82} discusses the use of these risks and recommends
taking care in applying these criteria. For example, the average
consumer's risk may be a poor indication of what is likely really
desired; namely, a maximum probability $\beta$ that $\pi\leq\pi_1$
for a test that passes. The average consumer's risk given in
Eq.~\ref{ch10:eqn4} may be substantially larger than this desired
maximum conditional probability $\beta$. The prior probability
that $\pi \leq \pi_1$ may be quite small; however, if indeed $\pi
\leq \pi_1$, the probability of passing the test may be large. In
such a situation, using the average consumer's risk may be
inappropriate, and therefore misleading. \index[aut]{Martz, H.}
\index[aut]{Waller, R.}

\subsection{Posterior Risk
Criteria}\label{ch10:sec1:ss3}\index[sub]{risk!posterior} We now
consider fully Bayesian posterior risks that convey a completely
different outlook from the corresponding classical or average
risks. While the classical or average
risks\index[sub]{risk!average} provide assurance that satisfactory
devices will pass the test and that unsatisfactory devices will
fail it, posterior risks provide precisely the assurance that
practitioners often desire: if the test is passed, then the
consumer desires a maximum probability $\beta$ that $\pi \leq
\pi_1$. On the other hand, if the test is failed, then the
producer desires a maximum probability $\alpha$ that $\pi \geq
\pi_0$. Unlike the average risks, these posterior risks are fully
Bayesian in the sense that they are subjective probability
statements about $\pi$.

For a test that fails, the \emph{posterior producer's
risk}\index[sub]{risk!posterior producer's} is the probability
that $\pi\geq\pi_{0}$, or $\PP(\pi \ge \pi_0 \con Test\mbox{
}Is\mbox{ }Failed)$. Notice that this is simply the posterior
probability that $\pi \ge \pi_0$ given that we have observed more
than $c$ failures. Using Bayes' Theorem, and assuming a maximum
allowable posterior producer's risk $\alpha$, an expression for
the posterior producer's risk\index[sub]{risk!posterior
producer's} for the binomial test plan $(n,c)$\index[sub]{test
plan!binomial} is
\begin{eqnarray}\label{ch10:eqn5}
Posterior\mbox{ }Producer's\mbox{ }Risk & = &
\PP(\pi \geq \pi_{0}\con Test\mbox{ }Is\mbox{ }Failed)\\
\mbox{} & = & \int_{\pi_0}^{1} p(\pi \con y > c) \D \pi \nonumber\\
\mbox{} & = & \int_{\pi_0}^{1} \frac{f(y > c \con \pi)
p(\pi)}{\int_{0}^{1} f(y > c \con \pi) p(\pi) \D \pi} \,\, \D \pi \nonumber\\
\mbox{} & = & \frac{\int_{\pi_0}^{1} \left[
\sum^{n}_{y=c+1}(_y^n)(1-\pi)^{y}\pi^{n-y} \right] p(\pi) \D
\pi}{\int_{0}^{1} \left[
\sum^{n}_{y=c+1}(_y^n)(1-\pi)^{y}\pi^{n-y} \right] p(\pi) \D
\pi}\nonumber\\ \mbox{} & = & \frac{\int_{\pi_0}^{1} \left[
1-\sum^{c}_{y=0}(_y^n)(1-\pi)^{y}\pi^{n-y} \right] p(\pi) \D
\pi}{1-\int_{0}^{1} \left[\sum^{c}_{y=0}(_y^n)(1-\pi)^{y}\pi^{n-y}
\right] p(\pi) \D \pi} \leq \alpha.\nonumber
\end{eqnarray}

Similarly, given that the test is passed, the \emph{posterior
consumer's risk}\index[sub]{risk!posterior consumer's} is the
probability that $\pi \leq \pi_1$, or $\PP(\pi \leq \pi_1 \con
Test\mbox{ }Is\mbox{ }Passed)$. Notice that this is simply the
posterior probability that $\pi \leq \pi_1$ given that we have
observed no more than $c$ failures. Using Bayes' Theorem, and
assuming a maximum allowable posterior consumer's risk $\beta$, an
expression for the posterior consumer's
risk\index[sub]{risk!posterior consumer's} for the binomial test
plan\index[sub]{test plan!binomial} $(n,c)$ is
\begin{eqnarray}\label{ch10:eqn6}
Posterior\mbox{ }Consumer's\mbox{ }Risk & = &
\PP(\pi \leq \pi_{1}\con Test\mbox{ }Is\mbox{ }Passed)\\
\mbox{} & = & \int_{0}^{\pi_1} p(\pi \con y \leq c) \D \pi \nonumber\\
\mbox{} & = & \int_{0}^{\pi_1} \frac{f(y \leq c \con \pi)
p(\pi)}{\int_{0}^{1} f(y \leq c \con \pi) p(\pi) \D \pi} \,\, \D \pi \nonumber\\
\mbox{} & = & \frac{\int_{0}^{\pi_1} \left[
\sum^{c}_{y=0}(_y^n)(1-\pi)^{y}\pi^{n-y} \right] p(\pi) \D
\pi}{\int_{0}^{1} \left[ \sum^{c}_{y=0}(_y^n)(1-\pi)^{y}\pi^{n-y}
\right] p(\pi) \D \pi}\leq \beta.\nonumber
\end{eqnarray}

\begin{sidebar}\label{ch10:ex1} {\bf Binomial test plan for new modems.}
Consider finding a binomial test plan \index[sub]{test
plan!binomial} using the posterior consumer's risk criterion.
\citet{H90} develops a reliability assurance test for a new modem,
denoted by \emph{B}, that is similar to an earlier modem, denoted
by \emph{A}. Modem $A$ is currently in production and is very
reliable. The major difference between the two modems is that $B$
operates at a different frequency than $A$. Also, the same
production line that builds $A$ will produce $B$ and both modems
use most of the same components. Further, \citet{H90} reports that
a binomial assurance test for modem $A$ on 150 units yielded 6
failures.\index[aut]{Hart, L.}

One of the test objectives is to show that, after successful
testing, the 0.1 quantile of the posterior reliability
distribution for $B$ is at least 0.938, the 0.1 quantile of $A$'s
posterior reliability distribution. Similar to \citet{H90}, we use
a $Beta[86.4, 3.6]=Beta[(0.6 \times 150)(144/150), (0.6 \times
150)(6/150)]$ prior distribution for $\pi$. This prior
distribution arises from treating an $A$ test as ``worth'' 60\% of
a $B$ test or $90=0.6 \times 150$ total tests. Note that the 0.1
quantile of this prior distribution is 0.932, which is only
slightly smaller than the requirement. Therefore, we anticipate
that the test plan will require only a small sample of $B$ modems.
\index[aut]{Hart, L.}

A \emph{minimum sample size} (or \emph{zero-failure}) test plan is
one in which we test $n$ modems and state that the test is passed
if there are no failures, that is, $c = 0$. Given our
$Beta(86.4,3.6)$ prior distribution, $\pi_1 = 0.938$, $\beta =
0.10$, and $c = 0$, we find the desired Bayesian zero-failure test
plan by solving Eq.~\ref{ch10:eqn6} for sample size or number of
tests $n$. Using Eq.~\ref{ch10:eqn6} yields the expression
\index[sub]{test plan!minimum sample size}\index[sub]{test
plan!zero-failure}
\begin{eqnarray}\label{ch10:eqn7}
\lefteqn{\PP(\pi \leq 0.938 \con Test\mbox{ }Is\mbox{ }Passed)}\hspace{0.5in}\\
& & = \frac
{\int^{0.938}_{0}\left(_0^n\right)(1-\pi)^{0}\pi^{n}p(\pi) \D
\pi}{\int^{1}_{0} \left(_0^n\right)(1-\pi)^{0}\pi^{n}
p(\pi) \D \pi}\nonumber\\
& & = \frac {\int^{0.938}_{0}
\pi^{n}\frac{\Gamma(86.4+3.6)}{\Gamma(86.4)\Gamma(3.6)}
\pi^{86.4-1}(1-\pi)^{3.6-1} \D \pi}{\int^{1}_{0}
\pi^{n}\frac{\Gamma(86.4 + 3.6)}{\Gamma(86.4)\Gamma(3.6)}
\pi^{86.4-1}(1-\pi)^{3.6-1} \D \pi} \nonumber \\
& & = I(0.938;86.4 + n, 3.6) \leq 0.10 \, ,\nonumber
\end{eqnarray}
where $I(z; \alpha, \beta)$ denotes the \emph{incomplete beta
function ratio}\index[sub]{beta function!incomplete ratio}. Upon
evaluating the incomplete beta function ratio in
Eq.~\ref{ch10:eqn7} for increasing values of $n$, we find that $n
= 9$ is the smallest integer that satisfies the inequality.
Consequently, the plan consists of testing 9 $B$ modems. If none
fail, we can then claim that $\PP(\pi \leq 0.938 \con No\mbox{
}Failures\mbox{ }in\mbox{ }9\mbox{ }Tests) = 0.097 < 0.10$, as
required. In this case, given no failures in the 9 $B$ modem
tests, the 0.1 quantile of the posterior distribution of $\pi$ is
0.9384. Finally, the unconditional probability of passing the test
is simply
\begin{eqnarray*}
\PP[ Test\mbox{ }Is\mbox{ }Passed] & = & {\int^{1}_{0}
\left(_0^n\right)(1-\pi)^{0}\pi^{n}
p(\pi) \D \pi}\\
& =  & \frac{\Gamma(86.4+n)\Gamma(3.6)}{\Gamma(86.4+3.6+n)}
\frac{\Gamma(86.4+3.6)}{\Gamma(86.4)\Gamma(3.6)}\\
& = & \frac{\Gamma(95.4)\Gamma(90)}{\Gamma(99)\Gamma(86.4)} = 0.70. \\
\end{eqnarray*}
\end{sidebar}

\section{Binomial Testing}\label{ch10:sec2}\index[sub]{test
plan!binomial}\index[sub]{assurance
testing}\index[sub]{test!assurance} Now consider both the
average\index[sub]{risk!average} and posterior
risks\index[sub]{risk!posterior} for the binomial sampling
\index[sub]{sampling!binomial distribution} distribution within a
hierarchical framework. Suppose that we have failure count data
from $m > 1$ situations, such as $m$ different plants. Let $x_{i}$
denote the observed number of failures in a sample of size $n_{i}$
for $i = 1, \ldots, m$, and let $\vec{x}$ represent all the
observed failure count data. Then, conditional on the success
probability $\pi_{i}$, assume that the $X_i$ are conditionally
independent and that $X_{i} \con \pi_{i} \sim Binomial(n_{i}, 1 -
\pi_{i})$. Also assume that the $\pi_i$ can be modeled
hierarchically --- specifically, that given $\delta$ and $\gamma$
they are independent and identically distributed (i.i.d.)\ with a
common $Beta(\delta, \gamma)$ distribution. Finally, we specify a
prior distribution for the hyperparameters $(\delta, \gamma)$,
denoted by $p(\delta, \gamma)$, which is a proper (but usually
diffuse) joint distribution.

\subsection{Binomial Posterior Consumer's and Producer's
Risks}\label{ch10:sec2:ss1} Given that there are observed data
$X_i \sim Binomial(n_i, 1 - \pi_i)$, suppose that we are
interested in developing a binomial test plan $(n,c)$ using the
posterior risk\index[sub]{risk!posterior} criteria as our test
criteria. Our test plan is for a situation ``similar'' to those
previously observed, where we describe similarity by assuming that
for the new situation, an item has probability $\pi$ of surviving
the test, where given $\delta$ and $\gamma$, $\pi$ and the $\pi_i$
are i.i.d.\ $Beta(\delta, \gamma)$.

Recall that both the posterior producer's
risk\index[sub]{risk!posterior producer's} and posterior
consumer's risk\index[sub]{risk!posterior consumer's} specify
criteria on the posterior distribution for the binomial
probability of success $\pi$. Since there are now observed data
$\vec{x}$, we condition on that data and now use $p(\pi \con
\vec{x})$ in place of $p(\pi)$ in Eqs.~\ref{ch10:eqn5} and
\ref{ch10:eqn6}. In particular, for a binomial test plan $(n,c)$,
an expression for the posterior producer's risk is
\begin{eqnarray}\label{ch10:eqn8}
\PP(\pi \geq \pi_{0} & \con & Test\mbox{ }Is\mbox{ }Failed,\vec{x})\\
& =& \frac{\int_{\pi_0}^{1} \left[
1-\sum^{c}_{y=0}(_y^{n})(1-\pi)^{y}\pi^{n-y} \right] p(\pi \con
\vec{x}) \D \pi}{1-\int_{0}^{1}
\left[\sum^{c}_{y=0}(_y^{n})(1-\pi)^{y}\pi^{n-y} \right] p(\pi
\con \vec{x}) \D \pi}\, .\nonumber
\end{eqnarray}
Similarly, the posterior consumer's risk is
\begin{eqnarray}\label{ch10:eqn9}
\PP(\pi \leq \pi_{0} & \con & Test\mbox{ }Is\mbox{ }Passed,\vec{x})\\
& =& \frac{\int_{0}^{\pi_1} \left[
\sum^{c}_{y=0}(_y^{n})(1-\pi)^{y}\pi^{n-y} \right] p(\pi \con
\vec{x}) \D \pi}{\int_{0}^{1}
\left[\sum^{c}_{y=0}(_y^{n})(1-\pi)^{y}\pi^{n-y} \right] p(\pi
\con \vec{x}) \D \pi} \, .\nonumber
\end{eqnarray}

Now we must determine how to evaluate these criteria. There are
two equivalent ways to approach the problem. First, notice that
both of the posterior risk criteria are probability statements
about the posterior distribution of $\pi$ given different data.
For a given choice of $(n,c)$, the posterior producer's risk can
be calculated by using Markov chain Monte Carlo (MCMC) to find the
posterior distribution of $\pi$ given $\vec{x}$ and $y > c$ and
then calculating the proportion of posterior draws with $\pi \geq
\pi_0$. Similarly, for a given choice of $(n,c)$, the posterior
consumer's risk can be calculated by using MCMC to find the
posterior distribution of $\pi$ given $\vec{x}$ and $y \leq c$ and
then calculating the proportion of posterior draws with $\pi \leq
\pi_1$. Notice, however, that for each choice of $(n,c)$, this
requires using MCMC to calculate two posterior distributions for
$\pi$.

Suppose instead that we condition only the data $X_i \sim
Binomial(n_i, 1-\pi_i)$ with $\pi_i \sim Beta(\delta,\gamma)$ and
use MCMC to obtain the posterior predictive distribution $p(\pi
\con \vec{x})$. We can obtain draws from the posterior predictive
distribution $p(\pi \con \vec{x})$ using the $N$ posterior draws
for $(\delta, \gamma)$ by drawing $\pi^{(j)} \sim
Beta(\delta^{(j)}, \gamma^{(j)})$, and then use these samples to
evaluate Eqs.~\ref{ch10:eqn8} and \ref{ch10:eqn9} using Monte
Carlo integration. In general, to evaluate $\rE[g(x)] = \int g(x)
p(x) dx$, obtain a random sample $x_1, \ldots, x_N$ from $p(x)$
and approximate the expectation as $\frac{1}{N} \sum_{i=1}^{N}
g(x_i)$.

We evaluate the posterior producer's risk as
\begin{eqnarray*}
\lefteqn{\PP[\pi \geq \pi_{1}\con Test\mbox{ }Is\mbox{ }Failed,
\vec{x} ] \approx} \\
 & & \frac{\frac{1}{N} \sum^{N}_{j=1} \left[1-
\sum^{c}_{y=0}(_y^{n})(1-\pi^{(j)})^{y}(\pi^{(j)})^{n-y} \right]
I(\pi^{(j)} \geq \pi_0)}{1- \frac{1}{N}
\sum^{N}_{j=1}\left[\sum^{c}_{y=0}(_y^{n})(1-\pi^{(j)})^{y}(\pi^{(j)})^{n-y}
\right]} \, ,
\end{eqnarray*}
and the posterior consumer's risk as
\begin{eqnarray*}
\lefteqn{\PP[\pi \leq \pi_{1} \con Test\mbox{ }Is\mbox{ }Passed, \vec{x} ] \approx} \\
& & \frac{\sum^{N}_{j=1} \left[
\sum^{c}_{y=0}(_y^{n})(1-\pi^{(j)})^{y}(\pi^{(j)})^{n-y} \right]
I(\pi^{(j)} \leq \pi_1)}{\sum^{N}_{j=1}\left[
\sum^{c}_{y=0}(_y^{n})(1-\pi^{(j)})^{y}(\pi^{(j)})^{n-y} \right]}
\, .
\end{eqnarray*}
The expression for the unconditional probability of passing the
test is
\begin{equation}\label{ch10:eqn9a}
\PP(Test\mbox{ }Is\mbox{ }Passed \con \vec{x} ) \approx \frac
{1}{N}\sum^{N}_{j=1}\left[
\sum^{c}_{y=0}(_y^{n})(1-\pi^{(j)})^{y}(\pi^{(j)})^{n-y} \right]
\, .
\end{equation}
Let
\begin{displaymath}
b^{(j)}(y) = \frac{(_y^{n})B(n-y+\delta^{(j)},y+\gamma^{(j)})}
{B(\delta^{(j)},\gamma^{(j)})} \, ,
\end{displaymath}
where $B(\alpha, \beta)$ is the beta function. We can also
evaluate the posterior producer's risk using the posterior draws
$\delta^{(j)}, \gamma^{(j)} \con \vec{x}$ as
\begin{eqnarray*}
\lefteqn{\PP[\pi \geq \pi_{0}\con Test\mbox{ }Is\mbox{ }Failed,
\vec{x} ] \approx} \\
 & & \frac
{\sum^{N}_{j=1} \left[
1-I(\pi_{0};\delta^{(j)},\gamma^{(j)})-\sum^{c}_{y=0}
b^{(j)}(y)[1-I(\pi_{0};n-y+\delta^{(j)}, y+\gamma^{(j)})] \right]}
{\sum^{N}_{j=1} \left[1-\sum^{c}_{y=0} b^{(j)}(y) \right]} \, ,
\end{eqnarray*}
and the posterior consumer's risk as
\begin{eqnarray*}
\lefteqn{\PP[\pi \leq \pi_{1} \con Test\mbox{ }Is\mbox{ }Passed, \vec{x} ] \approx} \\
& & \frac {\sum^{N}_{j=1} \left[\sum^{c}_{y=0} b^{(j)}(y)
I(\pi_{1};n-y+\delta^{(j)},y+\gamma^{(j)})\right]}{\sum^{N}_{j=1}
\sum^{c}_{y=0} b^{(j)}(y)} \, ,
\end{eqnarray*}
where $I(z; \alpha, \beta)$ is the incomplete beta function ratio.
An additional expression for the unconditional probability of
passing the test is
\begin{eqnarray*}
\PP(Test\mbox{ }Is\mbox{ }Passed \con \vec{x} ) & \approx &
\frac{1}{N}\sum^{N}_{j=1} \sum^{c}_{y=0} b^{(j)}(y)\\
\mbox{} & \approx & \frac
{1}{N}\sum^{N}_{j=1}\left[\sum^{c}_{y=0}\frac{(_y^{n})B(n-y+\delta^{(j)},y+\gamma^{(j)})}
{B(\delta^{(j)},\gamma^{(j)})}\right] \, .
\end{eqnarray*}

To obtain a test plan, simultaneously solve the pair of
inequalities given by
\begin{equation}\label{ch10:eqn10}
\PP[\pi \geq \pi_{0}\con Test\mbox{ }Is\mbox{ }Failed, \vec{x} ]
\leq \alpha
\end{equation}
and
\begin{equation}\label{ch10:eqn11}
\PP[\pi \leq \pi_{1}\con Test\mbox{ }Is\mbox{ }Passed, \vec{x}
]\leq \beta,
\end{equation}
for the pair of integers $(n,c)$, where $0 \leq c < n$, and where
$\alpha$ and $\beta$ are the desired maximum posterior producer's
and consumer's risks.

We can find such test plans because Eqs.~\ref{ch10:eqn10} and
\ref{ch10:eqn11} have opposite effects. For fixed $c$, as $n$
increases, $\PP[\pi \leq \pi_{1} \con Test\mbox{ }Is\mbox{
}Passed, \vec{x} ]$ decreases, whereas $\PP[\pi \geq \pi_{0}\con
Test\mbox{ }Is\mbox{ }Failed, \vec{x} ]$ increases. On the other
hand, for fixed $n$, as $c$ increases, the opposite is true.
Consequently, we can use the algorithm in Fig.~\ref{ch10:fig1} to
find the required test plan.

\begin{figure}
\setlength{\unitlength}{0.095in} \centering
\begin{picture}(40,40)
\put(0,36){\framebox(5,4){Begin}} \put(2.5,36){\vector(0,-1){4}}
\put(0,28){\framebox(5,4){\shortstack{$n=1$ \\ $c=0$}}}
\put(2.5,28){\vector(0,-1){4}}
\put(0,20){\framebox(21,4){\shortstack{Posterior Producer's Risk
\\ $\PP[\pi \ge \pi_0 \con \mbox{Test is Failed}, \vec{x}] \le \alpha$?}}}
\put(2.5,20){\vector(0,-1){4}}
\put(0,12){\framebox(21,4){\shortstack{Posterior Consumer's Risk
\\ $\PP[\pi \le \pi_1 \con \mbox{Test is Passed}, \vec{x}] \le \beta$?}}}
\put(2.5,12){\vector(0,-1){4}} \put(0,4){\framebox(5,4){End}}
\put(24,20){\framebox(8,4){$c < n - 1$}}
\put(21,22){\vector(1,0){3}} \put(36,20){\framebox(8,4){$c = c +
1$}} \put(24,12){\framebox(8,4){$n = n + 1$}}
\put(36,12){\framebox(8,4){$n = n + 1$}}
\put(21,14){\vector(1,0){3}} \put(32,22){\vector(1,0){4}}
\put(16,18){\vector(0,1){2}} \put(16,18){\line(1,0){12}}
\put(28,18){\line(0,-1){2}} \put(30,20){\line(0,-1){2}}
\put(30,18){\line(1,0){10}} \put(40,18){\vector(0,-1){2}}
\put(40,24){\line(0,1){2}} \put(40,26){\line(-1,0){20}}
\put(20,26){\vector(0,-1){2}} \put(0,18){Yes} \put(0,10){Yes}
\put(22,22.5){No} \put(22,14.5){No} \put(33,22.5){Yes}
\put(33,18.5){No} \put(42,16){\vector(0,1){4}}
\end{picture}
\caption{An algorithm for finding Bayesian hierarchical binomial test
plans.}\label{ch10:fig1}
\end{figure}

\begin{sidebar}\label{ch10:ex2} {\bf Hierarchical binomial test plan for EDGs.}
\index[sub]{test plan!binomial} \citet{MKA96} analyzes failure
count data from EDGs in 63 U.S.\ commercial nuclear power plants
to assess their reliability of accepting the electrical load and
run (\emph{load-run}) on demand. See Table~\ref{ch10:tab1}, which
summarizes the data collected over the four-year period
1988-1991.\index[aut]{Martz, H.} \index[aut]{Kvam, P.}
\index[aut]{Abramson, L.}

\begin{table}
\caption{EDG load-run demand data ($x$ failures out of $n$
demands) \citep{MKA96}}\label{ch10:tab1} \centering
\begin{tabular}{crr|crr|ccr}
\hline \multicolumn{1}{c}{Plant} & \mbox{}  $x$ & \mbox{}  $n$
\mbox{} & \multicolumn{1}{c}\mbox{}
Plant & \mbox{}  $x$ & \mbox{}  $n$ \mbox{}&\multicolumn{1}{c}\mbox{}  Plant & $x$ & \mbox{}  $n$\\
\hline%
1  \mbox{}&  11 \mbox{} & 854\phantom{*} &\mbox{}  22  \mbox{} &  0  \mbox{} &   238 \mbox{}& \hspace{0.05in}43 &  5  \mbox{} &  216 \\
2  \mbox{}&  2  \mbox{} & 373\phantom{*} &\mbox{}  23  \mbox{} &  1  \mbox{} &   370 \mbox{}& \hspace{0.05in}44 &  0  \mbox{} &  252 \\
3  \mbox{}&  5  \mbox{} & 618\phantom{*} &\mbox{}  24  \mbox{} &  2  \mbox{} &   302 \mbox{}& \hspace{0.05in}45 &  1  \mbox{} &  419 \\
4  \mbox{}&  5  \mbox{} & 157\phantom{*} &\mbox{}  25  \mbox{} &  3  \mbox{} &   152 \mbox{}& \hspace{0.05in}46 &  0  \mbox{} &  136 \\
5  \mbox{}&  3  \mbox{} & 542\phantom{*} &\mbox{}  26  \mbox{} &  2  \mbox{} &   294 \mbox{}& \hspace{0.05in}47 &  3  \mbox{} &  185 \\
6  \mbox{}&  2  \mbox{} & 202\phantom{*} &\mbox{}  27  \mbox{} &  0  \mbox{} &   101 \mbox{}& \hspace{0.05in}48 &  7  \mbox{} &  382 \\
7  \mbox{}&  0  \mbox{} & 65\phantom{*}  &\mbox{}  28  \mbox{} &  0  \mbox{} &   283 \mbox{}& \hspace{0.05in}49 &  6  \mbox{} &  304 \\
8  \mbox{}&  2  \mbox{} & 166\phantom{*} &\mbox{}  29  \mbox{} &  2  \mbox{} &   117 \mbox{}& \hspace{0.05in}50 &  2  \mbox{} &  130 \\
9  \mbox{}&  4  \mbox{} & 574\phantom{*} &\mbox{}  30  \mbox{} &  0  \mbox{} &   115 \mbox{}& \hspace{0.05in}51 &  1  \mbox{} &  121 \\
10 \mbox{}&  2  \mbox{} & 201\phantom{*} &\mbox{}  31  \mbox{} &  1  \mbox{} &   196 \mbox{}& \hspace{0.05in}52 &  2  \mbox{} &  295 \\
11 \mbox{}&  8  \mbox{} & 388\phantom{*} &\mbox{}  32  \mbox{} &  0  \mbox{} &   310 \mbox{}& \hspace{0.05in}53 &  1  \mbox{} &  289 \\
12 \mbox{}&  2  \mbox{} & 287\phantom{*} &\mbox{}  33  \mbox{} &  4  \mbox{} &   134 \mbox{}& \hspace{0.05in}54 &  0  \mbox{} &  181 \\
13 \mbox{}&  3  \mbox{} & 431\phantom{*} &\mbox{}  34  \mbox{} &  2  \mbox{} &   132 \mbox{}& \hspace{0.05in}55 &  2  \mbox{} &  150 \\
14 \mbox{}&  5  \mbox{} & 358\phantom{*} &\mbox{}  35  \mbox{} &  0  \mbox{} &   242 \mbox{}& \hspace{0.05in}56 &  0  \mbox{} &  334 \\
15 \mbox{}& 14  \mbox{} & 1120\phantom{*} &\mbox{} 36  \mbox{} &  4  \mbox{} &   132 \mbox{}& \hspace{0.05in}57 &  2  \mbox{} &  263 \\
16 \mbox{}&  1  \mbox{} & 321\phantom{*} &\mbox{}  37  \mbox{} &  4  \mbox{} &   320 \mbox{}& \hspace{0.05in}58 &  0  \mbox{} &  92 \\
17 \mbox{}&  3  \mbox{} & 225\phantom{*} &\mbox{}  38  \mbox{} &  0  \mbox{} &   996 \mbox{}& \hspace{0.05in}59 &  2  \mbox{} &  466 \\
18 \mbox{}&  8  \mbox{} & 433\phantom{*} &\mbox{}  39  \mbox{} &  1  \mbox{} &   253 \mbox{}& \hspace{0.05in}60 &  2  \mbox{} &  387 \\
19 \mbox{}&  7  \mbox{} & 468\phantom{*} &\mbox{}  40  \mbox{} & 13  \mbox{} &   704 \mbox{}& \hspace{0.05in}61 &  1  \mbox{} &  183 \\
20 \mbox{}&  1  \mbox{} & 218\phantom{*} &\mbox{}  41  \mbox{} &  2  \mbox{} &   151 \mbox{}& \hspace{0.05in}62 &  5  \mbox{} &  278 \\
21 \mbox{}&  9  \mbox{} & 317\phantom{*} &\mbox{}  42  \mbox{} &  2  \mbox{} &   385 \mbox{}& \hspace{0.05in}63 &  0  \mbox{} &  212\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

We model the failure counts $X_i$ as conditionally independent given
$\pi_i$ with $Binomial(n_i,1 - \pi_i)$ distributions, where
$\pi_i$ is the $i$th plant reliability. Because the plants have
all been built and operated to the same Nuclear Regulatory
Commission (NRC)-controlled safety standards, model the 63
$\pi_i \con \delta, \gamma$ as i.i.d.\ with a common
$Beta(\delta,\gamma)$ distribution. In our analysis of these data,
we use independent and diffuse $InverseGamma(0.1,0.1)$ prior
distributions for $\delta$ and $\gamma$. See
Table~\ref{ch10:tab2}, which summarizes the marginal posterior
distributions for $\delta$ and $\gamma$ and the predictive
distribution for $\pi$. The hierarchical binomial model fits the
load-run demand data well (see
Exercise~\ref{ch4}.\ref{exercise:ch4EDG}).

\begin{table}
\caption{Posterior distribution summaries for the hyperparameters
$\delta$ and $\gamma$ and the predictive distribution for
$\pi$}\label{ch10:tab2}
 \centering
\begin{tabular}{crrrrrrrrrrrrrr}
\hline                              &       &    &       &       &
 &                                & & \multicolumn{3}{c}{Quantiles}  & &
 \\ \cline{7-15}
 Parameter&\mbox{}&Mean&\mbox{}&Std
 Dev&\mbox{}\mbox{}\mbox{}
 &\multicolumn{1}{r}{0.025}&\mbox{}&\multicolumn{1}{r}{0.05}&\mbox{}&0.50 & \mbox{} & \multicolumn{1}{r}{0.95}& \mbox{} & \multicolumn{1}{r}{0.975}\\
\hline%
$\delta$ &\mbox{}   &286.4&\mbox{}  &135.6&\mbox{}  &121.5&\mbox{}  &136.9&\mbox{}  &253.2&\mbox{}  &557.4&\mbox{}   &652.8\\
$\gamma$&\mbox{}    &2.710&\mbox{}  &1.243&\mbox{}  &1.226&\mbox{}  &1.360&\mbox{}  &2.402&\mbox{}  &5.171&\mbox{}   &6.204\\
$\pi$&\mbox{}& 0.9903 &\mbox{}& 0.0067 &\mbox{}& 0.9735 &\mbox{}& 0.9778 &\mbox{}& 0.9917 &\mbox{}& 0.9981 &\mbox{}& 0.9987 \\
\hline
\end{tabular}
\end{table}

Using the posterior risk criteria, suppose now that we want to
find the test plan having the posterior consumer's and producer's
risks $\beta = 0.05$ for $\pi_{1} = 0.985$, and $\alpha = 0.10$
for $\pi_{0} = 0.999$, respectively.

Using the algorithm in Fig.~\ref{ch10:fig1}, we obtain the
required test plan $n = 42$ and $c = 0$. For this test plan, the
actual posterior consumer's risk \linebreak $\PP[\pi \leq 0.985
\con Test\mbox{ }Is\mbox{ }Passed, \vec{x}] = 0.0014$ and the
actual posterior producer's risk $\PP[\pi \geq 0.999\con
Test\mbox{ }Is\mbox{ }Failed,\vec{x}] = 0.0992$. Therefore, at the
new plant, load and run the EDGs 42 times. (Note that we are also
assuming here that all the EDGs at the new plant have the same
load-run demand reliability.) If there are no failures, then we
can assure an EDG load-run demand reliability of 0.985 with a 0.95
probability. On the other hand, if the test is failed, we have the
assurance that the EDG load-run demand reliability is not greater
than 0.999 with a 0.90 probability. Finally, from
Eq.~\ref{ch10:eqn9a}, the unconditional probability of passing
this test is approximately 0.69.
\end{sidebar}

\subsection{Hybrid Risk Criterion}\label{ch10:sec1:ss4}\index[sub]{risk!hybrid}
\citet{FMP99} uses the posterior consumer's
risk\index[sub]{risk!posterior consumer's} criterion in
Eq.~\ref{ch10:eqn6} and the average producer's risk criterion in
Eq.~\ref{ch10:eqn3} to \index[sub]{risk!average producer's}
determine alternative binomial test plans. These ``hybrid''
criteria are appropriate in situations where we are interested in
a single specified level of reliability, which \citet{FMP99}
refers to as the \emph{target reliability
level}\index[sub]{reliability!target}. \citet{FMP99} reasons that,
in many applications of reliability assurance testing, the
consumer and producer are one and the same. Consequently, in such
situations, there may be less adversarial tension in determining
appropriate risk criteria, and therefore, little motivation to
specify two different (and acceptable) levels of reliability
($\pi_{0}$ and $\pi_{1}$) for the required test
plan.\index[aut]{Fitzgerald, M.} \index[aut]{Martz, H.}
\index[aut]{Parker, R.}\index[aut]{Fitzgerald, M.}
\index[aut]{Martz, H.} \index[aut]{Parker, R.}

Likewise, we use this hybrid approach and seek a Bayesian binomial
test plan for which there is a probability of at most $\beta$ that
$\pi \leq \pi^{*}$ for a passing test, and simultaneously, there
is a probability of at most $\alpha$ that a test is failed given
$\pi \geq \pi^{*}$.

Notationally, we want to find the test plan $(n,c)$ that satisfies
the hybrid risk criteria\index[sub]{risk!hybrid} given by
\begin{equation}\label{ch10:eqn12}
\PP[Test\mbox{ }Is\mbox{ }Failed \con\pi\geq\pi^{*}, \vec{x}] \leq
\alpha
\end{equation}
and
\begin{equation}\label{ch10:eqn13}
\PP[\pi \leq \pi^{*} \con Test\mbox{ }Is\mbox{ }Passed,\vec{x}]
\leq \beta.
\end{equation}

For test plan $(n,c)$, we can approximate the average producer's
risk by
\begin{eqnarray}\label{ch10:eqn14}
\lefteqn{\PP[Test\mbox{ }Is\mbox{ }Failed \con \pi\geq\pi^{*},
\vec{x}] \approx} \\
& & \frac{\sum^{N}_{j=1} \left[
1-I(\pi^{*};\delta^{(j)},\gamma^{(j)})-\sum^{c}_{y=0} b^{(j)}(y)
[1-I(\pi^{*};n-y+\delta^{(j)}, y+\gamma^{(j)})] \right]}
{\sum^{N}_{j=1} \left[ 1-I(\pi^{*};\delta^{(j)},\gamma^{(j)})
\right] } .\nonumber
\end{eqnarray}

We find the desired Bayesian test plan by employing the algorithm
in Fig.~\ref{ch10:fig1}, where Eq.~\ref{ch10:eqn14} replaces the
producer's risk inequality statement used in the algorithm.

\begin{sidebar}\label{ch10:ex3} {\bf Hierarchical binomial test plan using hybrid
criteria.} Again consider Example~\ref{ch10:ex2}. Consider finding
a Bayesian test plan having the posterior consumer's and
average producer's risks $\beta = 0.05$ and $\alpha = 0.05$ for
$\pi^{*} = 0.98$, respectively. Using the algorithm in
Fig.~\ref{ch10:fig1} with the modification described above, we
obtain the required test plan $n = 71$ and $c = 2$. For this test
plan, the actual posterior consumer's risk is
$\PP[\pi\leq 0.98 \con Test\mbox{ }Is\mbox{ }Passed, \vec{x} ] =
0.0497$ and the actual average producer's risk $\PP[Test\mbox{
}Is\mbox{ }Failed \con \pi\geq 0.98, \vec{x}] = 0.0333$. Because we
now only consider a single target reliability level, this test
plan requires significantly more testing than that found in
Example~\ref{ch10:ex2}, in which two different reliability values
were specified. From Eq.~\ref{ch10:eqn9a}, the unconditional
probability of passing this test is approximately 0.951.
\end{sidebar}

\section{Poisson Testing}\label{ch10:sec3}\index[sub]{test
plan!Poisson}\index[sub]{assurance
testing}\index[sub]{test!assurance} We now move from binomial
testing within a hierarchical framework to Poisson testing. Recall
from Chap.~\ref{ch6} that a homogeneous Poisson
process\index[sub]{Poisson process!homogeneous} generates a
sequence of events for which the times between successive failures
(the \emph{interfailure times}) are independently and identically
$Exponential(\lambda)$ distributed. For a particular Poisson
testing situation, let us develop a Bayesian test plan for
assuring that the \emph{failure rate} $\lambda$ does not exceed a
specified requirement. From Poisson process theory, the number of
failures $X$ occurring in fixed total test or operating time $T$
has a $Poisson(\lambda T)$ distribution. Let $T$ represent the
total operating or exposure time of the devices during which we
assume that devices are either repaired or replaced when they
fail.

Suppose that the plan tests $n$ devices for the length of time
$t_{0}$, replacing devices as they fail, so that the total
operating time is $T = nt_{0}$. In determining a Bayesian test
plan, we seek $(T,c)$, where $c$ is the maximum allowed number of
failures. The test is passed if no more than $c$ failures occur in
total test time $T$. Note that any combination of $n$ and $t_{0}$
satisfying $T = nt_{0}$ provides an acceptable test plan.

As with binomial testing, let us assume in Poisson testing that
there are data available from $m > 1$ situations. Let $x_{i}$
denote the observed number of failures in total operating time
$T_{i}$ for the $i$th situation, and let $\vec{x}$ represent all
the observed failure data. Then, conditioning on $\lambda_{i}$,
$X_{i} \sim Poisson(\lambda_{i}T_{i})$, where the $X_{i}$ are
conditionally independent. We model the $\lambda_{i}$
hierarchically, assuming they are i.i.d.\ $Gamma(\eta, \kappa)$,
given $\eta$ and $\kappa$, and specify a prior distribution for
the hyperparameters $(\eta, \kappa)$, denoted by $p(\eta,
\kappa)$.

We can write an expression for the posterior producer's
risk\index[sub]{risk!posterior producer's} for the Poisson test
plan\index[sub]{test plan!Poisson} $(T,c)$, where $\lambda_{0}$ is
the rejectable failure rate and there is a maximum allowable
posterior producer's risk $\alpha$:
\begin{eqnarray}\label{ch10:ppr}
Posterior\mbox{ }Producer's\mbox{ }Risk & = &
\PP(\lambda \leq \lambda_{0}\con Test\mbox{ }Is\mbox{ }Failed)\\
\mbox{} & = & \int_{0}^{\lambda_0} p(\lambda \con y > c) \D \lambda \nonumber\\
\mbox{} & = & \int_{0}^{\lambda_0} \frac{f(y > c \con \lambda)
p(\lambda)}{\int_{0}^{\infty} f(y > c \con \lambda) p(\lambda) \D \lambda} \,\, \D \lambda \nonumber\\
\mbox{} & = & \frac{\int_{0}^{\lambda_0} \left[1-
\sum^{c}_{y=0}\frac{(\lambda T)^y \exp(-\lambda T)}{y!} \right]
p(\lambda) \D \lambda}{\int_{0}^{\infty} \left[ 1- \sum^{c}_{y=0}
\frac{(\lambda T)^y \exp(-\lambda T)}{y!} \right] p(\lambda) \D
\lambda}\nonumber \leq \alpha.\nonumber
\end{eqnarray}

Similarly, given that the test is passed, we can write an
expression for the posterior consumer's
risk\index[sub]{risk!posterior consumer's} for the Poisson test
plan\index[sub]{test plan!Poisson} $(T,c)$, with acceptable
failure rate $\lambda_{1}$ and maximum allowable posterior
consumer's risk $\beta$, as
\begin{eqnarray}\label{ch10:pcr}
Posterior\mbox{ }Consumer's\mbox{ }Risk & = &
\PP(\lambda \geq \lambda_{1}\con Test\mbox{ }Is\mbox{ }Passed)\\
\mbox{} & = & \int_{\lambda_1}^{\infty} p(\lambda \con y \leq c) \D \lambda \nonumber\\
\mbox{} & = & \int_{\lambda_1}^{\infty} \frac{f(y \leq c \con
\lambda)
p(\lambda)}{\int_{0}^{\infty} f(y \leq c \con \lambda) p(\lambda) \D \lambda} \,\, \D \lambda \nonumber\\
\mbox{} & = & \frac{\int_{\lambda_1}^{\infty} \left[
\sum^{c}_{y=0}\frac{(\lambda T)^y \exp(-\lambda T)}{y!} \right]
p(\lambda) \D \lambda}{\int_{0}^{\infty} \left[\sum^{c}_{y=0}
\frac{(\lambda T)^y \exp(-\lambda T)}{y!} \right] p(\lambda) \D
\lambda}\nonumber \leq \beta.\nonumber
\end{eqnarray}

Since there are available data $\vec{x}$, we use the posterior
distribution for $\lambda$, $p(\lambda \con \vec{x})$, in
Eqs.~\ref{ch10:ppr} and \ref{ch10:pcr} to construct our test plan
for a new situation. We can calculate the posterior producer's
risk either using posterior predictive draws $\lambda^{(j)}$ or
using posterior draws $(\eta^{(j)}, \kappa^{(j)})$. Let
\begin{displaymath}
g^{(j)}(y) = \frac {(\kappa^{(j)})^{\eta^{(j)}}T^{y}}{y!
\Gamma(\eta^{(j)})(T+\kappa^{(j)})^{y+\eta^{(j)}}} \, .
\end{displaymath}

\begin{eqnarray*}
\PP[ \lambda & \leq & \lambda_{0} \con Test\mbox{ }Is\mbox{ }Failed,\vec{x}]\\
\mbox{} & \approx & \frac{\sum_{j=1}^{N} \left[1-
\sum^{c}_{y=0}\frac{(\lambda^{(j)} T)^y \exp(-\lambda^{(j)}
T)}{y!} \right]I(\lambda^{(j)} \leq \lambda_0)}{\sum_{j=1}^{N}
\left[ 1- \sum^{c}_{y=0}
\frac{(\lambda^{(j)} T)^y \exp(-\lambda^{(j)} T)}{y!} \right]}\\
\mbox{} & \approx & \frac { \sum^{N}_{j=1} \left[
\gamma(\eta^{(j)},\kappa^{(j)}\lambda_{0})/\Gamma(\eta^{(j)})-
\sum^{c}_{y=0} g^{(j)}(y)
\gamma[y+\eta^{(j)},(T+\kappa^{(j)})\lambda_{0}] \right]}
{\sum^{N}_{j=1} \left[ 1- \sum^{c}_{y=0} g^{(j)}(y)
\Gamma(y+\eta^{(j)})\right] } \, ,
\end{eqnarray*}
where $\gamma(q, z)$ denotes the \emph{lower incomplete gamma
function}\index[sub]{gamma function!lower incomplete}.

The expressions for the posterior consumer's
risk\index[sub]{risk!posterior consumer's} are
\begin{eqnarray*}
\PP[\lambda & \geq & \lambda_{1}  \con  Test\mbox{ }Is\mbox{
}Passed, \vec{x} ]\\
\mbox{} & \approx & \frac{\sum_{j=1}^{N} \left[
\sum^{c}_{y=0}\frac{(\lambda^{(j)} T)^y \exp(-\lambda^{(j)}
T)}{y!} \right] I(\lambda^{(j)} \geq \lambda_1)} {\sum_{j=1}^{N}
\left[\sum^{c}_{y=0}
\frac{(\lambda^{(j)} T)^y \exp(-\lambda^{(j)} T)}{y!} \right]}\\
& \approx & \frac { \sum^{N}_{j=1} \left[ \sum^{c}_{y=0}
g^{(j)}(y) \{ \Gamma(y+\eta^{(j)})
-\gamma[y+\eta^{(j)},(T_{0}+\kappa^{(j)})\lambda_{1}] \} \right] }
{ \sum^{N}_{j=1} \left[ \sum^{c}_{y=0} g^{(j)}(y)
\Gamma(y+\eta^{(j)}) \right] } \, .
\end{eqnarray*}

We can also write the unconditional probability of passing the
test as
\begin{eqnarray*}
\PP[ Test \mbox{ }Is \mbox{ }Passed | \vec{x}] & \approx &
\frac{1}{N} \sum_{j=1}^{N} \left[\sum^{c}_{y=0}
\frac{(\lambda^{(j)} T)^y \exp(-\lambda^{(j)} T)}{y!} \right]\\
\mbox{} & \approx & \frac {1}{N} \sum^{N}_{j=1}
\sum^{c}_{y=0} g^{(j)}(y) \Gamma(y+\eta^{(j)})\\
\mbox{} & \approx & \frac {1}{N} \sum^{N}_{j=1}\left[
\sum^{c}_{y=0} \frac
{(\kappa^{(j)})^{\eta^{(j)}}T^{y}\Gamma(y+\eta^{(j)})}{y!
\Gamma(\eta^{(j)})(T+\kappa^{(j)})^{y+\eta^{(j)}}}\right].
\end{eqnarray*}

To obtain a test plan, simultaneously solve the following
pair of nonlinear inequalities:
\begin{equation}\label{ch10:eqn17}
\PP[\lambda\leq\lambda_{0} \con Test\mbox{ }Is\mbox{ }Failed,
\vec{x} ]\leq \alpha
\end{equation}
and
\begin{equation}\label{ch10:eqn18}
\PP[\lambda\geq\lambda_{1} \con Test \mbox{ }Is\mbox{ }Passed,
\vec{x}]\leq\beta,
\end{equation}
where $\lambda_{0} \leq \lambda_{1}$.

Because $T$ is continuous, we can hold either of the risks in
Eqs.~\ref{ch10:eqn17} and \ref{ch10:eqn18} at its precise value.
Holding the posterior producer's risk at exactly $\alpha$, use the
algorithm in Fig. \ref{ch10:fig2} to obtain the desired test plan.
On the other hand, holding the posterior consumer's risk at
precisely $\beta$, simply reverse the two main steps in the
procedure.

\begin{figure}
\setlength{\unitlength}{0.1in} \centering
\begin{picture}(40,40)
\put(0,36){\framebox(5,4){Begin}} \put(2.5,36){\vector(0,-1){4}}
\put(0,28){\framebox(5,4){$c=0$}} \put(2.5,28){\vector(0,-1){4}}
\put(0,16){\framebox(21,8){\shortstack{Posterior Producer's Risk
\\ Solve the nonlinear equation \\ $\PP[\lambda \leq \lambda_0 \con \mbox{Test is Failed}, \vec{x}] = \alpha$ \\ for $T$}}}
\put(2.5,16){\vector(0,-1){4}}
\put(0,8){\framebox(21,4){\shortstack{Posterior Consumer's Risk
\\ $\PP[\lambda \ge \lambda_1 \con \mbox{Test is Passed}, \vec{x}] \le \beta$?}}}
\put(2.5,8){\vector(0,-1){4}} \put(0,0){\framebox(5,4){End}}
\put(0,6){Yes} \put(24,8){\framebox(8,4){$c = c + 1$}}
\put(22,10){No}\put(21,9.5){\vector(1,0){3}}\put(32,10){\line(1,0){2}}
\put(34,10){\line(0,1){10}}\put(34,20){\vector(-1,0){13}}
\end{picture}
\caption{An algorithm for finding Bayesian Poisson test
plans.}\label{ch10:fig2}
\end{figure}

\begin{sidebar}\label{ch10:ex4}
{\bf Hierarchical Poisson test plan for pumps.} \citet{GO87}
provides the data shown in Table~\ref{ch10:tab3} on the number of
pump failures $x$ observed in $t$ thousands of operating hours for
$m = 10$ different systems at the Farley 1 U.S.\ commercial
nuclear power plant.\index[aut]{Gaver, D.}
\index[aut]{O'Muircheartaigh, I.}

\begin{table}
\caption{Pump failure count data from Farley 1 U.S.\ nuclear power
plant (number of failures $x$ in $t$ thousands of operating hours)
\citep{GO87}}\label{ch10:tab3}
 \centering
\begin{tabular}{cccccll}
\hline
\mbox{} & \mbox{} & \multicolumn{1}{c}{$x_{i}$} & \mbox{} & \multicolumn{1}{c}{$t_{i}$} & \mbox{} & \multicolumn{1}{c}{$\widehat{\lambda}$}\\
$\mbox{System}$ & \mbox{} & \multicolumn{1}{c}{(failures)} & \mbox{} & \multicolumn{1}{c}{(thousand hours)} & \mbox{} & \multicolumn{1}{c}{(MLE)}\\
\hline%
1  & \mbox{} & \hspace{0.05in}5  & \mbox{} & \hspace{0.05in}94.320  & \mbox{} & 5.3 x $10^{-2}$\\
2  & \mbox{} & \hspace{0.05in}1  & \mbox{} & \hspace{0.05in}15.720  & \mbox{} & 6.4 x $10^{-2}$\\
3  & \mbox{} & \hspace{0.05in}5  & \mbox{} & \hspace{0.05in}62.880  & \mbox{} & 8.0 x $10^{-2}$\\
4  & \mbox{} & 14 & \mbox{} & 125.760 & \mbox{} & 11.1 x $10^{-2}$\\
5  & \mbox{} & \hspace{0.05in}3  & \mbox{} & \hspace{0.11in}5.240   & \mbox{} & 57.3 x $10^{-2}$\\
6  & \mbox{} & 19 & \mbox{} & \hspace{0.05in}31.440  & \mbox{} & 60.4 x $10^{-2}$\\
7  & \mbox{} &\hspace{0.05in}1   & \mbox{} & \hspace{0.11in}1.048   & \mbox{} & 95.4 x $10^{-2}$\\
8  & \mbox{} & \hspace{0.05in}1  & \mbox{} & \hspace{0.11in}1.048   & \mbox{} & 95.4 x $10^{-2}$\\
9  & \mbox{} & \hspace{0.05in}4  & \mbox{} & \hspace{0.11in}2.096   & \mbox{} & 191.0 x $10^{-2}$\\
10 & \mbox{} & 22 & \mbox{} & \hspace{0.05in}10.480  & \mbox{} & 209.9 x $10^{-2}$\\
\hline
\end{tabular}
\end{table}
Note that we have listed the data in increasing order of the
corresponding maximum likelihood estimates (MLEs)
$\widehat{\lambda}$.

We model the failures as conditionally independent given their
individual failure rates $\lambda_{i}$ with $Poisson(\lambda_i
t_i)$ distributions. Given $\eta$ and $\kappa$, we model the
$\lambda_i$ as i.i.d.\ $Gamma(\eta, \kappa)$ and use independent
and diffuse $InverseGamma(0.001,0.001)$ prior distributions for
$\eta$ and $\kappa$. Table~\ref{ch10:tab4} summarizes the marginal
posterior distributions of $\eta$ and $\kappa$ as well as the
predictive distribution of $\lambda$. The hierarchical Poisson
model fits the pump failure count data well (see
Exercise~\ref{ch4}.\ref{ch4:ex6}).

\begin{table}
\caption{Posterior distribution summaries for the
gamma distribution hyperparameters ($\eta, \kappa$) given
$\vec{x}$ and of the predictive distribution for $\lambda$ for pump example}\label{ch10:tab4}
 \centering
\begin{tabular}{crrrrrrrrrrrrrr}
\hline                              &       &    &       &       &
 &                                & & \multicolumn{3}{c}{Quantiles}  & &
 \\\cline{7-15}
  Parameter&\mbox{}&Mean&\mbox{}&Std
 Dev&\mbox{}\mbox{}\mbox{}
 &\multicolumn{1}{r}{0.025}&\mbox{}&\multicolumn{1}{r}{0.05}&\mbox{}&0.50 & \mbox{} & \multicolumn{1}{r}{0.95}& \mbox{} & \multicolumn{1}{r}{0.975}\\
\hline%
    $\eta$  &\mbox{} & 0.7981&\mbox{} & 0.3635&\mbox{} &        0.2995&\mbox{} &    0.3419&\mbox{} &    0.7272&\mbox{} &    1.4840&\mbox{} &    1.6950 \\
    $\kappa$&\mbox{} &  1.284&\mbox{} &     0.855&\mbox{} &         0.229&\mbox{} &     0.306&\mbox{} &      1.087&\mbox{} &    2.971&\mbox{} &     3.460 \\
    $\lambda$&\mbox{} &     0.796&\mbox{} &     1.306&\mbox{} &         0.002&\mbox{} &     0.007&\mbox{} &      0.390&\mbox{} &    2.939&\mbox{} &     4.037 \\
\hline
\end{tabular}
\end{table}

Using the posterior risk criteria in Eqs.~\ref{ch10:eqn17} and
\ref{ch10:eqn18}, suppose that we want to find the Poisson test
plan\index[sub]{test plan!Poisson} with risk parameters
$\lambda_{0} = 0.2$, $\alpha = 0.05$, $\lambda_{1} = 0.7$, and
$\beta = 0.05$. Using the algorithm in Fig.~\ref{ch10:fig2} with
$N = 10,000$ joint posterior draws of $(\eta, \kappa)$ given
$\vec{x}$, we find the required test plan $T_{0} = 5.43$ and $c =
1$. The actual risks for this test plan are $\PP[\lambda\geq 0.7
\con Test\mbox{ }Is\mbox{ }Passed, \vec{x} ] = 0.0171$ and $\PP[
\lambda\leq 0.2 \con Test\mbox{ }Is\mbox{ } Failed, \vec{x} ] =
0.0500$, and the unconditional probability of passing this test is
approximately 0.44. To implement this test plan for new systems,
accumulate 5,430 hours of pump operating time with repair (or
replacement) of the failed pumps. If no more than one failure
occurs, then the test is passed, otherwise, the test is failed.
\end{sidebar}

Although it is inappropriate for Example~\ref{ch10:ex4}, in many
cases we are free to accumulate the required total test time $T$
by choosing any desired combination of $n$ devices and time on
test $t_{0}$ satisfying $T=nt_{0}$. To illustrate this trade-off,
Fig.~\ref{ch10:fig3} shows selected combinations of the number of
test devices $n$ and required test time $t_{0}$ satisfying $nt_{0}
= 5,430$ hours. For example, if $n = 5$, then test each of these
pumps (with repair or replacement) for $t_{0} = 1,000$ hours each.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth,angle=270]{Chapter10/ch10_fig3.eps}
\caption{The required test time
$t_{0}$ in hours versus the number of test devices $n$ for a Poisson test plan.}\label{ch10:fig3}
\end{figure}

\section{Weibull Testing}\label{ch10:sec4}\index[sub]{test
plan!Weibull}\index[sub]{assurance
testing}\index[sub]{test!assurance} The previous sections on
binomial and Poisson testing\index[sub]{test
plan!binomial}\index[sub]{test plan!Poisson} considered attribute
test data, which capture the survival/nonsurvival of each device
on test. This section focuses on lifetime data, where testers
record the actual failure times. We assume that the failure times
$t$ follow a $Weibull(\lambda, \beta)$ distribution with scale
parameter $\lambda$ and shape parameter $\beta$, with probability
density function
\begin{equation}\label{ch10:eqn19}
f(t|\lambda,\beta)=\lambda\beta t^{\beta-1}\exp(-\lambda
t^{\beta}), \, \, \, t > 0, \, \lambda > 0, \, \beta>0.
\end{equation}

Suppose that we would like to use the posterior risk criteria to
develop a Weibull test plan $(n,t_0,c)$, where we put $n$ units on
test for $t_0$ time units and the test passes if no more than $c$
units fail. To define the risk criteria, we specify requirements
on reliability at time $t_*$, $R(t_*)$. Let
\begin{eqnarray*}
m(y) & = & (1 - \exp[-\lambda t_0^{\beta}])^{y}
\exp[-(n-y)\lambda t_0^{\beta}] \, ,\\
k_0 & = & -\log(\pi_0)t_*^{-\beta} \quad \mbox{, and}\\
k_1 & = & -\log(\pi_1)t_*^{-\beta} \, .\\
\end{eqnarray*}
For a Weibull test plan\index[sub]{test plan!Weibull} $(n,t_0,c)$,
we calculate the posterior producer's risk as
\begin{eqnarray}\label{ch10:wppr}
\PP(R(t_*) & \geq & \pi_0 \con Test\mbox{ }Is\mbox{ }Failed)\\
\mbox{} & = & \PP(\exp(-\lambda t_*^\beta) \geq \pi_0 \con
Test\mbox{ }Is\mbox{ }Failed)\nonumber\\ \mbox{} & = & \PP(\lambda
\leq -\log(\pi_0)t_*^{-\beta} \con Test\mbox{ }Is\mbox{ }Failed)\nonumber\\
\mbox{} & = & \int_{0}^{\infty} \int_{0}^{k_0} f(\lambda, \beta
\con
Test\mbox{ }Is\mbox{ }Failed) \, \, \D \lambda \D \beta\nonumber\\
\mbox{} & = & \int_{0}^{\infty} \int_{0}^{k_0}
\frac{\PP(Test\mbox{ }Is\mbox{ }Failed \con \lambda, \beta)
p(\lambda, \beta)}{\int_0^{\infty}\int_0^{\infty} \PP(Test\mbox{
}Is\mbox{ }Failed \con \lambda, \beta)p(\lambda,\beta) \, \, \D
\lambda \D \beta} \, \, \D \lambda \D \beta\nonumber\\ \mbox{} & =
& \frac{\int_{0}^{\infty} \int_{0}^{k_0} \left[1 - \sum_{y=0}^{c}
m(y) \right] p(\lambda,\beta) \, \, \D \lambda \D
\beta}{\int_0^{\infty}\int_0^{\infty} \left[1 - \sum_{y=0}^{c}
m(y) \right] p(\lambda,\beta) \, \, \D \lambda \D \beta}\nonumber
\, \, .
\end{eqnarray}
We calculate the posterior consumer's risk as
\begin{eqnarray}\label{ch10:wpcr}
\PP(R(t_*) & \leq & \pi_1 \con Test\mbox{ }Is\mbox{ }Passed)\\
\mbox{} & = & \PP(\exp(-\lambda t_*^\beta) \leq \pi_1 \con
Test\mbox{ }Is\mbox{ }Passed)\nonumber\\ \mbox{} & = & \PP(\lambda
\geq -\log(\pi_1)t_*^{-\beta} \con Test\mbox{ }Is\mbox{ }Passed)\nonumber\\
\mbox{} & = & \int_{0}^{\infty} \int_{k_1}^{\infty} f(\lambda,
\beta \con
Test\mbox{ }Is\mbox{ }Passed) \, \, \D \lambda \D \beta\nonumber\\
\mbox{} & = & \int_{0}^{\infty} \int_{k_1}^{\infty}
\frac{\PP(Test\mbox{ }Is\mbox{ }Passed \con \lambda, \beta)
p(\lambda,\beta)}{\int_0^{\infty}\int_0^{\infty} \PP(Test\mbox{
}Is\mbox{ }Passed \con \lambda, \beta) p(\lambda,\beta) \, \, \D
\lambda \D \beta} \, \, \D \lambda \D \beta\nonumber\\ \mbox{} & =
& \frac{\int_{0}^{\infty} \int_{k_1}^{\infty} \left[\sum_{y=0}^{c}
m(y)] \right] p(\lambda,\beta) \, \, \D \lambda \D
\beta}{\int_0^{\infty}\int_0^{\infty} \left[\sum_{y=0}^{c} m(y)
\right] p(\lambda,\beta) \, \, \D \lambda \D \beta}\nonumber \, \,
.
\end{eqnarray}

\subsection{Single Weibull Population
Testing}\label{ch10:sec4:ss1}\index[sub]{test
plan!Weibull}\index[sub]{assurance
testing}\index[sub]{test!assurance} One description of a failure
time distribution is its reliable life. The \emph{reliable
life}\index[sub]{reliable life}, $t_{R}$, for specified $R$, is
the time beyond which $100 \times R\%$ of the population will
survive. In other words, $t_{R}$ is the $(1 - R)$th quantile of
the failure time distribution. For the Weibull distribution
described by Eq.~\ref{ch10:eqn19}, $t_{R} =
\lambda^{-1/\beta}[-\log (R)]^{1/\beta}$.

Among a variety of testing schemes, we focus here on a minimum
sample size (or zero-failure) test plan $(n,
t_{0},c=0)$\index[sub]{test plan!minimum sample
size}\index[sub]{test plan!zero-failure}. For a zero-failure test
plan, test $n$ devices each for a length of time $t_{0}$, and the
test is passed if we observe no failures. To use such a test plan,
we must determine appropriate values for both $n$ and $t_{0}$.
\citet{ME98} considers such classical test plans in situations
where the Weibull shape parameter $\beta$ is known. We relax this
restriction here by considering plans within a Bayesian
hierarchical framework. In turn, there are two such cases to
study: (1) an assurance test plan based on available data from a
single Weibull population, and (2) an assurance test plan based on
available data from a Weibull accelerated life test
program.\index[aut]{Meeker, W.} \index[aut]{Escobar, L.}

Consider developing a test criterion to assure that $t_{R} >
t_{R^*}$. For example, a manufacturer may want to assure that
$99\%$ of a certain expensive electronic product will survive a
one-year warranty period; in this case, $R = 0.99$ and $t_{R^*} =
8,760$ hours. We use the posterior risk criterion $P[t_{R} >
t_{R^*} \con Test\mbox{ }Is\mbox{ }Passed] \geq 1 - \alpha$. If
the test is passed, we would like a high probability ($1 -
\alpha$) that $t_{R} > t_{R^*}$ --- a high probability that the
0.99 quantile of the lifetime of the electronic products is
greater than 8,760 hours. This leads to the expression
\begin{eqnarray}\label{ch10:wtc}
\PP(t_{R} & > & t_{R^*} \con Test\mbox{ } Is\mbox{ }Passed)\\
\mbox{} & = & \PP(
\lambda^{-1/\beta}[-\log(R)]^{1/\beta} > t_{R^*} \con Test\mbox{ } Is\mbox{ }Passed)\nonumber\\
\mbox{} & = & \PP(\lambda < -\log(R)t_{R^*}^{-\beta} \con
Test\mbox{ } Is\mbox{ }Passed)\nonumber\\
\mbox{} & = & \int_0^{\infty} \int_{0}^{-\log(R)t_{R^*}^{-\beta}}
f(\lambda,\beta \con Test\mbox{ } Is\mbox{
}Passed) \,\, \D \lambda \D \beta\nonumber\\
\mbox{} & = & \int_0^{\infty} \int_{0}^{-\log(R)t_{R^*}^{-\beta}}
\frac{\PP(Test\mbox{ }Is\mbox{ }Passed \con \lambda,
\beta)p(\lambda, \beta)}{\int_{0}^{\infty} \int_{0}^{\infty}
\PP(Test\mbox{
}Is\mbox{ }Passed \con \lambda, \beta)p(\lambda, \beta) \D\lambda \D \beta} \,\, \D \lambda \D \beta\nonumber\\
& = & \frac{\int_0^\infty \int^{-\log(R)t_{R^*}^{-\beta}}_0
\exp(-n\lambda t_0^{\beta}) p(\lambda, \beta) \D \lambda \D
\beta}{\int_0^\infty \int_0^\infty \exp(-n\lambda t_0^{\beta})
p(\lambda, \beta) \D \lambda \D \beta} \geq 1 - \alpha \, .
\nonumber
\end{eqnarray}
Notice the similarities of this risk formulation to the posterior
consumer's risk. As with the Poisson test plan, for a fixed $n$,
we can solve for $t_0$ to meet the desired risk criteria.
With the chosen $c = 0$, this also specifies the level of posterior
producer's risk.

Suppose now that we have failure time data from $m > 1$
situations. Note that some of the available failure time data may
be censored. Let $t_{ij}, i = 1, \ldots, m,  j = 1, \ldots,
n_{i}$, denote the observed failure or censoring time for the
$j$th device in the $i$th situation, and let $\vec{t}$ denote all
the observed failure time data. Given $\lambda_{i}$ and $\beta$,
model the $T_{ij}$ as conditionally independent with $T_{ij} \sim
Weibull(\lambda_{i}, \beta)$. We assume a common shape parameter,
because in practice, the failure times of similar devices often
(but not always) exhibit the same general Weibull shape because
they share common intrinsic failure mechanisms. To complete the
model, let us use the following prior distributions:
\begin{eqnarray*}
\lambda_{i} & \sim & Gamma(\eta, \kappa), \quad i = 1, \ldots, m, \\
(\eta, \kappa) & \sim & p(\eta, \kappa), \mbox{ and}\\
\beta & \sim & p(\beta),
\end{eqnarray*}
with known hyperparameters for $p(\eta, \kappa)$ and $p(\beta)$.

We want to develop a zero-failure test plan for a new situation
where we assume the failure time data will be distributed
$Weibull(\lambda,\beta)$, with $\lambda \sim \Gamma(\eta,
\kappa)$. Conditioning on the observed data $\vec{t}$ in
Eq.~\ref{ch10:wtc},
\begin{eqnarray}\label{ch10:wtc2}
\PP(t_{R} & > & t_{R^*} \con Test\mbox{ } Is\mbox{ }Passed,
\vec{t})\\\nonumber & = & \frac{\int_0^\infty
\int^{-\log(R)t_{R^*}^{-\beta}}_0 \exp(-n\lambda t_0^{\beta})
p(\lambda, \beta \con \vec{t}) \D \lambda \D \beta}{\int_0^\infty
\int_0^\infty \exp(-n\lambda t_0^{\beta}) p(\lambda, \beta \con
\vec{t}) \D \lambda \D \beta} \, .
\end{eqnarray}

Assuming that we have $j = 1, \ldots, N$ MCMC draws from the
posterior distributions (given $\vec{t}$) of $\eta$, $\kappa$, and
$\beta$ and $N$ draws from the predictive distribution of
$\lambda$, $\lambda^{(j)} \sim \Gamma(\eta^{(j)},\kappa^{(j)})$,
we can calculate our criterion as follows:
\begin{eqnarray}\label{ch10:wtc3}
\PP(t_{R} & > & t_{R^*} \con Test\mbox{ } Is\mbox{ }Passed,
\vec{t})\\\nonumber & = & \frac{\int_0^\infty
\int^{-\log(R)t_{R^*}^{-\beta}}_0 \exp(-n\lambda t_0^{\beta})
p(\lambda, \beta \con \vec{t}) \D \lambda \D \beta}{\int_0^\infty
\int_0^\infty \exp(-n\lambda t_0^{\beta}) p(\lambda, \beta \con
\vec{t}) \D \lambda \D \beta}\\\nonumber \mbox{} & \approx &
\frac{\sum_{j=1}^{N} \exp(-n\lambda^{(j)}
t_0^{\beta^{(j)}})I[\lambda^{(j)} \leq
-\log(R)t_{R^*}^{-\beta^{(j)}}]} {\sum_{j=1}^{N}
\exp(-n\lambda^{(j)} t_0^{\beta^{(j)}})}\\\nonumber \mbox{} &
\approx & \frac{\sum^{N}_{j=1} \frac{{(\kappa^{(j)})}^{\eta^{(j)}}
\gamma[\eta^{(j)},[-\log (R)]
(\kappa^{(j)}+nt^{\beta^{(j)}}_{0})/t^{\beta^{(j)}}_{R*}]}{(\kappa^{(j)}+nt^{\beta^{(j)}}_{0})^{\eta^{(j)}}\Gamma(\eta^{(j)})
} }{\sum^{N}_{j=1} \frac{{(\kappa^{(j)})}^{\eta^{(j)}}}
{(\kappa^{(j)}+nt^{\beta^{(j)}}_{0})^{\eta^{(j)}}}}\nonumber \, ,
\end{eqnarray}
where $\gamma(q, z)$ denotes the lower incomplete gamma function.

Note that we may base the choice of number of test devices $n$ on
other considerations, such as cost. It may also be interesting and
useful to see how $t_{0}$ functionally depends on $n$, which we
can examine by varying $n$ over an appropriate range, solving for
$t_{0}$, and plotting the results.

\begin{sidebar}\label{ch10:ex5} {\bf Hierarchical Weibull test plan for pressure
vessels.}\index[sub]{test plan!Weibull} \citet{GK83}  provides the
failure times (in hours) for pressure vessels that were wrapped in
Kevlar-49 fibers and subsequently tested at four different
stresses: 23.4, 25.5, 27.6, and 29.7 megapascals (MPa).
\citet{CKSS91} analyzes these data assuming a constant Weibull
shape parameter. The fibers came from eight different spools
(numbered 1--8) of material, and both studies conclude that there
is a significant spool effect. In this example, consider only the
failure time data obtained at 23.4 MPa. See Table~\ref{ch10:tab5},
which displays the failure time data at all the stresses; an
asterisk indicates a time- or Type I-censored observation.
\index[aut]{Gerstle, F.} \index[aut]{Kunz, S.}\index[aut]{Crowder,
M.} \index[aut]{Kimber, A.} \index[aut]{Smith, R.}
\index[aut]{Sweeting, T.}

\begin{table}
\caption{Failure times of Kevlar-49-wrapped pressure vessels at
four stress levels (An asterisk indicates a time-censored or Type
I-censored observation) \citep{GK83}}\label{ch10:tab5}
% \centering
\begin{tabular}{ccl}\\
\hline Stress (MPa) &  Spool&  \hspace{0.2in} Failure Time (hours)\\
\hline%
29.7& 1  & 444.4\hspace{0.02in} 755.2\hspace{0.02in} 952.2\hspace{0.02in} 1108.2\\
29.7& 2  &  2.2\hspace{0.02in} 8.5\hspace{0.02in} 9.1\hspace{0.02in} 10.2\hspace{0.02in} 22.1\hspace{0.02in} 55.4\hspace{0.02in} 111.4\hspace{0.02in} 158.7\\
29.7& 3  &  12.5\hspace{0.02in} 14.6\hspace{0.02in} 18.7\hspace{0.02in} 101.0\\
29.7& 4  &  254.1\hspace{0.02in} 1148.5\hspace{0.02in} 1569.3\hspace{0.02in} 1750.6\hspace{0.02in} 1802.1\\
29.7& 5  &  8.3\hspace{0.02in} 13.3\hspace{0.02in} 87.5\hspace{0.02in} 243.9\\
29.7& 6  &  6.7\hspace{0.02in} 15.0\hspace{0.02in} 144.0\\
29.7& 7  &  4.0\hspace{0.02in} 4.0\hspace{0.02in} 4.6\hspace{0.02in} 6.1\hspace{0.02in} 7.9\hspace{0.02in} 14.0\hspace{0.02in} 45.9\hspace{0.02in} 61.2\\
29.7& 8  &  98.2\hspace{0.02in} 590.4\hspace{0.02in} 638.2\\

 27.6& 1  &  453.4\hspace{0.02in} 664.5\hspace{0.02in} 930.4\hspace{0.02in} 1755.5\\
 27.6& 2  &  71.2\hspace{0.02in} 199.1\hspace{0.02in} 403.7\hspace{0.02in} 432.2\hspace{0.02in} 514.1\hspace{0.02in} 544.9\hspace{0.02in} 694.1\\
 27.6& 3  &  19.1\hspace{0.02in} 24.3\hspace{0.02in} 69.8\hspace{0.02in} 136.0\\
 27.6& 4  &  876.7\hspace{0.02in} 1275.6\hspace{0.02in} 1536.8\hspace{0.02in} 6177.5\\
 27.6& 5  &  \\
 27.6& 6  &  514.2\hspace{0.02in} 541.6\hspace{0.02in} 1254.9\\
 27.6& 7  &  \\
 27.6& 8  &  554.2\hspace{0.02in} 2046.2\\

 25.5& 1  &  11487.3\hspace{0.02in} 14032.0\hspace{0.02in} 31008.0\\
 25.5& 2  &  1134.2\hspace{0.02in} 1824.3\hspace{0.02in} 1920.1\hspace{0.02in} 2383.0\hspace{0.02in} 3708.9\hspace{0.02in} 5556.0\\
 25.5& 3  &  1087.7\hspace{0.02in} 2442.5\\
 25.5& 4  &  13501.3\hspace{0.02in} 29808.0\\
 25.5& 5  &  11727.1\\
 25.5& 6  &  225.2\hspace{0.02in} 6271.1\hspace{0.02in} 7996.0\\
 25.5& 7  &  503.6\\
 25.5& 8  &  2974.6\hspace{0.02in} 4908.9\hspace{0.02in} 7332.0\hspace{0.02in} 7918.7\hspace{0.02in} 9240.3\hspace{0.02in} 9973.0\\

 23.4& 1  &  41000*\hspace{0.02in} 41000*\hspace{0.02in} 41000*\hspace{0.02in} 41000*\\
 23.4& 2  &  14400.0\\
 23.4& 3  &  8616.0\\
 23.4& 4  &  41000*\hspace{0.02in} 41000*\hspace{0.02in} 41000*\hspace{0.02in} 41000*\\
 23.4& 5  &  9120.0\hspace{0.02in} 20231.0\hspace{0.02in} 35880.0\\
 23.4& 6  &  7320.0\hspace{0.02in} 16104.0\hspace{0.02in} 20233.0\\
 23.4& 7  &  4000.0\hspace{0.02in} 5376.0\\
 23.4& 8  &  41000*\hspace{0.02in} 41000*\hspace{0.02in} 41000* \\

\hline
\end{tabular}
\end{table}

Because any difference in the reliability of the spools is
primarily due to uncontrollable random manufacturing process
variability (or noise), let us model the pressure vessel failure times
corresponding to each spool as conditionally independent with
$Weibull(\lambda_i,\beta)$ distributions. Given $\eta$ and
$\kappa$, the $\lambda_i$ are i.i.d.\ $Gamma(\eta, \kappa)$. In
our analysis of these data, we use independent and diffuse
$InverseGamma(0.01, 0.01)$ prior distributions for $\eta$ and
$\kappa$. Also, we use an independent $Exponential(1.0)$ prior
distribution for $\beta$; the motivation for this prior
distribution is the analysis results of \citet{CKSS91}, which
suggests values of $\beta$ near 1.0.  See Table~\ref{ch10:tab6},
which summarizes the marginal posterior distributions for $\eta$,
$\kappa$, and $\beta$ given $\vec{t}$. The hierarchical Weibull
model fits these data well (see Exercise~\ref{ch4}.\ref{ch4:ex7}).
Table~\ref{ch10:tab6} also summarizes the predictive distribution
of $\lambda$. \index[aut]{Crowder, M.} \index[aut]{Kimber, A.}
\index[aut]{Smith, R.} \index[aut]{Sweeting, T.}

\begin{table}
\caption{Posterior distribution summaries for $\eta$, $\kappa,$
and $\beta$ given $\vec{t}$ and of the predictive distribution for
$\lambda$}\label{ch10:tab6} \centering
\begin{tabular}{crrrrrrrrrrrr}
\hline      &       &    &      &       &
                                          \multicolumn{5}{c}{Quantiles}  &
 \\
 \cline{7-13}
  Parameter&\mbox{}&Mean  &\mbox{}&Std Dev &\mbox{}\mbox{}\mbox{}
 &\multicolumn{1}{r}{0.025}&\mbox{}&\mbox{}&0.50 & \mbox{} &  \mbox{}       & \multicolumn{1}{r}{0.975}\\
\hline
 $\beta$   &\mbox{}& 2.255&\mbox{}&   0.643&\mbox{}&      1.128&\mbox{}&  \mbox{}&  2.211&\mbox{}&   \mbox{}& 3.773\\
    $\eta$  &\mbox{}&0.2100&\mbox{}&    0.1730&\mbox{}&     0.0529&\mbox{}& \mbox{}& 0.1666&\mbox{}&  \mbox{}&    0.6113\\
    $\kappa$    &\mbox{}&2.313E+13&\mbox{}& 3.105E+14&\mbox{}&      7.346E+3&\mbox{}&   \mbox{} &1.121E+8   &\mbox{} &\mbox{} &6.463E+13\\
    $\lambda$   &\mbox{}&5.630E$-$6&\mbox{}&  1.221E$-$4&\mbox{}&       7.304E$-$25&\mbox{}&  \mbox{}&   3.832E$-$11&\mbox{}& \mbox{}&   1.273E$-$5\\
\hline
\end{tabular}
\end{table}

Now suppose that we want to find a Bayesian minimum sample size
test plan\index[sub]{test plan!minimum sample
size}\index[sub]{test plan!zero-failure} at a stress of 23.4 MPa
for $t_{R^*} = 2,000$ hours, $R = 0.9$, and $\alpha = 0.05$. By
letting $n = 1, 2, \ldots, 30$ and solving Eq.~\ref{ch10:wtc3} for
the corresponding test length $t_{0}$, we obtain the graph shown
in Fig.~\ref{ch10:fig4}.

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth,angle=270]{Chapter10/ex5Figt0VsnV2.ps}}
\caption{The required Weibull test duration $t_{0}$ versus the
number of test devices $n$ for the pressure vessels example.}\label{ch10:fig4}
\end{figure}

For example, suppose that we decide to test $n = 10$ pressure
vessels all wrapped from a particular spool of Kevlar-49 fibers.
Figure~\ref{ch10:fig4} indicates required testing of each of these
pressure vessels for approximately $t_{0} = 1,122$ hours at a
stress of 23.4 MPa. If none of these fail, we can then claim, with
0.95 probability, that at least 90\% of the pressure vessels
wrapped from this spool will survive 2,000 hours at this stress.
\end{sidebar}

\subsection{Combined Weibull Accelerated/Assurance
Testing}\label{ch10:sec4:ss2}\index[sub]{assurance
testing}\index[sub]{test plan!Weibull} Now consider a Bayesian
test plan based on data from a Weibull accelerated test
program\index[sub]{test plan!Weibull!accelerated test}.
Specifically, we consider again the failure time data in
Table~\ref{ch10:tab5}. Let $t_{ij}, i = 1, \ldots, m, j = 1,
\ldots, n_{i}$, denote either the observed failure or censoring
time for the $j$th device from the $i$th situation, with $\vec{t}$
denoting all of the observed failure time data. Let $s_{ij}$ be
the value of the stress $s$ under which we obtained $t_{ij}$.

Conditional on $\lambda_{ij}$ and $\beta$, we model the $T_{ij}$
conditionally independent with a $Weibull(\lambda_{ij}, \beta)$
distribution. Let us define a model for $\lambda_{ij}$ as
\begin{equation}\label{ch10:eqn23}
\lambda_{ij} = \exp(\gamma_{0})s_{ij}^{\gamma_{1}}\omega_{i} \, ,
\end{equation}
where $\omega_{i} > 0$ is the random effect associated with the
$i$th spool, and $\gamma_{0}$ and $\gamma_{1}$ are two regression
parameters used to model the relationship between $\lambda_{ij}$
and $s_{ij}$. Recall that we presented similar regression models
in Chap.~\ref{ch7} (see also \citet{LRAT07}).\index[aut]{Leon,
R.@Le\'{o}n, R.}\index[aut]{Ramachandran, R.}\index[aut]{Ashby,
A.}\index[aut]{Thyagarajan, J.}

We specify prior distributions $\omega_{i} \con \eta, \kappa \sim
Gamma(\eta, \kappa)$, $(\eta, \kappa) \sim p(\eta, \kappa)$,
$\beta \sim p(\beta)$, $\gamma_{0} \sim p(\gamma_{0})$,
$\gamma_{1} \sim p(\gamma_{1})$ with known hyperparameters for
$p(\eta, \kappa)$, $p(\beta)$, $p(\gamma_{0})$, and
$p(\gamma_{1})$.

To develop the Bayesian zero-failure test\index[sub]{test
plan!zero-failure}\index[sub]{test plan!minimum sample size} for a
new spool, we assume the plan consists of testing $n$ samples for
time $t_{0}$ at stress $s_{0}$. We use MCMC to obtain posterior
draws $\eta^{(j)}$, $\kappa^{(j)}$, $\beta^{(j)}$,
$\gamma_{0}^{(j)}$, $\gamma_{1}^{(j)}$ given $\vec{t}$ and
predictive draws $\omega^{(j)} \sim
\Gamma(\eta^{(j)},\kappa^{(j)})$. Let
\begin{eqnarray*}
\bt & = & (\omega, \gamma_0, \gamma_1, \beta) \quad \mbox{and}\\
q^{(j)} & = & \kappa^{(j)}+n
\exp(\gamma_{0}^{(j)})s^{\gamma_{1}^{(j)}}_{0}t^{\beta^{(j)}}_{0}
\, .
\end{eqnarray*}
Our test criterion is calculated as
\begin{eqnarray}\label{ch10:wtc4}
\PP(t_{R} & > & t_{R^*} \con Test\mbox{ } Is\mbox{ }Passed,
\vec{t})\\\nonumber & = & \frac{\int_0^\infty \int_0^\infty
\int_0^\infty
\int_0^{\frac{-\log(R)t_{R^*}^{-\beta}}{\exp(\gamma_0)s_0^{\gamma_1}}}
\exp(-n\exp(\gamma_0)s_0^{\gamma_1}\omega t_0^{\beta}) p(\bt \con
\vec{t}) \D \bt}{\int_0^\infty \int_0^\infty \int_0^\infty
\int_0^\infty \exp(-n\exp(\gamma_0)s_0^{\gamma_1}\omega
t_0^{\beta}) p(\bt \con \vec{t}) \D \bt}\\\nonumber \mbox{} &
\approx & \frac{\sum_{j=1}^{N}
\exp(-n\exp(\gamma_0^{(j)})s_0^{\gamma_1^{(j)}}\omega^{(j)}
t_0^{\beta^{(j)}}) I\left[\omega^{(j)} \leq
\frac{-\log(R)t_{R^*}^{-\beta^{(j)}}}{\exp(\gamma_0^{(j)})s_0^{\gamma_1^{(j)}}}\right]}
{\sum_{j=1}^{N}
\exp(-n\exp(\gamma_0^{(j)})s_0^{\gamma_1^{(j)}}\omega^{(j)}
t_0^{\beta^{(j)}})}\\\nonumber & \approx & \frac{ \sum^{N}_{j=1}
\frac{ {(\kappa^{(j)})}^{\eta^{(j)}} \gamma \left[ \eta^{(j)},
[-\log (R)] \exp(-\gamma_{0}^{(j)})
 s_{0}^{-\gamma_{1}^{(j)}}
 q^{(j)}
/t^{\beta^{(j)}}_{R^{*}} \right]}{\Gamma(\eta^{(j)}){(q^{(j)})
}^{\eta^{(j)}}}} { \sum^{N}_{j=1} \frac
{{(\kappa^{(j)})}^{\eta^{(j)}}}{{{(q^{(j)}) }^{\eta^{(j)}}}}
}\nonumber \, ,
\end{eqnarray}
where $\gamma(q, z)$ denotes the lower incomplete gamma function.

More specifically, to analyze the data in Table~\ref{ch10:tab5},
we use the following independent prior distributions:
\begin{eqnarray*}
\beta & \sim & Exponential(1.0),\\
\eta & \sim &
InverseGamma(0.01, 0.01),\\
\kappa & \sim & InverseGamma(0.01, 0.01),\\
\gamma_{0} & \sim & Normal(0, 10^{6}), \mbox{ and}\\
\gamma_{1} & \sim & Normal(0,10^{6}).
\end{eqnarray*}

See Table~\ref{ch10:tab7}, which summarizes the marginal posterior
distributions for these five parameters. The hierarchical Weibull
regression model fits these data well (see
Exercise~\ref{ch7}.\ref{exercise:goodnessOfFitCh10Example5}).

\begin{table}
\caption{Posterior distribution summaries for $\eta, \kappa,
\beta, \gamma_{0}$, and $\gamma_{1}$ given $\vec{t}$ and
predictive distribution for $\omega$ for pressure vessels
example}\label{ch10:tab7}

 \centering
\begin{tabular}{crrrrrrrrrrrr}
\hline     &             &       &       & &
 & & \multicolumn{3}{c}{Quantiles}  & &
 \\\cline{7-13}
  Parameter&\mbox{}&Mean&\mbox{}&Std
 Dev&\mbox{}\mbox{}\mbox{}
 &\multicolumn{1}{r}{0.025}&\mbox{}&\mbox{}&0.50 & \mbox{} &  \mbox{} & \multicolumn{1}{r}{0.975}\\
\hline%
    $\beta$&\mbox{} &   1.199 &\hspace{0.01in} &    0.085 &\hspace{0.01in} &        1.038 &\hspace{0.01in}  &\hspace{0.01in} &    1.199 &\hspace{0.01in} &    \hspace{0.01in} &   1.3650\\
    $\eta$&\mbox{} &    0.6522 &\hspace{0.01in} &   0.3068 &\hspace{0.01in} &       0.2198 &\hspace{0.01in} &\hspace{0.01in} &   0.5977 &\hspace{0.01in} &   \hspace{0.01in} &    1.391   \\
    $\gamma_0$&\mbox{} &    $-$84.81 &\hspace{0.01in} & 11.31 &\hspace{0.01in} &        $-$105.50 &\hspace{0.01in}  &\hspace{0.01in} &   $-$83.40 &\hspace{0.01in}  &\hspace{0.01in} & $-$66.32 \\
    $\gamma_1$&\mbox{} &    27.84 &\hspace{0.01in} &    1.81 &\hspace{0.01in} &     24.56 &\hspace{0.01in} &\hspace{0.01in} &    27.85 &\hspace{0.01in} &   \hspace{0.01in} &    31.31\\
    $\kappa$&\mbox{} &  3.704E+15 &\hspace{0.01in} &    5.666E+16 &\hspace{0.01in} &        2.403E$-$2 &\hspace{0.01in}  &\hspace{0.01in} &  4.873E+6 &\hspace{0.01in} &\hspace{0.01in} &    7.071E+15\\
$\omega$&\mbox{} & 2.512 &\hspace{0.01in} & 19.42 &\hspace{0.01in}
& 1.34E-17 &\hspace{0.01in}  &\hspace{0.01in} &
3.900E-08 &\hspace{0.01in} & \hspace{0.01in} & 19.73\\
 \hline
\end{tabular}
\end{table}

\iffalse Using $K=5$ bins, the value of the Bayesian $\chi^{2}$
goodness-of-fit test statistic discussed in Sect.~3.4 is computed
to be 4.1.  Comparing this to a $ChiSquared$(4) distribution, we
find that the p-value for testing whether the specified Weibull
regression model with random spool effects ``fits'' the data is
0.30.  Therefore, there is sufficient evidence to suggest that
this model provides an adequate fit to the data. \fi

We can see the effect that stress has on failure time by computing
the posterior distribution of the Weibull mean time to failure
(MTTF) as a function of $s$ for a randomly selected spool of
Kevlar 49. Recall that the MTTF of the Weibull distribution in
Eq.~\ref{ch10:eqn23} is $\lambda^{-1/\beta}\Gamma(1+1/\beta)$,
which, substituting using Eq.~\ref{ch10:eqn23}, becomes
$\exp(-\gamma_{0}/\beta)s^{-\gamma_{1}/\beta}\omega^{-1/\beta}\Gamma(1+1/\beta)$.

In Fig.~\ref{ch10:fig5}, we plot the median log MTTF and a 90\%
central credible interval as a function of stress $s$. Note the
decreasing trend in the Weibull log MTTF as $s$ increases, as well
as the extremely heavy right tail of the posterior log MTTF
distribution for a given value of $s$.

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth,angle=270]{Chapter10/tenfiveV2.ps}}
\caption{The posterior median and 90\% credible interval of the Weibull log MTTF as a function of stress
$s$ for pressure vessels example.}\label{ch10:fig5}
\end{figure}

We can also see the effect of stress on pressure vessel
reliability by computing the posterior distribution of reliability
as a function of $s$ for a randomly selected Kevlar-49 spool.
Substituting using Eq.~\ref{ch10:eqn23}, the reliability at $t =
2,000$ hours is $\exp[-\exp (\gamma_{0})s^{\gamma_{1}}\omega
(2,000)^{\beta}]$. In Fig.~\ref{ch10:fig6}, we plot the posterior
median and 90\% credible interval for pressure vessel reliability
at $2,000$ hours as a function of stress $s$. Note the significant
increase in the width of the 90\% credible intervals as the stress
$s$ increases.

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth,angle=270]{Chapter10/tensixV2.ps}}
\caption{The posterior median and 90\% credible interval for $R(2000)$ as a function of stress
$s$ for pressure vessels example.}\label{ch10:fig6}
\end{figure}

Now suppose that we want to find a Bayesian zero-failure test plan
for $t_{R^*} = 2,000$ hours, $R = 0.9$, $\alpha = 0.05$, and
$s_{0} = 23$ MPa. By letting $n = 1, 2, \ldots ,15$ and solving
Eq.~\ref{ch10:wtc4} for the corresponding test length $t_{0}$, we
obtain the solid curve in Fig.~\ref{ch10:fig7}. For example, in
testing $n = 10$ pressure vessels all wrapped from a spool of
Kevlar-49 fiber, Fig.~\ref{ch10:fig7} indicates testing each of
these vessels for approximately $t_{0} = 1,900$ hours. Note that
in Example~\ref{ch10:ex5}, a shorter time of $t_{0} = 1,132$ was
required because the reliability at 2,000 hours was assessed to be
higher based on the only 23 MPa data. If there are no failures,
then we can claim with 0.95 probability that at least 90\% of the
pressure vessels wrapped from this spool will survive 2,000 hours
at a stress of 23 MPa. Figure~\ref{ch10:fig7} also presents the
test length $t_{0}$ as a function of $n$ for stresses $s_{0} = 24$
MPa and $s_{0} = 27$ MPa.

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth,angle=270]{Chapter10/tensevenV3.ps}}
\caption{The required test duration $t_{0}$ versus the number of
test devices $n$ for three different values of stress $s_{0}$ in
MPa for pressure vessels example. The three stress values are 23
MPa (solid line), 24 MPa (short dashed line), and 27 MPa (long
dashed line).}\label{ch10:fig7}
\end{figure}

From Fig.~\ref{ch10:fig7}, we can make an important observation;
namely, for a given number of devices $n$, as the stress $s_0$
decreases, the required test time $t_{0}$ also decreases. This
desirable situation arises because the failure time data model
using the original accelerated life test data predicts that the
probability of surviving the required 2,000 hours of operation
increases dramatically as the stress decreases. In other words,
because the fitted model predicts long failure times at low
stress, achieving the required assurance needs very little
additional data. For those cases, in which there is high
reliability at low stress, the required assurance is already
embedded in the fitted model. On the other hand, if the
accelerated life test results indicate low reliability at low
stress, then significant assurance testing would be required to
overcome this situation.

\section{Related Reading}\label{ch10:sec5}
There is extensive literature on Bayesian assurance testing dating
back to the late 1960s, and \citet{MW82} describes this early
research. \citet{B86}  clarifies the distinction between a
posterior Bayes' and a modified classical (or average) producer's
risk and compares these two criteria for various test plans.
\index[aut]{Waller, R.}\index[aut]{Brush, G.} \citet{B86} also
highlights the importance of calculating a Bayes' producer's risk
as a supplement to the modified classical producer's
risk.\index[aut]{Brush, G.}\index[aut]{Martz, H.} \citet{SB92}
analyzes the performance of Bayes' and classical assurance test
plans for simultaneously specified consumer's and producer's
risks. Both \citet{B86} and \citet{SB92} conclude that Bayes' and
classical risks need consideration. \index[aut]{Sharma, K.}
\index[aut]{Bhutani, R.}

Since 1990 there have been several more articles concerned with
either Bayesian acceptance sampling or assurance test plans.
\citet{H90},  with comments by \citet{GHMF90}, uses Bayesian
methods to determine a test plan for qualifying the reliability of
some industrial products, whereas \citet{GU90} considers a
Bayesian approach to the assurance testing of highly reliable
devices. \citet{F91} proposes a Bayesian acceptance test plan for
binomial testing, while \citet{SF92} presents a method for
choosing a prior distribution for binomial testing.  In a Master's
thesis, \citet{J91}  develops Bayesian acceptance test plans based
on failure-free life tests and compares these with other test
plans. \citet{PT92}  considers a four-parameter beta prior in
binomial testing. In a somewhat different approach, \citet{MT92}
  uses both quadratic and step-function
loss functions in determining Bayesian acceptance test plans.
\citet{BS93} develops Bayesian sequential reliability
demonstration tests using two different approaches: posterior loss
and predictive loss.  In addition, \citet{BS93}  considers three
test data models. \citet{WYK94}  proposes two different approaches
for integrating life test data into a Bayesian analysis based on
the exponential distribution. For the exponential distribution,
\citet{DK94}  develops Bayesian stopping rules for use in
terminating a sequential assurance test. \citet{V99} considers the
optimization of reliability requirements from a manufacturer's
point of view. \citet{TP03}  proposes Bayesian reliability testing
for a new generation of semiconductor processing equipment, while
\citet{KSB04}  develops reliability demonstration test plans based
on minimizing life cycle costs.\index[aut]{Hart,
L.}\index[aut]{Ganter, W.} \index[aut]{Hart, L.}
\index[aut]{Martz, H.}  \index[aut]{Fisher, R.}\index[aut]{Guess,
F.} \index[aut]{Usher, J.} \index[aut]{Fan, D.} \index[aut]{Sheng,
Z.} \index[aut]{Fan, D.}\index[aut]{Jin, H.}\index[aut]{Pham, T.}
\index[aut]{Turkkan, N.}\index[aut]{Tang,
K.}\index[aut]{Moskowitz, H.}\index[aut]{Berger,
J.}\index[aut]{Berger, J.} \index[aut]{Sun, D.} \index[aut]{Sun,
D.}\index[aut]{Whitmore, G.} \index[aut]{Young, K.}
\index[aut]{Kimber, A.}\index[aut]{Deely, J.} \index[aut]{Keats,
K.}\index[aut]{Vintr, Z.}\index[aut]{Tobias, P.} \index[aut]{Pore,
M.}\index[aut]{Kleyner, A.} \index[aut]{Sandborn, P.}
\index[aut]{Boyle, J.}

\section{Exercises for Chapter~\ref{ch10}}
\begin{enumerate}[\ref{ch10}.1]
\item In determining a Bayesian reliability assurance test plan,
what happens if the prior distribution is especially strong and
satisfies the desired criteria prior to testing?
\begin{enumerate} \item How does one know when this is the case? \item
What calculations should one perform to check whether or not this
is the case?\end{enumerate}

\item \label{ch10:exr1} \begin{enumerate} \item What is the
(classical) producer's risk for a binomial test plan with $n =
15$, $c = 1$, and $\pi_0 = 0.9$? \item What is the (classical)
consumer's risk for a binomial test plan with $n = 15$, $c = 1$,
and $\pi_1 = 0.6$?
\end{enumerate}

\item \label{ch10:exr2} \begin{enumerate} \item What is the
average producer's risk for a binomial test plan with $n = 15$, $c
= 1$, $\pi_0 = 0.9$, and $p(\pi) \sim Beta(10,1)$? \item What is
the average consumer's risk for a binomial test plan with $n =
15$, $c = 1$, $\pi_1 = 0.6$, and $p(\pi) \sim Beta(10,1)$?
\end{enumerate}

\item \label{ch10:exr3} \begin{enumerate} \item What is the
posterior producer's risk for a binomial test plan with $n = 15$,
$c = 1$, $\pi_0 = 0.9$, and $p(\pi) \sim Beta(10,1)$? \item What
is the posterior consumer's risk for a binomial test plan with $n
= 15$, $c = 1$, $\pi_1 = 0.6$, and $p(\pi) \sim Beta(10,1)$?
\end{enumerate}

\item Discuss the similarities and differences between the
producer's and consumer's risks calculated in
Exercises~\ref{ch10}.\ref{ch10:exr1}, \ref{ch10}.\ref{ch10:exr2},
and \ref{ch10}.\ref{ch10:exr3}.

\item Calculate a binomial test plan with a $Uniform(0,1)$ prior
distribution for $\pi$, and $\pi_0 = 0.9$, $\pi_1 = 0.5$, $\alpha
= \beta = 0.05$.

\item \label{exercise:ch10AFW} The auxiliary feedwater (AFW)
system is an important standby safety system in a nuclear power
plant \citep{PGGGK98}. The AFW system probability of starting on demand is an
important indicator of its reliability. The data in
Table~\ref{ch10:tab8} are the number of AFW system failures to
start on demand $x_{i}$ in $n_{i}$ demands at 68 U.S.\ commercial
nuclear power plants. \begin{enumerate} \item Find the Bayesian
hierarchical test plan having the posterior consumer's and
producer's risk values $\pi_{1} = 0.985$, $\beta = 0.05$, $\pi_{0}
= 0.995$, and $\alpha = 0.10$. \item What are the actual posterior
risks when using this test plan? \item What is the unconditional
probability of passing the test when using this test plan? \item
Is there anything unusual about this problem?\end{enumerate}

\begin{table}
\caption{Number of AFW system failures to start on demand $x$
in $n$ demands at 68 U.S.\ commercial nuclear power
plants \citep{PGGGK98}}\label{ch10:tab8}
 \centering
\begin{tabular}{lcr |lcr}
\hline Plant     & $x$                   & $n${\hspace{0.1in}} & {\hspace{0.1in}}Plant            & $x$                   & $n$\\
\hline%
Arkansas       1 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 14\phantom{*}   &{\hspace{0.1in}}North Anna 2     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 18\\
Arkansas       2 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 9\phantom{*}    &{\hspace{0.1in}}Oconee 1         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 18\\
Beaver Valley 1  & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 24\phantom{*}   &{\hspace{0.1in}}Oconee 2         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 18\\
Beaver Valley 2  & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 43\phantom{*}   &{\hspace{0.1in}}Oconee 3         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 12\\
Braidwood 1      & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 13\phantom{*}   &{\hspace{0.1in}}Palisades        & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 13 \\
Braidwood 2      & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 24\phantom{*}   &{\hspace{0.1in}}Palo Verde 1     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 7\\
Byron 1          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 11\phantom{*}   &{\hspace{0.1in}}Palo Verde 2     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 12\\
Byron 2          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 26\phantom{*}   &{\hspace{0.1in}}Palo Verde 3     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 9\\
Callaway         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 57\phantom{*}   &{\hspace{0.1in}}Point Beach 1    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 8\\
Calvert Cliffs 1 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 12\phantom{*}   &{\hspace{0.1in}}Point Beach 2    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 16\\
Calvert Cliffs 2 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 15\phantom{*}   &{\hspace{0.1in}}Prairie Island 1 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 3\\
Catawba 1        & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 41\phantom{*}   &{\hspace{0.1in}}Prairie Island 2 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 7\\
Catawba 2        & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 89\phantom{*}   &{\hspace{0.1in}}Robinson 2       & {\hspace{0.1in}}1\mbox{\hspace{0.1in}} & 28\\
Comanche Pk 1    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 66\phantom{*}   &{\hspace{0.1in}}Salem 1          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 24\\
Comanche Pk 2    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 14\phantom{*}   &{\hspace{0.1in}}Salem 2          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 32\\
Cook 1           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 18\phantom{*}   &{\hspace{0.1in}}San Onofre 2     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 13 \\
Cook 2           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 36\phantom{*}   &{\hspace{0.1in}}San Onofre 3     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 17\\
Crystal River 3  & {\hspace{0.1in}}1\mbox{\hspace{0.1in}} & 16\phantom{*}   &{\hspace{0.1in}}Seabrook         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 17\\
Diablo Canyon 1  & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 46\phantom{*}   &{\hspace{0.1in}}Sequoyah 1       & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 30\\
Diablo Canyon 2  & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 30\phantom{*}   &{\hspace{0.1in}}Sequoyah 2       & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 41\\
Farley 1         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 34\phantom{*}   &{\hspace{0.1in}}South Texas 1    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 69\\
Farley 2         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 54\phantom{*}   &{\hspace{0.1in}}South Texas 2    & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 87\\
Fort Calhoun     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 5\phantom{*}    &{\hspace{0.1in}}St. Lucie 1      & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 35\\
Ginna            & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 28\phantom{*}   &{\hspace{0.1in}}St. Lucie 2      & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 21\\
Harris           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 98\phantom{*}   &{\hspace{0.1in}}Summer           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 24 \\
Indian Point 2   & {\hspace{0.1in}}1\mbox{\hspace{0.1in}} & 24\phantom{*}   &{\hspace{0.1in}}Surry 1          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 26\\
Indian Point 3   & {\hspace{0.1in}}2\mbox{\hspace{0.1in}} & 32\phantom{*}   &{\hspace{0.1in}}Surry 2          & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 32\\
Kewaunee         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 26\phantom{*}   &{\hspace{0.1in}}Three Mile Isl 1 & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 6\\
Maine Yankee     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 23\phantom{*}   &{\hspace{0.1in}}Vogtle 1         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 103\\
McGuire 1        & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 45\phantom{*}   &{\hspace{0.1in}}Vogtle 2         & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 45\\
McGuire 2        & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 44\phantom{*}   &{\hspace{0.1in}}Waterford 3      & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 38\\
Millstone  2     & {\hspace{0.1in}}1\mbox{\hspace{0.1in}} & 11\phantom{*}   &{\hspace{0.1in}}Wolf Creek       & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 51\\
Millstone  3     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 54\phantom{*}   &{\hspace{0.1in}}Zion 1           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 13\\
North Anna 1     & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 20\phantom{*}   &{\hspace{0.1in}}Zion 2           & {\hspace{0.1in}}0\mbox{\hspace{0.1in}} & 8\\
\hline
\end{tabular}
\end{table}

\item Derive Eq.~\ref{ch10:eqn14}.

\item \label{ch10:hw4} \citet{B62} provides data that apparently
originated at the U.S.\ Bureau of Naval Weapons regarding the
number of minor, major, and critical defectives in successive
MIL-STD-105B samples of some material. The data in
Table~\ref{ch10:tab9} consist of the observed frequencies of the
number of minor defectives $x$ in samples of size $n = 150$ from
$m = 205$ lots each of size 2016 items of this material.
\begin{enumerate} \item Using the ``hybrid'' posterior consumer's and average
producer's risk criteria, find the Bayesian hierarchical test plan
having the risk values $\beta = 0.10$ and $\alpha = 0.05$ for
$\pi^* = 0.975$. \item What are the actual risks when using this
test plan? \item What is the unconditional probability of passing
this test?\end{enumerate} \index[aut]{Borg, J.}

\begin{table}
\caption{Minor defectives from MIL-STD-105B sampling of material
\citep{B62}}\label{ch10:tab9}
 \centering
\begin{tabular}{cccc|ccc}
\hline
$x$ & \mbox{} & Frequency & \mbox{} & $x$ & \mbox{} & Frequency\\
\hline%
0 & \mbox{} & 68 & \mbox{} & \hspace{0.05in}9  & \mbox{} & 2\\
1 & \mbox{} & 45 & \mbox{} & 10 & \mbox{} & 1\\
2 & \mbox{} & 24 & \mbox{} & 12 & \mbox{} & 1\\
3 & \mbox{} & 20 & \mbox{} & 13 & \mbox{} & 1\\
4 & \mbox{} & \hspace{0.05in}8  & \mbox{} & 15 & \mbox{} & 4\\
5 & \mbox{} & \hspace{0.05in}7  & \mbox{} & 18 & \mbox{} & 1\\
6 & \mbox{} & \hspace{0.05in}8  & \mbox{} & 20 & \mbox{} & 1\\
7 & \mbox{} & 10 & \mbox{} & 22 & \mbox{} & 1\\
8 & \mbox{}\ \ \ \ \  & \hspace{0.05in}3  & \mbox{} &  & \mbox{} & \\
\hline
\end{tabular}
\end{table}

\item Using the data in Exercise~\ref{ch10}.\ref{ch10:hw4}, find
the Bayesian hierarchical test plan having the posterior
consumer's and producer's risk values $\pi_{1} = 0.96$, $\beta =
0.10$, $\pi_{0} = 0.975$, and $\alpha = 0.05$.
\begin{enumerate} \item What are the actual risks when using this test
plan? \item What is the unconditional probability of passing this
test?\end{enumerate}

\item \label{ch10:exr4} \begin{enumerate} \item What is the
posterior producer's risk for a Poisson test plan with $T = 10$,
$c = 3$, $\lambda_0 = 3.0$, and $p(\lambda) \sim Gamma(5,1)$?
\item What is the posterior consumer's risk for a Poisson test
plan with $T = 10$, $c = 3.0$, $\lambda_1 = 7.0$, and $p(\lambda)
\sim Gamma(5,1)$?
\end{enumerate}

\item \label{ch10:hw6} For Poisson testing
presented in Sect.~\ref{ch10:sec3}, show that
\begin{displaymath}
\PP(Test\mbox{ }Is\mbox{
}Failed|\lambda\leq\lambda_{0},\eta,\kappa) =
1-\frac{\kappa^{\eta}\sum^{c}_{x=0}
\frac{T_{0}^{x}\gamma[x+\eta,(T_{0}+\kappa)\lambda_{0}]}
{x!(T_{0}+\kappa)^{x+\eta}}}{\gamma(\eta,\kappa\lambda_{0})} \, .
\end{displaymath}

\item Using the expression given in
Exercise~\ref{ch10}.\ref{ch10:hw6} and the pump failure data in
Table~\ref{ch10:tab3}, find the Bayesian hierarchical test plan
having the ``hybrid'' posterior consumer's and average producer's
risk values $\lambda_{1} = 0.3$, $\beta = 0.10$, $\lambda_{0}=
0.2$, and $\alpha = 0.05$. \begin{enumerate} \item What are the
actual risks for this test plan? \item What is the unconditional
probability of passing this test?\end{enumerate}

\item Using the pump failure data in Table~\ref{ch10:tab3}, find
the Bayesian hierarchical test plan having the posterior
consumer's and producer's risk values $\lambda_{1} = 0.1$, $\beta
= 0.10$, $\lambda_{0}= 0.05$, and $\alpha = 0.05$.
\begin{enumerate} \item What are the actual risks for this test plan? \item What is
the unconditional probability of passing this test? \item Is this
a good test plan to use?\end{enumerate}

\item \label{ch10:ex9} For the model in Sect.~\ref{ch10:sec4:ss1},
show that we may approximate the unconditional probability of
passing the Bayesian minimum sample size test plan by
\begin{displaymath}
 \PP[Test\mbox{ }Is\mbox{ }Passed \con \vec{t} ] \approx \frac
 {1}{N}\sum^{N}_{j=1}\left(\frac
 {\kappa^{(j)}}{\kappa^{(j)}+nt^{\beta^{(j)}}_{0}}\right)^{\eta^{(j)}}.
\end{displaymath}

\item Using the expression in Exercise~\ref{ch10}.\ref{ch10:ex9},
what is the approximate unconditional probability of passing the
Bayesian test plan ($n = 10, t_{0} = 1,122$) given in
Example~\ref{ch10:ex5}?

\item \citet{GK83}  gives the failure times for Kevlar-49-wrapped
pressure vessels at a stress of 25.5 MPa. Table~\ref{ch10:tab10}
displays these data. For $t_{R^*} = 300$ hours, $R = 0.9$, $\alpha
= 0.05$, and these Weibull distributed data, find the Bayesian
minimum sample size test plan time $t_{0}$ that we must test each
of $n = 5$ items. What is the unconditional probability of passing
this test? Is this a satisfactory test plan? \index[aut]{Gerstle,
F.} \index[aut]{Kunz, S.}

\begin{table}
\caption{Failure times of Kevlar-49-wrapped pressure vessels at a
stress of 25.5 MPa \citep{GK83}}\label{ch10:tab10}
 \centering
\begin{tabular}{cll}
\hline Spool & \mbox{} & \hspace{0.5in}Failure Time (hours) \\
\hline%
1 & \mbox{} & 11487.3, 14032.0, 31008.0\\
2 & \mbox{} & 1134.3, 1824.3, 1920.1, 2383.0,
 3708.9, 5556.0\\
3 & \mbox{} & 1087.7, 2442.5\\
4 & \mbox{} & 13501.3, 29808.0\\
5 & \mbox{} & 11727.1\\
6 & \mbox{} & 225.2, 6271.1, 7996.0\\
7 & \mbox{} & 503.6\\
8 & \mbox{} & 2974.6, 4908.9, 7332.0, 7918.7,
 9240.3, 9973.0\\
\hline
\end{tabular}
\end{table}

\item For the Weibull testing described in
Sect.~\ref{ch10:sec4}, suppose that we want to find a Bayesian
minimum sample size test plan to assure that, at some
specified time $t_{R}$, the Weibull reliability $R$ is at least as
large as a requirement $R^*$ at the $100\times (1 - \alpha)$\%
credible level. How does this test plan compare to the one based on
the reliable life criterion?
\end{enumerate}

\end{document}

### 2017-07-10 paperDraft.tex
added current paper stuff

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}

\begin{document}

\title{Bayesian Hierarchical Models for Common Components across Multiple System Configurations}

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of the Joint Light Tactical
    Vehicle (JLTV), which is a family of vehicles. The proposed model effectively combines information
    across three phases of testing and across common vehicle components. The analysis yields
    estimates of failure rates for specific failure modes and vehicles as well as an overall estimate of the
    failure rate for the family of vehicles. We are also able to obtain estimates of how well vehicle
    modifications between test phases improve failure rates. In addition to using all data to improve on
    current assessments of reliability and reliability growth, we illustrate how to leverage the information
    learned from the three phases to determine appropriate specifications for subsequent testing that will
    demonstrate if the reliability meets a given reliability threshold.
\end{abstract}

\section{Introduction}

\section{Data}

\section{Methodology}

\subsection{Modeling Reliability}
A standard reliability analysis employed by the Department of Defense (DoD) test
community considers each test phase independently and uses the exponential
distribution to model the miles between failure ~\cite{ref1}. The traditional
analysis is overly simplistic, relies on correct modeling assumptions
and ignores valuable information learned about the individual vehicles and their
failure modes.

In considering the following alternative approach we will begin by introducing a
hierarchical model structure that can use data across all test phases and
incorporate known similarities between vehicle failure modes.  Next, we will
explore the distributional assumptions of the model; how we can test these
assumptions and how misspecifications can effect our assessments of system
reliability.  This will then lead us into the next section on how this modeling
can be used for assurance test planning.

\subsubsection{Exponential Model}
In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an
exponential distribution with a failure rate parameter $\lambda_{ij}$.
Introducing notation,
\begin{align}
y_{ijk}\mid\lambda_{ij}\sim Exp(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
are the number of failures of vehicle $i$ failure mode $j$. The number of
failure modes is assumed fixed and known \textit{a priori}.

The prior distribution on the exponential failure rate parameter,
$\lambda_{ij}$, depends on whether failure mode $j$ is considered to be common
across vehicles or related but not identical. For the related failure modes,
we place a gamma prior distribution on the collection of $\lambda_{ij}$; in
other words, we assume each vehicle has a distinct failure rate in failure mode
$j$ but they arise from a common gamma distribution.

If failure mode $j$ is considered common across vehicles, the collection of
failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As
with the related failure modes, a gamma prior distribution is placed on the
single failure rate. The prior distributions are independent across failure
mode, and can potentially have different hyperparameters.

The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
each of the vehicles for failure modes that are related. We are assuming the
vehicles are conditionally independent, therefore the failure rate estimate for
the family of vehicles for such failure modes can be found by
$\sum_{i}\lambda_{ij}$. For failure modes that are common across vehicles the
Phase 1 analysis yields a $\lambda_{j}$, which is the failure rate for the
family of vehicles. Under the exponential modeling assumption the overall
failure rate across all failure modes can be found by $\sum_{j}\lambda_{j}$.

\subsubsection{Fix Effectiveness}
After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
these revisions, the PM2 reliability growth model \cite{EH06} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the downsides of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result that is less dependent on hard-coded assumptions.

One normal assumption used in reliability growth modeling is non-decreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems we will sometimes see decreases in
failure rates after adjustments are made.  Therefore for the Phase 2 data we
write the rate parameters as a function of the rate parameters found in Phase 1.
In particular, we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where
$\rho_{j}$ represents the between phase change in failure mode $j$. Given this
definition of $\lambda_{ij}^{P2}$, we again model the failure miles for a given
vehicle and failure mode using the exponential distribution. We assume the prior
distribution for the $\rho_{j}$ is a gamma distribution.  If $\rho_{j}$ is less
than one, this represents an improvement in reliability.  After Phase 2 we can
look again at failure rates across failure modes and vehicles and obtain an
overall estimate of the rate for the family of vehicles.  The analysis of Test
Phase 3 follows the same pattern as that shown in Phase 2. At the end of
Phase 3, we can look at failure rates across failure modes and vehicles and
obtain an overall estimate of the rate for the family of vehicles.
Future tests will be planned based on the inferences of Phase 3.

\subsubsection{Weibull Model}
The exponential model is by far the most common parametric distribution used in
reliability modeling because of its desirable math mathematical properties and
simple interpretations.   Dispite its common uses the assumption of a constant
failure rate over time is rarely justifiable.  It has been well documented
(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
the issues that can arise when this assumption is violated.  We will now
consider the same hierarchical model structure while using the Weibull
distribution for each miles between failure observation.
\begin{align}
y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\kappa_{i}$.  The exponential is a special
case of the Weibull, when $\kappa = 1$.
\\
Talk about how to index the shape parameter and what it means

\subsubsection{JLTV Model Fitting}
So far we have discussed a number of different models and the assumptions that
accompany them.  Now looking at the JLTV dataset we will run a few diagnostics to
decide what model we will use for inference and future test planning.
\\
Models: \\
Exponential and Weibull with no hierarchy \\
Exponential and Weibull full hierarchy \\
Exponential and Weibull full hierarchy \\
Weibull with multipule shape vs. one shape \\
\\
DIC \\
posterior predictive checks \\
QQ Plots \\
Shape Parameter Plot \\

\subsubsection{JLTV Reliability Results}

Results plots \\
Exponential vs. Weibull interpretation

\subsection{Assurance Test Planning}
Assurance Testing
consumer and producer risk

\subsubsection{Traditional Approach}
no producer risk

\subsubsection{Bayes Risk}

R(t) = reliability at time t (miles in our case)
\\
\\$ t_{*c} $ : time of interest to consumer
\\$ t_{*p} $ : time of interest to producer
\\
\\
\begin{itemize}
\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
\end{itemize}
\
\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
\\
\\
We would like to get reliability into a inequality in terms of something we have
a distribution for so we can evaluate the conditional probability statements.
\\
\\
\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80
miles is greater than 2
\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140
miles is less than 2

\subsubsection{Poisson Process}

Reliability: $R(t) = 1 - F(t)$ \\
Hazard or failure rate function: $\lambda(t) = \frac{f(t)}{R(t)}$ \\
Series system reliability: $R_S(t) = \prod_{i = 1}^N R_i(t)$
\\
\\
\textbf{Result:}
$$
\begin{aligned}
	R_S(t) &= \prod_{i = 1}^N R_i(t) \\
	\frac{dR_S(t)}{dt} &= \frac{d}{dt} \prod_{i = 1}^N R_i(t) \; \; \text{(derivative of both sides)} \\
	\frac{dR_S(t)}{dt} &= \sum_{i=1}^N \left[ \frac{dR_i(t)}{dt} \frac{dR_S(t)}{dR_i(t)} \right] \; \; \text{(product rule)} \\
    \frac{-\frac{dR_S(t)}{dt}}{R_S(t)} &= \sum_{i=1}^N \left[  \frac{-\frac{d}{dt}R_i(t)}{dR_i(t)} \right] \; \; \text{(divide both sides by $-R_S(t)$)} \\
    \lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \; \; \text{(because $\lambda(t) = \frac{f(t)}{R(t)} = \frac{-\frac{dR(t)}{dt}}{R(t)}$ )}
\end{aligned}
$$

\subsubsection{Non-Homogeneous Poisson Process}

\textbf{Definitions:} \\
\noindent
Number of failures before time t: $N(t) \sim \text{Poisson}(m(t))$ \\
Mean function: $m(t) = \int_0^t \lambda(s)ds$ (represents the expected number of failures before time t) \\
Weibull($\gamma, \beta $) failure rate: $\lambda(t) = \gamma\beta t^{\beta - 1}$
\\
\\
\textbf{Result:}\\
If we assume a constant shape parameter $\beta$ then,\\
$$
\begin{aligned}
	\lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \\
    &= \sum_{i = 1}^N \gamma_i\beta t^{\beta - 1} \\
    &= \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i
\end{aligned}
$$
\newpage
Then Solving for the mean function of the system,

$$
\begin{aligned}
	m_S(t) &= \int_0^t \lambda_S(s)ds \\
    &= \int_0^t \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i \\
    &= \sum_{i = 1}^N \gamma_i \int_0^t \beta t^{\beta -1} \\
    &= t^\beta \sum_{i = 1}^N \gamma_i
\end{aligned}
$$

This gives us: $N(t) \sim \text{Poisson}(t^\beta \sum_{i = 1}^N \gamma_i)$

\subsubsection{Exponential Case}

If we model the reliability of all 26 components in the system as $Y_{ij} \sim$
exponential$\;(\gamma_i) $ random variables, this leads to the system
reliability being the minimum or $Y_{system} \sim $ exponential
$ \;(\sum_{n = 1}^{26} \gamma_i) $
\\
\\
- Looking at consumer risk first:
\\
want to find Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
\\
Let $ \sum_{n = 1}^{26} \gamma_i = \lambda_S $
\\
The expected number of failures for the system per mile is
$ \mathbf{E}(Y_{system}) = \lambda_S $
\\
\\
This leads to our consumer risk probability constraint as follows.  Given the
test is passed, the consumer would like the probability of the expected number
of failures in 80 miles being greater than 2 to be smaller than $\alpha$.
\\
\\
Prob( $ \lambda_S \cdot (80) \geq 2 \; \vert $ Test is passed) $ \leq \alpha $
\\
\\
Let $ W $ be the number of failures during the test and $ W \leq c \Rightarrow $
Test is passed and $ W > c \Rightarrow $ Test is failed.
\\
\\
Because failures are exponential $ W \sim Poisson(\lambda_S T) $ where $ T $ is
the number of miles run during the test.
\\
\\
$$
\begin{aligned}
	 P(\lambda_S \geq 2/80 \; \vert \; W \leq c) &= \int_{1/40}^{\infty} P(\lambda_S \; \vert W < c) d\lambda_S \\
     &= \int_{1/40}^{\infty} \frac{f(W < c \; \vert \lambda_S) p(\lambda_S)}{f(W < c)}d\lambda_S\\
     &= \int_{1/40}^{\infty} \frac{f(W < c \; \vert \lambda_S) p(\lambda_S)}{\int_{0}^{\infty} f(W < c \; \vert \lambda_S) p(\lambda_S) d\lambda_S}d\lambda_S \\
     &= \frac{\int_{1/40}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
\end{aligned}
$$
\\
\\
For simplicity we fix c to be zero (The number of failures needed to pass the
test) and take N posterior draws $ \lambda_S^{(j)} $
$$
\begin{aligned}
	 P(\lambda_S \geq 1/40 \; \vert \; W = 0) &= \frac{\int_{1/40}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq \frac{1}{40})} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
\end{aligned}
$$
\\
\\
Using the same technique for producer risk we get the following. The producer
would like, given the test is failed, the probability of the expected number of
failures in 140 miles being less than 2 to be smaller than $\beta$.
\\
\\
$$
\begin{aligned}
	 P(\lambda_S \leq 1/70 \; \vert \; W > 0) &= \frac{\int_{0}^{1/70} [1 - exp(-\lambda_S T)]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [1 - exp(-\lambda_S T)]p(\lambda_S)d\lambda_S} \\
     &\approx  \frac{\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T)] I(\lambda_S^{(j)} \leq \frac{1}{70})} {\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T)]}
\end{aligned}
$$
\\
\\
By constraining these two probabilities to acceptable risk levels we can solve
for the smallest $ T $ that satisfies both.
\\
\\
Consumer Risk : $ P(\lambda_S \geq 2/80 \; \vert  W = 0) \leq \alpha $ \\
Producer Risk : $ P(\lambda_S \leq 2/140 \; \vert  W > 0) \leq \beta $

\subsubsection{Weibull Case}
Now if we model the reliability of all 26 components in the system as
$Y_{ij} \sim$ Weibull$\;(\gamma_i, \beta) $ random variables we are able to use
the the non-homogeneous result from part two to build our assurance test. This
follows the same process as the exponential test plan with all mile variables
adjusted by the $\beta$ exponent and the N posterior draws will use both
$\lambda_S^{(j)}$ and $\beta^{(j)}$.
\\
\\
Consumer risk:
\\
$$
	 P(80^\beta (\lambda_S) \geq 2 \; \vert \; W = 0) \approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T^{\beta^{(j)}})I(80^{\beta^{(j)}} (\lambda_S^{(j)}) \geq 2)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T^{\beta^{(j)}})}
$$
\\
\\
Producer risk:
\\
$$
	 P(140^\beta (\lambda_S) \leq 2 \; \vert \; W > 0) \approx  \frac{\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T^{\beta^{(j)}})] I(140^{\beta^{(j)}} (\lambda_S^{(j)}) \leq 2)} {\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T^{\beta^{(j)}})]}
$$
\\
\\
\textbf{Important note:} For the exponential test plan, the producer and
consumer risks were in terms of expected number of failures in a certain number
of miles, say $t$.  Because the exponential has a constant hazard rate this can
be considered the expected number of failures for a given number of miles
regardless of how many miles have been driven prior.  On the other hand the
Weibull does not have a constant hazard rate.  For the Weibull test plan
presented here the producer and consumer risk statements are now in terms of
expected number of failures in the first $t$ miles driven.

\subsubsection{Results}

\end{document}

### 2017-07-10 paperMath.tex
added current paper stuff

--- 2017-07-10 paperDraft.tex
@@
-\documentclass[12pt]{article}
+\documentclass{article}
+\usepackage[utf8]{inputenc}
 \usepackage{amsmath}
-\usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
-
 \begin{document}
 
-\title{Bayesian Hierarchical Models for Common Components across Multiple System Configurations}
+\title{Repairable Series System Assurance Testing}
 
-\begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of the Joint Light Tactical
-    Vehicle (JLTV), which is a family of vehicles. The proposed model effectively combines information
-    across three phases of testing and across common vehicle components. The analysis yields
-    estimates of failure rates for specific failure modes and vehicles as well as an overall estimate of the
-    failure rate for the family of vehicles. We are also able to obtain estimates of how well vehicle
-    modifications between test phases improve failure rates. In addition to using all data to improve on
-    current assessments of reliability and reliability growth, we illustrate how to leverage the information
-    learned from the three phases to determine appropriate specifications for subsequent testing that will
-    demonstrate if the reliability meets a given reliability threshold.
-\end{abstract}
+\section{Series System Failure Rate}
 
-\section{Introduction}
-
-\section{Data}
-
-\section{Methodology}
-
-\subsection{Modeling Reliability}
-A standard reliability analysis employed by the Department of Defense (DoD) test
-community considers each test phase independently and uses the exponential
-distribution to model the miles between failure ~\cite{ref1}. The traditional
-analysis is overly simplistic, relies on correct modeling assumptions
-and ignores valuable information learned about the individual vehicles and their
-failure modes.
-
-In considering the following alternative approach we will begin by introducing a
-hierarchical model structure that can use data across all test phases and
-incorporate known similarities between vehicle failure modes.  Next, we will
-explore the distributional assumptions of the model; how we can test these
-assumptions and how misspecifications can effect our assessments of system
-reliability.  This will then lead us into the next section on how this modeling
-can be used for assurance test planning.
-
-\subsubsection{Exponential Model}
-In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an
-exponential distribution with a failure rate parameter $\lambda_{ij}$.
-Introducing notation,
-\begin{align}
-y_{ijk}\mid\lambda_{ij}\sim Exp(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
-\end{align}
-where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
-$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
-are the number of failures of vehicle $i$ failure mode $j$. The number of
-failure modes is assumed fixed and known \textit{a priori}.
-
-The prior distribution on the exponential failure rate parameter,
-$\lambda_{ij}$, depends on whether failure mode $j$ is considered to be common
-across vehicles or related but not identical. For the related failure modes,
-we place a gamma prior distribution on the collection of $\lambda_{ij}$; in
-other words, we assume each vehicle has a distinct failure rate in failure mode
-$j$ but they arise from a common gamma distribution.
-
-If failure mode $j$ is considered common across vehicles, the collection of
-failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As
-with the related failure modes, a gamma prior distribution is placed on the
-single failure rate. The prior distributions are independent across failure
-mode, and can potentially have different hyperparameters.
-
-The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
-each of the vehicles for failure modes that are related. We are assuming the
-vehicles are conditionally independent, therefore the failure rate estimate for
-the family of vehicles for such failure modes can be found by
-$\sum_{i}\lambda_{ij}$. For failure modes that are common across vehicles the
-Phase 1 analysis yields a $\lambda_{j}$, which is the failure rate for the
-family of vehicles. Under the exponential modeling assumption the overall
-failure rate across all failure modes can be found by $\sum_{j}\lambda_{j}$.
-
-\subsubsection{Fix Effectiveness}
-After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
-these revisions, the PM2 reliability growth model \cite{EH06} is often used.
-This model explicitly captures testing phases, choices about which failure modes
-to correct, and the potential of not completely eliminating a failure upon
-repair. One of the downsides of PM2 is that many parameters of potential
-interest, such as the Fix Effectiveness Factor (FEF), which measures how much
-repairs improve failure rates, are typically fixed. A common value for FEF is
-0.70. We follow the premise of this type of model, but allow a more flexible and
-data-driven result that is less dependent on hard-coded assumptions.
-
-One normal assumption used in reliability growth modeling is non-decreasing
-failure rates; that is either the fixes were effective or had no effect, but did
-not degrade the family of vehicles.  This should generally be the case, but
-because we are dealing with complex systems we will sometimes see decreases in
-failure rates after adjustments are made.  Therefore for the Phase 2 data we
-write the rate parameters as a function of the rate parameters found in Phase 1.
-In particular, we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where
-$\rho_{j}$ represents the between phase change in failure mode $j$. Given this
-definition of $\lambda_{ij}^{P2}$, we again model the failure miles for a given
-vehicle and failure mode using the exponential distribution. We assume the prior
-distribution for the $\rho_{j}$ is a gamma distribution.  If $\rho_{j}$ is less
-than one, this represents an improvement in reliability.  After Phase 2 we can
-look again at failure rates across failure modes and vehicles and obtain an
-overall estimate of the rate for the family of vehicles.  The analysis of Test
-Phase 3 follows the same pattern as that shown in Phase 2. At the end of
-Phase 3, we can look at failure rates across failure modes and vehicles and
-obtain an overall estimate of the rate for the family of vehicles.
-Future tests will be planned based on the inferences of Phase 3.
-
-\subsubsection{Weibull Model}
-The exponential model is by far the most common parametric distribution used in
-reliability modeling because of its desirable math mathematical properties and
-simple interpretations.   Dispite its common uses the assumption of a constant
-failure rate over time is rarely justifiable.  It has been well documented
-(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
-the issues that can arise when this assumption is violated.  We will now
-consider the same hierarchical model structure while using the Weibull
-distribution for each miles between failure observation.
-\begin{align}
-y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
-\end{align}
-The Weibull distribution is a more flexible model with both a rate parameter
-$\lambda_{ij}$ and a shape parameter $\kappa_{i}$.  The exponential is a special
-case of the Weibull, when $\kappa = 1$.
-\\
-Talk about how to index the shape parameter and what it means
-
-\subsubsection{JLTV Model Fitting}
-So far we have discussed a number of different models and the assumptions that
-accompany them.  Now looking at the JLTV dataset we will run a few diagnostics to
-decide what model we will use for inference and future test planning.
-\\
-Models: \\
-Exponential and Weibull with no hierarchy \\
-Exponential and Weibull full hierarchy \\
-Exponential and Weibull full hierarchy \\
-Weibull with multipule shape vs. one shape \\
-\\
-DIC \\
-posterior predictive checks \\
-QQ Plots \\
-Shape Parameter Plot \\
-
-\subsubsection{JLTV Reliability Results}
-
-Results plots \\
-Exponential vs. Weibull interpretation
-
-\subsection{Assurance Test Planning}
-Assurance Testing
-consumer and producer risk
-
-\subsubsection{Traditional Approach}
-no producer risk
-
-\subsubsection{Bayes Risk}
-
-R(t) = reliability at time t (miles in our case)
-\\
-\\$ t_{*c} $ : time of interest to consumer
-\\$ t_{*p} $ : time of interest to producer
-\\
-\\
-\begin{itemize}
-\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
-\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
-\end{itemize}
-\
-\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
-\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
-\\
-\\
-We would like to get reliability into a inequality in terms of something we have
-a distribution for so we can evaluate the conditional probability statements.
-\\
-\\
-\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80
-miles is greater than 2
-\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140
-miles is less than 2
-
-\subsubsection{Poisson Process}
-
+\textbf{Definitions:} \\
+\noindent
 Reliability: $R(t) = 1 - F(t)$ \\
@@
 
-\subsubsection{Non-Homogeneous Poisson Process}
+\section{Non-Homogeneous Poisson Process}
 
@@
 
-\subsubsection{Exponential Case}
+\section{Building an Assurance Test}
 
-If we model the reliability of all 26 components in the system as $Y_{ij} \sim$
-exponential$\;(\gamma_i) $ random variables, this leads to the system
-reliability being the minimum or $Y_{system} \sim $ exponential
-$ \;(\sum_{n = 1}^{26} \gamma_i) $
+\textbf{Overview}
+
+R(t) = reliability at time t (miles in our case)
+\\
+\\$ t_{*c} $ : time of interest to consumer
+\\$ t_{*p} $ : time of interest to producer
+\\
+\\
+Two types of risk we want to control for:
+\begin{itemize}
+\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
+\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
+\end{itemize}
+\
+\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
+\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
+\\
+\\
+We would like to get reliability into a inequality in terms of something we have a distribution for so we can evaluate the conditional probability statements.
+\\
+\\
+\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80 miles is greater than 2
+\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140 miles is less than 2
+\\
+\\
+\textbf{Case 1 - Exponential}
+
+\noindent
+If we model the reliability of all 26 components in the system as $Y_{ij} \sim$ exponential$\;(\gamma_i) $ random variables, this leads to the system reliability being the minimum or $Y_{system} \sim $ exponential $ \;(\sum_{n = 1}^{26} \gamma_i) $
 \\
@@
 \\
-The expected number of failures for the system per mile is
-$ \mathbf{E}(Y_{system}) = \lambda_S $
+The expected number of failures for the system per mile is $ \mathbf{E}(Y_{system}) = \lambda_S $
 \\
 \\
-This leads to our consumer risk probability constraint as follows.  Given the
-test is passed, the consumer would like the probability of the expected number
-of failures in 80 miles being greater than 2 to be smaller than $\alpha$.
+This leads to our consumer risk probability constraint as follows.
+Given the test is passed, the consumer would like the probability of the expected number of failures in 80 miles being greater than 2 to be smaller than $\alpha$.
 \\
@@
 \\
-Let $ W $ be the number of failures during the test and $ W \leq c \Rightarrow $
-Test is passed and $ W > c \Rightarrow $ Test is failed.
+Let $ W $ be the number of failures during the test and $ W \leq c \Rightarrow $ Test is passed and $ W > c \Rightarrow $ Test is failed.
 \\
 \\
-Because failures are exponential $ W \sim Poisson(\lambda_S T) $ where $ T $ is
-the number of miles run during the test.
+Because failures are exponential $ W \sim Poisson(\lambda_S T) $ where $ T $ is the number of miles run during the test.
 \\
@@
 \\
-For simplicity we fix c to be zero (The number of failures needed to pass the
-test) and take N posterior draws $ \lambda_S^{(j)} $
+For simplicity we fix c to be zero (The number of failures needed to pass the test) and take N posterior draws $ \lambda_S^{(j)} $
 $$
@@
 \\
-Using the same technique for producer risk we get the following. The producer
-would like, given the test is failed, the probability of the expected number of
-failures in 140 miles being less than 2 to be smaller than $\beta$.
+Using the same technique for producer risk we get the following.
+The producer would like, given the test is failed, the probability of the expected number of failures in 140 miles being less than 2 to be smaller than $\beta$.
 \\
@@
 \\
-By constraining these two probabilities to acceptable risk levels we can solve
-for the smallest $ T $ that satisfies both.
+By constraining these two probabilities to acceptable risk levels we can solve for the smallest $ T $ that satisfies both.
 \\
@@
 Producer Risk : $ P(\lambda_S \leq 2/140 \; \vert  W > 0) \leq \beta $
+\\
+\\
+\textbf{Case 2 - Weibull}
 
-\subsubsection{Weibull Case}
-Now if we model the reliability of all 26 components in the system as
-$Y_{ij} \sim$ Weibull$\;(\gamma_i, \beta) $ random variables we are able to use
-the the non-homogeneous result from part two to build our assurance test. This
-follows the same process as the exponential test plan with all mile variables
-adjusted by the $\beta$ exponent and the N posterior draws will use both
-$\lambda_S^{(j)}$ and $\beta^{(j)}$.
+\noindent
+Now if we model the reliability of all 26 components in the system as $Y_{ij} \sim$ Weibull$\;(\gamma_i, \beta) $ random variables we are able to use the the non-homogeneous result from part two to build our assurance test.
+This follows the same process as the exponential test plan with all mile variables adjusted by the $\beta$ exponent and the N posterior draws will use both $\lambda_S^{(j)}$ and $\beta^{(j)}$.
 \\
@@
 \\
-\textbf{Important note:} For the exponential test plan, the producer and
-consumer risks were in terms of expected number of failures in a certain number
-of miles, say $t$.  Because the exponential has a constant hazard rate this can
-be considered the expected number of failures for a given number of miles
-regardless of how many miles have been driven prior.  On the other hand the
-Weibull does not have a constant hazard rate.  For the Weibull test plan
-presented here the producer and consumer risk statements are now in terms of
-expected number of failures in the first $t$ miles driven.
-
-\subsubsection{Results}
+\textbf{Important note:} For the exponential test plan, the producer and consumer risks were in terms of expected number of failures in a certain number of miles, say $t$.
+Because the exponential has a constant hazard rate this can be considered the expected number of failures for a given number of miles regardless of how many miles have been driven prior.
+On the other hand the Weibull does not have a constant hazard rate.
+For the Weibull test plan presented here the producer and consumer risk statements are now in terms of expected number of failures in the first $t$ miles driven.
 

### 2017-07-10 paperStart.tex
added current paper stuff

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce unblinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if1\blind
{
\title{Bayesian Hierarchical Models for Common Components across Multiple System Configurations}

\author{Kassandra M.\ Fronczyk\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{kfronczy@ida.org} \and
Rebecca M.\ Dickinson\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{rdickins@ida.org} \and
James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
Laura J.\ Freeman\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{lfreeman@ida.org}}
\maketitle} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Bayesian Hierarchical Models for Common Components across Multiple System Configurations}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
In this paper, we use a Bayesian hierarchical model to assess the reliability of the Joint Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed model effectively combines information across three phases of testing and across common vehicle components. The analysis yields estimates of failure rates across failure modes and vehicles as well as an overall estimate of the failure rate for the family of vehicles. We are also able to obtain estimates of the Fix Effectiveness Factor (FEF), a measure of how well repairs between test phases improve failure rates. In addition to using all data to improve on current assessments of reliability and reliability growth, we illustrate how to leverage the information learned from the three phases to determine the length of testing needed to demonstrate a given reliability threshold in subsequent testing.
\end{abstract}

\noindent%
{\it Keywords:}  Assurance Testing, Combining Information, Defense Acquisition, Reliability, Reliability Growth
\vfill

\newpage

\section{Introduction}

Reliability is a high priority in the testing of military systems. A common interest is {\em reliability growth}, which tracks the change, and ideally improvement, in the reliability of a system as it moves through testing phases and undergoes periodic corrective actions. Ideally, plans for future test events should be based on what is observed in previous testing.

In this paper, we look at combining information across multiple test phases with the objective of planing a future test. When combining information, there is no omnibus solution. Rather, models need to be carefully considered and evaluated to ensure that they accurately reflect the data and the underlying physical processes. Our analysis is motivated by reliability data from the Joint Light Tactical Vehicle (JLTV), which is a family of vehicles designed to replace one-third of the legacy high-mobility multipurpose wheeled vehicle (Humvee) fleet. There are four unique types of vehicles, and within types there are many possible variants. The primary mission of the family of vehicles is to provide ground mobility that is deployable worldwide and capable of operating across the range of military roles including combat, sustainment, police action, peace-keeping, and security patrol, in all weather and terrain conditions.

The JLTV has been through a series of test events as it has been developed. Engineering and Manufacturing Development (EMD) included three phases of testing, where fixes occurred only during a set Corrective Action Period (CAP) between each phase. For every vehicle, each failure encountered during testing was recorded and attributed to a specific failure mode. Failures discovered during mission execution that result in an abort or termination of a mission in progress are scored as Operational Mission Failures (OMF), and failures of mission essential components are scored as Essential Function Failures (EFF). The EFFs tend to include a large portion of the failure modes that drive maintenance costs and reduce system availability. While requirements are typically written in terms of OMFs, because OMFs are by definition EFFs that occurred at critical times, combining the failures provides a more robust reliability estimate. Since fixes were delayed to CAPs, analysis generally shows a distinct jump in the system reliability between test phases.

We propose a model that can effectively combine information across the three phases of testing and across common vehicle components. We use a Bayesian hierarchical model to assess the reliability of the family of vehicles. The model accounts for the commonality across vehicle types and allows for uncertainty quantification. Inferential objectives from the proposed model include an estimate of the mean miles between failure (MMBF) for each vehicle, failure mode, and phase of test, and an assessment of the effectiveness of the corrections completed in the CAPs. Additionally, because future tests are being planned, we propose methodology to leverage the information learned from the three phases to determine the length of testing needed to demonstrate a given reliability threshold in subsequent testing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \input{Data}

\section{Data}
Eight vehicle prototypes were used for reliability, availability, and maintainability (RAM) testing. There were four two-seat utility vehicles, two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a two-seat close combat weapons carrier. The close combat weapons carrier, one general purpose, and two utility vehicles were tested in Aberdeen, Maryland, where it is much colder in the winter months but the terrain is not as harsh, and the heavy weapons carrier, one general purpose, and two utility vehicles were tested in Yuma, Arizona, where it is warmer but with more challenging terrain, to attain testing in different environmental and terrain conditions. The vehicles were driven roughly 3000 to about 5000 miles in Phase 1, between 4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase 3.\footnote{The exact mileage has been altered to protect proprietary information.}

There are many similarities between vehicle types; in fact, the most dissimilar vehicles have over 80\% common parts. Consequently, some failure modes, such as brakes and radios, will be common to all eight vehicles. Other failure modes will be related, but not identical, as with hydraulics, frame, and body.

There are 91 OMFs and 1321 EFFs attributed to 26 failure modes recorded across all eight vehicles and all three test phases. In any given phase of test, every vehicle is not guaranteed to have a failure of all 26 failure modes, and each test phase does not necessarily end with a failure. Therefore, we have 624 right censored observations, accounting for miles driven without observed failures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \input{Methodology}

\section{Methodology}
A standard reliability analysis employed by the Department of Defense (DoD) test community considers each test phase independently and uses the exponential distribution to model the miles between failure ~\cite{ref1}. The traditional analysis is overly simplistic and ignores valuable information learned about the individual vehicles and their failure modes. Consider the following alternative approach.

In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an exponential distribution with a failure rate parameter $\lambda_{ij}$. Introducing notation,
\begin{align}\label{eq:m1}
y_{ijk}\mid\lambda_{ij}\sim Exp(\lambda_{ij}), \quad i = 1,2,...,v \quad j=1,2,...,s \quad k=1,2,...,n_{ij}
\end{align}
where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$, $v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The number of failure modes is assumed fixed and known \textit{a priori}.

The prior distribution on the exponential failure rate parameter, $\lambda_{ij}$, depends on whether failure mode $j$ is considered to be common across vehicles or related but not identical. For the related failure modes, we place a gamma prior distribution on the collection of $\lambda_{ij}$; in other words, we assume each vehicle has a distinct failure rate in failure mode $j$ but they arise from a common gamma distribution.

If failure mode $j$ is considered common across vehicles, the collection of failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As with the related failure modes, a gamma prior distribution is placed on the single failure rate. The prior distributions are independent across failure mode, and can potentially have different hyperparameters.

The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for each of the vehicles for failure modes that are related. We are assuming the vehicles are conditionally independent, therefore the failure rate estimate for the family of vehicles for such failure modes can be found by $\sum_{i}\lambda_{ij}$. For failure modes that are common across vehicles the Phase 1 analysis yields a $\lambda_{j}$, which is the failure rate for the family of vehicles. The overall failure rate across all failure modes can be found by $\sum_{j}\lambda_{j}$.

After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture these revisions, the PM2 reliability growth model \cite{EH06} is often used. This model explicitly captures testing phases, choices about which failure modes to correct, and the potential of not completely eliminating a failure upon repair. One of the downsides of PM2 is that many parameters of potential interest, such as the Fix Effectiveness Factor (FEF), which measures how much repairs improve failure rates, are typically fixed. A common value for FEF is 0.70. We follow the premise of this type of model, but allow a more data-driven result that is less dependent on hard-coded assumptions.

For Phase 2 data, we assume the failure rates are non-decreasing; either the fixes were effective or had no effect, but did not degrade the family of vehicles. Using this assumption, we write the Phase 2 rate parameters as a function of the rate parameters found in Phase 1. In particular, we define $\lambda_{ij}^{P2}=(1-\rho_{j})\lambda_{ij}^{P1}$ where $\rho_{j}$ is the FEF for failure mode $j$. Given this definition of $\lambda_{ij}^{P2}$, we again model the failure miles for a given vehicle and failure mode using the exponential distribution. We assume the prior distribution for the FEF is a beta distribution.

After Phase 2 we can look again at failure rates across failure modes and vehicles and obtain an overall estimate of the rate for the family of vehicles. The FEF provides an estimate of how effective the first CAP was and which failure modes are persisting.

The analysis of Test Phase 3 follows the same pattern as that shown in Phase 2. At the end of Phase 3, we can look at failure rates across failure modes and vehicles and obtain an overall estimate of the rate for the family of vehicles. Future tests are planned based on the inferences of Phase 3.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \input{Discussion}

\section{Discussion}
Preliminary results provide indications that our model is successfully capturing the failure rates across failure modes, inferring logical fix effectiveness factor distributions, and providing reliability estimates that can be leveraged for future test planning. In the traditional analysis, we do not typically look at failure rates of the failure modes, nor would we be able to leverage the commonalities across vehicles. The proposed modeling framework overcomes these limitations and allows for more realistic reliability estimates for vehicles with no observed failures. Additionally, our data-driven approach for reliability growth improves on the current growth models being used in the DoD, which are based solely on fixed quantities set by management.

While our basic approach provides reasonable initial inferences, there are several extensions to incorporate. For example, reliability estimates for vehicles with no observed failures are sensible; however, we should leverage more information across vehicles. Because the correlations induced by our current model are fairly low, potential methods for inducing more correlation between the vehicles in the related failure modes are being investigated. We also need to look more closely at our assumption of a fixed number of failure modes. Currently, the model specification assumes the number of failure modes is fixed at 26, as this is the number of unique failure modes that were observed in the data. It is possible, though, that in a future test phase a new failure mode will be discovered. To account for this, the number of failure modes may need to be specified as a random quantity in the model with a prior distribution, or we may look at limiting behavior as the number of failure modes becomes large.

Finally, inferences learned from the first three phases of testing will be used to develop a test plan for the next phase. Here the objective is to demonstrate that at a desired level of confidence, the system will meet or exceed a specified requirement. The methods to be employed will be similar to the assurance testing as discussed by Hamada et al. ~\cite{ref2}. Bayesian assurance tests are used to insure that the reliability of an item meets or exceeds a specified requirement with a desired probability. Although practitioners often use ``assure'' and ``demonstrate'' synonymously, Meeker and Escobar ~\cite{ME04} distinguish between reliability demonstration and reliability assurance testing. A \emph{reliability demonstration test} is essentially a classical hypothesis test, which uses only the data from the test to assess whether the reliability-related quantity of interest meets or exceeds the requirement. A \emph{reliability assurance test}, however, uses supplementary data and information to reduce the required amount of testing. Bayesian reliability assurance tests ~\cite{HWWGM13,JGHR03,HMRGJW04,EH06} have not addressed either analysis in a reliability growth context, nor the incorporation of covariates.

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz. Bayesian binomial assurance tests for system reliability using component data. \textit{Journal of Quality Technology} 46, 24-32 (2014).
\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese. A hierarchical model for estimating the reliability of complex systems. In Bayesian Statistics, Vol. 7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology. \textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
\end{thebibliography}

\end{document}

### 2017-07-12 paperDraft.tex
some on model selection and added plot

@@
 \\
-Talk about how to index the shape parameter and what it means
+***Talk about how to index the shape parameter and what it means
 
-\subsubsection{JLTV Model Fitting}
+\subsubsection{JLTV Model Selection}
 So far we have discussed a number of different models and the assumptions that
-accompany them.  Now looking at the JLTV dataset we will run a few diagnostics to
-decide what model we will use for inference and future test planning.
-\\
-Models: \\
-Exponential and Weibull with no hierarchy \\
-Exponential and Weibull full hierarchy \\
-Exponential and Weibull full hierarchy \\
-Weibull with multipule shape vs. one shape \\
-\\
-DIC \\
-posterior predictive checks \\
-QQ Plots \\
-Shape Parameter Plot \\
+accompany them.  We will now discuss the process of model selection.  The
+decision of which model to use can have a drastic impact on reliability
+assessment and future test planning.  We will use the JLTV dataset to
+demonstrate the process.
+
+The first model selection question we will explore is the parametric form,
+exponential versus Weibull.  In statistical modeling we often face the
+trade-off between fit and interpretability, and this situation is no different.
+Because the Weibull is a more flexible model, it will always, in a sense, fit the
+data better, but this comes at a price.  The exponential's convenient form
+makes both computation and interpretation straight forward.  When the Weibull's
+shape parameter is introduced this advantage is lost.  Thus, when the overall
+fit is close to the same between the exponential and the Weibull we will
+defualt to using the exponential.
+
+The first check we used to decide between the exponential and Weibull models is
+to fit the Weibull model and look at the posterior distributions of the
+shape parameters and determine if one is a reasonable value.  Looking at the
+plot below from the JLTV data, we see that for the 26 components it appears
+that the value of one falls in the extreme tails of the distributions.  This is
+our first clue that the exponential model will not be a good fit to this data.
+
+\includegraphics[width=6cm, height=5cm]{betaPostPlot}
+
+Not suprising, the exponential model assumes constant failure rate.  shapes less
+than 1 means wears out over time.  shapes more than 1 either fail early or last
+long time.
+
+Look at the DIC values for different indexings
+
+Last check, we do post predictive checks to see if we get reasonable values.
 

### 2017-07-15 paperDraft.tex
finished model selection section

@@
 \usepackage{enumerate}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 incorporate known similarities between vehicle failure modes.  Next, we will
-explore the distributional assumptions of the model; how we can test these
-assumptions and how misspecifications can effect our assessments of system
-reliability.  This will then lead us into the next section on how this modeling
-can be used for assurance test planning.
+look at a number different modeling and distributional assumptions.  We discuss
+different model diagnostics to consider when choosing a final model.  Then we
+illustrate how this decision can effect our assessments of system reliability.
+This will lead us into the next section on how this modeling can be used for
+assurance test planning.
 
@@
 $\rho_{j}$ represents the between phase change in failure mode $j$. Given this
-definition of $\lambda_{ij}^{P2}$, we again model the failure miles for a given
+definition of $\lambda_{ij}^{P2}$, we again model the miles to failure for a given
 vehicle and failure mode using the exponential distribution. We assume the prior
@@
 Phase 3 follows the same pattern as that shown in Phase 2. At the end of
-Phase 3, we can look at failure rates across failure modes and vehicles and
+Phase 3, we can look at failure rates across failure m odes and vehicles and
 obtain an overall estimate of the rate for the family of vehicles.
@@
 reliability modeling because of its desirable math mathematical properties and
-simple interpretations.   Dispite its common uses the assumption of a constant
+simple interpretations.   Despite its common uses the assumption of a constant
 failure rate over time is rarely justifiable.  It has been well documented
@@
 The Weibull distribution is a more flexible model with both a rate parameter
-$\lambda_{ij}$ and a shape parameter $\kappa_{i}$.  The exponential is a special
+$\lambda_{ij}$ and a shape parameter $\kappa_{j}$.  The exponential is a special
 case of the Weibull, when $\kappa = 1$.
 \\
-***Talk about how to index the shape parameter and what it means
+It should be noted that we are currently indexing both $\rho$ and $\kappa$, only
+by $j$ and not $i$, in other words we are assuming a single shape and rate
+change parameter for each failure mode across vehicles.  All of these parameters
+could also be indexed by $i$ and modeled hierarchical or with some combination
+of both.  This is something we will omit for this paper but hope to explore in
+the future.  One special case we will discuss is when a single shape parameter
+can be assumed across all failure modes.  When this is justifiable it can
+greatly simplify test planning calculations, as we will show in the assurance
+testing section.
 
@@
 data better, but this comes at a price.  The exponential's convenient form
-makes both computation and interpretation straight forward.  When the Weibull's
+makes both computation and interpretation straightforward.  When the Weibull's
 shape parameter is introduced this advantage is lost.  Thus, when the overall
 fit is close to the same between the exponential and the Weibull we will
-defualt to using the exponential.
+default to using the exponential.
 
@@
 
-Not suprising, the exponential model assumes constant failure rate.  shapes less
-than 1 means wears out over time.  shapes more than 1 either fail early or last
-long time.
+This is not a surprising result, because the exponential model assumes constant
+failure rate.  For most vehicle components we would expect the failure rate to
+increase as the distance driven grows larger, and this corresponds with a shape
+parameter between zero and one.  On the other hand, when the shape parameter is
+larger than 1, the failure rate will decrease with time/distance.
 
-Look at the DIC values for different indexings
+Now a more formal diagnostic tool used for model selection is the Deviance
+information criterion (DIC).  This is a popular method for comparing the
+goodness of fit of multiple models.  The DIC method gives a slight penalty for
+larger numbers of parameters.  The DIC value is a unitless measure with lower
+values indicating a better fit to the data.  In the table below we show the DIC
+results for the different distribution and structure combinations we considered
+with the JLTV dataset.
 
-Last check, we do post predictive checks to see if we get reasonable values.
+\begin{tabular}{|l|l|r|}
+\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
+\cline{1-3}
+Distribution    & Structure & DIC \\
+\hline
+Exponential   & Single Rate                       & 23258               \\
+              & Hierarchical Rate                 & 23022               \\
+Weibull       & Single Rate                       & 18750               \\
+              & Hierarchical Rate                 & \textbf{18556}      \\
+              & Hierarchical Rate (One shape)     & 18677               \\
+\hline
+\end{tabular}
+
+The single rate structure represents the non-hierarchical model, using one rate
+parameter all 8 vehicles for a given failure mode.  The hierarchical rate
+structure uses the common gamma distribution for the failure modes that are
+common across vehicles.  The final entry in the table is the model that uses one
+shape parameter across all 26 failure modes.
+
+While we have shown that the hierarchical Weibull model fits much better than
+the exponential, these test still do not tell us that this model is a good fit
+for the data.  The last method we will present is called posterior predictive
+checking ***reference***.  Here we are given important features of the data.
+In the JLTV case we were interested in the total failure counts for each phase
+and the number of time the miles between failures was less than 140.  We then
+used the final model to simulate 5,000 new datasets.  We then plot histograms
+for each of the 8 vehicles for all 3 phases.  In Figure 1 are examples of the
+histograms produced, with the line showing where the value of the true dataset
+fell.  For this method we don’t expect all of the true values to fall in the
+center of the distribution.  Values in the tales are to be expected in a random
+processes like this one.  We will only be concerned if we find true values
+falling in the extreme tails or if we see a common bias to the high or low side
+of the distributions.
+
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.4\linewidth]{Rplot1}
+  \caption{Plot 1}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.4\linewidth]{Rplot2}
+  \caption{Plot 2}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{Posterior Predictive Plots}
+\label{fig:test}
+\end{figure}
 
@@
 
-\subsubsection{Bayes Risk}
+\subsubsection{Bayesian Approach}
 

### 2017-07-21 paperDraft.tex
start of assurance test section

@@
 \subsection{Assurance Test Planning}
-Assurance Testing
-consumer and producer risk
+For all statisticical test planning we are interested in minimizing error rates
+while using the resoruces avalible as efficently as possible.  In the DoD
+acquisition process the error rates will be refrenced in terms of risk.
+Consumer risk being the probability of a unacceptable product passing a given
+test.  Producer risk being the probability of an acceptable product failing a
+given test.
 
 \subsubsection{Traditional Approach}
-no producer risk
+Traditional methods do not use any past data for determining the testing
+proceedure.  The only rely on distributional assumptions and asymptoic results.
 
 \subsubsection{Bayesian Approach}
+
+With Bayesian statistical approach we can incorperate the supplementary data
+from previous testing phases with the hopes of minimizing the resorces needed
+for testing.
 

### 2017-07-23 paperDraft.tex
start on assurance section

--- 2017-07-15 paperDraft.tex
@@
 Introducing notation,
-\begin{align}
-y_{ijk}\mid\lambda_{ij}\sim Exp(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
-\end{align}
+\begin{equation}
+f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
+y_{ijk}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
+\end{equation}
 where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
@@
 failure rate over time is rarely justifiable.  It has been well documented
-(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
-the issues that can arise when this assumption is violated.  We will now
-consider the same hierarchical model structure while using the Weibull
-distribution for each miles between failure observation.
-\begin{align}
-y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
-\end{align}
+(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2
+http://www.nap.edu/catalog/9655.html) the issues that can arise when this
+assumption is violated.  We will now consider the same hierarchical model
+structure while using the Weibull distribution.  Now we assume that the failure
+times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
+parameter $\lambda$ and shape parameter $\gamma$, with probability density
+function
+\begin{equation}
+f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i} y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij}
+y_{ijk}^{\gamma_{i}}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
+\end{equation}
 The Weibull distribution is a more flexible model with both a rate parameter
-$\lambda_{ij}$ and a shape parameter $\kappa_{j}$.  The exponential is a special
-case of the Weibull, when $\kappa = 1$.
+$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
+case of the Weibull, when $\gamma = 1$.
 \\
-It should be noted that we are currently indexing both $\rho$ and $\kappa$, only
+It should be noted that we are currently indexing both $\rho$ and $\gamma$, only
 by $j$ and not $i$, in other words we are assuming a single shape and rate
@@
 \subsection{Assurance Test Planning}
-Assurance Testing
-consumer and producer risk
+In this section inferences learned from the first three phases of testing will
+be used to develop a test plan for the next phase.  Here the objective is to
+demonstrate that at a desired level of confidence, the system will meet or
+exceed a specified requirement. The methods to be employed will be similar to
+the assurance testing as discussed by Hamada et al. ~\cite{ref2}. Bayesian
+assurance tests are used to insure that the reliability of an item meets or
+exceeds a specified requirement with a desired probability. Although
+practitioners often use ``assure'' and ``demonstrate'' synonymously, Meeker and
+Escobar ~\cite{ME04} distinguish between reliability demonstration and
+reliability assurance testing. A \emph{reliability demonstration test} is
+essentially a classical hypothesis test, which uses only the data from the test
+to assess whether the reliability-related quantity of interest meets or exceeds
+the requirement. A \emph{reliability assurance test}, however, uses
+supplementary data and information in order to testing as efficient as possible.
 
-\subsubsection{Traditional Approach}
-no producer risk
+In both classical and Bayesian test planning scenario we are interested in
+controlling error rates while minimizing the resources required for testing.  In
+the DoD acquisition process the error rates will be referenced in terms of risk.
+\textit{Consumer risk} which considers the event of purchasing a product that
+does not meet reliability requirements.  \textit{Producer risk} which considers
+the event of a product with acceptable reliability failing a given test and not
+being considered for purchase.  Introducing the notation for this section, In
+the JLTV case study we will be determining how many miles on test $t_0$, are
+required and how many system failures to allow $c$, before the product is
+considered unacceptable.  We will let $\pi$ represent  the system reliability at
+a given time. It is common to base both classical and Bayesian test plans on two
+specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
+(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
+\leq  \pi_0$.  Although the precise definition of ARL and RRL differ between the
+classical and Bayesian test criteria, we use them in an equivalent way.
 
-\subsubsection{Bayesian Approach}
+\subsubsection{Reliability Demonstration Test}
+Traditional methods do not use any past data for determining the testing
+proceedure.  The only rely on distributional assumptions and asymptoic results.
+
+\subsubsection{Reliability Assurance Test}
+
+With Bayesian statistical approach we can incorperate the supplementary data
+from previous testing phases with the hopes of minimizing the resorces needed
+for testing.
 
@@
 
+%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{thebibliography}{99}
+\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
+\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
+\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
+\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz.
+Bayesian binomial assurance tests for system reliability using component data.
+\textit{Journal of Quality Technology} 46, 24-32 (2014).
+\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese.
+A hierarchical model for estimating the reliability of complex systems.
+In Bayesian Statistics, Vol.
+7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
+\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
+for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
+\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology.
+\textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
+\end{thebibliography}
+
 \end{document}

### 2017-07-23 paperDraft.tex
work on expo assurance section

@@
 \documentclass[12pt]{article}
-\usepackage{amsmath}
+\usepackage{amsmath, amssymb, fullpage}
+\usepackage{array}
 \usepackage{graphicx,psfrag,epsf}
@@
 the DoD acquisition process the error rates will be referenced in terms of risk.
-\textit{Consumer risk} which considers the event of purchasing a product that
-does not meet reliability requirements.  \textit{Producer risk} which considers
-the event of a product with acceptable reliability failing a given test and not
+\emph{Consumer risk} which considers the event of purchasing a product that does
+not meet reliability requirements.  \emph{Producer risk} which considers the
+event of a product with acceptable reliability failing a given test and not
 being considered for purchase.  Introducing the notation for this section, In
-the JLTV case study we will be determining how many miles on test $t_0$, are
+the JLTV case study we will be determining how many miles on test $T$, are
 required and how many system failures to allow $c$, before the product is
-considered unacceptable.  We will let $\pi$ represent  the system reliability at
+considered unacceptable.  We will define $W(t)$ as a random variable that
+represents the total number of system failures after $t$ miles.  Suppose that
+$\pi$ denotes some quantity of interest that is related to system reliability at
 a given time. It is common to base both classical and Bayesian test plans on two
@@
 
-\subsubsection{Reliability Demonstration Test}
-Traditional methods do not use any past data for determining the testing
-proceedure.  The only rely on distributional assumptions and asymptoic results.
+\subsubsection{Classical Approach}
+It is quite common to use two criteria in determining classical test plans. The
+\emph{producer's risk} is the probability of failing the test when $\pi =
+\pi_0$, whereas the \emph{consumer's risk} is the probability of passing the
+test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$, of
+the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
+test planning, these criteria become
+$$
+\begin{aligned}
+	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\
+    &= P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
+\end{aligned}
+$$
+and
+$$
+\begin{aligned}
+	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\
+    &= P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
+\end{aligned}
+$$
+To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
+we assume a distributional form that defines the relationship between the number
+of system failyres $W(t)$ and the reliability $\pi$.  Then we can simply find
+the combinations of these probabilities by simultaneously solving these two
+equations.  In the case where the component failure times are assumed to be
+exponentially distributed with rate parameter $\lambda_i$ the failure counts for
+each component come from a homogeneous Poisson process $W_i(t) \sim
+\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
+\text{Poisson}(\lambda_S t)$  Numerous textbooks provide additional details of
+this purely classical approach.
 
-\subsubsection{Reliability Assurance Test}
+\subsubsection{Bayesian Approach}
+Traditional methods for determining the testing proceedure only rely on
+distributional assumptions and/or asymptoic results. With the Bayesian approach
+we incorperate the supplementary data from the previous testing phases with the
+hopes of minimizing the resorces needed for testing.
 
-With Bayesian statistical approach we can incorperate the supplementary data
-from previous testing phases with the hopes of minimizing the resorces needed
-for testing.
+We now consider fully Bayesian posterior risks that convey a completely
+different outlook from the corresponding classical risks. While the classical
+provide assurance that satisfactory devices will pass the test and that
+unsatisfactory devices will fail it, posterior risks provide precisely the
+assurance that practitioners often desire: if the test is passed, then the
+consumer desires a maximum probability $\beta$ that $\pi \leq \pi_1$. On the
+other hand, if the test is failed, then the producer desires a maximum
+probability $\alpha$ that $\pi \geq \pi_0$. Unlike the average risks, these
+posterior risks are fully Bayesian in the sense that they are subjective
+probability statements about $\pi$.
 
-R(t) = reliability at time t (miles in our case)
-\\
-\\$ t_{*c} $ : time of interest to consumer
-\\$ t_{*p} $ : time of interest to producer
+For a test that fails, the \emph{posterior producer's risk} is the probability
+that $\pi \geq \pi_{0}$, or $P \text{(}\pi \ge \pi_0 \vert \text{Test Is
+Failed)}$. Notice that this is simply the posterior probability that $\pi \ge
+\pi_0$ given that we have observed more than $c$ failures. In the exponential
+case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
+Theorem, and assuming a maximum allowable posterior producer's risk $\alpha$, an
+expression for the posterior producer's risk for the exponential test plan
+$(T,c)$ is
+$$
+\begin{aligned}
+    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S \geq \lambda_0 \; \vert \; W > c) \\
+	&= \int_{\lambda_0}^{\infty} p(\lambda_S \; \vert W > c) d\lambda_S \\
+    &= \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\
+    &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
+\end{aligned}
+$$
 \\
 \\
-\begin{itemize}
-\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
-\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
-\end{itemize}
-\
-\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
-\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
+For simplicity we if fix c to be zero and then perform Monte Carlo integration using N posterior draws $ \lambda_S^{(j)} $
+$$
+\begin{aligned}
+	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{\lambda_0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
+     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
+\end{aligned}
+$$
+
+Similarly, given that the test is passed, the \emph{posterior
+consumer's risk} is the
+probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert \text{Test Is
+Passed)}$. Notice that this is simply the
+posterior probability that $\pi \leq \pi_1$ given that we have
+observed no more than $c$ failures. In the exponential
+case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
+Theorem, and assuming a maximum allowable posterior consumer's risk $\beta$, an
+expression for the posterior producer's risk for the exponential test plan
+$(T,c)$ is
+
+$$
+\begin{aligned}
+    P(\lambda_S \leq \lambda_1 \; \vert \; \text{Test Is Passed)} &= P(\lambda_S \leq \lambda_1 \; \vert \; W \leq c) \\
+	&= \int_{0}^{\lambda_1} p(\lambda_S \; \vert W > c) d\lambda_S \\
+    &= \int_{0}^{\lambda_1} \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\
+    &= \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
+\end{aligned}
+$$
 \\
 \\
-We would like to get reliability into a inequality in terms of something we have
-a distribution for so we can evaluate the conditional probability statements.
-\\
-\\
-\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80
-miles is greater than 2
-\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140
-miles is less than 2
+For simplicity we if fix c to be zero and then perform Monte Carlo integration using N posterior draws $ \lambda_S^{(j)} $
+$$
+\begin{aligned}
+	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
+     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
+\end{aligned}
+$$
 
+\subsubsection{Weibull Case}
+
+In the exponential case we defined our quantity of interest that is related to system reliability at
+a given time $\pi$ to be equal to the system failure rate $\lambda_S$.  This gave us a convenient distributional form
+for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
+
+\subsubsection{Results}
+
+%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{thebibliography}{99}
+\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
+\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
+\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
+\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz.
+Bayesian binomial assurance tests for system reliability using component data.
+\textit{Journal of Quality Technology} 46, 24-32 (2014).
+\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese.
+A hierarchical model for estimating the reliability of complex systems.
+In Bayesian Statistics, Vol.
+7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
+\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
+for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
+\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology.
+\textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
+\end{thebibliography}
+
+\newpage
+
+\subsection{Additional Material}
 \subsubsection{Poisson Process}
@@
 $$
-\newpage
+
 Then Solving for the mean function of the system,
@@
 \subsubsection{Exponential Case}
+
+R(t) = reliability at time t (miles in our case)
+\\
+\\$ t_{*c} $ : time of interest to consumer
+\\$ t_{*p} $ : time of interest to producer
+\\
+\\
+\begin{itemize}
+\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
+\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
+\end{itemize}
+\
+\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
+\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
+\\
+\\
+We would like to get reliability into a inequality in terms of something we have
+a distribution for so we can evaluate the conditional probability statements.
+\\
+\\
+\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80
+miles is greater than 2
+\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140
+miles is less than 2
 
@@
 
-\subsubsection{Results}
-
-%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{thebibliography}{99}
-\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
-\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
-\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
-\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz.
-Bayesian binomial assurance tests for system reliability using component data.
-\textit{Journal of Quality Technology} 46, 24-32 (2014).
-\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese.
-A hierarchical model for estimating the reliability of complex systems.
-In Bayesian Statistics, Vol.
-7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
-\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
-for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
-\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology.
-\textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
-\end{thebibliography}
-
 \end{document}

### 2017-08-18 paperDraft2.tex
first half close to done

--- 2017-07-23 paperDraft.tex
@@
 
-\title{Bayesian Hierarchical Models for Common Components across Multiple System Configurations}
+\title{Bayesian Hierarchical Models for Common Components across Multiple System
+Configurations}
 
 \begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of the Joint Light Tactical
-    Vehicle (JLTV), which is a family of vehicles. The proposed model effectively combines information
-    across three phases of testing and across common vehicle components. The analysis yields
-    estimates of failure rates for specific failure modes and vehicles as well as an overall estimate of the
-    failure rate for the family of vehicles. We are also able to obtain estimates of how well vehicle
-    modifications between test phases improve failure rates. In addition to using all data to improve on
-    current assessments of reliability and reliability growth, we illustrate how to leverage the information
-    learned from the three phases to determine appropriate specifications for subsequent testing that will
-    demonstrate if the reliability meets a given reliability threshold.
+    We use a Bayesian hierarchical model to assess the reliability of the Joint
+    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
+    model effectively combines information across three phases of testing and
+    across common vehicle components. The analysis yields estimates of failure
+    rates for specific failure modes and vehicles as well as an overall estimate
+    of the failure rate for the family of vehicles. We are also able to obtain
+    estimates of how well vehicle modifications between test phases improve
+    failure rates. In addition to using all data to improve on current
+    assessments of reliability and reliability growth, we illustrate how to
+    leverage the information learned from the three phases to determine
+    appropriate specifications for subsequent testing that will demonstrate if
+    the reliability meets a given reliability threshold.
 \end{abstract}
@@
 \section{Introduction}
+Reliability is a high priority in the testing of military systems. A common
+interest is {\em reliability growth}, which tracks the change, and ideally
+improvement, in the reliability of a system as it moves through testing phases
+and undergoes periodic corrective actions. Ideally, plans for future test events
+should be based on what is observed in previous testing.
+
+In this paper, we look at combining information across multiple test phases with
+the objective of planning a future test. When combining information, there is no
+omnibus solution. Rather, models need to be carefully considered and evaluated
+to ensure that they accurately reflect the data and the underlying physical
+processes. Our analysis is motivated by reliability data from the Joint Light
+Tactical Vehicle (JLTV), which is a family of vehicles designed to replace
+one-third of the legacy high-mobility multipurpose wheeled vehicle (Humvee)
+fleet. There are four unique types of vehicles, and within types there are many
+possible variants. The primary mission of the family of vehicles is to provide
+ground mobility that is deployable worldwide and capable of operating across the
+range of military roles including combat, sustainment, police action,
+peacekeeping, and security patrol, in all weather and terrain conditions.
+
+The JLTV has been through a series of test events as it has been developed.
+Engineering and Manufacturing Development (EMD) included three phases of
+testing, where fixes occurred only during a set Corrective Action Period (CAP)
+between each phase. For every vehicle, each failure encountered during testing
+was recorded and attributed to a specific failure mode. Failures discovered
+during mission execution that result in an abort or termination of a mission in
+progress are scored as Operational Mission Failures (OMF), and failures of
+mission essential components are scored as Essential Function Failures (EFF).
+The EFFs tend to include a large portion of the failure modes that drive
+maintenance costs and reduce system availability. While requirements are
+typically written in terms of OMFs, because OMFs are by definition EFFs that
+occurred at critical times, combining the failures provides a more robust
+reliability estimate. Since fixes were delayed to CAPs, analysis generally shows
+a distinct jump in the system reliability between test phases.
+
+We propose a model that can effectively combine information across the three
+phases of testing and across common vehicle components. We use a Bayesian
+hierarchical model to assess the reliability of the family of vehicles. The
+model accounts for the commonality across vehicle types and allows for
+uncertainty quantification. Inferential objectives from the proposed model
+include an estimate of the mean miles between failure (MMBF) for each vehicle,
+failure mode, and phase of test, and an assessment of the effectiveness of the
+corrections completed in the CAPs. Additionally, because future tests are being
+planned, we propose methodology to leverage the information learned from the
+three phases to determine the length of testing needed to demonstrate a given
+reliability threshold in subsequent testing.
 
 \section{Data}
+Eight vehicle prototypes were used for reliability, availability,
+and maintainability (RAM) testing. There were four two-seat utility vehicles,
+two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
+two-seat close combat weapons carrier. The close combat weapons carrier, one
+general purpose, and two utility vehicles were tested in Aberdeen, Maryland,
+where it is much colder in the winter months but the terrain is not as harsh,
+and the heavy weapons carrier, one general purpose, and two utility vehicles
+were tested in Yuma, Arizona, where it is warmer but with more challenging
+terrain, to attain testing in different environmental and terrain conditions.
+The vehicles were driven roughly 3000 to about 5000 miles in Phase 1, between
+4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
+3.\footnote{The exact mileage has been altered to protect proprietary
+information.}
+
+There are many similarities between vehicle types; in fact, the most dissimilar
+vehicles have over 80\% common parts. Consequently, some failure modes, such as
+brakes and radios, will be common to all eight vehicles. Other failure modes
+will be related, but not identical, as with hydraulics, frame, and body.
+
+There are 91 OMFs and 1321 EFFs attributed to 26 failure modes recorded across
+all eight vehicles and all three test phases. In any given phase of test, every
+vehicle is not guaranteed to have a failure of all 26 failure modes, and each
+test phase does not necessarily end with a failure. Therefore, we have 624 right
+censored observations, accounting for miles driven without observed failures.
 
@@
 
-In considering the following alternative approach we will begin by introducing a
-hierarchical model structure that can use data across all test phases and
-incorporate known similarities between vehicle failure modes.  Next, we will
-look at a number different modeling and distributional assumptions.  We discuss
-different model diagnostics to consider when choosing a final model.  Then we
-illustrate how this decision can effect our assessments of system reliability.
-This will lead us into the next section on how this modeling can be used for
-assurance test planning.
+In this paper we propose an alternative approach using a Bayesian hierarchical
+model.  We will begin by introducing a hierarchical structure that models the
+relationships in the data across all test phases and incorporate known
+similarities between vehicle failure modes.  Next, we will consider different
+modeling and distributional assumptions and their implications.  We will aslo
+discuss model diagnostics to consider when choosing a final model. Then we will
+use the JLTV data to illustrate this process and discuss system reliability
+results. This will lead us into the next section on using these results to
+improve the planning of furture test.
 
-\subsubsection{Exponential Model}
-In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an
-exponential distribution with a failure rate parameter $\lambda_{ij}$.
+\subsubsection{Model Structure}
+In the first phase of testing, we assume the vehicle miles at failure, $y$,
+follow a lifetime distribution $Y$ with an unknown set of parameters that include
+a rate parameter $\lambda_{ij}$.
 Introducing notation,
 \begin{equation}
-f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
-y_{ijk}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
+y_{ijk}\mid\lambda_{ij}\sim Y(\lambda_{ij},...), \quad i = 1,2,...,v \quad
+j=1,2,...,s \quad k=1,2,...,n_{ij}
 \end{equation}
@@
 
-The prior distribution on the exponential failure rate parameter,
-$\lambda_{ij}$, depends on whether failure mode $j$ is considered to be common
-across vehicles or related but not identical. For the related failure modes,
-we place a gamma prior distribution on the collection of $\lambda_{ij}$; in
-other words, we assume each vehicle has a distinct failure rate in failure mode
-$j$ but they arise from a common gamma distribution.
+The prior distribution on failure rate parameter, $\lambda_{ij}$, depends on
+whether failure mode $j$ is considered to be common across vehicles or related
+but not identical. For the related failure modes, we place a prior distribution
+on the collection of $\lambda_{ij}$; in other words, we assume each vehicle has
+a distinct failure rate in failure mode $j$ but they arise from a common
+distribution.
 
@@
 failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As
-with the related failure modes, a gamma prior distribution is placed on the
-single failure rate. The prior distributions are independent across failure
-mode, and can potentially have different hyperparameters.
+with the related failure modes, a prior distribution is placed on the single
+failure rate. The prior distributions are independent across failure mode, and
+can potentially have different hyperparameters.
 
@@
 Phase 1 analysis yields a $\lambda_{j}$, which is the failure rate for the
-family of vehicles. Under the exponential modeling assumption the overall
-failure rate across all failure modes can be found by $\sum_{j}\lambda_{j}$.
+family of vehicles. If we assume the miles at failure come from an exponential
+distribution the overall failure rate across all failure modes can be easily
+calculated by $\sum_{j}\lambda_{j}$.  The exponential distribution is commonly
+used in reliability analysis because of its convenience, but as we will discuss
+in later sections it can be unrealistic in many real-world situations.
 
@@
 
-One normal assumption used in reliability growth modeling is non-decreasing
+One normal assumption used in reliability growth modeling is nondecreasing
 failure rates; that is either the fixes were effective or had no effect, but did
 not degrade the family of vehicles.  This should generally be the case, but
-because we are dealing with complex systems we will sometimes see decreases in
-failure rates after adjustments are made.  Therefore for the Phase 2 data we
-write the rate parameters as a function of the rate parameters found in Phase 1.
-In particular, we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where
-$\rho_{j}$ represents the between phase change in failure mode $j$. Given this
-definition of $\lambda_{ij}^{P2}$, we again model the miles to failure for a given
-vehicle and failure mode using the exponential distribution. We assume the prior
-distribution for the $\rho_{j}$ is a gamma distribution.  If $\rho_{j}$ is less
-than one, this represents an improvement in reliability.  After Phase 2 we can
-look again at failure rates across failure modes and vehicles and obtain an
-overall estimate of the rate for the family of vehicles.  The analysis of Test
-Phase 3 follows the same pattern as that shown in Phase 2. At the end of
-Phase 3, we can look at failure rates across failure m odes and vehicles and
-obtain an overall estimate of the rate for the family of vehicles.
-Future tests will be planned based on the inferences of Phase 3.
+because we are dealing with complex systems and testing conditions are rarely
+completely consistent, we will sometimes see decreases in failure rates after
+adjustments are made.  Therefore for the Phase 2 data, we write the rate
+parameters as a function of the rate parameters found in Phase 1. In particular,
+we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where $\rho_{j}$
+represents the between phase change in failure mode $j$. Given this definition
+of $\lambda_{ij}^{P2}$, we again model the miles to failure for a given vehicle
+and failure mode using the same lifetime distribution from Test Phase 1.  We
+will choose a prior distribution for the parameter $\rho_{j}$ that has positive
+support.  If $\rho_{j}$ is less than one, this represents an improvement in
+reliability.  After Phase 2 we can look again at failure rates across failure
+modes and vehicles and obtain an overall estimate of the rate for the family of
+vehicles.  The analysis of Test Phase 3 follows the same pattern as that shown
+in Phase 2. At the end of Phase 3, we can look at failure rates across failure
+modes and vehicles and obtain an overall estimate of the rate for the family of
+vehicles. Future tests will be planned based on the inferences of Phase 3.
 
-\subsubsection{Weibull Model}
-The exponential model is by far the most common parametric distribution used in
-reliability modeling because of its desirable math mathematical properties and
-simple interpretations.   Despite its common uses the assumption of a constant
-failure rate over time is rarely justifiable.  It has been well documented
-(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2
+\subsubsection{Distributional Assumption}
+The next modeling choice that must be made is slecting an appropriate
+probability model This includes a slecting a sampling distribution for the data
+and prior distributions for each parameter on which the sampling distribution
+depends.  For lifetime data there are a number sampling distribution to choose
+from.  Some common choices are exponential, Weibull, lognormal, gamma, inverse
+Gaussian, and normal failure time models.  Because all of these distributions
+have rate parameter (sometimes called scale = 1/rate) they can be applied to
+the proposed modeling structure.  For this paper we will focus on the
+exponential and Weibull distributions.
+
+First the exponential model, Test Phase 1,
+\begin{equation} f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
+y_{ijk})
+\end{equation}
+Test Phase 2,
+\begin{equation}
+f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{1,j}
+\exp(-\lambda_{ij}\rho_{1,j} y_{ijk})
+\end{equation}
+Test Phase 3,
+\begin{equation}
+f(y_{ijk}|\lambda_{ij}\rho1_{j}\rho2_{j})=\lambda_{ij}\rho1_{j}\rho2_{j}
+\exp(-\lambda_{ij}\rho1_{j}\rho2_{j} y_{ijk})
+\end{equation}
+
+This is by far the most common parametric distribution used in reliability
+modeling because of its desirable math mathematical properties and simple
+interpretations.  One of these properties is that the failure rate is constant.
+For the JLTV setting this would assume that a given component is equally likely
+to fail in the first mile of testing as it is in the thousandth.  This may be
+reasonable for some reliability settings, but in general we expect vehicle
+components to wear down and become more likely to fail the longer they are
+driven.
+
+Despite its common uses the assumption of a constant failure rate over time is
+rarely justifiable.  It has been well documented (Statistics, Testing, and
+Defense Acquisition: Background Papers chapter - 2
 http://www.nap.edu/catalog/9655.html) the issues that can arise when this
@@
 parameter $\lambda$ and shape parameter $\gamma$, with probability density
-function
+function for Test Phase 1,
 \begin{equation}
-f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i} y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij}
-y_{ijk}^{\gamma_{i}}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
+f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
+y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}})
 \end{equation}
@@
 case of the Weibull, when $\gamma = 1$.
-\\
+
 It should be noted that we are currently indexing both $\rho$ and $\gamma$, only
-by $j$ and not $i$, in other words we are assuming a single shape and rate
-change parameter for each failure mode across vehicles.  All of these parameters
-could also be indexed by $i$ and modeled hierarchical or with some combination
-of both.  This is something we will omit for this paper but hope to explore in
-the future.  One special case we will discuss is when a single shape parameter
-can be assumed across all failure modes.  When this is justifiable it can
-greatly simplify test planning calculations, as we will show in the assurance
-testing section.
+by $j$ and not $i$, in other words we are assuming a single shape and between
+phase adjustment parameter for each failure mode across vehicles.  All of these
+parameters could also be indexed by $i$ and modeled hierarchical or with some
+combination of both.  This is something we will omit for this paper but hope to
+explore in the future.  One special case we will discuss is when a single
+Weibull shape parameter can be assumed across all failure modes.  When this is
+justifiable it can greatly simplify test planning calculations, as we will show
+in the assurance testing section.
 
-\subsubsection{JLTV Model Selection}
+\subsubsection{Model Diagnostics}
 So far we have discussed a number of different models and the assumptions that
-accompany them.  We will now discuss the process of model selection.  The
+accompany them.  We will now discuss the process of choosing a final model.  The
 decision of which model to use can have a drastic impact on reliability
@@
 
-Results plots \\
-Exponential vs. Weibull interpretation
-
 \subsection{Assurance Test Planning}
@@
 \begin{aligned}
-	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\
-    &= P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
+	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
+	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
 \end{aligned}
@@
 \begin{aligned}
-	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\
-    &= P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
+	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
+	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
 \end{aligned}
@@
 \begin{aligned}
-    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S \geq \lambda_0 \; \vert \; W > c) \\
-	&= \int_{\lambda_0}^{\infty} p(\lambda_S \; \vert W > c) d\lambda_S \\
-    &= \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\
-    &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
+    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
+    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
+    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
+    \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S)
+    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c
+    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
+    {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
+    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
+\end{aligned}
+$$
+\\
+\\
+For simplicity we if fix c to be zero and then perform Monte Carlo integration
+using N posterior draws $ \lambda_S^{(j)} $
+$$
+\begin{aligned}
+	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
+	 \frac{\int_{\lambda_0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
+	 {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
+	 \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
+	 \lambda_0)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)} \end{aligned}
+$$
+
+Similarly, given that the test is passed, the \emph{posterior consumer's risk}
+is the probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert
+\text{Test Is Passed)}$. Notice that this is simply the posterior probability
+that $\pi \leq \pi_1$ given that we have observed no more than $c$ failures. In
+the exponential case, if we let $\pi$ be the system failure rate $\lambda_S$,
+then using Bayes' Theorem, and assuming a maximum allowable posterior consumer's
+risk $\beta$, an expression for the posterior producer's risk for the
+exponential test plan $(T,c)$ is
+
+$$
+\begin{aligned}
+    P(\lambda_S \leq \lambda_1 \; \vert \; \text{Test Is Passed)} &= P(\lambda_S
+    \leq \lambda_1 \; \vert \; W \leq c) \\ &= \int_{0}^{\lambda_1} p(\lambda_S \;
+    \vert W > c) d\lambda_S \\ &= \int_{0}^{\lambda_1} \frac{f(W > c \vert
+    \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\ &=
+    \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W
+    exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [
+    \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
+    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
 \end{aligned}
@@
 \begin{aligned}
-	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{\lambda_0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
-     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
-\end{aligned}
-$$
-
-Similarly, given that the test is passed, the \emph{posterior
-consumer's risk} is the
-probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert \text{Test Is
-Passed)}$. Notice that this is simply the
-posterior probability that $\pi \leq \pi_1$ given that we have
-observed no more than $c$ failures. In the exponential
-case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
-Theorem, and assuming a maximum allowable posterior consumer's risk $\beta$, an
-expression for the posterior producer's risk for the exponential test plan
-$(T,c)$ is
-
-$$
-\begin{aligned}
-    P(\lambda_S \leq \lambda_1 \; \vert \; \text{Test Is Passed)} &= P(\lambda_S \leq \lambda_1 \; \vert \; W \leq c) \\
-	&= \int_{0}^{\lambda_1} p(\lambda_S \; \vert W > c) d\lambda_S \\
-    &= \int_{0}^{\lambda_1} \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\
-    &= \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
-\end{aligned}
-$$
-\\
-\\
-For simplicity we if fix c to be zero and then perform Monte Carlo integration using N posterior draws $ \lambda_S^{(j)} $
-$$
-\begin{aligned}
-	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
-     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
+	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1}
+	 exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S
+	 T)p(\lambda_S)d\lambda_S} \\ &\approx \frac{\sum_{j = 1}^{N}
+	 exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N}
+	 exp(-\lambda_S^{(j)} T)}
 \end{aligned}
@@
 
-In the exponential case we defined our quantity of interest that is related to system reliability at
-a given time $\pi$ to be equal to the system failure rate $\lambda_S$.  This gave us a convenient distributional form
-for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
+In the exponential case we defined our quantity of interest that is related to
+system reliability at a given time $\pi$ to be equal to the system failure rate
+$\lambda_S$.  This gave us a convenient distributional form for our system
+failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
 
-\subsubsection{Results}
+\subsubsection{JLTV Test Plan Results}
 
@@
 \begin{thebibliography}{99}
-\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
-\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
-\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
-\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz.
-Bayesian binomial assurance tests for system reliability using component data.
-\textit{Journal of Quality Technology} 46, 24-32 (2014).
-\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese.
-A hierarchical model for estimating the reliability of complex systems.
-In Bayesian Statistics, Vol.
-7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
-\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
-for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
-\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology.
-\textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
+\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of
+system reliability availability maintainability - A primer; Third Edition
+(1982).
+\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+Bayesian Reliability. Springer (2008). \bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\
+Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology
+and Quantitative Management} 1, 1-25 (2004). \bibitem{HWWGM13} M.\ S.\ Hamada,
+A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz. Bayesian
+binomial assurance tests for system reliability using component data.
+\textit{Journal of Quality Technology} 46, 24-32 (2014). \bibitem{JGHR03} V.\
+E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese. A hierarchical
+model for estimating the reliability of complex systems. In Bayesian Statistics,
+Vol. 7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\
+Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University
+Press (2003). \bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese,
+T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
+for combining multilevel failure information in fault tree quantification and
+optimal follow-on resource allocation. \textit{Reliability Engineering and
+System Safety} 86, 397-405 (2004). \bibitem{EH06} P.\ M.\ Ellner and J.\ B.\
+Hall, An approach to reliability growth planning based on failure mode discovery
+and correction using AMSAA projection methodology. \textit{IEEE Proceedings of
+the Annual Reliability and Maintainability Symposium} (2006).
 \end{thebibliography}
 
-\newpage
-
-\subsection{Additional Material}
-\subsubsection{Poisson Process}
-
-Reliability: $R(t) = 1 - F(t)$ \\
-Hazard or failure rate function: $\lambda(t) = \frac{f(t)}{R(t)}$ \\
-Series system reliability: $R_S(t) = \prod_{i = 1}^N R_i(t)$
-\\
-\\
-\textbf{Result:}
-$$
-\begin{aligned}
-	R_S(t) &= \prod_{i = 1}^N R_i(t) \\
-	\frac{dR_S(t)}{dt} &= \frac{d}{dt} \prod_{i = 1}^N R_i(t) \; \; \text{(derivative of both sides)} \\
-	\frac{dR_S(t)}{dt} &= \sum_{i=1}^N \left[ \frac{dR_i(t)}{dt} \frac{dR_S(t)}{dR_i(t)} \right] \; \; \text{(product rule)} \\
-    \frac{-\frac{dR_S(t)}{dt}}{R_S(t)} &= \sum_{i=1}^N \left[  \frac{-\frac{d}{dt}R_i(t)}{dR_i(t)} \right] \; \; \text{(divide both sides by $-R_S(t)$)} \\
-    \lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \; \; \text{(because $\lambda(t) = \frac{f(t)}{R(t)} = \frac{-\frac{dR(t)}{dt}}{R(t)}$ )}
-\end{aligned}
-$$
-
-\subsubsection{Non-Homogeneous Poisson Process}
-
-\textbf{Definitions:} \\
-\noindent
-Number of failures before time t: $N(t) \sim \text{Poisson}(m(t))$ \\
-Mean function: $m(t) = \int_0^t \lambda(s)ds$ (represents the expected number of failures before time t) \\
-Weibull($\gamma, \beta $) failure rate: $\lambda(t) = \gamma\beta t^{\beta - 1}$
-\\
-\\
-\textbf{Result:}\\
-If we assume a constant shape parameter $\beta$ then,\\
-$$
-\begin{aligned}
-	\lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \\
-    &= \sum_{i = 1}^N \gamma_i\beta t^{\beta - 1} \\
-    &= \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i
-\end{aligned}
-$$
-
-Then Solving for the mean function of the system,
-
-$$
-\begin{aligned}
-	m_S(t) &= \int_0^t \lambda_S(s)ds \\
-    &= \int_0^t \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i \\
-    &= \sum_{i = 1}^N \gamma_i \int_0^t \beta t^{\beta -1} \\
-    &= t^\beta \sum_{i = 1}^N \gamma_i
-\end{aligned}
-$$
-
-This gives us: $N(t) \sim \text{Poisson}(t^\beta \sum_{i = 1}^N \gamma_i)$
-
-\subsubsection{Exponential Case}
-
-R(t) = reliability at time t (miles in our case)
-\\
-\\$ t_{*c} $ : time of interest to consumer
-\\$ t_{*p} $ : time of interest to producer
-\\
-\\
-\begin{itemize}
-\item Consumer Risk :   Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
-\item Producer Risk :   Prob( $ R(t_{*p}) \geq \pi_p \vert $ Test is failed)
-\end{itemize}
-\
-\\$ \pi_c $ : minimum reliability acceptable to the consumer at $ t_{*c} $
-\\$ \pi_p $ : minimum reliability goal of the producer at $ t_{*p} $
-\\
-\\
-We would like to get reliability into a inequality in terms of something we have
-a distribution for so we can evaluate the conditional probability statements.
-\\
-\\
-\\$ R(t_{*c}) \leq \pi_c \Rightarrow $ average number of system failures in 80
-miles is greater than 2
-\\$ R(t_{*p}) \geq \pi_p \Rightarrow $ average number of system failures in 140
-miles is less than 2
-
-If we model the reliability of all 26 components in the system as $Y_{ij} \sim$
-exponential$\;(\gamma_i) $ random variables, this leads to the system
-reliability being the minimum or $Y_{system} \sim $ exponential
-$ \;(\sum_{n = 1}^{26} \gamma_i) $
-\\
-\\
-- Looking at consumer risk first:
-\\
-want to find Prob( $ R(t_{*c}) \leq \pi_c \vert $ Test is passed)
-\\
-Let $ \sum_{n = 1}^{26} \gamma_i = \lambda_S $
-\\
-The expected number of failures for the system per mile is
-$ \mathbf{E}(Y_{system}) = \lambda_S $
-\\
-\\
-This leads to our consumer risk probability constraint as follows.  Given the
-test is passed, the consumer would like the probability of the expected number
-of failures in 80 miles being greater than 2 to be smaller than $\alpha$.
-\\
-\\
-Prob( $ \lambda_S \cdot (80) \geq 2 \; \vert $ Test is passed) $ \leq \alpha $
-\\
-\\
-Let $ W $ be the number of failures during the test and $ W \leq c \Rightarrow $
-Test is passed and $ W > c \Rightarrow $ Test is failed.
-\\
-\\
-Because failures are exponential $ W \sim Poisson(\lambda_S T) $ where $ T $ is
-the number of miles run during the test.
-\\
-\\
-$$
-\begin{aligned}
-	 P(\lambda_S \geq 2/80 \; \vert \; W \leq c) &= \int_{1/40}^{\infty} P(\lambda_S \; \vert W < c) d\lambda_S \\
-     &= \int_{1/40}^{\infty} \frac{f(W < c \; \vert \lambda_S) p(\lambda_S)}{f(W < c)}d\lambda_S\\
-     &= \int_{1/40}^{\infty} \frac{f(W < c \; \vert \lambda_S) p(\lambda_S)}{\int_{0}^{\infty} f(W < c \; \vert \lambda_S) p(\lambda_S) d\lambda_S}d\lambda_S \\
-     &= \frac{\int_{1/40}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
-\end{aligned}
-$$
-\\
-\\
-For simplicity we fix c to be zero (The number of failures needed to pass the
-test) and take N posterior draws $ \lambda_S^{(j)} $
-$$
-\begin{aligned}
-	 P(\lambda_S \geq 1/40 \; \vert \; W = 0) &= \frac{\int_{1/40}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\
-     &\approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq \frac{1}{40})} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)}
-\end{aligned}
-$$
-\\
-\\
-Using the same technique for producer risk we get the following. The producer
-would like, given the test is failed, the probability of the expected number of
-failures in 140 miles being less than 2 to be smaller than $\beta$.
-\\
-\\
-$$
-\begin{aligned}
-	 P(\lambda_S \leq 1/70 \; \vert \; W > 0) &= \frac{\int_{0}^{1/70} [1 - exp(-\lambda_S T)]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [1 - exp(-\lambda_S T)]p(\lambda_S)d\lambda_S} \\
-     &\approx  \frac{\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T)] I(\lambda_S^{(j)} \leq \frac{1}{70})} {\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T)]}
-\end{aligned}
-$$
-\\
-\\
-By constraining these two probabilities to acceptable risk levels we can solve
-for the smallest $ T $ that satisfies both.
-\\
-\\
-Consumer Risk : $ P(\lambda_S \geq 2/80 \; \vert  W = 0) \leq \alpha $ \\
-Producer Risk : $ P(\lambda_S \leq 2/140 \; \vert  W > 0) \leq \beta $
-
-\subsubsection{Weibull Case}
-Now if we model the reliability of all 26 components in the system as
-$Y_{ij} \sim$ Weibull$\;(\gamma_i, \beta) $ random variables we are able to use
-the the non-homogeneous result from part two to build our assurance test. This
-follows the same process as the exponential test plan with all mile variables
-adjusted by the $\beta$ exponent and the N posterior draws will use both
-$\lambda_S^{(j)}$ and $\beta^{(j)}$.
-\\
-\\
-Consumer risk:
-\\
-$$
-	 P(80^\beta (\lambda_S) \geq 2 \; \vert \; W = 0) \approx \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T^{\beta^{(j)}})I(80^{\beta^{(j)}} (\lambda_S^{(j)}) \geq 2)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T^{\beta^{(j)}})}
-$$
-\\
-\\
-Producer risk:
-\\
-$$
-	 P(140^\beta (\lambda_S) \leq 2 \; \vert \; W > 0) \approx  \frac{\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T^{\beta^{(j)}})] I(140^{\beta^{(j)}} (\lambda_S^{(j)}) \leq 2)} {\sum_{j = 1}^{N} [1 - exp(-\lambda_S^{(j)} T^{\beta^{(j)}})]}
-$$
-\\
-\\
-\textbf{Important note:} For the exponential test plan, the producer and
-consumer risks were in terms of expected number of failures in a certain number
-of miles, say $t$.  Because the exponential has a constant hazard rate this can
-be considered the expected number of failures for a given number of miles
-regardless of how many miles have been driven prior.  On the other hand the
-Weibull does not have a constant hazard rate.  For the Weibull test plan
-presented here the producer and consumer risk statements are now in terms of
-expected number of failures in the first $t$ miles driven.
-
 \end{document}

### 2017-08-24 paperDraft2.tex
small edits

@@
 \subsection{Assurance Test Planning}
-In this section inferences learned from the first three phases of testing will
-be used to develop a test plan for the next phase.  Here the objective is to
-demonstrate that at a desired level of confidence, the system will meet or
-exceed a specified requirement. The methods to be employed will be similar to
-the assurance testing as discussed by Hamada et al. ~\cite{ref2}. Bayesian
-assurance tests are used to insure that the reliability of an item meets or
-exceeds a specified requirement with a desired probability. Although
-practitioners often use ``assure'' and ``demonstrate'' synonymously, Meeker and
-Escobar ~\cite{ME04} distinguish between reliability demonstration and
-reliability assurance testing. A \emph{reliability demonstration test} is
-essentially a classical hypothesis test, which uses only the data from the test
-to assess whether the reliability-related quantity of interest meets or exceeds
-the requirement. A \emph{reliability assurance test}, however, uses
-supplementary data and information in order to testing as efficient as possible.
+In this section we use the resulting reliability model from the previous section
+develop a plan for future testing.  Here the objective is to demonstrate that at
+a desired level of confidence, the system will meet or exceed a specified
+requirement. The methods to be employed will be similar to the assurance testing
+as discussed by Hamada et al. ~\cite{ref2}. Bayesian assurance tests are used to
+insure that the reliability of an item meets or exceeds a specified requirement
+with a desired probability. Although practitioners often use ``assure'' and
+``demonstrate'' synonymously, Meeker and Escobar ~\cite{ME04} distinguish
+between reliability demonstration and reliability assurance testing. A
+\emph{reliability demonstration test} is essentially a classical hypothesis
+test, which uses only the data from the test to assess whether the
+reliability-related quantity of interest meets or exceeds the requirement. A
+\emph{reliability assurance test}, however, uses supplementary data and
+information in order to testing as efficient as possible.
 
-In both classical and Bayesian test planning scenario we are interested in
-controlling error rates while minimizing the resources required for testing.  In
-the DoD acquisition process the error rates will be referenced in terms of risk.
+In both classical and Bayesian test planning we are interested in controlling
+error rates while minimizing the resources required for testing.  In the DoD
+acquisition process the error rates will be referenced in terms of risk.
 \emph{Consumer risk} which considers the event of purchasing a product that does
@@
 It is quite common to use two criteria in determining classical test plans. The
-\emph{producer's risk} is the probability of failing the test when $\pi =
-\pi_0$, whereas the \emph{consumer's risk} is the probability of passing the
-test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$, of
-the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
+\emph{producer's risk}, defined as the probability of failing the test when $\pi =
+\pi_0$, and the \emph{consumer's risk}, defined as the probability of passing
+the test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$,
+of the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
 test planning, these criteria become
@@
 \text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
-\text{Poisson}(\lambda_S t)$  Numerous textbooks provide additional details of
+\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
 this purely classical approach.
@@
 Traditional methods for determining the testing proceedure only rely on
-distributional assumptions and/or asymptoic results. With the Bayesian approach
-we incorperate the supplementary data from the previous testing phases with the
+distributional assumptions and/or asymptoic results. With a Bayesian approach we
+incorperate the supplementary data from the previous testing phases with the
 hopes of minimizing the resorces needed for testing.
@@
 \\
-For simplicity we if fix c to be zero and then perform Monte Carlo integration using N posterior draws $ \lambda_S^{(j)} $
-$$
+For simplicity we if fix c to be zero and then perform Monte Carlo integration
+using N posterior draws $ \lambda_S^{(j)} $ $$
 \begin{aligned}
@@
 failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
+
+For allowed failures of zero and 1 the math isn't too bad, but when dealing with
+systems that  wear down (shape < 1) this will lead to no test plans that will
+meet required risk criteria or extreame test plans in terms of resorces.
+
+For more than 1 allowed failure test plans the Weibull computations become
+complicated especially for systems with a large number of components.  The one
+exception is when a single shape parameter can be assumed accross all compoents.
 

### 2017-08-27 paperDraft2.tex
work on weibull section

@@
 Despite its common uses the assumption of a constant failure rate over time is
-rarely justifiable.  It has been well documented (Statistics, Testing, and
-Defense Acquisition: Background Papers chapter - 2
-http://www.nap.edu/catalog/9655.html) the issues that can arise when this
-assumption is violated.  We will now consider the same hierarchical model
+rarely justifiable.  It has been well documented the issues that can arise when this
+assumption is violated ~\cite{ref2}.  We will now consider the same hierarchical model
 structure while using the Weibull distribution.  Now we assume that the failure
@@
 justifiable it can greatly simplify test planning calculations, as we will show
-in the assurance testing section.
+in the assurance testing section.  In this paper we will also be assuming on
+site repairs return the component to a "good as new" condition and that all
+component failures are independent.  That is, when a component such as the
+breaks are fixed during a test phase we will treat it as if it is brand  new and
+this failure has no effect on the reliability of other components such as the
+armor.
 
@@
 
-Now a more formal diagnostic tool used for model selection is the Deviance
-information criterion (DIC).  This is a popular method for comparing the
-goodness of fit of multiple models.  The DIC method gives a slight penalty for
-larger numbers of parameters.  The DIC value is a unitless measure with lower
-values indicating a better fit to the data.  In the table below we show the DIC
-results for the different distribution and structure combinations we considered
-with the JLTV dataset.
+Now a more formal diagnostic tool, the Deviance information criterion (DIC).
+This is a popular method for comparing the goodness of fit of multiple models.
+The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
+value is a unitless measure with lower values indicating a better fit to the
+data.  In the table below we show the DIC results for the different distribution
+and structure combinations we considered with the JLTV dataset.
 
@@
 \subsubsection{JLTV Reliability Results}
+*** TODO ***
+Now that we have selected a model for the data we can use the posterior
+distributions  of the systems parameters to estimate reliability-related
+quantities of interest.
+
+Expected miles to failure.
+
+Plot comparing exponential results vs. Weibull.
 
 \subsection{Assurance Test Planning}
-In this section we use the resulting reliability model from the previous section
+In this section, we use the resulting reliability model from the previous section
 develop a plan for future testing.  Here the objective is to demonstrate that at
@@
 requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref2}. Bayesian assurance tests are used to
-insure that the reliability of an item meets or exceeds a specified requirement
+as discussed by Hamada et al. ~\cite{ref3}. Bayesian assurance tests are used to
+ensure that the reliability of an item meets or exceeds a specified requirement
 with a desired probability. Although practitioners often use ``assure'' and
@@
 \emph{reliability assurance test}, however, uses supplementary data and
-information in order to testing as efficient as possible.
+information in order to test as efficient as possible.
 
@@
 error rates while minimizing the resources required for testing.  In the DoD
-acquisition process the error rates will be referenced in terms of risk.
+acquisition process, the error rates will be referenced in terms of risk.
 \emph{Consumer risk} which considers the event of purchasing a product that does
@@
 being considered for purchase.  Introducing the notation for this section, In
-the JLTV case study we will be determining how many miles on test $T$, are
+the JLTV case study, we will be determining how many miles on test $T$, are
 required and how many system failures to allow $c$, before the product is
@@
 exponentially distributed with rate parameter $\lambda_i$ the failure counts for
-each component come from a homogeneous Poisson process $W_i(t) \sim
+each component come from a homogeneous Poisson process $w_i(t) \sim
 \text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
@@
 \subsubsection{Bayesian Approach}
-Traditional methods for determining the testing proceedure only rely on
-distributional assumptions and/or asymptoic results. With a Bayesian approach we
-incorperate the supplementary data from the previous testing phases with the
-hopes of minimizing the resorces needed for testing.
+Traditional methods for determining the testing procedure only rely on
+distributional assumptions and/or asymptotic results. With a Bayesian approach we
+incorporate the supplementary data from the previous testing phases with the
+hopes of minimizing the resources needed for testing.
 
@@
     p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
-    \frac{f(W > c \vert \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S)
+    \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
     d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c
@@
 \subsubsection{Weibull Case}
+In the exponential case, we defined our quantity of interest that is related to
+system reliability at a given time $\pi$ to be equal to the system failure rate
+$\lambda_S$.  This distributional assumption gave us a convenient distributional
+form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
+When we assume the miles to failure for each system component follows a Weibull
+distribution the system failure counts no longer follow a homogeneous Poisson
+process.  Because each component failure rate now varies with time each
+component failure count follows a non-homogeneous Poisson process $w_i(t) \sim
+\text{Poisson}(\gamma_i \lambda_i t^{\gamma_i})$.  In this case we no longer
+have a closed form for the system failure rate $\lambda_S$.  The exception being
+if we can assume a single shape parameter $\gamma$ for all components.  In this
+case, it can be shown that the system failure count follows a non-homogeneous
+Poisson process $W(t) \sim \text{Poisson}(\gamma \lambda_S t^{\gamma})$.  Now,
+we can use the same approach as with the exponential distribution. An expression
+for the posterior producer's risk for the exponential test plan $(T,c)$ is
+$$
+\begin{aligned}
+    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
+    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
+    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{0}^{\infty}
+    \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty}
+    \int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S d\gamma} d\lambda_S
+    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty}
+    [\sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W exp(-\gamma \lambda_S
+    T^{\gamma})}{W!}]p(\lambda_S)p(\gamma)d\lambda_S d\gamma} {\int_{0}^{\infty}
+    \int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
+    exp(-\gamma \lambda_S T^{\gamma})} {W!}]p(\lambda_S) p(\gamma)
+    d\lambda_Sd\gamma} \leq \alpha
+\end{aligned}
+$$
+\\
+\\
+Once again we can simplify by setting c to be zero and then perform Monte Carlo
+integration using N posterior draws for both $\lambda_S^{(j)}$ and
+$\gamma^{(j)}$
+$$
+\begin{aligned}
+	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
+	 \int_{\lambda_0}^{\infty} exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
+	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} exp(-
+	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
+	 &\approx \frac{\sum_{j = 1}^{N} exp(-\gamma^{(j)} \lambda_S^{(j)}
+	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N}
+	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})} \end{aligned}
+$$
 
-In the exponential case we defined our quantity of interest that is related to
-system reliability at a given time $\pi$ to be equal to the system failure rate
-$\lambda_S$.  This gave us a convenient distributional form for our system
-failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
-
-For allowed failures of zero and 1 the math isn't too bad, but when dealing with
-systems that  wear down (shape < 1) this will lead to no test plans that will
-meet required risk criteria or extreame test plans in terms of resorces.
-
-For more than 1 allowed failure test plans the Weibull computations become
-complicated especially for systems with a large number of components.  The one
-exception is when a single shape parameter can be assumed accross all compoents.
+In the case of multiple shape parameters, these calculations can still be done.
+The practitioner must be careful in defining the system reliability quantity of
+interest, accounting for each component failure rate.  The computation can
+quickly become  unmanagable as the number of components and/or number of allowed
+failures becomes large.
 
 \subsubsection{JLTV Test Plan Results}
+*** TODO ***
 
@@
 (1982).
-\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
-Bayesian Reliability. Springer (2008). \bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\
+\bibitem{ref2} National Research Council. Statistics, Testing, and Defense Acquisition:
+Background Papers. \textit{National Academies Press} (1999).
+\bibitem{ref3} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+Bayesian Reliability. Springer (2008).
+\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\
 Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology

### 2017-08-28 paperDraft2.tex
small edits

@@
 similarities between vehicle failure modes.  Next, we will consider different
-modeling and distributional assumptions and their implications.  We will aslo
+distributional assumptions and their implications.  We will aslo
 discuss model diagnostics to consider when choosing a final model. Then we will
@@
 a distinct failure rate in failure mode $j$ but they arise from a common
-distribution.
-
-If failure mode $j$ is considered common across vehicles, the collection of
+distribution.  If failure mode $j$ is considered common across vehicles, the collection of
 failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As
@@
 each of the vehicles for failure modes that are related.  We are assuming the
-vehicles are conditionally independent, therefore the failure rate estimate for
-the family of vehicles for such failure modes can be found by
-$\sum_{i}\lambda_{ij}$. For failure modes that are common across vehicles the
-Phase 1 analysis yields a $\lambda_{j}$, which is the failure rate for the
-family of vehicles. If we assume the miles at failure come from an exponential
-distribution the overall failure rate across all failure modes can be easily
-calculated by $\sum_{j}\lambda_{j}$.  The exponential distribution is commonly
-used in reliability analysis because of its convenience, but as we will discuss
-in later sections it can be unrealistic in many real-world situations.
+vehicles are conditionally independent, if we also assume the miles at failure
+come from an exponential distribution the overall failure rate across all
+failure modes can be easily calculated by $\sum_{j}\lambda_{j}$.  The
+exponential distribution is commonly used in reliability analysis because of its
+convenience, but as we will discuss in later sections it can be unrealistic in
+many real-world situations.
 
@@
 Despite its common uses the assumption of a constant failure rate over time is
-rarely justifiable.  It has been well documented the issues that can arise when this
-assumption is violated ~\cite{ref2}.  We will now consider the same hierarchical model
-structure while using the Weibull distribution.  Now we assume that the failure
-times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
-parameter $\lambda$ and shape parameter $\gamma$, with probability density
-function for Test Phase 1,
+rarely justifiable.  It has been well documented the issues that can arise when
+this assumption is violated ~\cite{ref2}.  Thus we will also consider the same
+hierarchical model structure while using the Weibull distribution.  Now we
+assume that the failure times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
+distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
+probability density function for Test Phase 1,
 \begin{equation}
@@
 for the data.  The last method we will present is called posterior predictive
-checking ***reference***.  Here we are given important features of the data.
+checking ~\cite{ref3}.  Here we are given important features of the data.
 In the JLTV case we were interested in the total failure counts for each phase
@@
 requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref3}. Bayesian assurance tests are used to
+as discussed by Hamada et al. ~\cite{ref4}. Bayesian assurance tests are used to
 ensure that the reliability of an item meets or exceeds a specified requirement
@@
 if we can assume a single shape parameter $\gamma$ for all components.  In this
-case, it can be shown that the system failure count follows a non-homogeneous
+case, it can be shown [A1] that the system failure count follows a non-homogeneous
 Poisson process $W(t) \sim \text{Poisson}(\gamma \lambda_S t^{\gamma})$.  Now,
@@
 (1982).
-\bibitem{ref2} National Research Council. Statistics, Testing, and Defense Acquisition:
-Background Papers. \textit{National Academies Press} (1999).
-\bibitem{ref3} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+\bibitem{ref2} National Research Council. Statistics, Testing, and Defense
+Acquisition: Background Papers. \textit{National Academies Press} (1999).
+\bibitem{ref3} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
+predictive assessment of model fitness via realized discrepancies."
+\textit{Statistica sinica} 733-760 (1996).
+\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
 Bayesian Reliability. Springer (2008).
@@
 
+\section{Appendix A1}
+\subsection{Series System Failure Rate}
+
+\textbf{Definitions:} \\
+\noindent
+Reliability: $R(t) = 1 - F(t)$ \\
+Hazard or failure rate function: $\lambda(t) = \frac{f(t)}{R(t)}$ \\
+Series system reliability: $R_S(t) = \prod_{i = 1}^N R_i(t)$
+\\
+\\
+\textbf{Result:}
+$$
+\begin{aligned}
+	R_S(t) &= \prod_{i = 1}^N R_i(t) \\
+	\frac{dR_S(t)}{dt} &= \frac{d}{dt} \prod_{i = 1}^N R_i(t) \; \; \text{(derivative of both sides)} \\
+	\frac{dR_S(t)}{dt} &= \sum_{i=1}^N \left[ \frac{dR_i(t)}{dt} \frac{dR_S(t)}{dR_i(t)} \right] \; \; \text{(product rule)} \\
+    \frac{-\frac{dR_S(t)}{dt}}{R_S(t)} &= \sum_{i=1}^N \left[  \frac{-\frac{d}{dt}R_i(t)}{dR_i(t)} \right] \; \; \text{(divide both sides by $-R_S(t)$)} \\
+    \lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \; \; \text{(because $\lambda(t) = \frac{f(t)}{R(t)} = \frac{-\frac{dR(t)}{dt}}{R(t)}$ )}
+\end{aligned}
+$$
+
+\subsection{Non-Homogeneous Poisson Process}
+
+\textbf{Definitions:} \\
+\noindent
+Number of failures before time t: $N(t) \sim \text{Poisson}(m(t))$ \\
+Mean function: $m(t) = \int_0^t \lambda(s)ds$ (represents the expected number of failures before time t) \\
+Weibull($\gamma, \beta $) failure rate: $\lambda(t) = \gamma\beta t^{\beta - 1}$
+\\
+\\
+\textbf{Result:}\\
+If we assume a constant shape parameter $\beta$ then,\\
+$$
+\begin{aligned}
+	\lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \\
+    &= \sum_{i = 1}^N \gamma_i\beta t^{\beta - 1} \\
+    &= \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i
+\end{aligned}
+$$
+\newpage
+Then Solving for the mean function of the system,
+
+$$
+\begin{aligned}
+	m_S(t) &= \int_0^t \lambda_S(s)ds \\
+    &= \int_0^t \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i \\
+    &= \sum_{i = 1}^N \gamma_i \int_0^t \beta t^{\beta -1} \\
+    &= t^\beta \sum_{i = 1}^N \gamma_i
+\end{aligned}
+$$
+
+This gives us: $N(t) \sim \text{Poisson}(t^\beta \sum_{i = 1}^N \gamma_i)$
+
 \end{document}

### 2017-09-04 paperDraft2.tex
reorganized and reworded

@@
 f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
-y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}})
+y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}}).
 \end{equation}
@@
 
+\subsubsection{JLTV Reliability}
+So far we have discussed a number of different models and the assumptions that
+accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
+Then we can use the posterior distributions of the systems parameters to
+estimate reliability-related quantities of interest.
+
+Plot with expected miles to failure for each of 3 models to show the Weibull and
+exponential give very different results.
+
 \subsubsection{Model Diagnostics}
-So far we have discussed a number of different models and the assumptions that
-accompany them.  We will now discuss the process of choosing a final model.  The
+needs new transition into this section
+
+We will now discuss the process of choosing a final model.  The
 decision of which model to use can have a drastic impact on reliability
@@
 \hline
-Exponential   & Single Rate                       & 23258               \\
-              & Hierarchical Rate                 & 23022               \\
-Weibull       & Single Rate                       & 18750               \\
-              & Hierarchical Rate                 & \textbf{18556}      \\
+Exponential   & Hierarchical Rate                 & 23022               \\
+Weibull       & Hierarchical Rate                 & \textbf{18556}      \\
               & Hierarchical Rate (One shape)     & 18677               \\
@@
 
-\subsubsection{JLTV Reliability Results}
-*** TODO ***
-Now that we have selected a model for the data we can use the posterior
-distributions  of the systems parameters to estimate reliability-related
-quantities of interest.
+\subsection{Assurance Test Planning}
+In this section, we use the resulting reliability model from the previous
+section develop a plan for future testing.  Here the objective is to demonstrate
+that at a desired level of confidence, the system will meet or exceed a
+specified requirement. The methods to be employed will be similar to the
+assurance testing as discussed by Hamada et al. ~\cite{ref4}. Bayesian
+\emph{reliability assurance tests} are used to ensure that the reliability of
+an item meets or exceeds a specified requirement with a desired probability.
+Meeker and Escobar ~\cite{ME04} established the difference between this and the
+more traditional  \emph{reliability demonstration test}.  The difference being
+that the assurance test plan incorporates supplementary data and information,
+where the demonstration test only uses test data.
 
-Expected miles to failure.
-
-Plot comparing exponential results vs. Weibull.
-
-\subsection{Assurance Test Planning}
-In this section, we use the resulting reliability model from the previous section
-develop a plan for future testing.  Here the objective is to demonstrate that at
-a desired level of confidence, the system will meet or exceed a specified
-requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref4}. Bayesian assurance tests are used to
-ensure that the reliability of an item meets or exceeds a specified requirement
-with a desired probability. Although practitioners often use ``assure'' and
-``demonstrate'' synonymously, Meeker and Escobar ~\cite{ME04} distinguish
-between reliability demonstration and reliability assurance testing. A
-\emph{reliability demonstration test} is essentially a classical hypothesis
-test, which uses only the data from the test to assess whether the
-reliability-related quantity of interest meets or exceeds the requirement. A
-\emph{reliability assurance test}, however, uses supplementary data and
-information in order to test as efficient as possible.
-
-In both classical and Bayesian test planning we are interested in controlling
-error rates while minimizing the resources required for testing.  In the DoD
-acquisition process, the error rates will be referenced in terms of risk.
-\emph{Consumer risk} which considers the event of purchasing a product that does
-not meet reliability requirements.  \emph{Producer risk} which considers the
-event of a product with acceptable reliability failing a given test and not
-being considered for purchase.  Introducing the notation for this section, In
-the JLTV case study, we will be determining how many miles on test $T$, are
-required and how many system failures to allow $c$, before the product is
-considered unacceptable.  We will define $W(t)$ as a random variable that
-represents the total number of system failures after $t$ miles.  Suppose that
-$\pi$ denotes some quantity of interest that is related to system reliability at
-a given time. It is common to base both classical and Bayesian test plans on two
-specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
-(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
-\leq  \pi_0$. Although the precise definition of ARL and RRL differ between the
-classical and Bayesian test criteria, we use them in an equivalent way.
+In both test planning methods we are interested in controlling error rates while
+minimizing the resources required for testing.  In the DoD acquisition process,
+the error rates will be referenced in terms of risk. \emph{Consumer risk} which
+considers the event of purchasing a product that does not meet reliability
+requirements.  \emph{Producer risk} which considers the event of a product with
+acceptable reliability failing a given test and not being considered for
+purchase.  Introducing the notation for this section, In the JLTV case study, we
+will be determining how many miles on test $T$, are required and how many system
+failures to allow $c$, before the product is considered unacceptable.  We will
+define $W(t)$ as a random variable that represents the total number of system
+failures after $t$ miles.  Suppose that $\pi$ denotes some quantity of interest
+that is related to system reliability at a given time. It is common to base both
+classical and Bayesian test plans on two specified levels of $\pi$: $\pi_0$, an
+\emph{acceptable reliability level} (ARL), and $\pi_1$, a \emph{rejectable
+reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although the precise
+definition of ARL and RRL differ between the classical and Bayesian test
+criteria, we use them in an equivalent way.
 

### 2017-09-09 paperDraft2.tex
small changes

@@
 Then we can use the posterior distributions of the systems parameters to
-estimate reliability-related quantities of interest.
-
-Plot with expected miles to failure for each of 3 models to show the Weibull and
-exponential give very different results.
+estimate reliability-related quantities of interest for each of the eight
+vehicle types.  We are able to look at a number of different statistics related
+to reliability at both  the component and system level.  In this study our main
+quantity of interest is expected miles to  failure.  In the following figure we
+have box plots showing the posterior distributions of  the expected miles to
+failure for one of the vehicle types for each of the three  phases using each of
+the three models we are considering.
 

### 2017-09-10 paperDraft2.tex
start on assurance test results

@@
 In the first phase of testing, we assume the vehicle miles at failure, $y$,
-follow a lifetime distribution $Y$ with an unknown set of parameters that include
+follow a lifetime distribution with an unknown set of parameters that include
 a rate parameter $\lambda_{ij}$.
@@
 \begin{equation}
-y_{ijk}\mid\lambda_{ij}\sim Y(\lambda_{ij},...), \quad i = 1,2,...,v \quad
+y_{ijk}\mid\lambda_{ij}\sim f(\lambda_{ij},...), \quad i = 1,2,...,v \quad
 j=1,2,...,s \quad k=1,2,...,n_{ij}
@@
 have box plots showing the posterior distributions of  the expected miles to
-failure for one of the vehicle types for each of the three  phases using each of
-the three models we are considering.
+failure for one of the vehicle types for each of the three phases, first using
+the exponential model and second using the more general Weibull model.
+
+\includegraphics[width=6cm, height=5cm]{Boxplots}
+
+The plots show that the posterior distributions from the Weibull model have a
+good amount more spread than the exponential.  This is somewhat expected given
+the Weibull model is estimating two model parameters to the exponentials one,
+but what is concerning is that the center of the distributions is also quite
+different between the two models.  All of the Weibull EMTF posterior means
+are higher than the exponentials.  This is the first sign that the exponential
+model may not be a good fit to the data.
 
 \subsubsection{Model Diagnostics}
-needs new transition into this section
-
-We will now discuss the process of choosing a final model.  The
-decision of which model to use can have a drastic impact on reliability
-assessment and future test planning.  We will use the JLTV dataset to
-demonstrate the process.
-
-The first model selection question we will explore is the parametric form,
-exponential versus Weibull.  In statistical modeling we often face the
-trade-off between fit and interpretability, and this situation is no different.
-Because the Weibull is a more flexible model, it will always, in a sense, fit the
-data better, but this comes at a price.  The exponential's convenient form
-makes both computation and interpretation straightforward.  When the Weibull's
-shape parameter is introduced this advantage is lost.  Thus, when the overall
-fit is close to the same between the exponential and the Weibull we will
-default to using the exponential.
+As seen in the last section with the JLTV data, the decision of which model to
+use can have a drastic impact on reliability assessment and future test
+planning.  We will now look at a few  goodness-of-fit methods that can be used
+to help in this decision.  The first model selection question we will explore is
+the parametric form, exponential versus Weibull.  In statistical modeling we
+often face the trade-off between fit and interpretability, and this situation is
+no different. Because the Weibull is a more flexible model, it will always, in a
+sense, fit the data better, but this comes at a price.  The exponential's
+convenient form makes both computation and interpretation straightforward.  When
+the Weibull's shape parameter is introduced this advantage is lost.  Thus, when
+the overall fit is close to the same between the exponential and the Weibull we
+will default to using the exponential.
 
@@
 \hline
-Exponential   & Hierarchical Rate                 & 23022               \\
-Weibull       & Hierarchical Rate                 & \textbf{18556}      \\
+Exponential   & Single Rate                       & 23258               \\
+              & Hierarchical Rate                 & 23022               \\
+Weibull       & Single Rate                       & 18750               \\
+              & Hierarchical Rate                 & \textbf{18556}      \\
               & Hierarchical Rate (One shape)     & 18677               \\
@@
 \subsubsection{JLTV Test Plan Results}
-*** TODO ***
+The first step in applying this method to our JLTV dataset is defining $\pi_0$,
+$\pi_1$, $\alpha$ and $\beta$.  That is the ARL, RRL, acceptable producer risk
+and acceptable consumer risk respectively.  With input from subject matter
+experts  we will define the producer's target or ARL as the expected number of
+failures in the first 140 miles to be less  than 2, and the consumer's minimum
+requirements or RRL as the expected number of failures in  the first 80 miles to
+greater than 2.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
+$\beta$ respectively, but in practice these values should always be set based on
+the true risk tolerances of the consumer and producers.  This gives us the
+following probability statements to satisfy when designing the test:
+\\
+Consumer Risk : $ P(80^\beta (\lambda_S) \geq 2 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
+Producer Risk : $ P(140^\beta (\lambda_S) \leq 2 \; \vert \; \text{Test Is Failed}) \leq 0.05 $
+
+\begin{tabular}{|l|l|r|}
+\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
+\cline{1-2}
+Failures Allowed    & Test Miles Required \\
+\hline
+1   & 5,300      \\
+2   & 6,500      \\
+3   & 7,800      \\
+4   & 11,100     \\
+5   & 13,100     \\
+\hline
+\end{tabular}
 

### 2017-09-12 paperDraft2.tex
finished assurnace section

@@
 
+It should be noted that in this test planning process you would use the
+posterior distribution of $\lambda_S$ from the final developmental testing
+phase.  It is also common to incorporate a degradation factor to account for an
+expected reduction in reliability from the developmental phase to the
+operational phase.  In the Bayesian framework, this entails adding another
+multiplicative parameter to the rate parameter with an appropriate prior.   A
+10-30 percent reduction from the developmental phase to the operational phase is
+common in many DoD applications.
+
 \subsubsection{JLTV Test Plan Results}
@@
 
+From here we are able to find combinations of failures allowed and test miles
+required that satisfy both risk requirements.  The table below show the
+resulting combinations for the JLTV data.
+
 \begin{tabular}{|l|l|r|}
@@
 \end{tabular}
+
+It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
+unrealisitc values there can be situations where no combinations of failures
+allowed and test miles required will satisfy these probability statements.  In
+this paper we have focused on test plans for single units, but this methodology
+can be extended to find test plans that allow for a changing number of testing
+units.  In this case you would find combinations of failures allowed and test
+miles required and number of vehicles tested that satisfy the risk requirements.
+More details and examples of this can be found in the assurance testing section
+of Hamada et al. ~\cite{ref4}
+
+\subsection{Discussion}
 

### 2017-09-12 paperDraft2.tex
small edits

@@
 
-In this paper we propose an alternative approach using a Bayesian hierarchical
+In this paper, we propose an alternative approach using a Bayesian hierarchical
 model.  We will begin by introducing a hierarchical structure that models the
-relationships in the data across all test phases and incorporate known
+relationships in the data across all test phases and incorporates known
 similarities between vehicle failure modes.  Next, we will consider different
-distributional assumptions and their implications.  We will aslo
+distributional assumptions and their implications.  We will also
 discuss model diagnostics to consider when choosing a final model. Then we will
@@
 results. This will lead us into the next section on using these results to
-improve the planning of furture test.
+improve the planning of future test.
 
@@
 \subsubsection{Distributional Assumption}
-The next modeling choice that must be made is slecting an appropriate
-probability model This includes a slecting a sampling distribution for the data
+The next modeling choice that must be made is selecting an appropriate
+probability model This includes a selecting a sampling distribution for the data
 and prior distributions for each parameter on which the sampling distribution
@@
 have rate parameter (sometimes called scale = 1/rate) they can be applied to
-the proposed modeling structure.  For this paper we will focus on the
+the proposed modeling structure.  For this paper, we will focus on the
 exponential and Weibull distributions.
@@
 interpretations.  One of these properties is that the failure rate is constant.
-For the JLTV setting this would assume that a given component is equally likely
+For the JLTV, setting this would assume that a given component is equally likely
 to fail in the first mile of testing as it is in the thousandth.  This may be
@@
 It should be noted that we are currently indexing both $\rho$ and $\gamma$, only
-by $j$ and not $i$, in other words we are assuming a single shape and between
+by $j$ and not $i$, in other words, we are assuming a single shape and between
 phase adjustment parameter for each failure mode across vehicles.  All of these
@@
 data.  In the table below we show the DIC results for the different distribution
-and structure combinations we considered with the JLTV dataset.
+and structure combinations, we considered with the JLTV dataset.
 

### 2017-10-22 paperDraft3.tex
started edits

--- 2017-09-12 paperDraft2.tex
@@
 \subsubsection{Model Structure}
-In the first phase of testing, we assume the vehicle miles at failure, $y$,
-follow a lifetime distribution with an unknown set of parameters that include
-a rate parameter $\lambda_{ij}$.
-Introducing notation,
+Introducing notation, for each phase of testing we have failure time data for a
+given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
+t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
+testing phase. In the first phase of testing, we assume the vehicle miles
+between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime
+distribution with an unknown set of parameters that include a rate parameter
+$\lambda_{ij}$.
 \begin{equation}
-y_{ijk}\mid\lambda_{ij}\sim f(\lambda_{ij},...), \quad i = 1,2,...,v \quad
+y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
 j=1,2,...,s \quad k=1,2,...,n_{ij}
 \end{equation}
-where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
-$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
-are the number of failures of vehicle $i$ failure mode $j$. The number of
-failure modes is assumed fixed and known \textit{a priori}.
+where $v$ is the number of vehicles, $s$ is the number of failure modes, and
+$n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The number
+of failure modes is assumed fixed and known \textit{a priori}.
 
@@
 a distinct failure rate in failure mode $j$ but they arise from a common
-distribution.  If failure mode $j$ is considered common across vehicles, the collection of
-failure rates is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As
-with the related failure modes, a prior distribution is placed on the single
-failure rate. The prior distributions are independent across failure mode, and
-can potentially have different hyperparameters.
+distribution.  If failure mode $j$ is considered common across vehicles, the
+collection of failure rates is collapsed to a single parameter, $\lambda_{ij} =
+\lambda_j$. As with the related failure modes, a prior distribution is placed on
+the single failure rate. The prior distributions are independent across failure
+mode, and can potentially have different hyperparameters.
 
@@
 
+% This section needs a little work to make it more clear about the different
+% phases having the same lambda.  The notation should work together with the
+% distribution section after it.
 One normal assumption used in reliability growth modeling is nondecreasing
@@
 parameters as a function of the rate parameters found in Phase 1. In particular,
-we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where $\rho_{j}$
+we define $\lambda_{ij}=(\rho_{j}^{P2})\lambda_{ij}$ where $\rho_{j}^{P2}$
 represents the between phase change in failure mode $j$. Given this definition
-of $\lambda_{ij}^{P2}$, we again model the miles to failure for a given vehicle
-and failure mode using the same lifetime distribution from Test Phase 1.  We
-will choose a prior distribution for the parameter $\rho_{j}$ that has positive
-support.  If $\rho_{j}$ is less than one, this represents an improvement in
-reliability.  After Phase 2 we can look again at failure rates across failure
-modes and vehicles and obtain an overall estimate of the rate for the family of
-vehicles.  The analysis of Test Phase 3 follows the same pattern as that shown
-in Phase 2. At the end of Phase 3, we can look at failure rates across failure
-modes and vehicles and obtain an overall estimate of the rate for the family of
-vehicles. Future tests will be planned based on the inferences of Phase 3.
+of of the rate parameter, we again model the miles to failure for a given
+vehicle and failure mode using the same lifetime distribution from Test Phase 1.
+We will choose a prior distribution for the parameter $\rho_{j}^{P2}$ that has
+positive support.  If $\rho_{j}^{P2}$ is less than one, this represents an
+improvement in reliability.  After Phase 2 we can look again at failure rates
+across failure modes and vehicles and obtain an overall estimate of the rate for
+the family of vehicles.  The analysis of Test Phase 3 failure rate
+$\lambda_{ij}=(\rho_{j}^{P3})\rho_{j}^{P2}\lambda_{ij}$, following the same
+pattern as that shown in Phase 2. At the end of Phase 3, we can look at failure
+rates across failure modes and vehicles and obtain an overall estimate of the
+rate for the family of vehicles. Future tests will be planned based on the
+inferences of Phase 3.
 
@@
 \begin{equation}
-f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{1,j}
-\exp(-\lambda_{ij}\rho_{1,j} y_{ijk})
+f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{j}^{P2}
+\exp(-\lambda_{ij}\rho_{j}^{P2} y_{ijk})
 \end{equation}
@@
 \begin{equation}
-f(y_{ijk}|\lambda_{ij}\rho1_{j}\rho2_{j})=\lambda_{ij}\rho1_{j}\rho2_{j}
-\exp(-\lambda_{ij}\rho1_{j}\rho2_{j} y_{ijk})
+f(y_{ijk}|\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2})=\lambda_{ij}\rho_{1,j}\rho_{2,j}
+\exp(-\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2} y_{ijk})
 \end{equation}
@@
 
-\includegraphics[width=6cm, height=5cm]{Boxplots}
+% going to add a table that will have the posterior means and 90% credible
+% interval limits
+\begin{figure}
+  \centering
+      \includegraphics[width=8cm, height=6cm]{Boxplots}
+  \caption{Comparing EMTF for Different Models}
+\end{figure}
 
-The plots show that the posterior distributions from the Weibull model have a
+Figure 1 show that the posterior distributions from the Weibull model have a
 good amount more spread than the exponential.  This is somewhat expected given
@@
 model may not be a good fit to the data.
+
+\pagebreak
 
@@
 
+% this plot will be remade without title and smaller xlim
+\begin{figure}
+  \centering
       \includegraphics[width=6cm, height=5cm]{betaPostPlot}
+  \caption{Posterior Plots of Shape Parameter}
+\end{figure}
 
@@
 
+% these plots will be redone and I plan to add a contrasting version of them
+% using the exponential model
 \begin{figure}
@@
     \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
-    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c
+    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} 1 - [ \sum_{W=0}^c
     \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
-    {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
+    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
     T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
@@
 	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
-	 \frac{\int_{\lambda_0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
-	 {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
-	 \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
-	 \lambda_0)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)} \end{aligned}
+	 \frac{\int_{\lambda_0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
+	 {\int_{0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
+	 \frac{\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
+	 \lambda_0)} {\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)} \end{aligned}
 $$
@@
     \vert W > c) d\lambda_S \\ &= \int_{0}^{\lambda_1} \frac{f(W > c \vert
-    \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\ &=
+    \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\ &=
     \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W
@@
     \int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S d\gamma} d\lambda_S
-    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty}
+    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty} 1 -
     [\sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W exp(-\gamma \lambda_S
     T^{\gamma})}{W!}]p(\lambda_S)p(\gamma)d\lambda_S d\gamma} {\int_{0}^{\infty}
-    \int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
+    \int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
     exp(-\gamma \lambda_S T^{\gamma})} {W!}]p(\lambda_S) p(\gamma)
@@
 	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
-	 \int_{\lambda_0}^{\infty} exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
-	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} exp(-
+	 \int_{\lambda_0}^{\infty} 1 - exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
+	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} 1 - exp(-
 	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
-	 &\approx \frac{\sum_{j = 1}^{N} exp(-\gamma^{(j)} \lambda_S^{(j)}
-	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N}
+	 &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\gamma^{(j)} \lambda_S^{(j)}
+	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
 	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})} \end{aligned}
@@
 
+% This part should be expanded quite a bit and will extend into the discussion
+% section.
 It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
@@
 
+\subsection{Notes}
+Need to say somewhere we are assuming "bad-a-old" for the Weibull model.
+
 \end{document}

### 2017-10-26 paperDraft3.tex
working on edits

@@
 community considers each test phase independently and uses the exponential
-distribution to model the miles between failure ~\cite{ref1}. The traditional
-analysis is overly simplistic, relies on correct modeling assumptions
-and ignores valuable information learned about the individual vehicles and their
-failure modes.
+distribution to model the miles between failure for the system ~\cite{ref1}. The
+traditional analysis is overly simplistic, relies on correct modeling
+assumptions and ignores valuable information learned about the individual
+vehicles and their failure modes.
 
@@
 improve the planning of future test.
+
+In this reliability setting we are analysing time to failure data measured in
+miles for a multiple component system with the primary interest in the system
+failure rate and future failure counts.  The most common models used in this
+failure rate analysis are lifetime distributions and the most common for failure
+count analysis is the \emph{Poisson process} counting model.  We will utilize
+both and the relationships between them.
+
+The methodology section is organized as follows... section 3.1...
 

### 2017-12-05 paperDraft2.tex
boxplot figure updated
adjusted model structure and started removing one shape

@@
 
+\title{Bayesian modeling and test planning for multi-phase reliability assessment}
+\author{Alyson Wilson,  Kassandra Fronczyk, James Gilman}
+
 \begin{document}
-
-\title{Bayesian Hierarchical Models for Common Components across Multiple System
-Configurations}
+\maketitle
 
 \begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of the Joint
-    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
-    model effectively combines information across three phases of testing and
-    across common vehicle components. The analysis yields estimates of failure
-    rates for specific failure modes and vehicles as well as an overall estimate
-    of the failure rate for the family of vehicles. We are also able to obtain
-    estimates of how well vehicle modifications between test phases improve
-    failure rates. In addition to using all data to improve on current
-    assessments of reliability and reliability growth, we illustrate how to
-    leverage the information learned from the three phases to determine
-    appropriate specifications for subsequent testing that will demonstrate if
-    the reliability meets a given reliability threshold.
+We use a Bayesian hierarchical model to assess the reliability of a family of
+vehicles. The proposed model effectively combines information across three
+phases of testing and across common vehicle components. The analysis yields
+estimates of failure rates across failure modes and vehicles as well as an overall
+estimate of the failure rate for the family of vehicles. We are also able to
+obtain estimates of the Fix Effectiveness Factor (FEF), a measure of how well
+repairs between test phases improve failure rates. In addition to using all data
+to improve on current assessments of reliability and reliability growth, we
+illustrate how to leverage the information learned from the three developmental
+test phases to determine the length of testing needed to demonstrate a given
+reliability threshold in the next testing phase.
 \end{abstract}
@@
 \begin{equation}
-y_{ijk}\mid\lambda_{ij}\sim f(\lambda_{ij},...), \quad i = 1,2,...,v \quad
+y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
 j=1,2,...,s \quad k=1,2,...,n_{ij}
@@
 \begin{equation}
-f(y_{ijk}|\lambda_{ij}\rho1_{j}\rho2_{j})=\lambda_{ij}\rho1_{j}\rho2_{j}
-\exp(-\lambda_{ij}\rho1_{j}\rho2_{j} y_{ijk})
+f(y_{ijk}|\lambda_{ij}\rho_{1,j}\rho_{2,j})=\lambda_{ij}\rho_{1,j}\rho_{2,j}
+\exp(-\lambda_{ij}\rho_{1,j}\rho_{2,j} y_{ijk})
 \end{equation}
@@
 
+% this plot will be remade without title and smaller xlim %
+\begin{figure}
+  \centering
       \includegraphics[width=6cm, height=5cm]{betaPostPlot}
+  \caption{Posterior Plots of Shape Parameter}
+\end{figure}
 

### 2017-12-05 paperDraft3.tex
adjusted model structure and started removing one shape

@@
 t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
-testing phase. In the first phase of testing, we assume the vehicle miles
-between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime
-distribution with an unknown set of parameters that include a rate parameter
-$\lambda_{ij}$.
-\begin{equation}
-y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
-j=1,2,...,s \quad k=1,2,...,n_{ij}
-\end{equation}
-where $v$ is the number of vehicles, $s$ is the number of failure modes, and
-$n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The number
-of failure modes is assumed fixed and known \textit{a priori}.
+testing phase. In each phase of testing, we assume the vehicle miles between
+failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime distribution with
+an unknown set of parameters that include a rate parameter.  For the first phase
+the rate parameter for vehicle $i$ and failure mode $j$ will be denoted as
+$\lambda_{ij}$.  Then for the next stage we will use the same $\lambda_{ij}$ but
+add a multiplicative correction parameter $\rho_{1,j}$ that represents the
+change in this rate due to the CAP.  This proceedure is then repeated for each
+subsequent stage.  The correction parameter will be discussed more in the next
+section but the general model is as follows,
+\begin{align*}
+\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
+j=1,2,...,s \quad k=1,2,...,n_{ij}\\
+\text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
+\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot)
+\end{align*}
+where $v$ represents the number of vehicles, $s$ is the number of failure modes,
+and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The
+number of failure modes is assumed fixed and known \textit{a priori}.
 
-The prior distribution on failure rate parameter, $\lambda_{ij}$, depends on
-whether failure mode $j$ is considered to be common across vehicles or related
-but not identical. For the related failure modes, we place a prior distribution
-on the collection of $\lambda_{ij}$; in other words, we assume each vehicle has
-a distinct failure rate in failure mode $j$ but they arise from a common
-distribution.  If failure mode $j$ is considered common across vehicles, the
-collection of failure rates is collapsed to a single parameter, $\lambda_{ij} =
-\lambda_j$. As with the related failure modes, a prior distribution is placed on
-the single failure rate. The prior distributions are independent across failure
-mode, and can potentially have different hyperparameters.
+For this model we will assume a prior distribution on failure rate parameter
+$\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
+considered to be common across vehicles or related but not identical. For the
+related failure modes, we place a prior distribution on the collection of
+$\lambda_{ij}$; in other words, we assume each vehicle has a distinct failure
+rate in failure mode $j$ but they arise from a common distribution.  If failure
+mode $j$ is considered common across vehicles, the collection of failure rates
+is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As with the
+related failure modes, a prior distribution is placed on the single failure
+rate. The prior distributions are independent across failure mode, and can
+potentially have different hyperparameters.
 
+% not sure we need this paragraph %
 The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
@@
 
-% This section needs a little work to make it more clear about the different
-% phases having the same lambda.  The notation should work together with the
-% distribution section after it.
 One normal assumption used in reliability growth modeling is nondecreasing
@@
 completely consistent, we will sometimes see decreases in failure rates after
-adjustments are made.  Therefore for the Phase 2 data, we write the rate
-parameters as a function of the rate parameters found in Phase 1. In particular,
-we define $\lambda_{ij}=(\rho_{j}^{P2})\lambda_{ij}$ where $\rho_{j}^{P2}$
-represents the between phase change in failure mode $j$. Given this definition
-of of the rate parameter, we again model the miles to failure for a given
-vehicle and failure mode using the same lifetime distribution from Test Phase 1.
-We will choose a prior distribution for the parameter $\rho_{j}^{P2}$ that has
-positive support.  If $\rho_{j}^{P2}$ is less than one, this represents an
-improvement in reliability.  After Phase 2 we can look again at failure rates
-across failure modes and vehicles and obtain an overall estimate of the rate for
-the family of vehicles.  The analysis of Test Phase 3 failure rate
-$\lambda_{ij}=(\rho_{j}^{P3})\rho_{j}^{P2}\lambda_{ij}$, following the same
-pattern as that shown in Phase 2. At the end of Phase 3, we can look at failure
-rates across failure modes and vehicles and obtain an overall estimate of the
-rate for the family of vehicles. Future tests will be planned based on the
-inferences of Phase 3.
+adjustments are made.  Thus we will choose a prior distribution for the
+correction parameter $\rho_{j}^{P2}$ that has positive support.  If
+$\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
+And the same thinking is applied to $\rho_{j}^{P3}$ for the correction period
+between phases two and three.  With this structure we can use the posterior
+distributions of the correction parameters to make infrence on the effectiveness
+of the repairs and the join posterior distributions to evaluate the overall
+system reliability within each phase.
 
@@
 
-First the exponential model, Test Phase 1,
-\begin{equation} f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
-y_{ijk})
-\end{equation}
-Test Phase 2,
-\begin{equation}
-f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{j}^{P2}
-\exp(-\lambda_{ij}\rho_{j}^{P2} y_{ijk})
-\end{equation}
-Test Phase 3,
-\begin{equation}
-f(y_{ijk}|\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2})=\lambda_{ij}\rho_{1,j}\rho_{2,j}
-\exp(-\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2} y_{ijk})
-\end{equation}
+First the exponential model,
+\begin{equation*}
+    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk})
+\end{equation*}
 
@@
 probability density function for Test Phase 1,
-\begin{equation}
+\begin{equation*}
     f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
     y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}}).
-\end{equation}
+\end{equation*}
 The Weibull distribution is a more flexible model with both a rate parameter

### 2017-12-05 paperDraft3.tex
work on removing one shape

@@
 \subsubsection{Model Structure}
-Introducing notation, for each phase of testing we have failure time data for a
-given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
+Introducing notation, for each phase of testing we have failure mileage data for
+a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
 t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
@@
 hierarchical model structure while using the Weibull distribution.  Now we
-assume that the failure times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
+assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
 distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
-probability density function for Test Phase 1,
+probability density function,
 \begin{equation*}
-    f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
-    y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}}).
+    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
+    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
 \end{equation*}
@@
 $\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
-case of the Weibull, when $\gamma = 1$.
+case of the Weibull, when $\gamma = 1$.  You should notice here we are now
+modeling the actual failure mileage $t_{ijk}$ instead of the miles between
+failures $y_{ijk}$.  This means we are treating all intra-test repairs as "bad
+as old".  We could have continued with the miles between failures and assumed
+"good as new" repairs, but "bad as old" modeling will be more convenient for
+developing assurance test plans in later sections.  This distinction is
+important in the Weibull case because the failure rate is not constant in time.
+In practice the decision on intra-test repair assumptions should be made based
+on the application.  In many cases repairs should be treated as somewhere
+between "good as new" and "bad as old".  This requires more complex modeling
+that is beyond the scope of this paper.
 
-It should be noted that we are currently indexing both $\rho$ and $\gamma$, only
-by $j$ and not $i$, in other words, we are assuming a single shape and between
-phase adjustment parameter for each failure mode across vehicles.  All of these
-parameters could also be indexed by $i$ and modeled hierarchical or with some
-combination of both.  This is something we will omit for this paper but hope to
-explore in the future.  One special case we will discuss is when a single
-Weibull shape parameter can be assumed across all failure modes.  When this is
-justifiable it can greatly simplify test planning calculations, as we will show
-in the assurance testing section.  In this paper we will also be assuming on
-site repairs return the component to a "good as new" condition and that all
-component failures are independent.  That is, when a component such as the
-breaks are fixed during a test phase we will treat it as if it is brand  new and
-this failure has no effect on the reliability of other components such as the
-armor.
+It should  also be noted that we are currently indexing both $\rho$ and
+$\gamma$, only by $j$ and not $i$, in other words, we are assuming a single
+shape and between phase adjustment parameter for each failure mode across
+vehicles.  All of these parameters could also be indexed by $i$ and modeled
+hierarchical or with some combination of both.  This is something we will omit
+for this paper but hope to explore in the future.
 
@@
 
+% need to recheck these numbers %
 \begin{tabular}{|l|l|r|}
@@
 \hline
-Exponential   & Single Rate                       & 23258               \\
-              & Hierarchical Rate                 & 23022               \\
-Weibull       & Single Rate                       & 18750               \\
-              & Hierarchical Rate                 & \textbf{18556}      \\
-              & Hierarchical Rate (One shape)     & 18677               \\
+Exponential   & All Common Rate                      & 20,778.09             \\
+              & All Hierarchical Rate                & 21,308.72             \\
+              & Mixture Rate                         & 20,606.75             \\
+Weibull       & All Common Rate                      & 20,202.39             \\
+              & All Hierarchical Rate                & 17,984.85             \\
+              & Mixture Rate                         & \textbf{17,710.85}    \\
 \hline
@@
 
-The single rate structure represents the non-hierarchical model, using one rate
-parameter all 8 vehicles for a given failure mode.  The hierarchical rate
-structure uses the common gamma distribution for the failure modes that are
-common across vehicles.  The final entry in the table is the model that uses one
-shape parameter across all 26 failure modes.
-
-While we have shown that the hierarchical Weibull model fits much better than
-the exponential, these test still do not tell us that this model is a good fit
-for the data.  The last method we will present is called posterior predictive
-checking ~\cite{ref3}.  Here we are given important features of the data.
-In the JLTV case we were interested in the total failure counts for each phase
-and the number of time the miles between failures was less than 140.  We then
-used the final model to simulate 5,000 new datasets.  We then plot histograms
-for each of the 8 vehicles for all 3 phases.  In Figure 1 are examples of the
-histograms produced, with the line showing where the value of the true dataset
-fell.  For this method we don’t expect all of the true values to fall in the
-center of the distribution.  Values in the tales are to be expected in a random
-processes like this one.  We will only be concerned if we find true values
-falling in the extreme tails or if we see a common bias to the high or low side
-of the distributions.
+The mixture rate models use a combination of common rate and hierarchical rate
+parameterizations depending on the failure mode.  While we have shown that the
+hierarchical Weibull model fits much better than the exponential, these test
+still do not tell us that this model is a good fit for the data.  The last
+method we will present is called posterior predictive checking ~\cite{ref3}.
+Here we are given important features of the data. In the JLTV case we were
+interested in the total failure counts for each phase and the number of time the
+miles between failures was less than 140.  We then used the final model to
+simulate 5,000 new datasets.  We then plot histograms for each of the 8 vehicles
+for all 3 phases.  In Figure 1 are examples of the histograms produced, with the
+line showing where the value of the true dataset fell.  For this method we don’t
+expect all of the true values to fall in the center of the distribution.  Values
+in the tales are to be expected in a random processes like this one.  We will
+only be concerned if we find true values falling in the extreme tails or if we
+see a common bias to the high or low side of the distributions.
 
@@
 \text{Poisson}(\gamma_i \lambda_i t^{\gamma_i})$.  In this case we no longer
-have a closed form for the system failure rate $\lambda_S$.  The exception being
+have a closed form for the system failure rate $\lambda_S$.
+
+% need to redo this without the single rate %
+The exception being
 if we can assume a single shape parameter $\gamma$ for all components.  In this

### 2017-12-07 paperDraft3.tex
fixed abstract

@@
 \begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of the Joint
-    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
-    model effectively combines information across three phases of testing and
-    across common vehicle components. The analysis yields estimates of failure
-    rates for specific failure modes and vehicles as well as an overall estimate
-    of the failure rate for the family of vehicles. We are also able to obtain
-    estimates of how well vehicle modifications between test phases improve
-    failure rates. In addition to using all data to improve on current
-    assessments of reliability and reliability growth, we illustrate how to
-    leverage the information learned from the three phases to determine
-    appropriate specifications for subsequent testing that will demonstrate if
-    the reliability meets a given reliability threshold.
+    We use a Bayesian hierarchical model to assess the reliability of a family
+    of vehicles. The proposed model effectively combines information across
+    three phases of testing and across common vehicle components. The analysis
+    yields estimates of failure rates across failure modes and vehicles as well
+    as an overall estimate of the failure rate for the family of vehicles. We
+    are also able to obtain estimates of the Fix Effectiveness Factor (FEF), a
+    measure of how well repairs between test phases improve failure rates. In
+    addition to using all data to improve on current assessments of reliability
+    and reliability growth, we illustrate how to leverage the information
+    learned from the three developmental test phases to determine the length of
+    testing needed to demonstrate a given reliability threshold in the next
+    testing phase.
 \end{abstract}

### 2017-12-07 paperDraft3.tex
removed failure types from intro

@@
 between each phase. For every vehicle, each failure encountered during testing
-was recorded and attributed to a specific failure mode. Failures discovered
-during mission execution that result in an abort or termination of a mission in
-progress are scored as Operational Mission Failures (OMF), and failures of
-mission essential components are scored as Essential Function Failures (EFF).
-The EFFs tend to include a large portion of the failure modes that drive
-maintenance costs and reduce system availability. While requirements are
-typically written in terms of OMFs, because OMFs are by definition EFFs that
-occurred at critical times, combining the failures provides a more robust
-reliability estimate. Since fixes were delayed to CAPs, analysis generally shows
-a distinct jump in the system reliability between test phases.
+was recorded and attributed to a specific failure mode.  Since fixes were
+delayed to CAPs, analysis generally shows a distinct jump in the system
+reliability between test phases.
 
@@
 
-There are 91 OMFs and 1321 EFFs attributed to 26 failure modes recorded across
+There are 1412 observed failures attributed to 26 failure modes recorded across
 all eight vehicles and all three test phases. In any given phase of test, every

### 2017-12-08 paperDraft3.tex
notes for tomorrow
small changes

@@
 modeling because of its desirable math mathematical properties and simple
-interpretations.  One of these properties is that the failure rate is constant.
+interpretations.  One of these properties is that the hazard rate is constant.
 For the JLTV, setting this would assume that a given component is equally likely
 to fail in the first mile of testing as it is in the thousandth.  This may be
-reasonable for some reliability settings, but in general we expect vehicle
-components to wear down and become more likely to fail the longer they are
-driven.
+reasonable for some reliability settings, but in most setting we observe either
+a decreasing hazard rate where failures are likely to occur early in testing
+but less likely as the test goes on, or increasing hazard rate where we see the
+system wear down as the test goes on.
 
-Despite its common uses the assumption of a constant failure rate over time is
+Despite its common uses the assumption of a constant hazard rate over time is
 rarely justifiable.  It has been well documented the issues that can arise when
@@
 distribution the system failure counts no longer follow a homogeneous Poisson
-process.  Because each component failure rate now varies with time each
+process.
+
+% something about how using bad as old makes this work...
+Because each component failure rate now varies with time each
 component failure count follows a non-homogeneous Poisson process $w_i(t) \sim

### 2017-12-13 paperDraft3.tex
update

@@
 \hline
-Exponential   & All Common Rate                      & 20,778.09             \\
-              & All Hierarchical Rate                & 21,308.72             \\
-              & Mixture Rate                         & 20,606.75             \\
-Weibull       & All Common Rate                      & 20,202.39             \\
-              & All Hierarchical Rate                & 17,984.85             \\
-              & Mixture Rate                         & \textbf{17,710.85}    \\
+Exponential   & Common Rate Model                     & 21,264.19             \\
+              & Hierarchical Rate Model               & 21,244.47             \\
+Weibull       & Common Rate Model                     & 20,658.25             \\
+              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
 \hline
@@
 
-The mixture rate models use a combination of common rate and hierarchical rate
-parameterizations depending on the failure mode.  While we have shown that the
-hierarchical Weibull model fits much better than the exponential, these test
-still do not tell us that this model is a good fit for the data.  The last
-method we will present is called posterior predictive checking ~\cite{ref3}.
-Here we are given important features of the data. In the JLTV case we were
-interested in the total failure counts for each phase and the number of time the
-miles between failures was less than 140.  We then used the final model to
-simulate 5,000 new datasets.  We then plot histograms for each of the 8 vehicles
-for all 3 phases.  In Figure 1 are examples of the histograms produced, with the
-line showing where the value of the true dataset fell.  For this method we don’t
-expect all of the true values to fall in the center of the distribution.  Values
-in the tales are to be expected in a random processes like this one.  We will
-only be concerned if we find true values falling in the extreme tails or if we
-see a common bias to the high or low side of the distributions.
+Here we have shown that the hierarchical Weibull model fits the data much better
+than the exponential, but in general information criteria comparisons do not
+tell us if the model is truely a good representation of the underlying process.
+The last method we will present is called posterior predictive checking
+~\cite{ref3}. Here we are given important features of the data. In the JLTV case
+we were interested in the total failure counts for each phase and the number of
+time the miles between failures was less than 140.  We then used the final model
+to simulate 5,000 new datasets. We then plot histograms for each of the 8
+vehicles for all 3 phases.  In Figure 1 are examples of the histograms produced,
+with the line showing where the value of the true dataset fell.  For this method
+we don’t expect all of the true values to fall in the center of the
+distribution.  Values in the tales are to be expected in a random processes like
+this one.  We will only be concerned if we find true values falling in the
+extreme tails or if we see a common bias to the high or low side of the
+distributions.
 
@@
 \subsection{Assurance Test Planning}
-In this section, we use the resulting reliability model from the previous
-section develop a plan for future testing.  Here the objective is to demonstrate
-that at a desired level of confidence, the system will meet or exceed a
-specified requirement. The methods to be employed will be similar to the
-assurance testing as discussed by Hamada et al. ~\cite{ref4}. Bayesian
-\emph{reliability assurance tests} are used to ensure that the reliability of
-an item meets or exceeds a specified requirement with a desired probability.
-Meeker and Escobar ~\cite{ME04} established the difference between this and the
-more traditional \emph{reliability demonstration test}.  The difference being
-that the assurance test plan incorporates supplementary data and information,
-where the demonstration test only uses test data.
+In this section, we will use the reliability models fit in section two section
+to develop a plan for future testing.  Here the objective is to demonstrate that
+at a desired level of confidence, the system will meet or exceed a specified
+requirement. The methods to be employed will be similar to the assurance testing
+as discussed by Hamada et al. ~\cite{ref4}. Bayesian \emph{reliability assurance
+tests} are used to ensure that the reliability of an item meets or exceeds a
+specified requirement with a desired probability. Meeker and Escobar
+~\cite{ME04} established the difference between this and the more traditional
+\emph{reliability demonstration test}.  The difference being that the assurance
+test plan incorporates supplementary data and information, where the
+demonstration test only uses test data.
 
@@
 acceptable reliability failing a given test and not being considered for
-purchase.  Introducing the notation for this section, In the JLTV case study, we
+purchase.  Introducing the notation for this section, in the JLTV case study, we
 will be determining how many miles on test $T$, are required and how many system
@@
 define $W(t)$ as a random variable that represents the total number of system
-failures after $t$ miles.  Suppose that $\pi$ denotes some quantity of interest
+failures after $t$ miles.  We will let $\pi$ denote some quantity of interest
 that is related to system reliability at a given time. It is common to base both
@@
 \subsubsection{Classical Approach}
-It is quite common to use two criteria in determining classical test plans. The
-\emph{producer's risk}, defined as the probability of failing the test when $\pi =
-\pi_0$, and the \emph{consumer's risk}, defined as the probability of passing
-the test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$,
-of the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
-test planning, these criteria become
+In the frequentist (classical) version we will use two criteria in determining
+the test plans. The \emph{producer's risk}, defined as the probability of
+failing the test when $\pi = \pi_0$, and the \emph{consumer's risk}, defined as
+the probability of passing the test when $\pi = \pi_1$.  Suppose that we specify
+a maximum value, $\alpha$, of the producer's risk and a maximum value, $\beta$,
+of the consumer's risk. For test planning, these criteria become
 $$
@@
 distribution the system failure counts no longer follow a homogeneous Poisson
-process.
-
-% something about how using bad as old makes this work...
-Because each component failure rate now varies with time each
-component failure count follows a non-homogeneous Poisson process $w_i(t) \sim
-\text{Poisson}(\gamma_i \lambda_i t^{\gamma_i})$.  In this case we no longer
-have a closed form for the system failure rate $\lambda_S$.
-
-% need to redo this without the single rate %
-The exception being
-if we can assume a single shape parameter $\gamma$ for all components.  In this
-case, it can be shown [A1] that the system failure count follows a non-homogeneous
-Poisson process $W(t) \sim \text{Poisson}(\gamma \lambda_S t^{\gamma})$.  Now,
-we can use the same approach as with the exponential distribution. An expression
-for the posterior producer's risk for the exponential test plan $(T,c)$ is
-$$
-\begin{aligned}
-    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
-    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
-    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{0}^{\infty}
-    \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty}
-    \int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S d\gamma} d\lambda_S
-    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty} 1 -
-    [\sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W exp(-\gamma \lambda_S
-    T^{\gamma})}{W!}]p(\lambda_S)p(\gamma)d\lambda_S d\gamma} {\int_{0}^{\infty}
-    \int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
-    exp(-\gamma \lambda_S T^{\gamma})} {W!}]p(\lambda_S) p(\gamma)
-    d\lambda_Sd\gamma} \leq \alpha
-\end{aligned}
-$$
-\\
-\\
-Once again we can simplify by setting c to be zero and then perform Monte Carlo
-integration using N posterior draws for both $\lambda_S^{(j)}$ and
-$\gamma^{(j)}$
+process.  When assuming "bad as old" intra-test repairs we do find that the
+failure count for a given failure mode does follow a nonhomogeneous Poisson
+process, $w(t)_i \sim \text{Poisson}( (\lambda_i t)^{\gamma_i} )$.  In this case
+we no longer have a closed form for the system failure rate $\lambda_S = \sum_i
+(\lambda_i t)^{\gamma_i}$.  Because of this, using our previous approach leads to
+an unpleasant series of integals with parameters in the bounds.  Thankfully we
+can once again lean on Monte Carlo integration and the expression for the
+posterior producer's risk for the Weibull test plan $(T,c)$ simplifies to
 $$
@@
 	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
-	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})} \end{aligned}
+	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})}
+\end{aligned}
 $$
-
-In the case of multiple shape parameters, these calculations can still be done.
-The practitioner must be careful in defining the system reliability quantity of
-interest, accounting for each component failure rate.  The computation can
-quickly become  unmanagable as the number of components and/or number of allowed
-failures becomes large.
+\\
+Once again set c to be zero and used N posterior draws for both
+$\lambda_S^{(j)}$ and $\gamma^{(j)}$
 
@@
 \section{Appendix A1}
-\subsection{Series System Failure Rate}
+\textbf{Exponential Model:}
+\begin{equation*}
+L(\lambda_1, ..., \lambda_8, \rho^{P2}, \rho^{P3}, \vert Y) = \prod_{i = 1}^8
+  \Bigg[\prod_{j = 1}^{n_j}(\lambda_i p^*e^{-\lambda_i p^* y_{ij}})\prod_{j =
+  1}^R(e^{-\lambda_i p^*
+  y_{ij}})\Big(\frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+  1}e^{-\beta\lambda_i}\Big)\Bigg]
+\end{equation*}
+\[p^* =   \left\{
+\begin{array}{ll}
+      1 & y_{ij}\in \text{Phase 1} \\
+      \rho_{j}^{P2} & y_{ij} \in \text{Phase 2} \\
+      \rho_{j}^{P2} \rho_{j}^{P3} & y_{ij} \in \text{Phase }
+\end{array}
+\right. \]
+$R$ is the number of right-censored observations, and n is the number of
+non-censored observations.
 
-\textbf{Definitions:} \\
-\noindent
-Reliability: $R(t) = 1 - F(t)$ \\
-Hazard or failure rate function: $\lambda(t) = \frac{f(t)}{R(t)}$ \\
-Series system reliability: $R_S(t) = \prod_{i = 1}^N R_i(t)$
-\\
-\\
-\textbf{Result:}
-$$
-\begin{aligned}
-	R_S(t) &= \prod_{i = 1}^N R_i(t) \\
-	\frac{dR_S(t)}{dt} &= \frac{d}{dt} \prod_{i = 1}^N R_i(t) \; \; \text{(derivative of both sides)} \\
-	\frac{dR_S(t)}{dt} &= \sum_{i=1}^N \left[ \frac{dR_i(t)}{dt} \frac{dR_S(t)}{dR_i(t)} \right] \; \; \text{(product rule)} \\
-    \frac{-\frac{dR_S(t)}{dt}}{R_S(t)} &= \sum_{i=1}^N \left[  \frac{-\frac{d}{dt}R_i(t)}{dR_i(t)} \right] \; \; \text{(divide both sides by $-R_S(t)$)} \\
-    \lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \; \; \text{(because $\lambda(t) = \frac{f(t)}{R(t)} = \frac{-\frac{dR(t)}{dt}}{R(t)}$ )}
-\end{aligned}
-$$
+\begin{equation*}
+\pi(\alpha, \beta, \rho^{P2}, \rho^{P3}) \propto (\alpha^{a_1-1}e^{-\alpha
+  a_2})(\beta^{b_1 - 1}e^{-\beta b_2})(\rho^{P2*c_1 - 1}e^{-\rho^{P2}
+  c_2})(\rho^{P3*d_1 - 1}e^{-\rho^{P3} d_2})
+\end{equation*}
 
-\subsection{Non-Homogeneous Poisson Process}
+\begin{align*}
+\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
+\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
+\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
+\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
+\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
+\end{align*}
 
-\textbf{Definitions:} \\
-\noindent
-Number of failures before time t: $N(t) \sim \text{Poisson}(m(t))$ \\
-Mean function: $m(t) = \int_0^t \lambda(s)ds$ (represents the expected number of failures before time t) \\
-Weibull($\gamma, \beta $) failure rate: $\lambda(t) = \gamma\beta t^{\beta - 1}$
-\\
-\\
-\textbf{Result:}\\
-If we assume a constant shape parameter $\beta$ then,\\
-$$
-\begin{aligned}
-	\lambda_S(t) &= \sum_{i = 1}^N \lambda_i(t) \\
-    &= \sum_{i = 1}^N \gamma_i\beta t^{\beta - 1} \\
-    &= \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i
-\end{aligned}
-$$
-\newpage
-Then Solving for the mean function of the system,
+$N_1$ and $N_2$ are the total non-censored observations for phases two and three
+and phase three, respectively.
 
-$$
-\begin{aligned}
-	m_S(t) &= \int_0^t \lambda_S(s)ds \\
-    &= \int_0^t \beta t^{\beta -1} \sum_{i = 1}^N \gamma_i \\
-    &= \sum_{i = 1}^N \gamma_i \int_0^t \beta t^{\beta -1} \\
-    &= t^\beta \sum_{i = 1}^N \gamma_i
-\end{aligned}
-$$
+\textbf{Weibull Model (Bad as Old):}
+\begin{equation*}
+  L(\lambda_1, ..., \lambda_8, \gamma, \rho^{P2}, \rho^{P3}, \vert T) = \prod_{i =
+    1}^8 \Bigg[\prod_{j = 1}^{n_j}(\lambda_i p^*t_{ij}^{\gamma_i-1} e^{-\lambda_i
+    p^* t_{ij}^{\gamma_i}})\prod_{j = 1}^R(e^{-\lambda_i p^*
+    t_{ij}^{\gamma_i}})\Big(\frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+    1}e^{-\beta\lambda_i}\Big)\Bigg]
+\end{equation*}
+\[p^* =   \left\{
+\begin{array}{ll}
+      1 & t_{ij}\in \text{Phase 1} \\
+      \rho^{P2^\gamma} & t_{ij} \in \text{Phase 2} \\
+      \rho^{P2^\gamma} \rho^{P3^\gamma} & t_{ij} \in \text{Phase }
+\end{array}
+\right. \]
+$R$ is the number of right-censored observations, and n is the number of
+non-censored observations.
 
-This gives us: $N(t) \sim \text{Poisson}(t^\beta \sum_{i = 1}^N \gamma_i)$
+\begin{equation*}
+\pi(\alpha, \beta, \rho^{P2}, \rho^{P3}) \propto (\alpha^{a_1-1}e^{-\alpha
+  a_2})(\beta^{b_1 - 1}e^{-\beta b_2})(\rho^{P2*c_1 - 1}e^{-\rho^{P2}
+  c_2})(\rho^{P3 * d_1 - 1}e^{-\rho^{P3} d_2})(\gamma^{g_1 - 1}e^{-\gamma g_2})
+\end{equation*}
 
-\subsection{Notes}
-Need to say somewhere we are assuming "bad-a-old" for the Weibull model.
+\begin{align*}
+\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}t_{ij}^{\gamma_i} p^* + \beta) \\
+\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
+\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + c_2) \\
+\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
+\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}\\
+\gamma|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
+\end{align*}
+
+$N_1$ and $N_2$ are the total non-censored observations for phases two and three
+and phase three, respectively.
 

### 2017-12-14 paperDraft3.tex
fixed plots

@@
 \usepackage{subcaption}
+%\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
+
+%\pdfminorversion=4
+% NOTE: To produce unblinded version, replace "0" with "1" below.
+\newcommand{\blind}{1}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{-.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 
-\title{Bayesian Hierarchical Models for Common Components across Multiple System
-Configurations}
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if1\blind
+{
+\title{Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment}
+
+\author{Kassandra M.\ Fronczyk\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{kfronczy@ida.org} \and
+Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
+James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
+}
+\maketitle} \fi
+
+\if0\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
 
 \begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of a family
-    of vehicles. The proposed model effectively combines information across
-    three phases of testing and across common vehicle components. The analysis
-    yields estimates of failure rates across failure modes and vehicles as well
-    as an overall estimate of the failure rate for the family of vehicles. We
-    are also able to obtain estimates of the Fix Effectiveness Factor (FEF), a
-    measure of how well repairs between test phases improve failure rates. In
-    addition to using all data to improve on current assessments of reliability
-    and reliability growth, we illustrate how to leverage the information
-    learned from the three developmental test phases to determine the length of
-    testing needed to demonstrate a given reliability threshold in the next
-    testing phase.
+    We use a Bayesian hierarchical model to assess the reliability of the Joint
+    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
+    model effectively combines information across three phases of testing and
+    across common vehicle components. The analysis yields estimates of failure
+    rates for specific failure modes and vehicles as well as an overall estimate
+    of the failure rate for the family of vehicles. We are also able to obtain
+    estimates of how well vehicle modifications between test phases improve
+    failure rates. In addition to using all data to improve on current
+    assessments of reliability and reliability growth, we illustrate how to
+    leverage the information learned from the three phases to determine
+    appropriate specifications for subsequent testing that will demonstrate if
+    the reliability meets a given reliability threshold.
 \end{abstract}
+
+\noindent%
+{\it Keywords:}  Assurance Testing, Combining Information, Defense Acquisition, Reliability, Reliability Growth
+\vfill
+
+\newpage
 
@@
 % interval limits
-\begin{figure}
+\begin{figure}[h]
   \centering
-      \includegraphics[width=8cm, height=6cm]{Boxplots}
+      \includegraphics[width=9cm, height=7cm]{Boxplots}
   \caption{Comparing EMTF for Different Models}
@@
 model may not be a good fit to the data.
-
-\pagebreak
 
@@
 The first check we used to decide between the exponential and Weibull models is
-to fit the Weibull model and look at the posterior distributions of the
-shape parameters and determine if one is a reasonable value.  Looking at the
-plot below from the JLTV data, we see that for the 26 components it appears
-that the value of one falls in the extreme tails of the distributions.  This is
-our first clue that the exponential model will not be a good fit to this data.
+to fit the Weibull model and look at the posterior distributions of the shape
+parameters and determine if one is a reasonable value.  Looking at the plot in
+figure 2 below from the Weibull model fit with the JLTV data, we see that one is
+not a reasonable value for any of the 20 failure modes.  This is our first clue
+that the exponential model will not be a good fit to this data.
 
-% this plot will be remade without title and smaller xlim
-\begin{figure}
+\begin{figure}[h]
   \centering
-      \includegraphics[width=6cm, height=5cm]{betaPostPlot}
+      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
   \caption{Posterior Plots of Shape Parameter}
@@
 This is not a surprising result, because the exponential model assumes constant
-failure rate.  For most vehicle components we would expect the failure rate to
+failure rate.  For most vehicle failure modes we would expect the failure rate to
 increase as the distance driven grows larger, and this corresponds with a shape
@@
 The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
-value is a unitless measure with lower values indicating a better fit to the
+value is a unit-less measure with lower values indicating a better fit to the
 data.  In the table below we show the DIC results for the different distribution
@@
 % need to recheck these numbers %
+\begin{table}[h]
+\centering
 \begin{tabular}{|l|l|r|}
@@
 \end{tabular}
+\end{table}
 
@@
 than the exponential, but in general information criteria comparisons do not
-tell us if the model is truely a good representation of the underlying process.
-The last method we will present is called posterior predictive checking
-~\cite{ref3}. Here we are given important features of the data. In the JLTV case
-we were interested in the total failure counts for each phase and the number of
-time the miles between failures was less than 140.  We then used the final model
-to simulate 5,000 new datasets. We then plot histograms for each of the 8
-vehicles for all 3 phases.  In Figure 1 are examples of the histograms produced,
-with the line showing where the value of the true dataset fell.  For this method
-we don’t expect all of the true values to fall in the center of the
-distribution.  Values in the tales are to be expected in a random processes like
-this one.  We will only be concerned if we find true values falling in the
-extreme tails or if we see a common bias to the high or low side of the
-distributions.
+tell us if the model is truly a good representation of the underlying process.
+The last method we present is called posterior predictive checking ~\cite{ref3}.
+Here we are given important features of the data that we would expect to see if
+the experiment was repeted.  In the JLTV case one feature we were interested in
+was the number of miles between failure observations that were less than 140
+miles.  We then used the final models to simulate 5,000 new datasets for
+vehicles tested over the same number of miles for each of the three phases. We
+then plot the resulting distributions for each of the 8 vehicles for all 3
+phases.  In Figure 3 are two examples of the boxplots produced, one from the
+exponential model (left) and one from the Weibull model (right), with the dashed
+line showing where the value from the observed dataset fell.  For this method we
+don’t expect all of the true values to fall in the center of the distribution.
+Some values in the tales are to be expected in a random processes like this one,
+but when we see many observations in the tails, as we do with the exponential,
+we should consider other modeling options.
 
-% these plots will be redone and I plan to add a contrasting version of them
-% using the exponential model
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
   \centering
-  \includegraphics[width=.4\linewidth]{Rplot1}
-  \caption{Plot 1}
+  \includegraphics[width=.8\linewidth]{PPExpo}
+  %\caption{}
   \label{fig:sub1}
@@
   \centering
-  \includegraphics[width=.4\linewidth]{Rplot2}
-  \caption{Plot 2}
+  \includegraphics[width=.8\linewidth]{PPWeibull}
+  %\caption{}
   \label{fig:sub2}
 \end{subfigure}
-\caption{Posterior Predictive Plots}
+\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
 \label{fig:test}
@@
 \subsubsection{Classical Approach}
-In the frequentist (classical) version we will use two criteria in determining
+In the frequentest (classical) version we will use two criteria in determining
 the test plans. The \emph{producer's risk}, defined as the probability of
@@
 we assume a distributional form that defines the relationship between the number
-of system failyres $W(t)$ and the reliability $\pi$.  Then we can simply find
+of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
 the combinations of these probabilities by simultaneously solving these two
@@
 (\lambda_i t)^{\gamma_i}$.  Because of this, using our previous approach leads to
-an unpleasant series of integals with parameters in the bounds.  Thankfully we
+an unpleasant series of integrals with parameters in the bounds.  Thankfully we
 can once again lean on Monte Carlo integration and the expression for the
@@
 experts  we will define the producer's target or ARL as the expected number of
-failures in the first 140 miles to be less  than 2, and the consumer's minimum
+failures in the first 140 miles to be less  than 3, and the consumer's minimum
 requirements or RRL as the expected number of failures in  the first 80 miles to
-greater than 2.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
+greater than 3.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
 $\beta$ respectively, but in practice these values should always be set based on
@@
 \\
-Consumer Risk : $ P(80^\beta (\lambda_S) \geq 2 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
-Producer Risk : $ P(140^\beta (\lambda_S) \leq 2 \; \vert \; \text{Test Is Failed}) \leq 0.05 $
+Consumer Risk : $ P(80^\beta (\lambda_S) \geq 3 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
+Producer Risk : $ P(140^\beta (\lambda_S) \leq 3 \; \vert \; \text{Test Is Failed}) \leq 0.05 $
 
@@
 
+\begin{table}[h]
+\center
 \begin{tabular}{|l|l|r|}
@@
 \hline
-1   & 5,300      \\
-2   & 6,500      \\
-3   & 7,800      \\
-4   & 11,100     \\
-5   & 13,100     \\
+0   & 5,500      \\
+1   & 10,100      \\
+2   & 17,900      \\
+3   & 30,800     \\
+4   & 51,200     \\
 \hline
 \end{tabular}
+\end{table}
 

### 2017-12-15 paperDraft3.tex
getting close

@@
 
-\author{Kassandra M.\ Fronczyk\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{kfronczy@ida.org} \and
+\author{Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
 Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
@@
 
-The methodology section is organized as follows... section 3.1...
+The methodology section is organized as follows.  Section 3.1 describes the
+reliability modeling process, breaking it down into five subsections.  First, we
+introduce the general structure we will be using along and how to account for
+the correction period between phases.  Then we move onto distributional
+assumptions and model diagnostics which we illistrate with the JLTV case study
+data.  In section 3.2 we discuss methods of designing next stage test plans.
+First we outline the traditional approaches, then we walk through a Bayesian
+approach that allows the practitioner to incorperating the models developed from
+section 3.1 with the hopes of reducing testing resources required while still
+minimizing producer and consumer risks.
 
@@
 come from an exponential distribution the overall failure rate across all
-failure modes can be easily calculated by $\sum_{j}\lambda_{j}$.  The
-exponential distribution is commonly used in reliability analysis because of its
-convenience, but as we will discuss in later sections it can be unrealistic in
-many real-world situations.
+failure modes can be easily calculated by $\sum_{j}\lambda_{j}$ to give us the
+system failure rate.  The exponential distribution is commonly used in
+reliability analysis because of its convenience, but as we will discuss in later
+sections it can be unrealistic in many real-world situations.
 
@@
 After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
-these revisions, the PM2 reliability growth model \cite{EH06} is often used.
+these revisions, the PM2 reliability growth model \cite{ref2} is often used.
 This model explicitly captures testing phases, choices about which failure modes
@@
 rarely justifiable.  It has been well documented the issues that can arise when
-this assumption is violated ~\cite{ref2}.  Thus we will also consider the same
+this assumption is violated ~\cite{ref3}.  Thus we will also consider the same
 hierarchical model structure while using the Weibull distribution.  Now we
@@
 to reliability at both the component and system level.  In this study our main
-quantity of interest is expected miles to  failure.  In the following figure we
-have box plots showing the posterior distributions of  the expected miles to
-failure for one of the vehicle types for each of the three phases, first using
-the exponential model and second using the more general Weibull model.
+quantity of interest is expected miles to  failure.  In figure 1 we have box
+plots and summary statistics from the posterior distributions of the expected
+miles to failure for one of the vehicle types for each of the three phases,
+first using the exponential model and second using the more general Weibull
+model.
 
-% going to add a table that will have the posterior means and 90% credible
-% interval limits
-\begin{figure}[h]
+\begin{figure}[h!]
+\centering
+\begin{subfigure}{.5\textwidth}
   \centering
       \includegraphics[width=9cm, height=7cm]{Boxplots}
+  % \caption{Comparing EMTF for Different Models}
+  %\label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \center
+  \begin{tabular}{|c|c|c|c|c|}
+  \multicolumn{5}{c}{\textbf{Summary Statistics}} \\
+  \cline{1-5}
+  Model & Phase & Mean & 90\% CI Low & 90\% CI Up \\
+  \hline
+  Expo & P1   & 129.98   & 110.22 &  152.23 \\
+  Expo & P2   & 98.44  & 89.00 &  108.38  \\
+  Expo & P3   & 135.89   & 117.78 &  155.45 \\
+  Weibull & P1   & 169.96  & 116.95 & 236.16 \\
+  Weibull & P2   & 135.24   & 104.89 & 167.48 \\
+  Weibull & P3   & 175.51   & 138.87 & 214.23 \\
+  \hline
+  \end{tabular}
+  %\label{fig:sub2}
+\end{subfigure}
 \caption{Comparing EMTF for Different Models}
+\label{fig:test}
 \end{figure}
 
-Figure 1 show that the posterior distributions from the Weibull model have a
-good amount more spread than the exponential.  This is somewhat expected given
-the Weibull model is estimating two model parameters to the exponentials one,
-but what is concerning is that the center of the distributions is also quite
-different between the two models.  All of the Weibull EMTF posterior means
-are higher than the exponentials.  This is the first sign that the exponential
-model may not be a good fit to the data.
+You can see the posterior distributions from the Weibull model have a good
+amount more spread than the exponential.  This is somewhat expected given the
+Weibull model is estimating two model parameters to the exponentials one, but
+what is concerning is that the center of the distributions is also quite
+different between the two models.  All of the Weibull EMTF posterior means are
+higher than the exponentials.  This is the first sign that the exponential model
+may not be a good fit to the data.
 
@@
 tell us if the model is truly a good representation of the underlying process.
-The last method we present is called posterior predictive checking ~\cite{ref3}.
+The last method we present is called posterior predictive checking ~\cite{ref4}.
 Here we are given important features of the data that we would expect to see if
@@
   %\caption{}
-  \label{fig:sub1}
+  %\label{fig:sub1}
 \end{subfigure}%
@@
   %\caption{}
-  \label{fig:sub2}
+  %\label{fig:sub2}
 \end{subfigure}
 \caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
-\label{fig:test}
+%\label{fig:test}
 \end{figure}
@@
 requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref4}. Bayesian \emph{reliability assurance
+as discussed by Hamada et al. ~\cite{ref5}. Bayesian \emph{reliability assurance
 tests} are used to ensure that the reliability of an item meets or exceeds a
 specified requirement with a desired probability. Meeker and Escobar
-~\cite{ME04} established the difference between this and the more traditional
+~\cite{ref6} established the difference between this and the more traditional
 \emph{reliability demonstration test}.  The difference being that the assurance
@@
 the test plans. The \emph{producer's risk}, defined as the probability of
-failing the test when $\pi = \pi_0$, and the \emph{consumer's risk}, defined as
-the probability of passing the test when $\pi = \pi_1$.  Suppose that we specify
-a maximum value, $\alpha$, of the producer's risk and a maximum value, $\beta$,
-of the consumer's risk. For test planning, these criteria become
+failing the test under the null hypothesis $\pi = \pi_0$, and the
+\emph{consumer's risk}, defined as the probability of passing the test under an
+alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
+$\alpha$, of the producer's risk and a maximum value, $\beta$, of the consumer's
+risk. For test planning, these criteria become
 $$
@@
 \center
-\begin{tabular}{|l|l|r|}
+\begin{tabular}{|c|c|}
 \multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
@@
 
-% This part should be expanded quite a bit and will extend into the discussion
-% section.
-It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
-unrealisitc values there can be situations where no combinations of failures
-allowed and test miles required will satisfy these probability statements.  In
-this paper we have focused on test plans for single units, but this methodology
-can be extended to find test plans that allow for a changing number of testing
-units.  In this case you would find combinations of failures allowed and test
-miles required and number of vehicles tested that satisfy the risk requirements.
-More details and examples of this can be found in the assurance testing section
-of Hamada et al. ~\cite{ref4}
+These results alone do not provide much insite into how well the method is
+performing. A natural comparison would be with the frequentest test plan in this
+setting.  In general  we warn against this comparison because the test plan
+probability constrants for each  method are asking different questions.  The
+frequentest plan controls the error rates  under two different assumed settings.
+On the other hand, the Bayesian plan puts constrants  on the error when the test
+is passed and failed.  We would argue that in most settings  the Bayesian plan
+controls for the error the practitioner cares about.  In this case there are no
+reasonable combinations of allowed failures and required test miles  that
+satisfy both producer's and consumer's risk probability statements in the
+frequentest test plan.
+Both test planning approaches rely heavily on setting reasonable values for
+$\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealisitc
+values both proceedures can can result in no plan that satisfies the probability
+statements.  In this paper we have focused on test plans for single units, but
+th the assurance testing methodology can be extended to find test plans that
+allow for a changing number of testing units.  In this case you would find
+combinations of failures allowed and test miles required and number of vehicles
+tested that satisfy the risk requirements. More details and examples of this can
+be found in the assurance testing section of Hamada et al. ~\cite{ref5}
 
 \subsection{Discussion}
+The JLTV case study results provide indications that our model is successfully
+capturing the failure rates across failure modes, inferring logical fix
+effectiveness factor distributions, and providing reliability estimates that can
+be leveraged for future test planning. In the traditional analysis, we do not
+typically look at failure rates of the failure modes, nor would we be able to
+leverage the commonalities across vehicles. The proposed modeling framework
+overcomes these limitations and allows for more realistic reliability estimates
+for vehicles with no observed failures. Additionally, our data-driven approach
+for reliability growth improves on the current growth models being used in the
+DoD, which are based solely on fixed quantities set by management.
+
+While our basic approach provides reasonable initial inferences, there are
+several extensions to incorporate. For example, reliability estimates for
+vehicles with no observed failures are sensible; however, we should leverage
+more information across vehicles. Because the correlations induced by our
+current model are fairly low, potential methods for inducing more correlation
+between the vehicles in the related failure modes are being investigated. We
+also need to look more closely at the intra-phase repair assumptions.  Appling
+repairable system  methodology in the modeling and reliability assesment stage
+could be a good approach, but this could  add a great deal of complexity to the
+assurance planning stage.
 
@@
 \begin{thebibliography}{99}
-\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of
-system reliability availability maintainability - A primer; Third Edition
-(1982).
-\bibitem{ref2} National Research Council. Statistics, Testing, and Defense
+\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
+\bibitem{ref2} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability
+growth planning based on failure mode discovery and correction using AMSAA
+projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
+Maintainability Symposium} (2006).
+\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
 Acquisition: Background Papers. \textit{National Academies Press} (1999).
-\bibitem{ref3} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
+\bibitem{ref4} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
 predictive assessment of model fitness via realized discrepancies."
 \textit{Statistica sinica} 733-760 (1996).
-\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+\bibitem{ref5} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
 Bayesian Reliability. Springer (2008).
-\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\
-Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology
-and Quantitative Management} 1, 1-25 (2004). \bibitem{HWWGM13} M.\ S.\ Hamada,
-A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz. Bayesian
-binomial assurance tests for system reliability using component data.
-\textit{Journal of Quality Technology} 46, 24-32 (2014). \bibitem{JGHR03} V.\
-E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese. A hierarchical
-model for estimating the reliability of complex systems. In Bayesian Statistics,
-Vol. 7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\
-Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University
-Press (2003). \bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese,
-T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
-for combining multilevel failure information in fault tree quantification and
-optimal follow-on resource allocation. \textit{Reliability Engineering and
-System Safety} 86, 397-405 (2004). \bibitem{EH06} P.\ M.\ Ellner and J.\ B.\
-Hall, An approach to reliability growth planning based on failure mode discovery
-and correction using AMSAA projection methodology. \textit{IEEE Proceedings of
-the Annual Reliability and Maintainability Symposium} (2006).
+\bibitem{ref6} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
+dimension of quailty. \textit{Quality Technology and Quantitative Management} 1,
+1-25 (2004).
 \end{thebibliography}
@@
 
+Full conditionals for Gibbs sampling:
 \begin{align*}

### 2017-12-16 paperDraft3.tex
draft sent to Wilson

@@
 In this paper, we propose an alternative approach using a Bayesian hierarchical
-model.  We will begin by introducing a hierarchical structure that models the
-relationships in the data across all test phases and incorporates known
+model.  The methodology section is organized as follows.  In section 3.1 we
+begin by introducing a general structure that models the relationships in the
+data across all test phases while accounting for CAPs and incorporates known
 similarities between vehicle failure modes.  Next, we will consider different
-distributional assumptions and their implications.  We will also
-discuss model diagnostics to consider when choosing a final model. Then we will
-use the JLTV data to illustrate this process and discuss system reliability
-results. This will lead us into the next section on using these results to
-improve the planning of future test.
-
-In this reliability setting we are analysing time to failure data measured in
-miles for a multiple component system with the primary interest in the system
-failure rate and future failure counts.  The most common models used in this
-failure rate analysis are lifetime distributions and the most common for failure
-count analysis is the \emph{Poisson process} counting model.  We will utilize
-both and the relationships between them.
-
-The methodology section is organized as follows.  Section 3.1 describes the
-reliability modeling process, breaking it down into five subsections.  First, we
-introduce the general structure we will be using along and how to account for
-the correction period between phases.  Then we move onto distributional
-assumptions and model diagnostics which we illistrate with the JLTV case study
-data.  In section 3.2 we discuss methods of designing next stage test plans.
+distributional assumptions and their implications.  Using the JLTV case study we
+will illustrate the process of model selection using three different diagnostic
+checks.  In section 3.2 we discuss methods of designing next stage test plans.
 First we outline the traditional approaches, then we walk through a Bayesian
-approach that allows the practitioner to incorperating the models developed from
+approach that allows the practitioner to incorporating the models developed from
 section 3.1 with the hopes of reducing testing resources required while still
 minimizing producer and consumer risks.
+
+In this reliability setting we are analyzing time of failure data measured in
+miles for a multiple component system with the primary objective being
+assessment of the system failure rate and prediction of future failure counts.
+The most common models used in this failure rate analysis are lifetime
+distributions and the most common for failure count analysis is the
+\emph{Poisson process} family of counting model.  We will utilize both and
+specifically the relationships between them in planning future test.
 
@@
 a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
-t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
-testing phase. In each phase of testing, we assume the vehicle miles between
-failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime distribution with
-an unknown set of parameters that include a rate parameter.  For the first phase
-the rate parameter for vehicle $i$ and failure mode $j$ will be denoted as
-$\lambda_{ij}$.  Then for the next stage we will use the same $\lambda_{ij}$ but
-add a multiplicative correction parameter $\rho_{1,j}$ that represents the
-change in this rate due to the CAP.  This proceedure is then repeated for each
-subsequent stage.  The correction parameter will be discussed more in the next
-section but the general model is as follows,
+t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the censored
+observation at the end the testing phase. In each phase of testing, we assume
+the vehicle miles between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a
+lifetime distribution $f(\cdot)$, with an unknown set of parameters that include
+a rate parameter.  For the first phase the rate parameter for vehicle $i$ and
+failure mode $j$ will be denoted as $\lambda_{ij}$.  Then for the next stage we
+will use the same $\lambda_{ij}$ but add a multiplicative correction parameter
+$\rho_{j}^{P2}$ that represents the change in this rate due to the CAP.  This
+procedure is then repeated for each subsequent stage.  The correction parameter
+will be discussed more in the next section but the general model is as follows,
 \begin{align*}
@@
 where $v$ represents the number of vehicles, $s$ is the number of failure modes,
-and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The
-number of failure modes is assumed fixed and known \textit{a priori}.
+and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.
 
-For this model we will assume a prior distribution on failure rate parameter
+% The number of failure modes is assumed fixed and known \textit{a priori}.
+
+For the model we assume a prior distribution on failure rate parameter
 $\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
-considered to be common across vehicles or related but not identical. For the
-related failure modes, we place a prior distribution on the collection of
-$\lambda_{ij}$; in other words, we assume each vehicle has a distinct failure
-rate in failure mode $j$ but they arise from a common distribution.  If failure
-mode $j$ is considered common across vehicles, the collection of failure rates
-is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As with the
-related failure modes, a prior distribution is placed on the single failure
-rate. The prior distributions are independent across failure mode, and can
-potentially have different hyperparameters.
-
-% not sure we need this paragraph %
-The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
-each of the vehicles for failure modes that are related.  We are assuming the
-vehicles are conditionally independent, if we also assume the miles at failure
-come from an exponential distribution the overall failure rate across all
-failure modes can be easily calculated by $\sum_{j}\lambda_{j}$ to give us the
-system failure rate.  The exponential distribution is commonly used in
-reliability analysis because of its convenience, but as we will discuss in later
-sections it can be unrealistic in many real-world situations.
+considered to be common across vehicles or related but not identical.  If
+failure mode $j$ is considered common across vehicles we will assume there is a
+single failure rate $\lambda_j$ that is shared by all eight vehicles with a
+prior distribution that has positive support.  In the JLTV study we will use a
+non-informative gamma distribution.  For failure modes that are considered
+related across vehicles but not expected to be exactly the same, we place a
+prior distribution on the collection of $\lambda_{ij}$; in other words, we
+assume each of the vehicles has a distinct failure rate for failure mode $j$ but
+they arise from a common distribution.  This is the common Bayesian hierarchical
+modeling structure, where we then place  hyperprior distributions on the shared
+distribution's parameters.  In the JLTV study we use a gamma distribution with
+non-informative hyperpriors for all related failure modes.  Many times in
+practice  it is difficult to know ahead of time if individual components should
+be modeled  as common or related.  In the JLTV study we fit models for each
+component with both model structures and used diagnostic tools  that are
+discussed in a later section to make our final decision.
 
@@
 between phases two and three.  With this structure we can use the posterior
-distributions of the correction parameters to make infrence on the effectiveness
+distributions of the correction parameters to make inference on the effectiveness
 of the repairs and the join posterior distributions to evaluate the overall
@@
 modeling because of its desirable math mathematical properties and simple
-interpretations.  One of these properties is that the hazard rate is constant.
-For the JLTV, setting this would assume that a given component is equally likely
-to fail in the first mile of testing as it is in the thousandth.  This may be
-reasonable for some reliability settings, but in most setting we observe either
-a decreasing hazard rate where failures are likely to occur early in testing
-but less likely as the test goes on, or increasing hazard rate where we see the
-system wear down as the test goes on.
+interpretations.  One of the convenient properties, because we are assuming
+independence between failure modes, is the overall system failures also follow
+an exponential distribution with a system failure rate $\lambda_S =
+\sum_{j}\lambda_{j}$.  A second, possibly less attractive property, is that the
+hazard rate is constant over miles.  For the JLTV, setting this would assume that a given
+component is equally likely to fail in the first mile of testing as it is in the
+thousandth.  This may be reasonable for some reliability settings, but in most
+setting we observe either a decreasing hazard rate where failures are likely to
+occur early in testing but less likely as the test goes on, or increasing hazard
+rate where we see the system wear down as the test progresses.
 
@@
 rarely justifiable.  It has been well documented the issues that can arise when
-this assumption is violated ~\cite{ref3}.  Thus we will also consider the same
-hierarchical model structure while using the Weibull distribution.  Now we
-assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
-distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
-probability density function,
+this assumption is violated ~\cite{ref3}.  Therefore we will also consider more
+flexible distributions when analyzing the data.  In our analysis of the JLTV
+data we fit the same hierarchical model structure using the Weibull as our
+lifetime distribution $f(\cdot)$.  Now we assume that the failure mileage
+$t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
+parameter $\lambda$ and shape parameter $\gamma$, with probability density
+function,
 \begin{equation*}
@@
 \end{equation*}
-The Weibull distribution is a more flexible model with both a rate parameter
-$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
-case of the Weibull, when $\gamma = 1$.  You should notice here we are now
-modeling the actual failure mileage $t_{ijk}$ instead of the miles between
-failures $y_{ijk}$.  This means we are treating all intra-test repairs as "bad
-as old".  We could have continued with the miles between failures and assumed
-"good as new" repairs, but "bad as old" modeling will be more convenient for
-developing assurance test plans in later sections.  This distinction is
-important in the Weibull case because the failure rate is not constant in time.
-In practice the decision on intra-test repair assumptions should be made based
-on the application.  In many cases repairs should be treated as somewhere
-between "good as new" and "bad as old".  This requires more complex modeling
-that is beyond the scope of this paper.
+The exponential is a special case of the Weibull, when $\gamma = 1$.  You should
+notice here we are now modeling the actual failure mileage $t_{ijk}$ instead of
+the miles between failures $y_{ijk}$.  This implies the "bad as old" assumption
+for intra-test repairs.  We could have continued with the miles between failures
+and assumed "good as new" repairs, but "bad as old" modeling will be more
+convenient for developing assurance test plans in later sections.  This
+distinction is important in the Weibull case because the failure rate is not
+constant in time. In practice the decision on intra-test repair assumptions
+should be made based on the application.  In many cases repairs should be
+treated as somewhere between "good as new" and "bad as old".  This requires more
+complex modeling that is beyond the scope of this paper.
 
@@
 \subsubsection{JLTV Reliability}
-So far we have discussed a number of different models and the assumptions that
-accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
-Then we can use the posterior distributions of the systems parameters to
+We have discussed different models structures and distributional assumptions
+that accompany them.  Using McMC we fit each of these models to the JLTV
+dataset.\footnote{The likelihoods and sampling distributions are available in the
+appendix.} Then we use the posterior distributions of the systems parameters to
 estimate reliability-related quantities of interest for each of the eight
 vehicle types.  We are able to look at a number of different statistics related
-to reliability at both the component and system level.  In this study our main
-quantity of interest is expected miles to  failure.  In figure 1 we have box
+to reliability at both the component and system level.  In this study, one
+quantity of interest is expected miles to failure(EMTF).  In figure 1 we have box
 plots and summary statistics from the posterior distributions of the expected
@@
 
-You can see the posterior distributions from the Weibull model have a good
-amount more spread than the exponential.  This is somewhat expected given the
-Weibull model is estimating two model parameters to the exponentials one, but
-what is concerning is that the center of the distributions is also quite
-different between the two models.  All of the Weibull EMTF posterior means are
-higher than the exponentials.  This is the first sign that the exponential model
-may not be a good fit to the data.
+You can see the posterior EMTF distributions from the Weibull model have more
+spread than the exponential.  This is generally expected, given the Weibull
+model is estimating two model parameters to the exponentials one, but what is
+concerning is that the center of the distributions is also quite different
+between the two models.  The Weibull EMTF posterior means are consistently
+larger than the exponentials.  We saw this across all eight vehicle types.  This
+was the first indication that the exponential model may not be a good fit to the
+data.
 
@@
 As seen in the last section with the JLTV data, the decision of which model to
-use can have a drastic impact on reliability assessment and future test
-planning.  We will now look at a few  goodness-of-fit methods that can be used
-to help in this decision.  The first model selection question we will explore is
-the parametric form, exponential versus Weibull.  In statistical modeling we
-often face the trade-off between fit and interpretability, and this situation is
-no different. Because the Weibull is a more flexible model, it will always, in a
-sense, fit the data better, but this comes at a price.  The exponential's
-convenient form makes both computation and interpretation straightforward.  When
-the Weibull's shape parameter is introduced this advantage is lost.  Thus, when
-the overall fit is close to the same between the exponential and the Weibull we
-will default to using the exponential.
+use can have a drastic impact on reliability assessment.  We will now look at a
+few  goodness-of-fit methods that can be used to help in this decision.  The
+first model selection question we will explore is the parametric form,
+exponential versus Weibull.  This an example of the classic statistical modeling
+the trade-off between fit and interpretability.  Because the Weibull is a more
+flexible model it will always, in a sense, fit the data better, but this comes
+at a price.  The exponentials convenient form makes both computation and
+interpretation straightforward.  When the Weibull's shape parameter is
+introduced this advantage is lost.  Thus, when the overall fit is close to the
+same between the exponential and the Weibull we will default to using the
+exponential.
 
-The first check we used to decide between the exponential and Weibull models is
+The first check we used in decide between the exponential and Weibull models is
 to fit the Weibull model and look at the posterior distributions of the shape
 parameters and determine if one is a reasonable value.  Looking at the plot in
-figure 2 below from the Weibull model fit with the JLTV data, we see that one is
-not a reasonable value for any of the 20 failure modes.  This is our first clue
-that the exponential model will not be a good fit to this data.
+figure 2 from the Weibull model fit with the JLTV data, we see that one is
+not a reasonable value for any of the failure modes.  This is another clue
+that the exponential model is not be a good fit to this data.
 
@@
       \includegraphics[width=8cm, height=7cm]{shapePostPlot}
-  \caption{Posterior Plots of Shape Parameter}
+  \caption{Posterior Plots of Weibull Shape Parameter}
 \end{figure}
 
-This is not a surprising result, because the exponential model assumes constant
-failure rate.  For most vehicle failure modes we would expect the failure rate to
-increase as the distance driven grows larger, and this corresponds with a shape
-parameter between zero and one.  On the other hand, when the shape parameter is
-larger than 1, the failure rate will decrease with time/distance.
-
-Now a more formal diagnostic tool, the Deviance information criterion (DIC).
-This is a popular method for comparing the goodness of fit of multiple models.
-The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
-value is a unit-less measure with lower values indicating a better fit to the
-data.  In the table below we show the DIC results for the different distribution
-and structure combinations, we considered with the JLTV dataset.
+Now a more formal diagnostic tool, the Deviance information criterion (DIC)
+~\cite{ref4}. This is a popular method for comparing the goodness of fit of
+multiple models. The DIC method includes a penalty term that grows with the
+numbers of unknown parameters in the model.  The DIC value is a unit-less
+measure with lower values indicating a better fit to the data.  In the table
+below we show the DIC results for the different distribution and structure
+combinations, we considered with the JLTV dataset.
 
@@
 \end{tabular}
+\caption{JLTV DIC Results}
+\label{table:ta}
 \end{table}
 
-Here we have shown that the hierarchical Weibull model fits the data much better
-than the exponential, but in general information criteria comparisons do not
-tell us if the model is truly a good representation of the underlying process.
-The last method we present is called posterior predictive checking ~\cite{ref4}.
-Here we are given important features of the data that we would expect to see if
-the experiment was repeted.  In the JLTV case one feature we were interested in
-was the number of miles between failure observations that were less than 140
-miles.  We then used the final models to simulate 5,000 new datasets for
-vehicles tested over the same number of miles for each of the three phases. We
-then plot the resulting distributions for each of the 8 vehicles for all 3
-phases.  In Figure 3 are two examples of the boxplots produced, one from the
-exponential model (left) and one from the Weibull model (right), with the dashed
-line showing where the value from the observed dataset fell.  For this method we
-don’t expect all of the true values to fall in the center of the distribution.
-Some values in the tales are to be expected in a random processes like this one,
-but when we see many observations in the tails, as we do with the exponential,
-we should consider other modeling options.
+The results in table 1 shown that the hierarchical Weibull model fits the data
+much better than the exponential, but in general information criteria
+comparisons do not tell us if the model is truly a good representation of the
+underlying process. The last model diagnostics method we present is called
+posterior predictive checking ~\cite{ref5}.  Here we start with important
+features of the data that we would expect to see if the experiment was repeated,
+these are usually provided by practitioner with knowledge about the random
+process being studied. In the JLTV case one feature we were interested in was
+the number of miles between failure observations that were less than 140 miles.
+We then used the final models to simulate 5,000 new datasets for vehicles tested
+over the same number of miles for each of the three phases. We then plot the
+resulting distributions for each of the 8 vehicles for all 3 phases.  In Figure
+3 are two examples of the boxplots produced, one from the exponential model
+(left) and one from the Weibull model (right), with the dashed line showing
+where the value from the observed dataset fell.  For this method we don’t expect
+all of the true values to fall in the center of the distribution. Some values in
+the tales are to be expected in a random processes like this one, but when we
+see many observations in the tails, as we do with the exponential, we should
+consider other modeling options.
 
@@
 \subsection{Assurance Test Planning}
-In this section, we will use the reliability models fit in section two section
-to develop a plan for future testing.  Here the objective is to demonstrate that
-at a desired level of confidence, the system will meet or exceed a specified
+In this section, we will use the reliability models fit in section two to
+develop a plan for future testing.  Here the objective is to demonstrate, at
+a desired level of confidence, that the system will meet or exceed a specified
 requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref5}. Bayesian \emph{reliability assurance
+as discussed by Hamada et al. ~\cite{ref6}. Bayesian \emph{reliability assurance
 tests} are used to ensure that the reliability of an item meets or exceeds a
 specified requirement with a desired probability. Meeker and Escobar
-~\cite{ref6} established the difference between this and the more traditional
+~\cite{ref7} established the difference between this and the more traditional
 \emph{reliability demonstration test}.  The difference being that the assurance
@@
 
-In both test planning methods we are interested in controlling error rates while
-minimizing the resources required for testing.  In the DoD acquisition process,
-the error rates will be referenced in terms of risk. \emph{Consumer risk} which
-considers the event of purchasing a product that does not meet reliability
-requirements.  \emph{Producer risk} which considers the event of a product with
-acceptable reliability failing a given test and not being considered for
-purchase.  Introducing the notation for this section, in the JLTV case study, we
-will be determining how many miles on test $T$, are required and how many system
-failures to allow $c$, before the product is considered unacceptable.  We will
-define $W(t)$ as a random variable that represents the total number of system
-failures after $t$ miles.  We will let $\pi$ denote some quantity of interest
-that is related to system reliability at a given time. It is common to base both
-classical and Bayesian test plans on two specified levels of $\pi$: $\pi_0$, an
-\emph{acceptable reliability level} (ARL), and $\pi_1$, a \emph{rejectable
-reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although the precise
-definition of ARL and RRL differ between the classical and Bayesian test
-criteria, we use them in an equivalent way.
+In most test planning settings we are interested in controlling error rates
+while minimizing the resources required for testing.  In the DoD acquisition
+process, the error rates are referenced in terms of risk. \emph{Consumer
+risk} which considers the event of purchasing a product that does not meet
+reliability requirements.  \emph{Producer risk} which considers the event of a
+product with acceptable reliability failing a given test and not being
+considered for purchase.  Introducing the notation for this section, in the JLTV
+case study, we will be determining how many miles on test $T$, are required and
+how many system failures to allow $c$, before the product is considered
+unacceptable.  We will define $W(t)$ as a random variable that represents the
+total number of system failures after $t$ miles.  We will let $\pi$ denote the
+quantity of interest that is related to system reliability at a given time. It
+is common to base both classical and Bayesian test plans on two specified levels
+of $\pi$: $\pi_0$, an \emph{acceptable reliability level} (ARL), and $\pi_1$, a
+\emph{rejectable reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although
+the precise definition of ARL and RRL differ between the classical and Bayesian
+test criteria, we use them in an equivalent way.
 
 \subsubsection{Classical Approach}
-In the frequentest (classical) version we will use two criteria in determining
-the test plans. The \emph{producer's risk}, defined as the probability of
+In the frequentest (classical) test planning setting the risk criteria
+are as follows. The \emph{producer's risk}, defined as the probability of
 failing the test under the null hypothesis $\pi = \pi_0$, and the
@@
 \text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
-this purely classical approach.
+this classical test planning approach.
 
 \subsubsection{Bayesian Approach}
-Traditional methods for determining the testing procedure only rely on
-distributional assumptions and/or asymptotic results. With a Bayesian approach we
+The classical methods for determining the testing procedure rely only on
+distributional assumptions or asymptotic results. With a Bayesian approach we
 incorporate the supplementary data from the previous testing phases with the
@@
 \pi_0$ given that we have observed more than $c$ failures. In the exponential
-case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
-Theorem, and assuming a maximum allowable posterior producer's risk $\alpha$, an
+case, if we let $\pi$ be the system failure rate $\lambda_S$ and $\pi_0$ be
+predetermined acceptable failure rate $\lambda_0$, then using Bayes' Theorem,
+and assuming a maximum allowable posterior producer's risk $\alpha$, an
 expression for the posterior producer's risk for the exponential test plan
@@
 is the probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert
-\text{Test Is Passed)}$. Notice that this is simply the posterior probability
-that $\pi \leq \pi_1$ given that we have observed no more than $c$ failures. In
-the exponential case, if we let $\pi$ be the system failure rate $\lambda_S$,
-then using Bayes' Theorem, and assuming a maximum allowable posterior consumer's
+\text{Test Is Passed)}$.  Now we let $\pi_1$ be a predetermined rejectable
+failure rate $\lambda_1$ and assuming a maximum allowable posterior consumer's
 risk $\beta$, an expression for the posterior producer's risk for the
@@
 failure count for a given failure mode does follow a nonhomogeneous Poisson
-process, $w(t)_i \sim \text{Poisson}( (\lambda_i t)^{\gamma_i} )$.  In this case
-we no longer have a closed form for the system failure rate $\lambda_S = \sum_i
-(\lambda_i t)^{\gamma_i}$.  Because of this, using our previous approach leads to
-an unpleasant series of integrals with parameters in the bounds.  Thankfully we
-can once again lean on Monte Carlo integration and the expression for the
-posterior producer's risk for the Weibull test plan $(T,c)$ simplifies to
+process, $w(t)_i \sim \text{Poisson}( \lambda_i t_i^{\gamma_i} )$.  The system
+failure counts then, for a given mileage $t$ become $W(t) \sim
+\text{Poisson}(\sum_i (\lambda_i t_i)^{\gamma_i})$.  In this case the acceptable
+and rejectable parameters $\pi_0$ and $\pi_1$ become quantities related to
+$\sum_i (\lambda_i t_i)^{\gamma_i}$.  This can lead to some unpleasant
+integration expression, but once again we can lean on Monte Carlo integration
+and our evaluation for the posterior producer's risk for the Weibull test plan
+$(T,c)$ becomes to
 $$
 \begin{aligned}
-	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
-	 \int_{\lambda_0}^{\infty} 1 - exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
-	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} 1 - exp(-
-	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
-	 &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\gamma^{(j)} \lambda_S^{(j)}
-	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
-	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})}
+	 P(\sum_i \lambda_i T^{\gamma_i} \geq \pi_0 \; \vert \; W = 0) &= \frac{
+	 \int_{\pi_0}^{\infty} 1 - exp(- \sum_i \gamma_i \lambda_i
+	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
+	 d\gamma_{1,...}} {\int_{0}^{\infty} 1 - exp(- \sum_i \gamma_i \lambda_i
+	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
+	 d\gamma_{1,...}} \\
+   &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\sum_i \gamma_i^{(j)}
+   \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\sum_i \lambda_i^{(j)}
+   T^{\gamma_i^{(j)}} \geq \pi_0)} {\sum_{j = 1}^{N} 1 - exp(- \sum_i
+   \gamma_i^{(j)} \lambda_i^{(j)} T^{\gamma_i^{(j)}})}
 \end{aligned}
@@
 \\
-Once again set c to be zero and used N posterior draws for both
-$\lambda_S^{(j)}$ and $\gamma^{(j)}$
+Where $\pi_0$ is some quantity related to the model parameters.  Again we set c
+to be zero and used N posterior draws for both $\lambda_i^{(j)}$ and
+$\gamma_i^{(j)}$.
 
-It should be noted that in this test planning process you would use the
-posterior distribution of $\lambda_S$ from the final developmental testing
-phase.  It is also common to incorporate a degradation factor to account for an
-expected reduction in reliability from the developmental phase to the
-operational phase.  In the Bayesian framework, this entails adding another
-multiplicative parameter to the rate parameter with an appropriate prior.   A
-10-30 percent reduction from the developmental phase to the operational phase is
-common in many DoD applications.
+It should be noted that in this test planning process the practitioner would use
+the posterior distribution of the rate parameters from the final developmental
+testing phase $\lambda_i\rho^{P2}\rho^{P3}$.  It is also common to incorporate a
+degradation factor to account for an expected reduction in reliability from the
+developmental phase to the operational phase.  In the Bayesian framework, this
+entails adding another multiplicative parameter to the rate parameter with an
+appropriate prior.   A 10-30 percent reduction from the developmental phase to
+the operational phase is common in many DoD applications.
 
@@
 \\
-Consumer Risk : $ P(80^\beta (\lambda_S) \geq 3 \; \vert \text{Test Is Passed}) \leq 0.1 $ \\
-Producer Risk : $ P(140^\beta (\lambda_S) \leq 3 \; \vert \; \text{Test Is Failed}) \leq 0.05 $
+$$
+\begin{aligned}
+  \text{Consumer Risk} &: P(\sum_i 80^{\gamma_i} \lambda_i \geq 3 \; \vert \text{Test Is Passed}) \leq 0.1  \\
+  \text{Producer Risk} &: P(\sum_i 140^{\gamma_i} \lambda_i \leq 3 \; \vert \; \text{Test Is Failed}) \leq 0.05
+\end{aligned}
+$$
 
 From here we are able to find combinations of failures allowed and test miles
-required that satisfy both risk requirements.  The table below show the
+required that satisfy both risk requirements.  Table 2 shows the
 resulting combinations for the JLTV data.
@@
 \end{tabular}
+\caption{JLTV Assurance Test Plan Results}
+\label{table:ta}
 \end{table}
 
-These results alone do not provide much insite into how well the method is
+These results alone do not provide much insight into how well the method is
 performing. A natural comparison would be with the frequentest test plan in this
 setting.  In general  we warn against this comparison because the test plan
-probability constrants for each  method are asking different questions.  The
+probability constraints for each  method are asking different questions.  The
 frequentest plan controls the error rates  under two different assumed settings.
-On the other hand, the Bayesian plan puts constrants  on the error when the test
+On the other hand, the Bayesian plan puts constraints  on the error when the test
 is passed and failed.  We would argue that in most settings  the Bayesian plan
@@
 Both test planning approaches rely heavily on setting reasonable values for
-$\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealisitc
-values both proceedures can can result in no plan that satisfies the probability
+$\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealistic
+values both procedures can can result in no plan that satisfies the probability
 statements.  In this paper we have focused on test plans for single units, but
@@
 tested that satisfy the risk requirements. More details and examples of this can
-be found in the assurance testing section of Hamada et al. ~\cite{ref5}
+be found in the assurance testing section of Hamada et al. ~\cite{ref6}
 
@@
 between the vehicles in the related failure modes are being investigated. We
-also need to look more closely at the intra-phase repair assumptions.  Appling
-repairable system  methodology in the modeling and reliability assesment stage
+also need to look more closely at the intra-phase repair assumptions.  Applying
+repairable system methodology in the modeling and reliability assessment stage
 could be a good approach, but this could  add a great deal of complexity to the
@@
 Acquisition: Background Papers. \textit{National Academies Press} (1999).
-\bibitem{ref4} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
-predictive assessment of model fitness via realized discrepancies."
+\bibitem{ref4} D.\ J.\ Spiegelhalter, N.\ Best, B.\ Carlin, and A.\ Van der
+Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
+Society}, Series B, 64: 583–640 (2002).
+\bibitem{ref5} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. Posterior
+predictive assessment of model fitness via realized discrepancies. (1996)
 \textit{Statistica sinica} 733-760 (1996).
-\bibitem{ref5} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+\bibitem{ref6} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
 Bayesian Reliability. Springer (2008).
-\bibitem{ref6} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
+\bibitem{ref7} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
 dimension of quailty. \textit{Quality Technology and Quantitative Management} 1,
@@
 
-\section{Appendix A1}
+\section{Appendix}
 \textbf{Exponential Model:}

### 2018-01-13 paperDraft3.tex
latest verstion

@@
 \documentclass[12pt]{article}
-\usepackage{amsmath, amssymb, fullpage}
+\usepackage{amsmath, amssymb, fullpage, bbm}
 \usepackage{array}
@@
 \usepackage{subcaption}
+\usepackage{setspace}
+\usepackage{color}
 %\usepackage{natbib}
@@
 
+%AGW: I just changed the margins and spacing to
+%make things easier to proofread. Uncomment the following and
+%comment out the doublespacing command below.
 % DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{-.3in}%
-\addtolength{\topmargin}{-.8in}%
+%\addtolength{\oddsidemargin}{-.5in}%
+%\addtolength{\evensidemargin}{-.5in}%
+%\addtolength{\textwidth}{1in}%
+%\addtolength{\textheight}{-.3in}%
+%\addtolength{\topmargin}{-.8in}%
 
@@
 
-\author{Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
-Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
-James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
-}
+\author{James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu} \and
+Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
+Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu}}
 \maketitle} \fi
@@
 \begin{abstract}
-    We use a Bayesian hierarchical model to assess the reliability of the Joint
-    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
+    We propose a Bayesian hierarchical model to assess the reliability of a family of vehicles, based on the development of the Joint
+    Light Tactical Vehicle (JLTV). The proposed
     model effectively combines information across three phases of testing and
@@
 \newpage
-
+\doublespacing
 \section{Introduction}
-Reliability is a high priority in the testing of military systems. A common
-interest is {\em reliability growth}, which tracks the change, and ideally
+Reliability is a high priority in the testing of defense systems. A common
+metric is {\em reliability growth}, which tracks the change, and ideally
 improvement, in the reliability of a system as it moves through testing phases
 and undergoes periodic corrective actions. Ideally, plans for future test events
-should be based on what is observed in previous testing.
+should be based on what has been observed in previous testing.
 
-In this paper, we look at combining information across multiple test phases with
+In this paper, we propose models for combining information across multiple test phases with
 the objective of planning a future test. When combining information, there is no
@@
 to ensure that they accurately reflect the data and the underlying physical
-processes. Our analysis is motivated by reliability data from the Joint Light
+processes. Our analysis is motivated by the reliability assessment of the Joint Light
 Tactical Vehicle (JLTV), which is a family of vehicles designed to replace
@@
 
-The JLTV has been through a series of test events as it has been developed.
+The JLTV was evaluated using multiple test events as it was developed.
 Engineering and Manufacturing Development (EMD) included three phases of
@@
 \section{Data}
-Eight vehicle prototypes were used for reliability, availability,
-and maintainability (RAM) testing. There were four two-seat utility vehicles,
+Eight vehicle prototypes were used for reliability, availability, and maintainability (RAM) testing of the JLTV. There were four two-seat utility vehicles,
 two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
 two-seat close combat weapons carrier. The close combat weapons carrier, one
-general purpose, and two utility vehicles were tested in Aberdeen, Maryland,
-where it is much colder in the winter months but the terrain is not as harsh,
-and the heavy weapons carrier, one general purpose, and two utility vehicles
-were tested in Yuma, Arizona, where it is warmer but with more challenging
-terrain, to attain testing in different environmental and terrain conditions.
-The vehicles were driven roughly 3000 to about 5000 miles in Phase 1, between
+general purpose, and two utility vehicles were tested in Aberdeen, Maryland, and the heavy weapons carrier, one general purpose, and two utility vehicles
+were tested in Yuma, Arizona.
+When comparing the test sites, the Maryland test site is much colder in the winter months but the terrain is not as harsh; in Arizona, it is warmer but with more challenging terrain.
+Using two test sites allows for the system to be tested under a broader range of environmental conditions.
+The vehicles were driven roughly 3000 to 5000 miles in Phase 1, between
 4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
-3.\footnote{The exact mileage has been altered to protect proprietary
-information.}
+3.\footnote{The exact mileage has been altered to protect proprietary information.
+\textcolor{red}{Any other changes to the data that we should describe?
+I think things were perhaps rescaled, constants added, etc.
+Let's be sure this isn't a JLTV assessment, but based on the JLTV assessment.}}
 
@@
 brakes and radios, will be common to all eight vehicles. Other failure modes
-will be related, but not identical, as with hydraulics, frame, and body.
-
-There are 1412 observed failures attributed to 26 failure modes recorded across
+will be related, but not identical, as with hydraulics, frame, and body. There are 1412 observed failures attributed to 26 failure modes recorded across
 all eight vehicles and all three test phases. In any given phase of test, every
@@
 \section{Methodology}
-
-\subsection{Modeling Reliability}
 A standard reliability analysis employed by the Department of Defense (DoD) test
 community considers each test phase independently and uses the exponential
-distribution to model the miles between failure for the system ~\cite{ref1}. The
-traditional analysis is overly simplistic, relies on correct modeling
-assumptions and ignores valuable information learned about the individual
-vehicles and their failure modes.
+distribution to model the miles between failure for the system ~\cite{ref1}. For many situations, including our example, this
+traditional analysis is overly simplistic, relying on incorrect modeling assumptions and ignoring valuable information learned about the individual vehicles and their failure modes.
 
-In this paper, we propose an alternative approach using a Bayesian hierarchical
-model.  The methodology section is organized as follows.  In section 3.1 we
-begin by introducing a general structure that models the relationships in the
-data across all test phases while accounting for CAPs and incorporates known
+We propose an alternative approach using a Bayesian hierarchical
+model.  The methodology section is organized as follows.  In Section~\ref{modrel}, we introduce a general structure that models the relationships in the
+data across all test phases, while accounting for CAPs, and incorporates known
 similarities between vehicle failure modes.  Next, we will consider different
@@
 will illustrate the process of model selection using three different diagnostic
-checks.  In section 3.2 we discuss methods of designing next stage test plans.
-First we outline the traditional approaches, then we walk through a Bayesian
+checks.  In Section~\ref{atp} we discuss methods of designing next stage test plans.
+First we outline the traditional approaches, then we propose a Bayesian
 approach that allows the practitioner to incorporating the models developed from
-section 3.1 with the hopes of reducing testing resources required while still
-minimizing producer and consumer risks.
+Section~\ref{modrel} with the hopes of reducing testing resources required while minimizing producer and consumer risks.
 
-In this reliability setting we are analyzing time of failure data measured in
-miles for a multiple component system with the primary objective being
-assessment of the system failure rate and prediction of future failure counts.
-The most common models used in this failure rate analysis are lifetime
-distributions and the most common for failure count analysis is the
-\emph{Poisson process} family of counting model.  We will utilize both and
-specifically the relationships between them in planning future test.
+\subsection{Modeling Reliability}\label{modrel}
+In this reliability setting, we are analyzing time to failure data measured in
+miles for a multiple component system with the primary objective of
+assessing the system failure rate and predicting future failure counts.
+The most common models used in this kind of failure rate analysis are lifetime
+distributions, and the most common for failure count analysis is the
+\emph{Poisson process} family of counting models.
 
 \subsubsection{Model Structure}
-Introducing notation, for each phase of testing we have failure mileage data for
+For each phase of testing we have failure mileage data for
 a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
@@
 the vehicle miles between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a
-lifetime distribution $f(\cdot)$, with an unknown set of parameters that include
-a rate parameter.  For the first phase the rate parameter for vehicle $i$ and
-failure mode $j$ will be denoted as $\lambda_{ij}$.  Then for the next stage we
-will use the same $\lambda_{ij}$ but add a multiplicative correction parameter
+lifetime distribution, $f(\cdot)$, with an unknown set of parameters that include
+a rate parameter.  For the first phase of testing, the rate parameter for vehicle $i$ and
+failure mode $j$ will be denoted as $\lambda_{ij}$.  For the next stage, we use the same $\lambda_{ij}$ but add a multiplicative correction parameter
 $\rho_{j}^{P2}$ that represents the change in this rate due to the CAP.  This
 procedure is then repeated for each subsequent stage.  The correction parameter
-will be discussed more in the next section but the general model is as follows,
+will be discussed more in the next section, but the general model is:
 \begin{align*}
-\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
-j=1,2,...,s \quad k=1,2,...,n_{ij}\\
+\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot) \\
 \text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
-\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot)
+\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot) \\
+\quad i = 1,2,...,v \quad &j=1,2,...,s \quad k=1,2,...,n_{ij}
 \end{align*}
 where $v$ represents the number of vehicles, $s$ is the number of failure modes,
-and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.
+and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.  \textcolor{blue}{The number of vehicles $v$ and number of failure modes $s$ are the same across each of the three phases.}
 
-% The number of failure modes is assumed fixed and known \textit{a priori}.
-
-For the model we assume a prior distribution on failure rate parameter
+For the model we assume a prior distribution on the failure rate parameter
 $\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
 considered to be common across vehicles or related but not identical.  If
-failure mode $j$ is considered common across vehicles we will assume there is a
+failure mode $j$ is considered common across vehicles, we will assume there is a
 single failure rate $\lambda_j$ that is shared by all eight vehicles with a
-prior distribution that has positive support.  In the JLTV study we will use a
+prior distribution that has positive support.  In the case study, we will use a
 non-informative gamma distribution.  For failure modes that are considered
-related across vehicles but not expected to be exactly the same, we place a
+related across vehicles, but that are not expected to be exactly the same, we place a
 prior distribution on the collection of $\lambda_{ij}$; in other words, we
@@
 modeling structure, where we then place  hyperprior distributions on the shared
-distribution's parameters.  In the JLTV study we use a gamma distribution with
+distribution's parameters.  In the case study, we use a gamma distribution with
 non-informative hyperpriors for all related failure modes.  Many times in
 practice  it is difficult to know ahead of time if individual components should
-be modeled  as common or related.  In the JLTV study we fit models for each
+be modeled  as common or related.  In the case study, we fit models for each
 component with both model structures and used diagnostic tools  that are
@@
 \subsubsection{Fix Effectiveness}
-After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
-these revisions, the PM2 reliability growth model \cite{ref2} is often used.
+After the first CAP, the second test phase begins with the repaired vehicles. To capture
+these repairs, the PM2 reliability growth model \cite{ref2} is often used.
 This model explicitly captures testing phases, choices about which failure modes
 to correct, and the potential of not completely eliminating a failure upon
-repair. One of the downsides of PM2 is that many parameters of potential
+repair. One of the features of PM2 is that many parameters of potential
 interest, such as the Fix Effectiveness Factor (FEF), which measures how much
-repairs improve failure rates, are typically fixed. A common value for FEF is
+repairs improve failure rates, are typically fixed, as PM2 is often used as a planning model. A common value for FEF is
 0.70. We follow the premise of this type of model, but allow a more flexible and
-data-driven result that is less dependent on hard-coded assumptions.
+data-driven result.
 
-One normal assumption used in reliability growth modeling is nondecreasing
-failure rates; that is either the fixes were effective or had no effect, but did
-not degrade the family of vehicles.  This should generally be the case, but
+One common assumption in reliability growth modeling is nondecreasing
+failure rates: either the fixes were effective or had no effect, but did
+not degrade the reliability of the family of vehicles.  This should generally be the case, but
 because we are dealing with complex systems and testing conditions are rarely
-completely consistent, we will sometimes see decreases in failure rates after
-adjustments are made.  Thus we will choose a prior distribution for the
-correction parameter $\rho_{j}^{P2}$ that has positive support.  If
+completely consistent, we will sometimes see decreases in failure rates after repairs are made.  Thus we choose a prior distribution for the
+FEF parameter $\rho_{j}^{P2}$ that has positive support.  If
 $\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
-And the same thinking is applied to $\rho_{j}^{P3}$ for the correction period
+The same approach is applied to $\rho_{j}^{P3}$ for the correction period
 between phases two and three.  With this structure we can use the posterior
 distributions of the correction parameters to make inference on the effectiveness
-of the repairs and the join posterior distributions to evaluate the overall
-system reliability within each phase.
+of the repairs and the joint posterior distributions to evaluate the overall system reliability within each phase.
 
@@
 The next modeling choice that must be made is selecting an appropriate
-probability model This includes a selecting a sampling distribution for the data
+probability model. This includes a selecting a sampling distribution for the data
 and prior distributions for each parameter on which the sampling distribution
-depends.  For lifetime data there are a number sampling distribution to choose
-from.  Some common choices are exponential, Weibull, lognormal, gamma, inverse
+depends. Some common distributional choices for lifetime data are exponential, Weibull, lognormal, gamma, inverse
 Gaussian, and normal failure time models.  Because all of these distributions
-have rate parameter (sometimes called scale = 1/rate) they can be applied to
-the proposed modeling structure.  For this paper, we will focus on the
-exponential and Weibull distributions.
+have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter) they can be applied in
+the proposed modeling structure. We focus on the
+exponential and Weibull distributions, which are commonly used for reliability.
 
-First the exponential model,
+The exponential model has probability density function
 \begin{equation*}
@@
 This is by far the most common parametric distribution used in reliability
-modeling because of its desirable math mathematical properties and simple
-interpretations.  One of the convenient properties, because we are assuming
-independence between failure modes, is the overall system failures also follow
+modeling because of its desirable mathematical properties and straightforward interpretations.  One convenient property, because we are assuming
+independence between failure modes, is that the overall system failures also follow
 an exponential distribution with a system failure rate $\lambda_S =
-\sum_{j}\lambda_{j}$.  A second, possibly less attractive property, is that the
-hazard rate is constant over miles.  For the JLTV, setting this would assume that a given
-component is equally likely to fail in the first mile of testing as it is in the
-thousandth.  This may be reasonable for some reliability settings, but in most
-setting we observe either a decreasing hazard rate where failures are likely to
-occur early in testing but less likely as the test goes on, or increasing hazard
-rate where we see the system wear down as the test progresses.
+\sum_{j}\lambda_{j}$.  A second, potentially less attractive property, is that the hazard rate is constant over miles.  For the case study, this implies that a given
+component is equally likely to fail in the first mile of testing as it is in the thousandth.
+This may be reasonable for some components, but in many settings we observe either a decreasing hazard rate, where failures are likely to
+occur early in testing but less likely as the test goes on, or an increasing hazard rate, where we see the system wear down as the test progresses.
 
-Despite its common uses the assumption of a constant hazard rate over time is
-rarely justifiable.  It has been well documented the issues that can arise when
-this assumption is violated ~\cite{ref3}.  Therefore we will also consider more
-flexible distributions when analyzing the data.  In our analysis of the JLTV
-data we fit the same hierarchical model structure using the Weibull as our
-lifetime distribution $f(\cdot)$.  Now we assume that the failure mileage
-$t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
+Despite its common use, the assumption of a constant hazard rate over time is rarely justifiable.
+The issues that arise when the modeling assumptions for the exponential distribution are violated are well-documented ~\cite{ref3}.
+Therefore, we will also consider more flexible distributions when analyzing the data.
+In our analysis of the case study, we also fit the same hierarchical model structure using the Weibull as our
+lifetime distribution, $f(\cdot)$. We assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
 parameter $\lambda$ and shape parameter $\gamma$, with probability density
@@
 \end{equation*}
-The exponential is a special case of the Weibull, when $\gamma = 1$.  You should
-notice here we are now modeling the actual failure mileage $t_{ijk}$ instead of
-the miles between failures $y_{ijk}$.  This implies the "bad as old" assumption
-for intra-test repairs.  We could have continued with the miles between failures
-and assumed "good as new" repairs, but "bad as old" modeling will be more
-convenient for developing assurance test plans in later sections.  This
-distinction is important in the Weibull case because the failure rate is not
-constant in time. In practice the decision on intra-test repair assumptions
-should be made based on the application.  In many cases repairs should be
-treated as somewhere between "good as new" and "bad as old".  This requires more
-complex modeling that is beyond the scope of this paper.
+The exponential is a special case of the Weibull, when $\gamma = 1$.
 
-It should  also be noted that we are currently indexing both $\rho$ and
-$\gamma$, only by $j$ and not $i$, in other words, we are assuming a single
+\textcolor{blue}{When a failure occurs during a testing phase the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.
+One must consider how these changes will effect the system reliability moving forward.
+In repairable system literature two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".
+``Good as new" assumes that a repaired component has returned to a brand-new state or in our case the the mileage is set to zero.
+On the other hand, ``bad as old" assumes the component has returned to the state it was at before the failure occurred.
+You will notice for the Weibull we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.}  We could have continued with the miles between failures and assumed "good as new" repairs, but "bad as old" modeling will be more
+convenient for developing assurance test plans in later sections.
+This distinction is important in the Weibull case because the failure rate is not constant in time.
+In practice the decision on intra-test repair assumptions should be made based on the application.
+In many cases repairs should be treated as somewhere between "good as new" and "bad as old".
+This requires more complex modeling that is beyond the scope of this paper.
+
+We index both $\rho$ and
+$\gamma$ only by $j$ and not $i$. In other words, we are assuming a single
 shape and between phase adjustment parameter for each failure mode across
 vehicles.  All of these parameters could also be indexed by $i$ and modeled
-hierarchical or with some combination of both.  This is something we will omit
-for this paper but hope to explore in the future.
+hierarchical or with some combination of both.
+\textcolor{blue}{When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.
+In the case study, we found 6 of the 26 failure modes had less than 10 observed (non-censored) failures across all 3 phase and 8 vehicle types.
+These failure modes were attributed to system components such as the engine and armor.
+To improve convergence we have binned these rare failure modes into a single "other" failure mode.
+This is also useful for future testing in the case of observing failures not originally accounted for.
+}
 
-\subsubsection{JLTV Reliability}
-We have discussed different models structures and distributional assumptions
-that accompany them.  Using McMC we fit each of these models to the JLTV
-dataset.\footnote{The likelihoods and sampling distributions are available in the
-appendix.} Then we use the posterior distributions of the systems parameters to
-estimate reliability-related quantities of interest for each of the eight
-vehicle types.  We are able to look at a number of different statistics related
-to reliability at both the component and system level.  In this study, one
-quantity of interest is expected miles to failure(EMTF).  In figure 1 we have box
-plots and summary statistics from the posterior distributions of the expected
-miles to failure for one of the vehicle types for each of the three phases,
-first using the exponential model and second using the more general Weibull
-model.
+\subsubsection{Model Diagnostics}
+The decision about which model to
+use can have a substantial impact on reliability assessment.  We consider a
+few  goodness-of-fit techniques that can be used to help with this decision for Bayesian reliability models.  The
+first model selection question we consider is the parametric form,
+exponential versus Weibull.  This an example of the classic statistical modeling
+the trade-off between fit and interpretability.  Because the Weibull is a more
+flexible model, containing the exponential as a special case, it will always fit the data at least as well as the exponential.
+The exponential distribution's convenient form makes both computation and
+interpretation straightforward.  However, when the Weibull distribution's shape parameter is
+introduced this advantage is lost.
+
+The first diagnostic we use to decide between the exponential and Weibull models is
+to fit the Weibull model and look at the posterior distributions of the shape
+parameters to determine whether their support contains 1.
+From Figure~\ref{Shape}, which shows the Weibull model fits for the case study for each failure mode, we see that 1 is not a reasonable value for any of the failure modes, which suggests that the exponential model may not fit this data well.
+
+\begin{figure}[h]
+  \centering
+      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
+  \caption{Posterior Plots of Weibull Shape Parameter}
+  \label{Shape}
+\end{figure}
+
+We also consider a more formal diagnostic tool, the Deviance information criterion (DIC)
+~\cite{ref4}. This is a popular method for comparing the goodness of fit of
+multiple models. The DIC method includes a penalty term that grows with the
+numbers of unknown parameters in the model.
+The DIC value is a unitless measure with smaller values indicating a better fit to the data.
+Table~\ref{table:ta1} shows the DIC results for the different distribution and structure
+combinations, we considered for the case study. The results show that the hierarchical Weibull model fits the data
+much better than the exponential or common rate models.
+
+% need to recheck these numbers %
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|r|}
+\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
+\cline{1-3}
+Distribution    & Structure & DIC \\
+\hline
+Exponential   & Common Rate Model                     & 21,264.19             \\
+              & Hierarchical Rate Model               & 21,244.47             \\
+Weibull       & Common Rate Model                     & 20,658.25             \\
+              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
+\hline
+\end{tabular}
+\caption{JLTV DIC Results}
+\label{table:ta1}
+\end{table}
+
+In general, information criteria
+comparisons do not tell us if the model is truly a good representation of the
+underlying process -- they only compare models. The final model diagnostics method we present is called
+posterior predictive checking ~\cite{ref5}.  We start with important
+features of the data that we would expect to see if the experiment was repeated.
+These are usually provided by practitioner with knowledge about the random
+process being studied. In the case study, \textcolor{blue}{one feature of interest is the count of miles between failure observations less than 140 miles, for a given vehicle and phase.}
+
+%\textcolor{blue}{for each phase, $\sum \mathbbm{1} [y_{ijk} < 140]$.}
+
+We used the final \textcolor{blue}{exponential and Weibull models with the lowest DIC} to simulate 5,000 new datasets for vehicles tested
+over the same number of miles for each of the three phases.
+We plot the resulting distributions for each of the 8 vehicles for all 3 phases.
+Figure~\ref{fig:test} shows two examples of the boxplots produced, one from the exponential model
+(left) and one from the Weibull model (right), with the dashed line showing
+where the value from the observed dataset fell.
+If the model fits reasonably well, we expect to see the value from the observed data falling within the support of the simulated data.
+This suggests that the Weibul model fits the case study data better than the exponential data.
 
 \begin{figure}[h!]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{PPExpo}
+  %\caption{}
+  %\label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{PPWeibull}
+  %\caption{}
+  %\label{fig:sub2}
+\end{subfigure}
+\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
+\label{fig:test}
+\end{figure}
+
+\subsubsection{Case Study Results}
+\textcolor{red}{Does this section need to come after the Model Diagnostics section?}
+We have introduced several models structures and distributional assumptions that accompany them.  Using Markov chain Monte Carlo (MCMC), we fit each of these models to the JLTV
+dataset.
+(The likelihoods and sampling distributions are available in the appendix.) We use the posterior distributions to estimate reliability-related quantities of interest for each of the eight vehicle types.
+We are able to examine a number of different summaries related to reliability at both the component and system level.
+
+In this study, one quantity of interest is mean miles to failure (MMTF).
+\textcolor{blue}{This is different than the commonly used mean miles between failures (MMBF).
+Due to the failure rate changing over time in the Weibull case MMBF depends on how many miles the vehicle is driven.
+Instead MMTF can be thought of as the average time until the first failure occurs.} Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).
+
+\begin{figure}[ht]
 \centering
@@
 \end{subfigure}
-\caption{Comparing EMTF for Different Models}
-\label{fig:test}
+\caption{Comparing MMTF for Different Models}
+\label{fig:MMTF Results}
 \end{figure}
 
-You can see the posterior EMTF distributions from the Weibull model have more
-spread than the exponential.  This is generally expected, given the Weibull
-model is estimating two model parameters to the exponentials one, but what is
-concerning is that the center of the distributions is also quite different
-between the two models.  The Weibull EMTF posterior means are consistently
-larger than the exponentials.  We saw this across all eight vehicle types.  This
-was the first indication that the exponential model may not be a good fit to the
-data.
+You can see the posterior MMTF distributions from the Weibull model consistently have more
+spread and larger means and medians than the exponential.
+We saw this across all eight vehicle types.
+\textcolor{blue}{This is a good example of how the choice of model can impact the final inference.}
 
-\subsubsection{Model Diagnostics}
-As seen in the last section with the JLTV data, the decision of which model to
-use can have a drastic impact on reliability assessment.  We will now look at a
-few  goodness-of-fit methods that can be used to help in this decision.  The
-first model selection question we will explore is the parametric form,
-exponential versus Weibull.  This an example of the classic statistical modeling
-the trade-off between fit and interpretability.  Because the Weibull is a more
-flexible model it will always, in a sense, fit the data better, but this comes
-at a price.  The exponentials convenient form makes both computation and
-interpretation straightforward.  When the Weibull's shape parameter is
-introduced this advantage is lost.  Thus, when the overall fit is close to the
-same between the exponential and the Weibull we will default to using the
-exponential.
-
-The first check we used in decide between the exponential and Weibull models is
-to fit the Weibull model and look at the posterior distributions of the shape
-parameters and determine if one is a reasonable value.  Looking at the plot in
-figure 2 from the Weibull model fit with the JLTV data, we see that one is
-not a reasonable value for any of the failure modes.  This is another clue
-that the exponential model is not be a good fit to this data.
-
-\begin{figure}[h]
-  \centering
-      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
-  \caption{Posterior Plots of Weibull Shape Parameter}
-\end{figure}
-
-Now a more formal diagnostic tool, the Deviance information criterion (DIC)
-~\cite{ref4}. This is a popular method for comparing the goodness of fit of
-multiple models. The DIC method includes a penalty term that grows with the
-numbers of unknown parameters in the model.  The DIC value is a unit-less
-measure with lower values indicating a better fit to the data.  In the table
-below we show the DIC results for the different distribution and structure
-combinations, we considered with the JLTV dataset.
-
-% need to recheck these numbers %
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|l|r|}
-\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
-\cline{1-3}
-Distribution    & Structure & DIC \\
-\hline
-Exponential   & Common Rate Model                     & 21,264.19             \\
-              & Hierarchical Rate Model               & 21,244.47             \\
-Weibull       & Common Rate Model                     & 20,658.25             \\
-              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
-\hline
-\end{tabular}
-\caption{JLTV DIC Results}
-\label{table:ta}
-\end{table}
-
-The results in table 1 shown that the hierarchical Weibull model fits the data
-much better than the exponential, but in general information criteria
-comparisons do not tell us if the model is truly a good representation of the
-underlying process. The last model diagnostics method we present is called
-posterior predictive checking ~\cite{ref5}.  Here we start with important
-features of the data that we would expect to see if the experiment was repeated,
-these are usually provided by practitioner with knowledge about the random
-process being studied. In the JLTV case one feature we were interested in was
-the number of miles between failure observations that were less than 140 miles.
-We then used the final models to simulate 5,000 new datasets for vehicles tested
-over the same number of miles for each of the three phases. We then plot the
-resulting distributions for each of the 8 vehicles for all 3 phases.  In Figure
-3 are two examples of the boxplots produced, one from the exponential model
-(left) and one from the Weibull model (right), with the dashed line showing
-where the value from the observed dataset fell.  For this method we don’t expect
-all of the true values to fall in the center of the distribution. Some values in
-the tales are to be expected in a random processes like this one, but when we
-see many observations in the tails, as we do with the exponential, we should
-consider other modeling options.
-
-\begin{figure}[h!]
+\textcolor{blue}{Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.
+The distributions look reasonable with most of the mass close to one.
+We notice a trend of more improvement in the second CAP period between phase two and three compared to the first CAP between phase one and two.}
+\begin{figure}[ht]
 \centering
@@
   \centering
-  \includegraphics[width=.8\linewidth]{PPExpo}
-  %\caption{}
+      \includegraphics[width=8cm, height=7cm]{CAP2}
+  % \caption{Corrective Action Period Parameters Posterior Distributions}
   %\label{fig:sub1}
@@
 \begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{PPWeibull}
-  %\caption{}
+  \center
+  	\includegraphics[width=8cm, height=7cm]{CAP3}
   %\label{fig:sub2}
 \end{subfigure}
-\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
-%\label{fig:test}
+\caption{Posterior Distributions for Correction Parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$}
+\label{fig:CAP}
 \end{figure}
 
-\subsection{Assurance Test Planning}
-In this section, we will use the reliability models fit in section two to
-develop a plan for future testing.  Here the objective is to demonstrate, at
-a desired level of confidence, that the system will meet or exceed a specified
-requirement. The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref6}. Bayesian \emph{reliability assurance
-tests} are used to ensure that the reliability of an item meets or exceeds a
-specified requirement with a desired probability. Meeker and Escobar
-~\cite{ref7} established the difference between this and the more traditional
-\emph{reliability demonstration test}.  The difference being that the assurance
-test plan incorporates supplementary data and information, where the
-demonstration test only uses test data.
+\subsection{Assurance Test Planning}\label{atp}
+In addition to fitting the data from the three phases of testing, we also want to use the reliability models to
+develop plans for future testing.
+The objective is to demonstrate, at a desired level of confidence, that the system will meet or exceed a specified requirement.
+The methods to be employed will be similar to the assurance testing
+as discussed by Hamada et al. ~\cite{ref6}.
+% Bayesian \emph{reliability assurance tests} are used to ensure that the reliability of an item meets or exceeds a specified requirement with a desired probability.
+Meeker and Escobar
+~\cite{ref7} describe the difference between assurance testing and the more traditional
+\emph{reliability demonstration test}: an assurance
+test plan incorporates supplementary data and information, where the demonstration test uses only data from the current test.
 
@@
 while minimizing the resources required for testing.  In the DoD acquisition
-process, the error rates are referenced in terms of risk. \emph{Consumer
-risk} which considers the event of purchasing a product that does not meet
-reliability requirements.  \emph{Producer risk} which considers the event of a
-product with acceptable reliability failing a given test and not being
-considered for purchase.  Introducing the notation for this section, in the JLTV
-case study, we will be determining how many miles on test $T$, are required and
-how many system failures to allow $c$, before the product is considered
-unacceptable.  We will define $W(t)$ as a random variable that represents the
-total number of system failures after $t$ miles.  We will let $\pi$ denote the
-quantity of interest that is related to system reliability at a given time. It
-is common to base both classical and Bayesian test plans on two specified levels
+process, the error rates are referenced in terms of risk. \emph{Consumer's
+risk} is the probability of purchasing a product that does not meet
+reliability requirements.  \emph{Producer's risk} is the probability that a
+product with acceptable reliability fails a given test.
+
+In the case study, we determine how many miles on test $T$, are required and how many system failures to allow $c$, before the product is considered unacceptable.
+We define $W(t)$ as a random variable that represents the total number of system failures after $t$ miles.
+We let $\pi$ denote a system reliability-related
+quantity of interest at a given time.
+
+It is common to base both classical and Bayesian test plans on two specified levels
 of $\pi$: $\pi_0$, an \emph{acceptable reliability level} (ARL), and $\pi_1$, a
@@
 the precise definition of ARL and RRL differ between the classical and Bayesian
-test criteria, we use them in an equivalent way.
+test criteria, we use them in a similar way.
 
@@
 In the frequentest (classical) test planning setting the risk criteria
-are as follows. The \emph{producer's risk}, defined as the probability of
+are as follows. The \emph{producer's risk} is defined as the probability of
 failing the test under the null hypothesis $\pi = \pi_0$, and the
-\emph{consumer's risk}, defined as the probability of passing the test under an
+\emph{consumer's risk} is defined as the probability of passing the test under an
 alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
@@
 we assume a distributional form that defines the relationship between the number
-of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
-the combinations of these probabilities by simultaneously solving these two
+of system failures $W(t)$ and the reliability $\pi$.  We then solve for
+the combinations of these probabilities that satisfy the risk constraints by simultaneously solving these two
 equations.  In the case where the component failure times are assumed to be
-exponentially distributed with rate parameter $\lambda_i$ the failure counts for
+exponentially distributed with rate parameter $\lambda_i$, the failure counts for
 each component come from a homogeneous Poisson process $w_i(t) \sim
@@
 \text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
-this classical test planning approach.
+this classical test planning approach. \textcolor{red}{add a cite or two}
 
 \subsubsection{Bayesian Approach}
-The classical methods for determining the testing procedure rely only on
-distributional assumptions or asymptotic results. With a Bayesian approach we
+The non-Bayesian methods for determining the testing procedure rely only on distributional assumptions or asymptotic results. With a Bayesian approach, we
 incorporate the supplementary data from the previous testing phases with the
-hopes of minimizing the resources needed for testing.
+hopes of minimizing the resources needed for additional testing.
 
-We now consider fully Bayesian posterior risks that convey a completely
-different outlook from the corresponding classical risks.  While the classical
-provide assurance that satisfactory devices will pass the test and that
+We consider fully Bayesian posterior risks, which provide a completely
+different outlook from the corresponding classical risks.  While the classical approach
+provides assurance that satisfactory devices will pass the test and that
 unsatisfactory devices will fail it, posterior risks provide precisely the
 assurance that practitioners often desire: if the test is passed, then the
-consumer desires a maximum probability $\beta$ that $\pi \leq \pi_1$. On the
+consumer desires a maximum probability $\beta$ that \textcolor{blue}{the true reliability is less than the rejectable level,} $\pi \leq \pi_1$. On the
 other hand, if the test is failed, then the producer desires a maximum
-probability $\alpha$ that $\pi \geq \pi_0$. Unlike the average risks, these
-posterior risks are fully Bayesian in the sense that they are subjective
-probability statements about $\pi$.
+probability $\alpha$ \textcolor{blue}{the true reliability is greater than the acceptable level,} that $\pi \geq \pi_0$.
+Notice these posterior risks are fully Bayesian in the sense that they are probability statements about $\pi$.
 
@@
     d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} 1 - [ \sum_{W=0}^c
-    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
-    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
+    \frac{(\lambda_S T)^W \exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
+    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W \exp(-\lambda_S
     T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
@@
 \\
-For simplicity we if fix c to be zero and then perform Monte Carlo integration
-using N posterior draws $ \lambda_S^{(j)} $
+For simplicity, if we set $c = 0$ and then perform Monte Carlo integration
+using $N$ posterior draws $ \lambda_S^{(j)} $
 $$
@@
 	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
-	 \frac{\int_{\lambda_0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
-	 {\int_{0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
-	 \frac{\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
-	 \lambda_0)} {\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)} \end{aligned}
+	 \frac{\int_{\lambda_0}^{\infty} 1 - \exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
+	 {\int_{0}^{\infty} 1 - \exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
+	 \frac{\sum_{j = 1}^{N} 1 - \exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
+	 \lambda_0)} {\sum_{j = 1}^{N} 1 - \exp(-\lambda_S^{(j)} T)} \end{aligned}
 $$
@@
 is the probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert
-\text{Test Is Passed)}$.  Now we let $\pi_1$ be a predetermined rejectable
-failure rate $\lambda_1$ and assuming a maximum allowable posterior consumer's
+\text{Test Is Passed)}$.  Let $\pi_1$ be a predetermined rejectable
+failure rate $\lambda_1$ \textcolor{red}{this is confusing}. Assuming a maximum allowable posterior consumer's
 risk $\beta$, an expression for the posterior producer's risk for the
@@
     \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W
-    exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [
-    \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
+    \exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [
+    \sum_{W=0}^c \frac{(\lambda_S T)^W \exp(-\lambda_S
     T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
@@
 \\
-For simplicity we if fix c to be zero and then perform Monte Carlo integration
-using N posterior draws $ \lambda_S^{(j)} $ $$
+For simplicity, if we fix $c = 0$ and then perform Monte Carlo integration
+using $N$ posterior draws $ \lambda_S^{(j)} $ $$
 \begin{aligned}
 	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1}
-	 exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S
+	 \exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} \exp(-\lambda_S
 	 T)p(\lambda_S)d\lambda_S} \\ &\approx \frac{\sum_{j = 1}^{N}
-	 exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N}
-	 exp(-\lambda_S^{(j)} T)}
+	 \exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N}
+	 \exp(-\lambda_S^{(j)} T)}
 \end{aligned}
@@
 \subsubsection{Weibull Case}
-In the exponential case, we defined our quantity of interest that is related to
-system reliability at a given time $\pi$ to be equal to the system failure rate
-$\lambda_S$.  This distributional assumption gave us a convenient distributional
-form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
-When we assume the miles to failure for each system component follows a Weibull
-distribution the system failure counts no longer follow a homogeneous Poisson
-process.  When assuming "bad as old" intra-test repairs we do find that the
-failure count for a given failure mode does follow a nonhomogeneous Poisson
-process, $w(t)_i \sim \text{Poisson}( \lambda_i t_i^{\gamma_i} )$.  The system
-failure counts then, for a given mileage $t$ become $W(t) \sim
-\text{Poisson}(\sum_i (\lambda_i t_i)^{\gamma_i})$.  In this case the acceptable
+In the exponential case, we defined our reliability quantity of interest $\pi$ as the system failure rate
+$\lambda_S$.  Assuming an exponential lifetime distribution gave us a convenient distributional
+form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$.
+
+When we assume the miles to failure for each system component follow a Weibull
+distribution, the system failure counts no longer follow a homogeneous Poisson
+process.  When assuming ``bad as old" intra-test repairs, \textcolor{blue}{as described in section 3.1.3}, we find that the
+failure count for a given failure mode follows a nonhomogeneous Poisson
+process, $w_i(t) \sim \text{Poisson}( \lambda_i t_i^{\gamma_i} )$.  The system
+failure counts for a given mileage $t$ have distribution $W(t) \sim
+\text{Poisson}(\sum_i (\lambda_i t_i)^{\gamma_i})$.  In this case, the acceptable
 and rejectable parameters $\pi_0$ and $\pi_1$ become quantities related to
-$\sum_i (\lambda_i t_i)^{\gamma_i}$.  This can lead to some unpleasant
-integration expression, but once again we can lean on Monte Carlo integration
-and our evaluation for the posterior producer's risk for the Weibull test plan
-$(T,c)$ becomes to
+$\sum_i (\lambda_i t_i)^{\gamma_i}$.  This leads to integration that is analytically intractable, but Monte Carlo integration
+allows our evaluation of the posterior producer's risk for the Weibull test plan
+$(T,c)$:
 $$
@@
 	 P(\sum_i \lambda_i T^{\gamma_i} \geq \pi_0 \; \vert \; W = 0) &= \frac{
-	 \int_{\pi_0}^{\infty} 1 - exp(- \sum_i \gamma_i \lambda_i
+	 \int_{\pi_0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
 	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
-	 d\gamma_{1,...}} {\int_{0}^{\infty} 1 - exp(- \sum_i \gamma_i \lambda_i
+	 d\gamma_{1,...}} {\int_{0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
 	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
 	 d\gamma_{1,...}} \\
-   &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\sum_i \gamma_i^{(j)}
+   &\approx \frac{\sum_{j = 1}^{N} 1 - \exp(-\sum_i \gamma_i^{(j)}
    \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\sum_i \lambda_i^{(j)}
-   T^{\gamma_i^{(j)}} \geq \pi_0)} {\sum_{j = 1}^{N} 1 - exp(- \sum_i
+   T^{\gamma_i^{(j)}} \geq \pi_0)} {\sum_{j = 1}^{N} 1 - \exp(- \sum_i
    \gamma_i^{(j)} \lambda_i^{(j)} T^{\gamma_i^{(j)}})}
@@
 \\
-Where $\pi_0$ is some quantity related to the model parameters.  Again we set c
-to be zero and used N posterior draws for both $\lambda_i^{(j)}$ and
+where $\pi_0$ is some quantity related to the model parameters.  Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
 $\gamma_i^{(j)}$.
@@
 appropriate prior.   A 10-30 percent reduction from the developmental phase to
-the operational phase is common in many DoD applications.
+the operational phase would be a common assumption in many DoD applications.
 
 \subsubsection{JLTV Test Plan Results}
-The first step in applying this method to our JLTV dataset is defining $\pi_0$,
-$\pi_1$, $\alpha$ and $\beta$.  That is the ARL, RRL, acceptable producer risk
+The first step in applying this method to our case study is defining $\pi_0$,
+$\pi_1$, $\alpha$ and $\beta$, which are the ARL, RRL, acceptable producer risk
 and acceptable consumer risk respectively.  With input from subject matter
-experts  we will define the producer's target or ARL as the expected number of
+experts,  we will define the producer's target as the average number of
 failures in the first 140 miles to be less than 3, and the consumer's minimum
-requirements or RRL as the expected number of failures in  the first 80 miles to
-greater than 3.  We will use traditional values of 0.1 and 0.05 for $\alpha$ and
-$\beta$ respectively, but in practice these values should always be set based on
+requirements as the average number of failures in the first 80 miles to
+greater than 3.
+\textcolor{blue}{The producer's targets and consumer's minimum requirements represent our cut off levels ARL and RRL respectively.
+This means if the true average number of failures in the first 140 miles is less than 3 the producer would expect his product to fail the test a small proportion of the time, $\alpha$.
+On the other hand, if the true average number of failures in the first 8 miles is greater than 3 the consumer would expect the product to pass the test a small proportion of the time, $\beta$.
+} We will use $\alpha = 0.1$ and $\beta = 0.05$, and in practice these values should always be set based on
 the true risk tolerances of the consumer and producers.  This gives us the
@@
 required that satisfy both risk requirements.  Table 2 shows the
-resulting combinations for the JLTV data.
+resulting combinations for the case study.
 
@@
 \begin{tabular}{|c|c|}
-\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
+\multicolumn{2}{c}{\textbf{Test Plan}} \\
 \cline{1-2}
@@
 \end{tabular}
-\caption{JLTV Assurance Test Plan Results}
+\caption{Assurance Test Plan Results}
 \label{table:ta}
@@
 performing. A natural comparison would be with the frequentest test plan in this
-setting.  In general  we warn against this comparison because the test plan
+setting.  In general,  we warn against this comparison because the test plan
 probability constraints for each  method are asking different questions.  The
-frequentest plan controls the error rates  under two different assumed settings.
+frequentist plan controls the error rates  under two different assumed settings \textcolor{red}{???}.
 On the other hand, the Bayesian plan puts constraints  on the error when the test
 is passed and failed.  We would argue that in most settings  the Bayesian plan
-controls for the error the practitioner cares about.  In this case there are no
+controls for the error the practitioner cares about.
+
+In this case there are no
 reasonable combinations of allowed failures and required test miles  that
 satisfy both producer's and consumer's risk probability statements in the
-frequentest test plan.
+frequentest test plan. \textcolor{red}{Can you come close? Can you calculate risks using the values from the Bayesian plans -- then we do have a comparison}
 Both test planning approaches rely heavily on setting reasonable values for
@@
 values both procedures can can result in no plan that satisfies the probability
-statements.  In this paper we have focused on test plans for single units, but
+statements \textcolor{red}{B.
+Weaver, M.
+Hamada, A.
+Wilson, J.
+Bakerman (2017).
+Bayesian Assurance Tests for Degradation Data.
+Quality and Reliability Engineering International 33(8): 2699-2709.}.
+In this paper we have focused on test plans for single units, but
 th the assurance testing methodology can be extended to find test plans that
@@
 \subsection{Discussion}
-The JLTV case study results provide indications that our model is successfully
+The case study results provide indications that our model is successfully
 capturing the failure rates across failure modes, inferring logical fix
@@
 vehicles with no observed failures are sensible; however, we should leverage
-more information across vehicles. Because the correlations induced by our
-current model are fairly low, potential methods for inducing more correlation
+more information across vehicles \textcolor{red}{More discussion here}. Because the correlations induced by our
+current model are fairly low \textcolor{red}{correlations between what?}, potential methods for inducing more correlation
 between the vehicles in the related failure modes are being investigated. We

### 2018-01-27 paperDraft3.tex
work on edits

@@
 improvement, in the reliability of a system as it moves through testing phases
-and undergoes periodic corrective actions. Ideally, plans for future test events
-should be based on what has been observed in previous testing.
+and undergoes periodic corrective actions. To most effectively use resources
+plans for future test events should be based on what has been observed in
+previous testing.
 
 In this paper, we propose models for combining information across multiple test phases with
-the objective of planning a future test. When combining information, there is no
+the ultimate objective of planning a future test. When combining information, there is no
 omnibus solution. Rather, models need to be carefully considered and evaluated
@@
 4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
-3.\footnote{The exact mileage has been altered to protect proprietary information.
-\textcolor{red}{Any other changes to the data that we should describe?
-I think things were perhaps rescaled, constants added, etc.
-Let's be sure this isn't a JLTV assessment, but based on the JLTV assessment.}}
+3.\footnote{The exact mileage has been altered to protect proprietary information.}
 
 There are many similarities between vehicle types; in fact, the most dissimilar
-vehicles have over 80\% common parts. Consequently, some failure modes, such as
+vehicles have over 80\% common parts. Consequently, some failure modes, such as those for
 brakes and radios, will be common to all eight vehicles. Other failure modes
@@
 test phase does not necessarily end with a failure. Therefore, we have 624 right
-censored observations, accounting for miles driven without observed failures.
+censored observations, which account for miles driven after the last observed failures.
 
 \section{Methodology}
-A standard reliability analysis employed by the Department of Defense (DoD) test
-community considers each test phase independently and uses the exponential
+A typical reliability analysis employed by the Department of Defense (DoD) test
+community would consider each test phase independently and use the exponential
 distribution to model the miles between failure for the system ~\cite{ref1}. For many situations, including our example, this
-traditional analysis is overly simplistic, relying on incorrect modeling assumptions and ignoring valuable information learned about the individual vehicles and their failure modes.
+traditional analysis is overly simplistic, relying on incorrect modeling assumptions and ignoring valuable information learned about the individual vehicles and their failure modes through multiple phases of testing.
 
@@
 similarities between vehicle failure modes.  Next, we will consider different
-distributional assumptions and their implications.  Using the JLTV case study we
+distributional assumptions and their implications.  Using the JLTV as a case study we
 will illustrate the process of model selection using three different diagnostic
@@
 First we outline the traditional approaches, then we propose a Bayesian
-approach that allows the practitioner to incorporating the models developed from
-Section~\ref{modrel} with the hopes of reducing testing resources required while minimizing producer and consumer risks.
+approach that allows the practitioner to leverage the information from previous test phases, using the models developed from Section~\ref{modrel}, with the hopes of reducing testing resources required while minimizing producer and consumer risks.
 
@@
 where $v$ represents the number of vehicles, $s$ is the number of failure modes,
-and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.  \textcolor{blue}{The number of vehicles $v$ and number of failure modes $s$ are the same across each of the three phases.}
+and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.  The number of vehicles $v$ and number of failure modes $s$ are considered fixed and the same across all phases.
 
@@
 be modeled  as common or related.  In the case study, we fit models for each
-component with both model structures and used diagnostic tools  that are
-discussed in a later section to make our final decision.
+component with both model structures and use diagnostic tools  that are
+discussed in Section~\ref{modd} to make our final decision.
 
-\subsubsection{Fix Effectiveness}
-After the first CAP, the second test phase begins with the repaired vehicles. To capture
+\subsubsection{Fix Effectiveness}\label{FEF}
+After the first CAP, the second test phase begins with repaired vehicles. To plan for the reliability improvement caused by
 these repairs, the PM2 reliability growth model \cite{ref2} is often used.
@@
 
-\textcolor{blue}{When a failure occurs during a testing phase the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.
-One must consider how these changes will effect the system reliability moving forward.
-In repairable system literature two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".
-``Good as new" assumes that a repaired component has returned to a brand-new state or in our case the the mileage is set to zero.
+When a failure occurs during a testing phase, the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.
+One must consider how these changes will affect the system reliability moving forward.
+In repairable system literature, two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".
+``Good as new" assumes that a repaired component has returned to a brand-new state or, in our case, that the mileage is set to zero.
 On the other hand, ``bad as old" assumes the component has returned to the state it was at before the failure occurred.
-You will notice for the Weibull we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.}  We could have continued with the miles between failures and assumed "good as new" repairs, but "bad as old" modeling will be more
-convenient for developing assurance test plans in later sections.
+The Weibull distribution implies we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.
 This distinction is important in the Weibull case because the failure rate is not constant in time.
-In practice the decision on intra-test repair assumptions should be made based on the application.
-In many cases repairs should be treated as somewhere between "good as new" and "bad as old".
+In the JLTV case study we have assumed ``bad as old" intra-test repairs based on input from subject matter experts.
+There will be applications where repairs should be treated as somewhere between ``good as new" and ``bad as old".
 This requires more complex modeling that is beyond the scope of this paper.
+An overview of repairable system models can be found in Hamada et al.
+~\cite{ref4}
 
@@
 vehicles.  All of these parameters could also be indexed by $i$ and modeled
-hierarchical or with some combination of both.
-\textcolor{blue}{When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.
+hierarchically or we could use a combination of common and ``related".
+When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.
 In the case study, we found 6 of the 26 failure modes had less than 10 observed (non-censored) failures across all 3 phase and 8 vehicle types.
@@
 This is also useful for future testing in the case of observing failures not originally accounted for.
-}
 
-\subsubsection{Model Diagnostics}
+\subsubsection{Model Diagnostics}\label{modd}
 The decision about which model to
@@
 flexible model, containing the exponential as a special case, it will always fit the data at least as well as the exponential.
-The exponential distribution's convenient form makes both computation and
-interpretation straightforward.  However, when the Weibull distribution's shape parameter is
-introduced this advantage is lost.
 
@@
 We also consider a more formal diagnostic tool, the Deviance information criterion (DIC)
-~\cite{ref4}. This is a popular method for comparing the goodness of fit of
+~\cite{ref5}. This is a popular method for comparing the goodness of fit of
 multiple models. The DIC method includes a penalty term that grows with the
 numbers of unknown parameters in the model.
-The DIC value is a unitless measure with smaller values indicating a better fit to the data.
-Table~\ref{table:ta1} shows the DIC results for the different distribution and structure
-combinations, we considered for the case study. The results show that the hierarchical Weibull model fits the data
-much better than the exponential or common rate models.
+The DIC is unitless, with smaller values indicating a better fit to the data.
+Table~\ref{table:ta1} shows the DIC results for the different distribution and structure combinations we considered for the case study.
+The results show that the hierarchical Weibull model fits the data much better than the exponential or common rate models.
 
-% need to recheck these numbers %
 \begin{table}[h]
@@
 underlying process -- they only compare models. The final model diagnostics method we present is called
-posterior predictive checking ~\cite{ref5}.  We start with important
+posterior predictive checking ~\cite{ref6}.  We start with important
 features of the data that we would expect to see if the experiment was repeated.
 These are usually provided by practitioner with knowledge about the random
-process being studied. In the case study, \textcolor{blue}{one feature of interest is the count of miles between failure observations less than 140 miles, for a given vehicle and phase.}
+process being studied. In the case study, one feature of interest is the count of miles between failure observations less than 140 miles, for a given vehicle and phase.
 
-%\textcolor{blue}{for each phase, $\sum \mathbbm{1} [y_{ijk} < 140]$.}
-
-We used the final \textcolor{blue}{exponential and Weibull models with the lowest DIC} to simulate 5,000 new datasets for vehicles tested
-over the same number of miles for each of the three phases.
+We used the final exponential and Weibull models with the lowest DIC to simulate 5,000 new datasets for vehicles tested over the same number of miles for each of the three phases.
 We plot the resulting distributions for each of the 8 vehicles for all 3 phases.
-Figure~\ref{fig:test} shows two examples of the boxplots produced, one from the exponential model
-(left) and one from the Weibull model (right), with the dashed line showing
+Figure~\ref{fig:test} shows two examples of the boxplots produced for one of the vehicle types, one plot from the exponential model
+(left) and one plot from the Weibull model (right), with the dashed line showing
 where the value from the observed dataset fell.
@@
 \subsubsection{Case Study Results}
-\textcolor{red}{Does this section need to come after the Model Diagnostics section?}
-We have introduced several models structures and distributional assumptions that accompany them.  Using Markov chain Monte Carlo (MCMC), we fit each of these models to the JLTV
+We have introduced several models structures and distributional assumptions that accompany them.  Using Markov chain Monte Carlo (MCMC), we fit each of these models to the JLTV case study
 dataset.
@@
 In this study, one quantity of interest is mean miles to failure (MMTF).
-\textcolor{blue}{This is different than the commonly used mean miles between failures (MMBF).
+This is different than the commonly used mean miles between failures (MMBF).
 Due to the failure rate changing over time in the Weibull case MMBF depends on how many miles the vehicle is driven.
-Instead MMTF can be thought of as the average time until the first failure occurs.} Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).
+Instead MMTF can be thought of as the average time until the first failure occurs.
+Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).
 
@@
   \centering
-      \includegraphics[width=9cm, height=7cm]{Boxplots}
+      \includegraphics[width=8cm, height=7cm]{Boxplots}
   % \caption{Comparing EMTF for Different Models}
@@
   \cline{1-5}
-  Model & Phase & Mean & 90\% CI Low & 90\% CI Up \\
+  Model & Phase & Mean & 90\% CI & 90\% CI \\
+   & & & Low & Up \\
   \hline
@@
 
-You can see the posterior MMTF distributions from the Weibull model consistently have more
-spread and larger means and medians than the exponential.
+Figure~\ref{fig:MMTF Results} shows that the posterior MMTF distributions from the Weibull model consistently have wider uncertainty intervals and larger means and medians than the exponential.
 We saw this across all eight vehicle types.
-\textcolor{blue}{This is a good example of how the choice of model can impact the final inference.}
+This is a good illustration of how the choice of model can impact the final inference.
 
-\textcolor{blue}{Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.
+Figure~\ref{fig:CAP} shows the posterior distributions for each of the FEF parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.
+These parameters were introduced in Section~\ref{FEF}.
+They are multiplicative parameters added in between phases to capture the change in failure rate due to improvements by the producer.
+Values less than one indicate a decrease in failure rate.
 The distributions look reasonable with most of the mass close to one.
-We notice a trend of more improvement in the second CAP period between phase two and three compared to the first CAP between phase one and two.}
+We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.
+
 \begin{figure}[ht]
@@
 The methods to be employed will be similar to the assurance testing
-as discussed by Hamada et al. ~\cite{ref6}.
-% Bayesian \emph{reliability assurance tests} are used to ensure that the reliability of an item meets or exceeds a specified requirement with a desired probability.
+as discussed by Hamada et al. ~\cite{ref4}.
 Meeker and Escobar
@@
 In most test planning settings we are interested in controlling error rates
-while minimizing the resources required for testing.  In the DoD acquisition
+while minimizing the resources required for testing.  In a typical DoD acquisition
 process, the error rates are referenced in terms of risk. \emph{Consumer's
@@
 of $\pi$: $\pi_0$, an \emph{acceptable reliability level} (ARL), and $\pi_1$, a
-\emph{rejectable reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although
-the precise definition of ARL and RRL differ between the classical and Bayesian
-test criteria, we use them in a similar way.
+\emph{rejectable reliability level} (RRL), where $\pi_1 \leq  \pi_0$. The precise definition of ARL and RRL differ between the classical and Bayesian test criteria and will be described below.
 
 \subsubsection{Classical Approach}
-In the frequentest (classical) test planning setting the risk criteria
+In the classical (frequentist) test planning setting the risk criteria
 are as follows. The \emph{producer's risk} is defined as the probability of
@@
 alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
-$\alpha$, of the producer's risk and a maximum value, $\beta$, of the consumer's
+$\alpha_c$, of the producer's risk and a maximum value, $\beta_c$, of the consumer's
 risk. For test planning, these criteria become
@@
 	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
-	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
+	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha_c
 \end{aligned}
@@
 	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
-	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
+	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta_c
 \end{aligned}
@@
 we assume a distributional form that defines the relationship between the number
-of system failures $W(t)$ and the reliability $\pi$.  We then solve for
-the combinations of these probabilities that satisfy the risk constraints by simultaneously solving these two
-equations.  In the case where the component failure times are assumed to be
-exponentially distributed with rate parameter $\lambda_i$, the failure counts for
+of system failures $W(t)$ and the reliability $\pi$.  We then find
+the combinations of time on test and allowed failures that satisfy the risk constraints by simultaneously solving these two equations.
+In the case where the component failure times are assumed to be exponentially distributed with rate parameter $\lambda_i$, the failure counts for
 each component come from a homogeneous Poisson process $w_i(t) \sim
-\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
+\text{Poisson}(\lambda_i t)$, and the system failure counts from $W(t) \sim
 \text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
-this classical test planning approach. \textcolor{red}{add a cite or two}
+this classical test planning approach. ~\cite{ref8}
 
@@
 
-We consider fully Bayesian posterior risks, which provide a completely
-different outlook from the corresponding classical risks.  While the classical approach
+We consider fully Bayesian posterior risks, which provides a
+different interpretation from the corresponding classical risks.  While the classical approach
 provides assurance that satisfactory devices will pass the test and that
@@
 assurance that practitioners often desire: if the test is passed, then the
-consumer desires a maximum probability $\beta$ that \textcolor{blue}{the true reliability is less than the rejectable level,} $\pi \leq \pi_1$. On the
+consumer desires a maximum probability $\beta_b$ that \textcolor{blue}{the true reliability is less than the rejectable level,} $\pi \leq \pi_1$. On the
 other hand, if the test is failed, then the producer desires a maximum
-probability $\alpha$ \textcolor{blue}{the true reliability is greater than the acceptable level,} that $\pi \geq \pi_0$.
+probability $\alpha_b$ \textcolor{blue}{the true reliability is greater than the acceptable level,} that $\pi \geq \pi_0$.
 Notice these posterior risks are fully Bayesian in the sense that they are probability statements about $\pi$.
@@
 predetermined acceptable failure rate $\lambda_0$, then using Bayes' Theorem,
-and assuming a maximum allowable posterior producer's risk $\alpha$, an
+and assuming a maximum allowable posterior producer's risk $\alpha_b$, an
 expression for the posterior producer's risk for the exponential test plan
@@
     {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W \exp(-\lambda_S
-    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
+    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha_b
 \end{aligned}
@@
 \text{Test Is Passed)}$.  Let $\pi_1$ be a predetermined rejectable
-failure rate $\lambda_1$ \textcolor{red}{this is confusing}. Assuming a maximum allowable posterior consumer's
-risk $\beta$, an expression for the posterior producer's risk for the
+failure rate $\lambda_1$. Assuming a maximum allowable posterior consumer's
+risk $\beta_b$, an expression for the posterior producer's risk for the
 exponential test plan $(T,c)$ is
@@
 distribution, the system failure counts no longer follow a homogeneous Poisson
-process.  When assuming ``bad as old" intra-test repairs, \textcolor{blue}{as described in section 3.1.3}, we find that the
+process.  When assuming ``bad as old" intra-test repairs, as described in Section 3.1.3, we find that the
 failure count for a given failure mode follows a nonhomogeneous Poisson
@@
 and rejectable parameters $\pi_0$ and $\pi_1$ become quantities related to
-$\sum_i (\lambda_i t_i)^{\gamma_i}$.  This leads to integration that is analytically intractable, but Monte Carlo integration
+$\lambda^* = \sum_i (\lambda_i t_i)^{\gamma_i}$.  This leads to integration that is analytically intractable, but Monte Carlo integration
 allows our evaluation of the posterior producer's risk for the Weibull test plan
 $(T,c)$:
+
 $$
 \begin{aligned}
-	 P(\sum_i \lambda_i T^{\gamma_i} \geq \pi_0 \; \vert \; W = 0) &= \frac{
+	 P(\lambda^* \geq \pi_0 \; \vert \; W = 0) &= \frac{
 	 \int_{\pi_0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
@@
    &\approx \frac{\sum_{j = 1}^{N} 1 - \exp(-\sum_i \gamma_i^{(j)}
-   \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\sum_i \lambda_i^{(j)}
-   T^{\gamma_i^{(j)}} \geq \pi_0)} {\sum_{j = 1}^{N} 1 - \exp(- \sum_i
+   \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\lambda^* \geq \pi_0)} {\sum_{j = 1}^{N} 1 - \exp(- \sum_i
    \gamma_i^{(j)} \lambda_i^{(j)} T^{\gamma_i^{(j)}})}
@@
 \\
-where $\pi_0$ is some quantity related to the model parameters.  Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
+Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
 $\gamma_i^{(j)}$.
 
-It should be noted that in this test planning process the practitioner would use
+It should be noted that in this test planning process, the practitioner would use
 the posterior distribution of the rate parameters from the final developmental
@@
 
-\subsubsection{JLTV Test Plan Results}
+\subsubsection{Case Study Test Plan Results}
 The first step in applying this method to our case study is defining $\pi_0$,
-$\pi_1$, $\alpha$ and $\beta$, which are the ARL, RRL, acceptable producer risk
+$\pi_1$, $\alpha_b$ and $\beta_b$, which are the ARL, RRL, acceptable producer risk
 and acceptable consumer risk respectively.  With input from subject matter
 experts,  we will define the producer's target as the average number of
-failures in the first 140 miles to be less than 3, and the consumer's minimum
-requirements as the average number of failures in the first 80 miles to
-greater than 3.
-\textcolor{blue}{The producer's targets and consumer's minimum requirements represent our cut off levels ARL and RRL respectively.
-This means if the true average number of failures in the first 140 miles is less than 3 the producer would expect his product to fail the test a small proportion of the time, $\alpha$.
-On the other hand, if the true average number of failures in the first 8 miles is greater than 3 the consumer would expect the product to pass the test a small proportion of the time, $\beta$.
-} We will use $\alpha = 0.1$ and $\beta = 0.05$, and in practice these values should always be set based on
+failures in the first 10,000 miles to be less than 155, and the consumer's minimum
+requirements as the average number of failures in the first 10,000 miles to
+greater than 175.
+The producer's targets and consumer's minimum requirements represent our cut off levels ARL and RRL respectively.
+This means if the true average number of failures in the first 10,000 miles is less than 155 the producer would expect his product to fail the test a small proportion of the time, $\alpha_b$.
+On the other hand, if the true average number of failures in the first 10,000 miles is greater than 175 the consumer would expect the product to pass the test a small proportion of the time, $\beta_b$.
+We will use $\alpha_b = 0.1$ and $\beta_b = 0.05$, and in practice these values should always be set based on
 the true risk tolerances of the consumer and producers.  This gives us the
@@
 \begin{aligned}
-  \text{Consumer Risk} &: P(\sum_i 80^{\gamma_i} \lambda_i \geq 3 \; \vert \text{Test Is Passed}) \leq 0.1  \\
-  \text{Producer Risk} &: P(\sum_i 140^{\gamma_i} \lambda_i \leq 3 \; \vert \; \text{Test Is Failed}) \leq 0.05
+  \text{Consumer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \geq 175 \; \vert \text{Test Is Passed}) \leq 0.1  \\
+  \text{Producer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \leq 155 \; \vert \; \text{Test Is Failed}) \leq 0.05
 \end{aligned}
@@
 From here we are able to find combinations of failures allowed and test miles
-required that satisfy both risk requirements.  Table 2 shows the
-resulting combinations for the case study.
+required that satisfy both risk requirements.
 
@@
 \center
-\begin{tabular}{|c|c|}
-\multicolumn{2}{c}{\textbf{Test Plan}} \\
-\cline{1-2}
-Failures Allowed    & Test Miles Required \\
+\begin{tabular}{|c|c|c|}
+\multicolumn{3}{c}{\textbf{Test Plans}} \\
+\cline{1-3}
+Failures & Assurance Test Plan & Classical Test Plan \\
+Allowed & Miles Required & Miles Required \\
+  & $\alpha_b$ = 0.1, $\beta_b$ = 0.05 & $\alpha_c$ = 0.1, $\beta_c$ = ? \\
 \hline
-0   & 5,500     \\
-1   & 10,100    \\
-2   & 17,900    \\
-3   & 30,800    \\
-4   & 51,200    \\
+1   & 240 & 225  ($\beta_c$ = 0.86) \\
+2   & 250 & 305  ($\beta_c$ = 0.85) \\
+3   & 260 & 385  ($\beta_c$ = 0.84) \\
+4   & 275 & 460  ($\beta_c$ = 0.83) \\
+5   & 290 & 530  ($\beta_c$ = 0.82) \\
 \hline
 \end{tabular}
-\caption{Assurance Test Plan Results}
+\caption{Test Plan Comparison}
 \label{table:ta}
@@
 
-These results alone do not provide much insight into how well the method is
-performing. A natural comparison would be with the frequentest test plan in this
-setting.  In general,  we warn against this comparison because the test plan
-probability constraints for each  method are asking different questions.  The
-frequentist plan controls the error rates  under two different assumed settings \textcolor{red}{???}.
-On the other hand, the Bayesian plan puts constraints  on the error when the test
-is passed and failed.  We would argue that in most settings  the Bayesian plan
-controls for the error the practitioner cares about.
+\textcolor{blue}{Table 2 compares the resulting test plans of our proposed method to the classical method.
+In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.
+In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.
+The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.
+On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.}
 
-In this case there are no
-reasonable combinations of allowed failures and required test miles  that
-satisfy both producer's and consumer's risk probability statements in the
-frequentest test plan. \textcolor{red}{Can you come close? Can you calculate risks using the values from the Bayesian plans -- then we do have a comparison}
-Both test planning approaches rely heavily on setting reasonable values for
-$\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealistic
-values both procedures can can result in no plan that satisfies the probability
-statements \textcolor{red}{B.
-Weaver, M.
-Hamada, A.
-Wilson, J.
-Bakerman (2017).
-Bayesian Assurance Tests for Degradation Data.
-Quality and Reliability Engineering International 33(8): 2699-2709.}.
-In this paper we have focused on test plans for single units, but
-th the assurance testing methodology can be extended to find test plans that
+We have provided one example where there was no solution that satisfied all of the constraints using the classical method.
+This problem does not only come up using the classical method.
+Both test planning approaches rely heavily on setting reasonable values for $\pi_0$, $\pi_1$, $\alpha$ and $\beta$.
+When these are set to unrealistic values both procedures can result in no plan that satisfies the probability statements.
+~\cite{ref9}
+
+In this paper we have focused on test plans for single units, but the assurance testing methodology can be extended to find test plans that
 allow for a changing number of testing units.  In this case you would find
-combinations of failures allowed and test miles required and number of vehicles
+9combinations of failures allowed and test miles required and number of vehicles
 tested that satisfy the risk requirements. More details and examples of this can
-be found in the assurance testing section of Hamada et al. ~\cite{ref6}
+be found in Hamada et al. ~\cite{ref4}
 
 \subsection{Discussion}
-The case study results provide indications that our model is successfully
+The JLTV results provide indications that our model is successfully
 capturing the failure rates across failure modes, inferring logical fix
@@
 vehicles with no observed failures are sensible; however, we should leverage
-more information across vehicles \textcolor{red}{More discussion here}. Because the correlations induced by our
-current model are fairly low \textcolor{red}{correlations between what?}, potential methods for inducing more correlation
-between the vehicles in the related failure modes are being investigated. We
+more information across vehicles. Because our
+current model assumes independence across failure modes, potential methods that model the correlation structure
+between failure modes are being investigated. We
 also need to look more closely at the intra-phase repair assumptions.  Applying
@@
 Acquisition: Background Papers. \textit{National Academies Press} (1999).
-\bibitem{ref4} D.\ J.\ Spiegelhalter, N.\ Best, B.\ Carlin, and A.\ Van der
+\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
+Bayesian Reliability. Springer (2008).
+\bibitem{ref5} D.\ J.\ Spiegelhalter, N.\ Best, B.\ Carlin, and A.\ Van der
 Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
 Society}, Series B, 64: 583–640 (2002).
-\bibitem{ref5} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. Posterior
+\bibitem{ref6} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. Posterior
 predictive assessment of model fitness via realized discrepancies. (1996)
-\textit{Statistica sinica} 733-760 (1996).
-\bibitem{ref6} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
-Bayesian Reliability. Springer (2008).
 \bibitem{ref7} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
@@
 1-25 (2004).
+\bibitem{ref8} \textcolor{red}{Need to find}
+\bibitem{ref9} B. Weaver, M. Hamada, A. Wilson, J. Bakerman (2017). Bayesian Assurance Tests for Degradation Data. Quality and Reliability Engineering International 33(8): 2699-2709.
 \end{thebibliography}

### 2018-01-27 paperDraft3.tex
finished edits

@@
 
-Figure~\ref{fig:CAP} shows the posterior distributions for each of the FEF parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.
+Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.
 These parameters were introduced in Section~\ref{FEF}.
@@
 Values less than one indicate a decrease in failure rate.
-The distributions look reasonable with most of the mass close to one.
+The distributions look reasonable with most of the mass close to the commonly used FEF value of 0.70.
 We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.
@@
 assurance that practitioners often desire: if the test is passed, then the
-consumer desires a maximum probability $\beta_b$ that \textcolor{blue}{the true reliability is less than the rejectable level,} $\pi \leq \pi_1$. On the
+consumer desires a maximum probability $\beta_b$ that the true reliability is less than the rejectable level, $\pi \leq \pi_1$. On the
 other hand, if the test is failed, then the producer desires a maximum
-probability $\alpha_b$ \textcolor{blue}{the true reliability is greater than the acceptable level,} that $\pi \geq \pi_0$.
+probability $\alpha_b$ the true reliability is greater than the acceptable level, that $\pi \geq \pi_0$.
 Notice these posterior risks are fully Bayesian in the sense that they are probability statements about $\pi$.
@@
 
-\textcolor{blue}{Table 2 compares the resulting test plans of our proposed method to the classical method.
+Table 2 compares the resulting test plans of our proposed method to the classical method.
 In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.
+Notice this leads to extremely high levels of producer risk under the classical plan.
 In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.
 The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.
-On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.}
+On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.
 
@@
 allow for a changing number of testing units.  In this case you would find
-9combinations of failures allowed and test miles required and number of vehicles
+combinations of failures allowed and test miles required and number of vehicles
 tested that satisfy the risk requirements. More details and examples of this can
@@
 \begin{thebibliography}{99}
-\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
-\bibitem{ref2} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability
+\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982.
+\bibitem{ref2} P.\ M.\ Ellner, J.\ B.\ Hall. An approach to reliability
 growth planning based on failure mode discovery and correction using AMSAA
 projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
-Maintainability Symposium} (2006).
+Maintainability Symposium} 2006.
 \bibitem{ref3} National Research Council. Statistics, Testing, and Defense
-Acquisition: Background Papers. \textit{National Academies Press} (1999).
-\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
-Bayesian Reliability. Springer (2008).
-\bibitem{ref5} D.\ J.\ Spiegelhalter, N.\ Best, B.\ Carlin, and A.\ Van der
+Acquisition: Background Papers. \textit{National Academies Press} 1999.
+\bibitem{ref4} M.\ Hamada, A.\  Wilson, C.\ Reese, H.\ Martz. Bayesian Reliability. Springer 2008.
+\bibitem{ref5} D.\  Spiegelhalter, N.\ Best, B.\ Carlin, A.\ Van der
 Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
-Society}, Series B, 64: 583–640 (2002).
-\bibitem{ref6} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. Posterior
-predictive assessment of model fitness via realized discrepancies. (1996)
-\bibitem{ref7} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
-dimension of quailty. \textit{Quality Technology and Quantitative Management} 1,
-1-25 (2004).
-\bibitem{ref8} \textcolor{red}{Need to find}
-\bibitem{ref9} B. Weaver, M. Hamada, A. Wilson, J. Bakerman (2017). Bayesian Assurance Tests for Degradation Data. Quality and Reliability Engineering International 33(8): 2699-2709.
+Society}, Series B, 64: 583-640 2002.
+\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statist. Sin.} 6, 733-807 1996.
+\bibitem{ref7} W.\ Meeker, L.\ Escobar. Reliability: the other
+dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 2004.
+\bibitem{ref8} J.\ F.\ Lawless. Statistical Models and Methods for Lifetime Data, 2nd Edition. John Wiley \& Sons 2011.
+\bibitem{ref9} B.\ Weaver, M.\ Hamada, A.\ Wilson, J.\ Bakerman. Bayesian Assurance Tests for Degradation Data. \textit{Quality and Reliability Engineering International} 33(8): 2699-2709  2017.
 \end{thebibliography}
@@
 \rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
-\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
+\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}
 \end{align*}
@@
 \rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
-\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}\\
-\gamma|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
+\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}\\
+\gamma|\cdot &\sim \prod_{i = 1}^8 \Bigg[ \prod_{j = 1}^{n_j}(t_{ij}^{\gamma_i-1} e^{-t_{ij}^{\gamma_i}})\prod_{j = 1}^R(e^{-t_{ij}^{\gamma_i}}) \Bigg] (\gamma^{g_1 - 1}e^{-\gamma g_2}) \text{(Metropolis-Hastings used for sampling)}
 \end{align*}

### 2018-01-31 Final_Draft.tex
added final draft

--- 2018-01-27 paperDraft3.tex
@@
 \documentclass[12pt]{article}
-\usepackage{amsmath, amssymb, fullpage, bbm}
+\usepackage{amsmath, amssymb, fullpage, bbm, float}
 \usepackage{array}
@@
 \usepackage{url} % not crucial - just used below for the URL
+\renewcommand{\vec}[1]{\mathbf{#1}}
 
@@
 % DON'T change margins - should be 1 inch all around.
-%\addtolength{\oddsidemargin}{-.5in}%
-%\addtolength{\evensidemargin}{-.5in}%
-%\addtolength{\textwidth}{1in}%
-%\addtolength{\textheight}{-.3in}%
-%\addtolength{\topmargin}{-.8in}%
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{-.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
+% \def\spacingset#1{\renewcommand{\baselinestretch}%
+% {#1}\small\normalsize} \spacingset{1}
 
@@
 \begin{abstract}
-    We propose a Bayesian hierarchical model to assess the reliability of a family of vehicles, based on the development of the Joint
-    Light Tactical Vehicle (JLTV). The proposed
-    model effectively combines information across three phases of testing and
-    across common vehicle components. The analysis yields estimates of failure
-    rates for specific failure modes and vehicles as well as an overall estimate
-    of the failure rate for the family of vehicles. We are also able to obtain
-    estimates of how well vehicle modifications between test phases improve
-    failure rates. In addition to using all data to improve on current
-    assessments of reliability and reliability growth, we illustrate how to
-    leverage the information learned from the three phases to determine
-    appropriate specifications for subsequent testing that will demonstrate if
-    the reliability meets a given reliability threshold.
+We propose a Bayesian hierarchical model to assess the reliability of a family of vehicles, based on the development of the Joint Light Tactical Vehicle (JLTV).
+The proposed model effectively combines information across three phases of testing and across common vehicle components.
+The analysis yields estimates of failure rates for specific failure modes and vehicles as well as an overall estimate of the failure rate for the family of vehicles.
+We are also able to obtain estimates of how well vehicle modifications between test phases improve failure rates.
+In addition to using all data to improve on current assessments of reliability and reliability growth, we illustrate how to leverage the information learned from the three phases to determine appropriate specifications for subsequent testing that will demonstrate if the reliability meets a given reliability threshold.
 \end{abstract}
@@
 4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
-3.\footnote{The exact mileage has been altered to protect proprietary information.}
+3. The actual mileage we use in our case study has been altered to protect proprietary information.
 
@@
 to correct, and the potential of not completely eliminating a failure upon
-repair. One of the features of PM2 is that many parameters of potential
-interest, such as the Fix Effectiveness Factor (FEF), which measures how much
-repairs improve failure rates, are typically fixed, as PM2 is often used as a planning model. A common value for FEF is
+repair. Since PM2 is used for planning, many parameters of potential
+interest are assumed fixed. An example is the Fix Effectiveness Factor (FEF), which measures how much
+repairs improve failure rates. A common value for FEF is
 0.70. We follow the premise of this type of model, but allow a more flexible and
@@
 Gaussian, and normal failure time models.  Because all of these distributions
-have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter) they can be applied in
+have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter), they can be applied in
 the proposed modeling structure. We focus on the
@@
 \begin{equation*}
-    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk})
+    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk}) \;.
 \end{equation*}
@@
 This requires more complex modeling that is beyond the scope of this paper.
-An overview of repairable system models can be found in Hamada et al.
+An overview of Bayesian approaches for repairable system models can be found in Hamada et al.
 ~\cite{ref4}
@@
 These failure modes were attributed to system components such as the engine and armor.
-To improve convergence we have binned these rare failure modes into a single "other" failure mode.
-This is also useful for future testing in the case of observing failures not originally accounted for.
+To improve convergence we have binned these rare failure modes into a single ``other" failure mode.
+This may also be useful for planning future testing to account for previously unobserved failure modes.
 
@@
 
-\begin{figure}[h]
-  \centering
-      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
-  \caption{Posterior Plots of Weibull Shape Parameter}
-  \label{Shape}
-\end{figure}
-
-We also consider a more formal diagnostic tool, the Deviance information criterion (DIC)
+We also consider a more formal diagnostic tool, the deviance information criterion (DIC)
 ~\cite{ref5}. This is a popular method for comparing the goodness of fit of
@@
 The results show that the hierarchical Weibull model fits the data much better than the exponential or common rate models.
-
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|l|r|}
-\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
-\cline{1-3}
-Distribution    & Structure & DIC \\
-\hline
-Exponential   & Common Rate Model                     & 21,264.19             \\
-              & Hierarchical Rate Model               & 21,244.47             \\
-Weibull       & Common Rate Model                     & 20,658.25             \\
-              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
-\hline
-\end{tabular}
-\caption{JLTV DIC Results}
-\label{table:ta1}
-\end{table}
 
@@
 If the model fits reasonably well, we expect to see the value from the observed data falling within the support of the simulated data.
-This suggests that the Weibul model fits the case study data better than the exponential data.
-
-\begin{figure}[h!]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{PPExpo}
-  %\caption{}
-  %\label{fig:sub1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{PPWeibull}
-  %\caption{}
-  %\label{fig:sub2}
-\end{subfigure}
-\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
-\label{fig:test}
-\end{figure}
+This suggests that the Weibull model fits the case study data better than the exponential data.
 
@@
 dataset.
-(The likelihoods and sampling distributions are available in the appendix.) We use the posterior distributions to estimate reliability-related quantities of interest for each of the eight vehicle types.
+(Details of the likelihoods and full conditional distributions are available in the appendix.) We use the posterior distributions to estimate reliability-related quantities of interest for each of the eight vehicle types.
 We are able to examine a number of different summaries related to reliability at both the component and system level.
@@
 Due to the failure rate changing over time in the Weibull case MMBF depends on how many miles the vehicle is driven.
-Instead MMTF can be thought of as the average time until the first failure occurs.
-Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).
-
-\begin{figure}[ht]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-      \includegraphics[width=8cm, height=7cm]{Boxplots}
-  % \caption{Comparing EMTF for Different Models}
-  %\label{fig:sub1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \center
-  \begin{tabular}{|c|c|c|c|c|}
-  \multicolumn{5}{c}{\textbf{Summary Statistics}} \\
-  \cline{1-5}
-  Model & Phase & Mean & 90\% CI & 90\% CI \\
-   & & & Low & Up \\
-  \hline
-  Expo & P1   & 129.98   & 110.22 &  152.23 \\
-  Expo & P2   & 98.44  & 89.00 &  108.38  \\
-  Expo & P3   & 135.89   & 117.78 &  155.45 \\
-  Weibull & P1   & 169.96  & 116.95 & 236.16 \\
-  Weibull & P2   & 135.24   & 104.89 & 167.48 \\
-  Weibull & P3   & 175.51   & 138.87 & 214.23 \\
-  \hline
-  \end{tabular}
-  %\label{fig:sub2}
-\end{subfigure}
-\caption{Comparing MMTF for Different Models}
-\label{fig:MMTF Results}
-\end{figure}
+MMTF can be thought of as the average time until the first failure occurs.
+Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to first failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).
 
@@
 Values less than one indicate a decrease in failure rate.
-The distributions look reasonable with most of the mass close to the commonly used FEF value of 0.70.
-We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.
-
-\begin{figure}[ht]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-      \includegraphics[width=8cm, height=7cm]{CAP2}
-  % \caption{Corrective Action Period Parameters Posterior Distributions}
-  %\label{fig:sub1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \center
-  	\includegraphics[width=8cm, height=7cm]{CAP3}
-  %\label{fig:sub2}
-\end{subfigure}
-\caption{Posterior Distributions for Correction Parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$}
-\label{fig:CAP}
-\end{figure}
+Interestingly, the distributions have most of their mass close to the commonly used FEF value of 0.70.
+We notice a trend of more improvement in the second CAP between phase two and three as compared to the first CAP between phase one and two.
 
@@
 
-\subsubsection{Classical Approach}
+\subsubsection{Classical Approach}\label{sec321:ca}
 In the classical (frequentist) test planning setting the risk criteria
@@
 \text{Poisson}(\lambda_i t)$, and the system failure counts from $W(t) \sim
-\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
-this classical test planning approach. ~\cite{ref8}
+\text{Poisson}(\lambda_S t)$.  Numerous textbooks (e.g., \cite{ref8}) provide additional details of
+this classical test planning approach.
 
@@
 	 \int_{\pi_0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
-	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
-	 d\gamma_{1,...}} {\int_{0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
-	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
-	 d\gamma_{1,...}} \\
+	 T^{\gamma_i})p(\vec{\lambda}) p(\vec{\gamma}) d\vec{\lambda}
+	 d\vec{\gamma}} {\int_{0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
+	 T^{\gamma_i})p(\vec{\lambda}) p(\vec{\gamma}) d\vec{\lambda}
+	 d\vec{\gamma}} \\
    &\approx \frac{\sum_{j = 1}^{N} 1 - \exp(-\sum_i \gamma_i^{(j)}
@@
 \\
-Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
+where $\vec{\lambda}$ and $\vec{\gamma}$ denote the vectors of $\lambda_i$ and $\gamma_i$. Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
 $\gamma_i^{(j)}$.
@@
 \subsubsection{Case Study Test Plan Results}
-The first step in applying this method to our case study is defining $\pi_0$,
+The first step in applying the Bayesian assurance test planning method to our case study is defining $\pi_0$,
 $\pi_1$, $\alpha_b$ and $\beta_b$, which are the ARL, RRL, acceptable producer risk
@@
 
-\begin{table}[h]
-\center
-\begin{tabular}{|c|c|c|}
-\multicolumn{3}{c}{\textbf{Test Plans}} \\
-\cline{1-3}
-Failures & Assurance Test Plan & Classical Test Plan \\
-Allowed & Miles Required & Miles Required \\
-  & $\alpha_b$ = 0.1, $\beta_b$ = 0.05 & $\alpha_c$ = 0.1, $\beta_c$ = ? \\
-\hline
-1   & 240 & 225  ($\beta_c$ = 0.86) \\
-2   & 250 & 305  ($\beta_c$ = 0.85) \\
-3   & 260 & 385  ($\beta_c$ = 0.84) \\
-4   & 275 & 460  ($\beta_c$ = 0.83) \\
-5   & 290 & 530  ($\beta_c$ = 0.82) \\
-\hline
-\end{tabular}
-\caption{Test Plan Comparison}
-\label{table:ta}
-\end{table}
+Table 2 compares the resulting test plans of our proposed method to the classical method.
+In general, we warn against making this comparison of test plans, because as we discuss below, each method makes different assumptions and the test plan probability constraints are addresses different questions.
 
-Table 2 compares the resulting test plans of our proposed method to the classical method.
-In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.
+As is common in DoD test planning, for the classical case we only controlled for the consumer's risk, not for both risks as described in Section~\ref{sec321:ca}.
 Notice this leads to extremely high levels of producer risk under the classical plan.
-In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.
-The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.
-On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.
+(Note that with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both classical risk criteria.) The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.
+For example, interpreting the first row of Table 1, if a system is put on test where the average number of failures in 10,000 miles is 155, the the probability of failing the test and observing two or more failures in 225 miles is 0.86.
+If a system is put on test where the average number of failures in 10,000 miles is 175, then the probability of passing the test and observing no more than one failure in 225 miles is 0.10.
+
+By comparison, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.
+From the study, the posterior producer risk is the probability the average number of failures in 10,000 miles for the system is less than 155 given that the test is failed and two or more failures are observed in 240 miles.
+The posterior consumers risk is the probability that the average number of failures in 10,000 miles for the system is greater than 175 given that the test is passed by observing no more than one failure in 240 miles.
 
@@
 Both test planning approaches rely heavily on setting reasonable values for $\pi_0$, $\pi_1$, $\alpha$ and $\beta$.
-When these are set to unrealistic values both procedures can result in no plan that satisfies the probability statements.
-~\cite{ref9}
+When these are set to unrealistic values both procedures can result in no plan that satisfies the probability statements ~\cite{ref9}.
 
@@
 \begin{thebibliography}{99}
-\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982.
+\bibitem{ref1} Director, Defense Test and Evaluation.
+Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982.
+\url{http://www.dtic.mil/dtic/tr/fulltext/u2/a120261.pdf}
 \bibitem{ref2} P.\ M.\ Ellner, J.\ B.\ Hall. An approach to reliability
 growth planning based on failure mode discovery and correction using AMSAA
-projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
+projection methodology. \textit{Proceedings of the Annual Reliability and
 Maintainability Symposium} 2006.
@@
 \bibitem{ref5} D.\  Spiegelhalter, N.\ Best, B.\ Carlin, A.\ Van der
-Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
-Society}, Series B, 64: 583-640 2002.
-\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statist. Sin.} 6, 733-807 1996.
+Linde Bayesian measures of model complexity and fit. \textit{Journal of the Royal Statistical
+Society, Series B}, 64: 583-640 2002.
+\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statistica Sinica} 6, 733-807 1996.
 \bibitem{ref7} W.\ Meeker, L.\ Escobar. Reliability: the other
@@
 \rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
-\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
-  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}
+\alpha|\cdot &\propto \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \;\; \text{(Metropolis-Hastings used for sampling)}
 \end{align*}
@@
 \rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
-\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
-  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}\\
-\gamma|\cdot &\sim \prod_{i = 1}^8 \Bigg[ \prod_{j = 1}^{n_j}(t_{ij}^{\gamma_i-1} e^{-t_{ij}^{\gamma_i}})\prod_{j = 1}^R(e^{-t_{ij}^{\gamma_i}}) \Bigg] (\gamma^{g_1 - 1}e^{-\gamma g_2}) \text{(Metropolis-Hastings used for sampling)}
+\alpha|\cdot &\propto \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
+  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \;\; \text{(Metropolis-Hastings used for sampling)}\\
+\gamma|\cdot &\propto \prod_{i = 1}^8 \Bigg[ \prod_{j = 1}^{n_j}(t_{ij}^{\gamma_i-1} e^{-t_{ij}^{\gamma_i}})\prod_{j = 1}^R(e^{-t_{ij}^{\gamma_i}}) \Bigg] (\gamma^{g_1 - 1}e^{-\gamma g_2}) \;\;\text{(Metropolis-Hastings used for sampling)}
 \end{align*}
@@
 
+\section{Tables}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|l|l|r|}
+\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
+\cline{1-3}
+Distribution    & Structure & DIC \\
+\hline
+Exponential   & Common Rate Model                     & 21,264.19             \\
+              & Hierarchical Rate Model               & 21,244.47             \\
+Weibull       & Common Rate Model                     & 20,658.25             \\
+              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
+\hline
+\end{tabular}
+\caption{JLTV DIC Results}
+\label{table:ta1}
+\end{table}
+
+\begin{table}[H]
+\center
+\begin{tabular}{|c|c|c|}
+\multicolumn{3}{c}{\textbf{Test Plans}} \\
+\cline{1-3}
+Failures & Assurance Test Plan & Classical Test Plan \\
+Allowed & Miles Required & Miles Required \\
+  & $\alpha_b$ = 0.1, $\beta_b$ = 0.05 & $\alpha_c$ = 0.1, $\beta_c$ = ? \\
+\hline
+1   & 240 & 225  ($\beta_c$ = 0.86) \\
+2   & 250 & 305  ($\beta_c$ = 0.85) \\
+3   & 260 & 385  ($\beta_c$ = 0.84) \\
+4   & 275 & 460  ($\beta_c$ = 0.83) \\
+5   & 290 & 530  ($\beta_c$ = 0.82) \\
+\hline
+\end{tabular}
+\caption{Test Plan Comparison}
+\label{table:ta}
+\end{table}
+
+\section{Figures}
+
+\begin{figure}[h]
+  \centering
+      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
+  \caption{Posterior Plots of Weibull Shape Parameter}
+  \label{Shape}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{PPExpo}
+\end{subfigure}%
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{PPWeibull}
+\end{subfigure}
+\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
+\label{fig:test}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+      \includegraphics[width=8cm, height=7cm]{Boxplots}
+  % \caption{Comparing EMTF for Different Models}
+  %\label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \center
+  \begin{tabular}{|c|c|c|c|c|}
+  \multicolumn{5}{c}{\textbf{Summary Statistics}} \\
+  \cline{1-5}
+  Model & Phase & Mean & 90\% CI & 90\% CI \\
+   & & & Low & Up \\
+  \hline
+  Expo & P1   & 129.98   & 110.22 &  152.23 \\
+  Expo & P2   & 98.44  & 89.00 &  108.38  \\
+  Expo & P3   & 135.89   & 117.78 &  155.45 \\
+  Weibull & P1   & 169.96  & 116.95 & 236.16 \\
+  Weibull & P2   & 135.24   & 104.89 & 167.48 \\
+  Weibull & P3   & 175.51   & 138.87 & 214.23 \\
+  \hline
+  \end{tabular}
+  %\label{fig:sub2}
+\end{subfigure}
+\caption{Comparing MMTF for Different Models}
+\label{fig:MMTF Results}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+      \includegraphics[width=8cm, height=7cm]{CAP2}
+  % \caption{Corrective Action Period Parameters Posterior Distributions}
+  %\label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \center
+  	\includegraphics[width=8cm, height=7cm]{CAP3}
+  %\label{fig:sub2}
+\end{subfigure}
+\caption{Posterior Distributions for Correction Parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$}
+\label{fig:CAP}
+\end{figure}
+
 \end{document}
